### 2022-03-01 Aug2021-CH2-.tex
upload paper to git

\documentclass[journal=jpcafh,manuscript=article,layout=onecolumn, 12pt]{achemso}
\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
\usepackage[T1]{fontenc}       % Use modern font encodings
\usepackage{amsmath}
\usepackage[dvipsnames]{xcolor}
% NB added command for in line cite
\newcommand{\onlinecite}[1]{\hspace{-1 ex} \nocite{#1}\citenum{#1}} 
%
\author{Benjamin~A.~Laws}
\email{b.laws@unsw.edu.au}
\affiliation{School of Chemistry, University of New South Wales, Sydney NSW 2052, Australia}
\alsoaffiliation{Research School of Physics, The Australian
	National University, Canberra ACT 2601, Australia}
\author{Zachariah~D.~Levey} 
\affiliation{School of Chemistry, University of New South Wales, Sydney NSW 2052, Australia}
\author{Timothy~W.~Schmidt} 
\affiliation{School of Chemistry, University of New South Wales, Sydney NSW 2052, Australia}
\author{Stephen~T.~Gibson}
\affiliation{Research School of Physics, The Australian
	National University, Canberra ACT 2601, Australia}
\title{C2H-}
\abbreviations{PES,PAD,EA,eKE,FWHM,VMI}
\begin{document} 
\begin{abstract}

\end{abstract}
\section{Introduction}
Carbon monohydrides C$_{2n}$H, are a class of linear radicals that play an important role in combustion and interstellar chemistry. These carbon chains have been observed in many interstellar environments, including planetary atmospheres, comets, dark clouds, and during heavy star formation. Due to their relatively high abundance in a variety of astronomical conditions, they have been proposed to be promising candidates for Diffuse Interstellar Band carriers. The corresponding anions C$_{2n}$H$^-$ are also believed to play an important role in interstellar chemistry. C$_6$H$^-$ was the first negative ion detected in space, after it was observed in the circumstellar envelope of IRC+10216 in 2006. More recently, anions C$_4$H$^-$ and C$_8$H$^-$ have also been detected in a range of environments, include dark clouds, prestellar cores, and prostellar envelopes.

Chain growth of the C$_{2n}$H radicals occurs predominately through acetylene addition,
\begin{equation}
\text{C}_{2n}\text{H} + \text{C}_2\text{H}_2 \rightarrow \text{C}_{2n+2}\text{H}+\text{H}_2.
\end{equation}
Conversely, the formation of anions in space is believed to be driven by radiative electron attachment, charge transfer, and dissociate electron attachment. However modelling these processes underestimates the abundance of C$_4$H$^-$ observed in IRC+10216. Therefore, ion-neutral reactions have been proposed as an additional chain growth mechanism that also needs to be considered,
 \begin{equation}
 \text{C}_{2n}\text{H}^- + \text{C}_2\text{H}_2 \rightarrow \text{C}_{2n+2}\text{H}^- + \text{H}_2.
 \end{equation}
Modelling of the extraterrestrial planetary atmosphere of Saturn's moon Titan, suggests that both C$_2$H and C$_2$H$^-$ play an important role in the atmospheric chemistry. Multiple reaction pathways were included for the ion C$_2$H$^-$ including, 
\begin{align}
\text{C}_2\text{H}^- &\xrightarrow[]{\text{H}^+} \text{C}_2\text{H}_2\\
&\xrightarrow[]{\text{HCN}} \text{CN}^-+\text{H}_2\\
&\xrightarrow[]{\text{C}_2\text{H}_2} \text{C}_4\text{H}^-+\text{H}_2\\
&\xrightarrow[]{\text{C}_2\text{H}_2} \text{C}_4^-+\text{H}_3.
\end{align}

Understanding interstellar chemistry relies critically on theory, to provide a link between astronomical observations and terrestrial laboratory studies. Microwave spectroscopy has successfully been used in this fashion to identify a large number of molecules in the ISM. However for some species, particularly those with low abundances, UV/vis spectroscopic methods are required for identification. This creates a challenge for theory, as electronic spectra calculations are a lot more sensitive to the level of theory employed than pure rotational spectra. This becomes even more challenging when vibronic coupling effects are introduced, as they can be exceedingly difficult to model.

These considerations may be explored by examining some of the smallest carbon monohydrides. The ethynyl radical C$_2$H may appear to be a simple linear triatomic molecule. However the electronic spectrum is complicated by the presence of the close-lying ground $^2\Sigma^+$ and first excited $^2\Pi$ surfaces, which are only separated by $\sim4,000~$cm$^{-1}$. The interaction of these surfaces produces a complex vibronic spectrum around the $\tilde{A}^2\Pi$ origin, where no single band corresponding to the $\tilde{X}-\tilde{A}$ origin has been observed. In C$_4$H the $^2\Sigma^+$ and $^2\Pi$ states are nearly degenerate, resulting in even stronger coupling, while in C$_6$H and C$_8$H the ordering of the states swaps, with a ground $^2\Pi$ state and a low lying excited $^2\Sigma^+$ state. Consequently, understanding these vibronic coupling interactions between the $^2\Sigma$ and $^2\Pi$ surfaces will be essential in order to accurately model the role these radicals (and their corresponding anions) are likely to play in the interstellar chemistry mentioned above, and to discern if they may be possible DIB carriers.

In this paper we study the vibronic spectrum of the ethynyl radical C$_2$H by employing High-Resolution Photoelectron Imaging (HR-PEI) in order to benchmark CFOUR \emph{ab-initio} vibronic-coupling calculations. C$_2$H is reported to be one of the most abundant molecules in the universe, and is the most thoroughly studied of the C$_{2n}$H species. Many different experimental techniques have been employed to try and resolve the complex vibronic spectrum, including electron spin resonance, laser magnetic resonance, microwave and milli-meter wave spectroscopy, infrared (matrix isolation and Fourier Transform) spectroscopy, and photoelectron spectroscopy. Extensive theoretical work on C$_2$H has also been carried out, in order to try and decode the surprisingly complex spectra that are observed in the experimental studies, however this has proven to be far from straightforward. In this work we demonstrate how the procedures set out in CFOUR may be used to calculate the strength of the vibronic interaction between coupled surfaces near a conical intersection, in order to simulate electronic and vibronic spectra. By employing anion HR-PEI both the $^2\Sigma^+$ and $^2\Pi$ surfaces are mapped out on an equal footing from the anion $\tilde{X}^1\Sigma^+$ state, allowing for direct comparison to the \emph{ab-initio} modelling.

\section{Results and Analysis}
Ethynyl ions were produced in a pulsed-jet discharge of pure C$_2$H$_4$ gas, and subsequently mass isolated via time of flight. Electrons were detached using a tuneable Sunlite Optical Parametric Oscillator (OPO) pumped with the third harmonic of a Nd:YAG laser. High electron counts could also be obtained by using the third and fourth harmonics of the Nd:YAG laser directly. The detached electrons were then mapped onto a micro channel plate detector using a Velocity Map Imaging (VMI) lens. An illustrative VMI of $\sim$4 million electrons collected from 355~nm (3.49~eV) photodetachment of C$_2$H$^-$ is shown in Fig.~\ref{fig:1}(a). The electrons are distributed radially according to their speed, with slow electrons at the image center, and fast electrons located towards the outer edge. Due to the relatively large C$_2$H$^-$ electron affinity (EA) of 2.969~eV~\cite{erv91}, photodetachment at 355~nm occurs close to threshold. This yields slow electrons, allowing for a low repeller voltage ($-600$~V) on the VMI lens, and high velocity resolution.

Despite being close to threshold, two electronic states of neutral C$_2$H are observed. The faster electrons on the outer edge correspond to C$_2$H$(\tilde{X}\,^2\Sigma^+)+e^- \leftarrow $C$_2$H$^-(\tilde{X}\,^1\Sigma^+)+h\nu$ photodetachment, and are preferentially distributed around the poles of the image, indicative of a positive anisotropy parameter. Conversely the angular distribution of the slower electrons near the center are skewed towards the equator, indicative of a negative anisotropy parameter. These electrons may be assigned to photodetachment to the first excited state C$_2$H$(\tilde{A}\,^2\Pi)+e^- \leftarrow $C$_2$H$^-(\tilde{X}\,^1\Sigma^+)+h\nu$.

\begin{figure}
	\includegraphics[width=0.8\textwidth]{figures/Fig1}
	\caption{(a) A 3D-representation of the velocity-map image of $\sim$ 4 million photoelectrons detached from C$2$H$^-$ at 355~nm. The outer rings, distributed around the vertical laser polarisation axis, represents photodetachment to the ground $\tilde{X}\,^2\Sigma^+$ state. The inner rings reprsent detachment to the first excited state $\tilde{A}\,^2\Pi$. (b) Photoelectron spectra of C$_2$H$^-$ at a range of detachment wavelengths, illustrating the change in electron intensity profile and energy resolution.}
	\label{fig:1}
\end{figure}

To investigate the vibronic coupling interaction between these two nearby $\Sigma^+$ and $\Pi$ surfaces, deuterated ethynyl C$_2$D$^-$ was also studied. C$_2$D$^-$ ions were produced in a discharge of pure C$_2$D$_4$ gas and measured under the same experimental conditions as C$_2$H$^-$. An illustrative VMI of photodetachment at 355~nm from C$_2$D$^-$ is shown in Fig.~\ref{fig:1}(b). Similarly to Fig~\ref{fig:1}(a) two electronic states are observed - fast electrons with a positive anisotropy corresponding to detachment to the $^2\Sigma^+$ surface, and slow electrons with a negative anisotropy corresponding to $^2\Pi$ detachment. While the fast electrons appear similar in both images, a striking difference is observed in the slow electrons near the detector center. In Fig.~\ref{fig:1}(a) a series of weak rings are observed, however in Fig.~\ref{fig:1}(b) two dominant rings are seen.

The VMI in Fig.~\ref{fig:1} were inverted using the Abel inversion methods detailed in pyAbel, to extract the corresponding photoelectron spectra, which are presented in Fig.~\ref{fig:1}(c). Below $27,000~$cm$^{-1}$ the C$_2$H$^-$ and C$_2$D$^-$ spectra appear very similar. Both are dominated by the origin transition, shifted by $\sim10~$cm$^{-1}$ in the deuterated spectrum, and show a progression in the 2$^{n+1}_0$ and 3$^1_02^{n+1}_0$ vibrational modes. Within the harmonic oscillator approximation, transitions involving an odd quanta of vibrational excitation in the non-symmetric $v_2 (\pi)$ mode should be totally forbidden. However, their presence in the photoelectron spectrum in Fig.~\ref{fig:1}(c) is likely an indicator of Herzberg-Teller (HT) vibronic coupling between the ground $^2\Sigma^+$ and nearby excited $^2\Pi$ electronic surfaces, as
\begin{equation}
\Sigma^+ \otimes \pi = \Pi. 
\end{equation}

Above $27,000~$cm$^{-1}$, near the $\tilde{A}^2\Pi$ state origin, large differences are observed between the C$_2$H$^-$ and C$_2$D$^-$ photoelectron spectra in Fig.~\ref{fig:1}(c). In the C$_2$H$^-$ spectrum 5 sharp peaks are observed, spaced by $\sim95~$cm$^{-1}$. However in the deuterated spectrum, one dominant peak is observed at $27,792$~cm$^{-1}$, with 3 weaker peaks centred around $27,360~$cm$^{-1}$. Unlike the structure below $27,000$~cm$^{-1}$ none of these peaks are able to be readily assigned to vibronic transitions, due to the presence of strong coupling interactions between the nearby $\Sigma^+$ and $\Pi$ surfaces.

%Discuss coupling now...

\subsection{Vibronic Coupling Interactions}
The surprisingly complex spectral structure observed near the $\tilde{A}^2\Pi$ state origin in the photoelectron spectra in Fig.~\ref{fig:1}(c), may be understood by considering the $v_2$ bending vibrational mode. To account for the degeneracy of this mode we may introduce the vibronic quantum number $\ell_i$, representing the angular momentum associated with the bending motion. This may take a value of $\ell_i = v_i, v_i-2, v_i-4,\dots,1$ or $0$, where $v_i$ is the quanta of bending excitation. In the Born-Oppenheimer approximation different vibronic energy levels $\ell_i$ are degenerate, however in cases with strong rovibronic coupling, this degeneracy in $\ell_i$ is lost.

In C$_2$H this effect creates a Renner-Teller (RT) pair in the excited state, where the usually degenerate $\Pi$ surfaces separate to form two non-degenerate electronic states $\Pi^+ (2A')$ and $\Pi^-(1A'')$. This involves separating a single potential energy surface (V) into two distinct but connected surfaces (V$^+$) and (V$^-$). Due to the strong coupling along the linear axis between the electronic and vibration angular momenta of the $2A'$ and $1A''$ components of the $^2\Pi$ state, stationary states cannot be explicitly assigned to either of the $\Pi^+(2A')$ or $\Pi^-(1A'')$ electronic surfaces. Instead, they exist as a combination of both states.

Due to the close lying nature of the ground {$\tilde{X} ^2\Sigma^+$} and excited {$\tilde{A} ^2\Pi$} electronic states, which are only separated by $\sim3700~$cm$^{-1}$, a pseudo Jahn-Teller effect is also observed. The Jahn-Teller theorem states that stability and degeneracy are not possible simultaneously unless the molecule is linear~\cite{jah37}, meaning that non-linear molecules with degenerate electronic states will undergo a symmetry breaking distortion in order to remove the degeneracy. However a similar effect has also been observed where coupling exists between a non-degenerate state and a nearby pair of degenerate states, even if a molecule is linear.

In the case of ethynyl this is seen as coupling between the ground $\Sigma^+(1A')$ and excited $\Pi^+(2A')$ states, induced by the bending motion of $v_2$. The ground state only couples to one of the Renner-Teller pair $\Pi^+(2A')$, as the other state $\Pi^-(1A'')$ has incorrect symmetry. This results in a very complex vibronic structure for the $\tilde{A}^2\Pi$ electronic state, with contributions from three coupled surfaces $\Sigma^+(1A'),$ $\Pi^+(2A'),$ and $\Pi^-(1A'')$.

These interactions spread the electronic orgin of the $\tilde{A}\,^2\Pi$ state over several vibronic levels. Therefore, instead of assigning a defined origin, the observed peaks in the spectrum may be assigned to coupled admixtures of vibronic transitions involving the three potential energy surfaces,
\begin{equation}
\Psi_f = \sum_\xi \psi_e^\xi \sum_k C_{fk}^\xi\phi_{fkm}^\xi,
\label{eq:teller3} 
\end{equation}
where $\psi_e^\xi$ is the diabatic electronic wavefunction, and $\phi_{fkm}^\xi$ is the spin-rovibrational wavefunction. $\xi$ represents the electronic states used in the expansion, and in this case $\xi=\Sigma^+(1A'),~\Pi^+(2A'),~\Pi^-(1A'')$. A depiction of these three interacting surfaces is given in Fig.~\ref{fig:3}.

\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{figures/Fig3}
	\caption{Adiabatic potential energy surfaces of $\tilde{X}^2\Sigma^+$, $\tilde{A}^2\Pi^-$, and $\tilde{A}^2\Pi^+$ states, calculated using the method developed by Tarroni and Carter~\cite{tar03} (E$_{1A'}$, E$_{2A'}$, and E$_{1A''}$ in Eq.~\ref{eq:teller3}).}
	\label{fig:3}
\end{figure}

Tarroni and Carter~\cite{tar03} have demonstrated that a large number of admixed vibronic levels may be calculated using the potential energy surfaces in Fig.~\ref{fig:3}. In fact, over 100 vibronic levels have been calculated, upto 6,400~cm$^{-1}$ above the $\tilde{X}$ state origin. However assigning these levels to experimental spectra has remained a challenge, partly due to the large number of calculated vibronic levels, and partly due to the resolution of the experimental data in the literature.

%The total number of vibronic levels that need to be considered may be reduced, by examining the symmetry of the level. Conservation of angular momentum dictates only transitions from the anion $\tilde{X}\,^1\Sigma^+$ origin to neutral states with $\Sigma^+$ or $\Pi$ symmetry will be allowed.

\subsection{Photoelectron Angular Distributions}
Symmetry considerations can be employed to help assign the admixed structure in the experimental photoelectron spectra around the $\tilde{A}^2\Pi$ origin. As the detachment laser is linearly polarized, the angular distribution of the electrons in Fig.~\ref{fig:1} may be linked to the symmetry of the detachment orbital. For polarised light, the differential cross section is given by   
\begin{equation}
\frac{\text{d}\sigma}{\text{d}\Omega}=\frac{\sigma_{\text{total}}}{4\pi}[1+\beta P_{2}(\cos\theta)],
\label{eq:beta1}
\end{equation}
where $\theta$ is the angle between the ejected electron and the (vertical) 
laser polarization, and $P_2$ is the second-order Legendre polynomial. The anisotropy parameter $\beta$ provides a quantitative measure of the angular distribution, and can range from -1 to +2 for a pure parallel and perpendicular transition respectively.** From Eq.~(\ref{eq:beta1}), $\beta$ may be determined for each transition in a photoelectron spectrum from the slope of I($\theta$) vs $P_2(\cos\theta)$. Through conservation of angular momentum, it can be shown that $\beta$ may also be expressed in terms of partial waves and dipole matrix elements. Explicitly,
	\begin{equation}
\beta_{\ell} = \frac{[\ell(\ell-1)\chi_{\ell,\ell-1}^2+(\ell+1)(\ell+2)\chi_{\ell,\ell+1}^2-6\ell(\ell+1)\chi_{\ell,\ell-1}\chi_{\ell,\ell+1}\cos\delta_{\ell+1,\ell-1}]/(2\ell+1)}{\ell\chi_{\ell,\ell-1}^2+(\ell+1)\chi_{\ell,\ell+1}^2},
\label{eq:cooper-zare}
\end{equation}
where $\ell$ is the electron orbital angular momentum of the parent anion 
orbital, $\chi_{\ell,\ell\pm1}$ is the radial 
dipole matrix element for the transition from an orbital $\ell$ to 
each of the $\ell\pm1$ partial waves, and $\delta_{\ell+1,\ell-1}$ is 
the phase shift between the two ($\ell\pm1$) partial waves.

As the radial dipole matrix elements will vary with electron kinetic energy, so too will $\beta$. Therefore, measuring anisotropy parameters at a range of energies will reveal the character of the detachment orbital. Anisotropy parameters were calculated for all resolved transitions in the C$_2$H$^-$ photoelectron spectra from $266-355$~nm, as shown in Fig.~\ref{fig:4}.

Photodetachment to the ground state of C$_2$H$^-$ $(\tilde{X}\,^1\Sigma^+)$ involves ejecting an electron from an $s-$like $5\sigma_g$ orbital, whereas detachment to the excited $(\tilde{A}\,^2\Pi)$ state occurs from a $p-$like $1\pi_u$ orbital.  For a pure $s$ and $p$ orbital, the energy dependence of the anisotropy parameter may be described by Equations (\ref{eq:b-s}) and (\ref{eq:b-p}) respectively,
\begin{equation}
\beta_s = 2,
\label{eq:b-s}
\end{equation}
and,
\begin{equation}
\beta_p = \frac{2\text{A}_1^2\epsilon^2-4\text{A}_1\epsilon\cos\delta_{2,0}}{1+2\text{A}_1^2\epsilon^2},
\label{eq:b-p}
\end{equation}
where the Hanstorp coefficient A$_1$ relates to the ratio of radial matrix elements $\frac{\chi_{1,2}}{\chi_{1,0}}$ and $\delta_{2,0}$ represents the partial wave phase shift. As molecular orbitals may not be pure, we can describe the detachment from C$_2$H$^-$ using the mixed $sp$ model of Sanov~\cite{san14},
\begin{equation}
\beta(\epsilon)_{sp} = \frac{2Z\epsilon+2\text{A}_1\epsilon^2-4\epsilon\cos\delta_{\ell\pm 1}}{\frac{1}{\text{A}_1}+2\text{A}_1\epsilon^2+Z\epsilon}
\label{eq:beta-sanov}
\end{equation}  
where $f$ is the percentage of $p$ character of the orbital,
\begin{equation}
Z = \frac{1-f}{f}\frac{8}{3}~~ \text{and} ~~ |\psi\rangle = \sqrt{1-f}|s\rangle + \sqrt{f}|p\rangle.
\end{equation}

Therefore, calculating the anisotropy parameter for a given transition will reveal the symmetry of the state, which can be compared to the symmetry of the calculated vibronic levels. However this is complicated by the presence of HT coupling, which allows for the electronic character of two surfaces to be mixed via a vibrational promoting mode. As shown in the Supplementary Materials, the transition dipole moment for a HT coupled transition may be rewritten as
\begin{align}
\mu_{\alpha}^{a-n} &= \langle \Psi_{\text{anion}}|\vec{\mu_{\alpha}}|\Psi_{\text{neutral}}\rangle\\
&= \mu_{\alpha:0}^{\tilde{X}-\tilde{X}}\langle\chi_{ms}''|\chi_{jt}'\rangle+\gamma_{kr,jt}\mu_{a:0}^{\tilde{A}-\tilde{X}}\langle\chi_{ms}''|Q_n|\chi_{kr}'\rangle
\label{eq:1}
\end{align}  
where $\mu_{\alpha:0}^{\tilde{X}-\tilde{X}}$ and $\mu_{a:0}^{\tilde{A}-\tilde{X}}$ are the electronic transition moments for the $\tilde{X}\leftarrow\tilde{X}$ and $\tilde{A}\leftarrow\tilde{X}$ transitions, $\chi_{ms}'',~\chi_{jt}',~$and$~\chi_{kr}'$ are the nuclear components of the anion and neutral respectively, and $\gamma_{kr,jt}$ is the vibronic coupling constant. Therefore, HT coupled transitions on the $\tilde{X}^2\Sigma^+$ surface are expected to have anisotropy parameters that reflect the coupled $\tilde{A}^2\Pi$ surface.

Anisotropy parameters were calculated for all strong transitions in the C$_2$H$^-$ photoelectron spectra from $355-266$~nm, as shown in Fig.~\ref{fig:4}.

%--------------------------------------------
%--Keep this for later (discussion or PAD)---
%--------------------------------------------
HT coupling allows for the electronic character of two surfaces to be mixed via a vibrational promoting mode. As shown in the Supplementary Materials, the transition dipole moment for a HT coupled transition may be rewritten as
\begin{align}
\mu_{\alpha}^{a-n} &= \langle \Psi_{\text{anion}}|\vec{\mu_{\alpha}}|\Psi_{\text{neutral}}\rangle\\
&= \mu_{\alpha:0}^{\tilde{X}-\tilde{X}}\langle\chi_{ms}''|\chi_{jt}'\rangle+\gamma_{kr,jt}\mu_{a:0}^{\tilde{A}-\tilde{X}}\langle\chi_{ms}''|Q_n|\chi_{kr}'\rangle
\label{eq:1}
\end{align}  
where $\mu_{\alpha:0}^{\tilde{X}-\tilde{X}}$ and $\mu_{a:0}^{\tilde{A}-\tilde{X}}$ are the electronic transition moments for the $\tilde{X}\leftarrow\tilde{X}$ and $\tilde{A}\leftarrow\tilde{X}$ transitions, $\chi_{ms}'',~\chi_{jt}',~$and$~\chi_{kr}'$ are the nuclear components of the anion and neutral respectively, and $\gamma_{kr,jt}$ is the vibronic coupling constant. By comparing Eq.~(\ref{eq:1}) to a Taylor series expansion of the transition dipole moment in $Q_n$ about the anion equilibrium geometry, one can see that the vibronic coupling constant may be defined as,
\begin{equation}
\left(\frac{\partial\mu_{\alpha}^{\tilde{X}-\tilde{X}}}{\partial Q_n}\right)_0 = \gamma_{kr,jt}\mu_{a:0}^{\tilde{A}-\tilde{X}}.
\label{eq:2}
\end{equation}
Equation~(\ref{eq:2}) shows that information about the vibronic coupling interaction between the neutral $\tilde{A}-\tilde{X}$ states may be obtained from determining the slope of the $\tilde{X}-\tilde{X}$ electronic transition moment along the vibrational promoting mode coordinate $Q_n$.

%--------------------------------------------------------------------------------
%---------------------------------------------------------------------------------

The resolution attainable using velocity-map imaging is dependent on the energy of the photoelectrons, $\Delta\epsilon\propto\epsilon$. Therefore, measurements close to threshold will provide the highest energy resolution, while shorter wavelength measurements will map a greater extent of the neutral vibrational structure. This variation is illustrated in Fig.~\ref{fig:1}(b), which shows the photoelectron spectra of C$_2$H$^-$ resulting from photodetachment at 266~nm, 300~nm, 310~nm, 320~nm, and 355~nm. In the shorter wavelength measurements, spectral structure related to the $\tilde{A}\,^2\Pi$ state is observed up to 6000~cm$^{-1}$ above the $\tilde{A}$ sate origin. A high resolution photoelectron spectrum of C$_2$H$^-$ detachment at 355~nm extracted from a 2048$\times$2048 image, similar to Fig.~\ref{fig:1}(a), via an inverse Abel transformation, is shown in Fig.~\ref{fig:C2H-355}

\section{Conclusions}

\section{Methods}
Details of the HR-PEI spectrometer are given in Refs~\onlinecite{cav07} and~\onlinecite{dev17}. CH$_2$CN$^-$ ions are produced by passing a 1:1 C$_2$H$_4$:N$_2$O gas mixture through a pulse valve, which then undergoes supersonic expansion into a high-voltage discharge. Negative ions are extracted, accelerated to 500~eV, and focussed into a novel gating, bunching, and re-referencing unit~\cite{ded01}. Anions are mass separated over a 2m time-of-flight region, with the ion of interest isolated by an electrostatic gate. The ion packet is crossed with a tuneable detachment laser beam, generated from a Sunlite EX optical parametric oscillator pumped by the third harmonic of a Continuum Powerlite 9010 Nd:YAG laser. The laser produces between 10-50mJ per pulse at 10Hz, depending on whether the idler or signal beam is used. The wavelength of the laser light is measured using a HighFinesse WS7 UV wavemeter.

A velocity-map imaging lens, a modified version of the original concept of Eppink and Parker, images the detached electrons to a 75mm diameter MCP/phosphor screen detector. Events are imaged by a 2014x2048 monochrome CCD camera (PCO 2000), with each frame transferred to a computer at a 10Hz repetition rate, and processed in real time to identify individual electron events. The electron positions are centroided to a sub-pixel accuracy, then written to a data file for subsequent analysis. The velocity-map image is centred and then circularized by an angular dependent-radial scaling determined by comparing adjacent radial slice intensity profiles~\cite{gas17}. An inverse Abel transformation of the VMI, based on the algorithm of Hansen and Law~\cite{han85,pya16}, returns a slice image of the 3D electron source distribution. Absolute energy calibration of the photoelectron spectra is achieved using published measurements of species, including O$^-$~\cite{cav07} and NO$_2^-$~\cite{law19}, that have been studied under similar conditions as used for the CH$_2$CN$^-$ measurements.

In standard operation, the energy distribution of the detached electrons is obtained by recording the velocity-mapped positions from photodetachment at a fixed wavelength. However the HR-PEI spectrometer may also be reconfigured into an electron counting mode, where the number of events per laser shot is recorded, while the detachment laser wavelength is varied.

%Hi~\cite{law17}

\begin{acknowledgement}
	This research was supported by the Australian Research Council Discovery
	Project Grants DP160102585 and DP190103151.  
\end{acknowledgement}

% Create the reference section using BibTeX: 
\bibliography{C2H.bib}

\end{document}
% ****** End of file apstemplate.tex ******

### 2022-03-01 Letter.tex
upload paper to git

--- 2022-03-01 Aug2021-CH2-.tex
@@
 Therefore, measuring anisotropy parameters at a range of energies will reveal the character of the detachment orbital.
-Anisotropy parameters were calculated for all resolved transitions in the C$_2$H$^-$ photoelectron spectra from $266-355$~nm, as shown in Fig.~\ref{fig:4}.
+Anisotropy parameters were calculated for all resolved transitions in the C$_2$H$^-$ photoelectron spectra from $266-355$~nm, and for C$_2$D$^-$ at 355~nm ,as shown in Fig.~\ref{fig:4}.
+
+\begin{figure}
+	\includegraphics[width=0.6\textwidth]{figures/PAD}
+	\caption{cat}
+	\label{fig:4}
+\end{figure}
 
@@
 
-Therefore, calculating the anisotropy parameter for a given transition will reveal the symmetry of the state, which can be compared to the symmetry of the calculated vibronic levels.
-However this is complicated by the presence of HT coupling, which allows for the electronic character of two surfaces to be mixed via a vibrational promoting mode.
-As shown in the Supplementary Materials, the transition dipole moment for a HT coupled transition may be rewritten as
-\begin{align}
-\mu_{\alpha}^{a-n} &= \langle \Psi_{\text{anion}}|\vec{\mu_{\alpha}}|\Psi_{\text{neutral}}\rangle\\
-&= \mu_{\alpha:0}^{\tilde{X}-\tilde{X}}\langle\chi_{ms}''|\chi_{jt}'\rangle+\gamma_{kr,jt}\mu_{a:0}^{\tilde{A}-\tilde{X}}\langle\chi_{ms}''|Q_n|\chi_{kr}'\rangle
-\label{eq:1}
-\end{align}  
-where $\mu_{\alpha:0}^{\tilde{X}-\tilde{X}}$ and $\mu_{a:0}^{\tilde{A}-\tilde{X}}$ are the electronic transition moments for the $\tilde{X}\leftarrow\tilde{X}$ and $\tilde{A}\leftarrow\tilde{X}$ transitions, $\chi_{ms}'',~\chi_{jt}',~$and$~\chi_{kr}'$ are the nuclear components of the anion and neutral respectively, and $\gamma_{kr,jt}$ is the vibronic coupling constant.
-Therefore, HT coupled transitions on the $\tilde{X}^2\Sigma^+$ surface are expected to have anisotropy parameters that reflect the coupled $\tilde{A}^2\Pi$ surface.
+Equation~(\ref{eq:beta-sanov}) may be fitted to the experimental anisotropy parameters in Fig.~\ref{fig:4} to determine the orbital character and Hanstorp coefficients.
+All transitions to the $\tilde{A}^2\Pi$ surface may be described by detachment from an orbital with 90\% $s$ character, and a Hanstorp coefficient of A=1.5(4)~eV$^{-1}$.
+However describing transitions to the $\tilde{X}^4\Sigma^+$ surface is complicated by the presence of HT coupling, which allows for the electronic character of two surfaces to be mixed via the promoting $v_2$ mode.
+The non-coupled allowed transitions may be described by detachment from an orbital with 90\% $p$ character, and a Hanstorp coefficient of A=0.66(4)~eV$^{-1}$.
+However the forbidden 2$^{2n+1}$ transitions follow the $s$-like detachment of the excited state.
+Therefore, measuring the anisotropy parameter of transitions near the conical intersection, where transitions to both surfaces overlap, will determine the symmetry of each level.
+This can then be compared to the calculated vibronic levels of Ref.** to help assign the transitions, as shown in Table~S1 and S2.
 
-Anisotropy parameters were calculated for all strong transitions in the C$_2$H$^-$ photoelectron spectra from $355-266$~nm, as shown in Fig.~\ref{fig:4}.
+\subsection{Coupling Calculations}
+In order to investigate the role of C$_{2n}$H and C$_{2n}$H$^-$ species in interstellar chemistry, theoretical approaches are required to link the terrestrial laboratory studies to astronomical observations.
+In particular, the ability to simulate electronic absorption spectra under interstellar conditions is required to survey potential DIB carriers.
+However the strong vibronic coupling in C$_{2n}$H species that has been explored in this study, makes these calculations exceedingly difficult.
+
+Here, we show how the photoelectron spectrum of C$_2$H$^-$, including vibronic coupling effects, may be simulated using a quasidiabatic Hamiltonian.
+Complications brought about by the vibronic interactions between the strongly coupled $\Sigma^+$ and $\Pi$ states in the adiabatic representation can be avoided - in principle - via a transformation to a diabatic model.
+A useful diabatic nuclear kinetic energy operator may be achieved by representing the wavefunction of the molecule as a product of the electronic wavefunction with electronic coordinates at a frozen reference geometry, and vibrational wavefunction
+\begin{equation}
+\Psi_{\text{diabatic}} = \psi_{0} \chi.
+\end{equation}
+The electronic states responsible for the failure of the adiabatic model may be isolated (in the diabatic basis) from the rest of the electronic states (in the adiabatic basis).
+This mixing of states prevents the electronic Hamiltonian from being strictly diagonal.
+However, if the frozen electronic states are well-chosen, then the off-diagonal terms in the kinetic
+energy operator are small and can be effectively neglected. This resulting electronic basis is the quasidiabatic representation.
+
+\begin{equation*}
+\boldsymbol{V} = 
+\begin{pmatrix}
+\Delta_0^X + \sum\limits_i F^{X}_{i}q_{i} + \frac{1}{2}\sum\limits_i F^{X}_{ij}q_{i}q_{j}  &
+\sum\limits_i \lambda_{i}^{XA}q_{i} \\
+\sum\limits_i \lambda_{i}^{AX}q_{i} &
+\Delta_0^A + \sum\limits_i F^{A}_{i}q_{i} + \frac{1}{2}\sum\limits_i F^{A}_{ij}q_{i}q_{j} \\  
+\end{pmatrix}
+\end{equation*}
+
+The diagonal terms of $\boldsymbol{V}$ represent the quasidiabatic potential energy surfaces, and contain force constants F associated with the normal modes i,j.
+$\Delta_0$ is the vertical electron detachment energy from C2H$^-$ to the neutral $\tilde{X}^2\Sigma^+$ ground state of C2H, denoted X, and the low-lying $\tilde{A}^2\Pi$ excited state, denoted A.
+The off-diagonal terms of $\boldsymbol{V}$ contain the coupling constants between the quasidiabatic electronic states, $\lambda$.
+The adiabatic potential energy surfaces, $\nu_x$ and $\nu_a$, are obtained through the diagonalization of $\boldsymbol{V}$ and are equal to the quasidiabatic surfaces at a reference geometry, $R_0$.
+Additionally, this applies to all structures displaced from $R_0$ along totally symmetric coordinates, but loses this correspondence along coupling coordinates, particularly at a conical intersection.
+Therefore, all force constants in the diagonal blocks of $\boldsymbol{V}$ in the quasidiabatic representation that are associated with totally symmetric coordinates are equivalent to those obtained in the adiabatic representation and, thus, can be generated using standard ab initio quantum-chemical calculations.
+
+\begin{equation*}
+F^X_i = \left(\frac{\delta\nu}{\delta q_i}\right)_{R_0} ; \quad F^X_i = \left(\frac{\delta\nu^2}{\delta q_i\delta q_j}\right)_{R_0} ;\quad ...
+\end{equation*}
+
+\begin{equation*}
+\forall i,j...\in\Gamma{_tot.symm.},
+\end{equation*}
+
+For the case in which the normal modes, ij, correspond to coupling modes, the diabatic force constants $F_{ij}$ and the adiabatic force constants are not equal due to the off-diagonal coupling terms, and are instead written
+
+\begin{equation*}
+F^{X(A)}_{ij} = f_{ij}^{X(A)} + \frac{2\lambda_{i}\lambda_{j}}{\Delta^{A(X)}_{X(A)}}, \quad \Delta^{A}_{B} = E_A - E_X,
+\end{equation*}
+
+where $F_{ij}$ and $f_{ij}$ are the quasidiabatic and adiabatic force constants, respectively.
+$\Delta^{A}_{X}$ is equal to the vertical energy difference between the coupled states X and A at the reference geometry.
+Furthermore, due to the large geometrical differences between the reference and final states, force fields are not calculated at the reference geometry -- on the adiabatic surface -- but rather, are calculated at the minima of the final states and are transformed into the basis of the reduced normal coordinates of the reference state.
+This is known as "adiabatic parametrization", and is necessary to generate reasonable diabatic force constants.
+
+Lastly, the off-diagonal terms of $\boldsymbol{V}$ are the coupling constants between the vibronically mixed final states and were determined analytically.
+***Need John's help...Did we do any transformation to make PJT quasidiabatic...***
+
+The adiabatic potential energy surfaces were calculated using the coupled cluster
+method with single, double and triple excitations (CCSDT).
+A restricted Hartree-Fock (RHF) reference function was used, along with the atomic natural orbital (ANO) basis set.
+The basis included...***help*** (ANO2).
+The geometries for each state were determined using a RHF-CCSDT/ANO2 optimization procedure based on analytic gradients.
+The quadratic force constants were calculated from harmonic frequency calculations based on analytic derivatives.
+The resulting coupling constants and force constants are presented in Table 1.
+
+The resulting simulated spectrum is presented in Fig.~\ref{fig:5} alongside the experimental photoelectron spectrum.
+
+Discuss difference in C2H and C2D...
 

### 2022-03-01 scripts/D-PAD.py

@@ -1,0 +1,167 @@
+import json
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy.optimize import curve_fit
+from matplotlib.ticker import (MultipleLocator, FormatStrFormatter,
+                               AutoMinorLocator)
+
+
+def bet(E,A,f):
+    Z = (8*(1-f))/(3*f)
+    num = 2*Z*E+2*A*E**2-4*E
+    den = 1/A+2*A*E**2+Z*E
+    return num/den
+
+
+with open('beta-raw.json') as json_file:
+    data = json.load(json_file)
+    
+peaks = [211,0,210,310,210310,230310,'G','H','I','J','K','B1','B2','B3']
+col = ['C1','C1','C1','C1','C1','C1','C0','C0','C0','C0','C0','C3','C3','C3']
+
+width = 3.487
+height = width/1.4
+one_col = (2*width,2*height)
+
+fig = plt.figure(figsize=one_col)
+ax = plt.subplot(111)
+
+n = np.size(peaks)
+for j in range (0,n):
+    x = peaks[j]
+    eKE = []
+    b = []
+    err = []
+    c = col[j]
+    for i in data:
+        p = i['Peak']
+        if x != p: continue
+        pea = str(p)
+        b.append(i['Beta'])
+        eKE.append(i['eKE'])
+        err.append(i['Error'])
+    #plt.errorbar(eKE,b,yerr=err,fmt='o',markersize=8,color=c,label=pea)
+
+xeKE = []
+xb = []
+xerr = []
+xhteKE =[]
+xhtb = []
+xhterr = []
+aeKE = []
+ab = []
+aerr = []
+
+for i in data:
+    p = i['Peak']
+    if p in (211,0,310):
+        xeKE.append(i['eKE']/8065.74)
+        xb.append(i['Beta'])
+        xerr.append(i['Error'])
+    if p in (210,210310,230310):
+        xhteKE.append(i['eKE']/8065.74)
+        xhtb.append(i['Beta'])
+        xhterr.append(i['Error'])
+    if p in ('G','H','I','J','K','B1','B2','B3'):
[…]

### 2022-03-01 scripts/Fig1a.py

@@ -1,0 +1,47 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+width = 3.487*1.5
+#height = width/1.618 #golden ratio
+height = width/1
+one_col = (width, height)
+
+VMI = np.loadtxt("C2H-18N1CM512.txt")
+rows, cols = VMI.shape
+trim = 46
+#r2 = rows//2 - trim
+#c2 = cols//2 - trim
+r2 = rows//2
+c2 = cols//2
+
+
+VMI = VMI[trim:-trim, trim:-trim]
+
+fig, ax = plt.subplots()
+
+vmi = ax.imshow(VMI, extent=[-r2, r2, -c2, c2], vmin=-0, cmap="jet")
+#ax.set_xlabel(r"radius (pixels)", ha='left')
+ax.axes.get_yaxis().set_ticks([])
+plt.setp(ax.spines.values(), linewidth=1.5)
+label = ax.set_xlabel("Radius (pixels)", fontsize='14')
+ax.xaxis.set_label_coords(0.7, -0.08)
+ax.set_xticks([0, 256])
+ax.set_xticklabels(["0", "1024"],fontsize=12)
+# colour bar
+cbaxes = fig.add_axes([0.82, 0.5, 0.018, 0.38])
+cbaxes.yaxis.set_label_coords(2, 0.5)
+plt.colorbar(vmi, cax=cbaxes, ticks=[0, int(VMI.max()/1.1/10)*10])
+cbaxes.tick_params(labelsize=12)
+cbaxes.set_ylabel("Electrons", fontsize='14')
+
+ax.annotate('', xy=(-0.1, 0.2), xycoords='axes fraction', xytext=(-0.1, 0.8), 
+            arrowprops=dict(arrowstyle="<-", color='k',lw=1.5))
+ax.annotate('Laser Polarisation',xy=(-0.1, 0.2), rotation=90, xycoords='axes fraction', xytext=(-0.15, 0.5),fontsize=14, ha='center', va='center')
+
+plt.setp(ax.spines.values(), linewidth=1.5)
+ax.tick_params(width=1.5)
+
+plt.savefig("Fig1a.pdf", dpi=600, bbox_inches='tight')
+plt.show()
+print('old version')
+

### 2022-03-01 scripts/Fig1b.py

@@ -1,0 +1,47 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+width = 3.487*1.5
+#height = width/1.618 #golden ratio
+height = width/1
+one_col = (width, height)
+
+VMI = np.loadtxt("C2D-22M1CM512.txt")
+rows, cols = VMI.shape
+trim = 46
+#r2 = rows//2 - trim
+#c2 = cols//2 - trim
+r2 = rows//2
+c2 = cols//2
+
+
+VMI = VMI[trim:-trim, trim:-trim]
+
+fig, ax = plt.subplots()
+
+vmi = ax.imshow(VMI, extent=[-r2, r2, -c2, c2], vmin=-0, cmap="jet")
+#ax.set_xlabel(r"radius (pixels)", ha='left')
+ax.axes.get_yaxis().set_ticks([])
+plt.setp(ax.spines.values(), linewidth=1.5)
+label = ax.set_xlabel("Radius (pixels)", fontsize='14')
+ax.xaxis.set_label_coords(0.7, -0.08)
+ax.set_xticks([0, 256])
+ax.set_xticklabels(["0", "1024"],fontsize=12)
+# colour bar
+cbaxes = fig.add_axes([0.82, 0.5, 0.018, 0.38])
+cbaxes.yaxis.set_label_coords(2, 0.5)
+plt.colorbar(vmi, cax=cbaxes, ticks=[0, int(VMI.max()/1.1/10)*10])
+cbaxes.tick_params(labelsize=12)
+cbaxes.set_ylabel("Electrons", fontsize='14')
+
+ax.annotate('', xy=(-0.1, 0.2), xycoords='axes fraction', xytext=(-0.1, 0.8), 
+            arrowprops=dict(arrowstyle="<-", color='k',lw=1.5))
+ax.annotate('Laser Polarisation',xy=(-0.1, 0.2), rotation=90, xycoords='axes fraction', xytext=(-0.15, 0.5),fontsize=14, ha='center', va='center')
+
+plt.setp(ax.spines.values(), linewidth=1.5)
+ax.tick_params(width=1.5)
+
+plt.savefig("Fig1b.pdf", dpi=600, bbox_inches='tight')
+plt.show()
+print('old version')
+

### 2022-03-01 scripts/PAD.py

@@ -1,0 +1,144 @@
+import json
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy.optimize import curve_fit
+from matplotlib.ticker import (MultipleLocator, FormatStrFormatter,
+                               AutoMinorLocator)
+
+
+def bet(E,A,f):
+    Z = (8*(1-f))/(3*f)
+    num = 2*Z*E+2*A*E**2-4*E
+    den = 1/A+2*A*E**2+Z*E
+    return num/den
+
+
+with open('beta-raw.json') as json_file:
+    data = json.load(json_file)
+    
+peaks = [211,0,210,310,210310,230310,'G','H','I','J','K','B1','B2','B3']
+col = ['C1','C1','C1','C1','C1','C1','C0','C0','C0','C0','C0','C3','C3','C3']
+
+width = 3.487
+height = width/1.4
+one_col = (2*width,2*height)
+
+fig = plt.figure(figsize=one_col)
+ax = plt.subplot(111)
+
+n = np.size(peaks)
+for j in range (0,n):
+    x = peaks[j]
+    eKE = []
+    b = []
+    err = []
+    c = col[j]
+    for i in data:
+        p = i['Peak']
+        if x != p: continue
+        pea = str(p)
+        b.append(i['Beta'])
+        eKE.append(i['eKE'])
+        err.append(i['Error'])
+    #plt.errorbar(eKE,b,yerr=err,fmt='o',markersize=8,color=c,label=pea)
+
+xeKE = []
+xb = []
+xerr = []
+xhteKE =[]
+xhtb = []
+xhterr = []
+aeKE = []
+ab = []
+aerr = []
+
+for i in data:
+    p = i['Peak']
+    if p in (211,0,310):
+        xeKE.append(i['eKE']/8065.74)
+        xb.append(i['Beta'])
+        xerr.append(i['Error'])
+    if p in (210,210310,230310):
+        xhteKE.append(i['eKE']/8065.74)
+        xhtb.append(i['Beta'])
+        xhterr.append(i['Error'])
+    if p in ('G','H','I','J','K','B1','B2','B3'):
+        aeKE.append(i['eKE']/8065.74)
[…]

### 2022-03-01 scripts/plotPES.py

@@ -1,0 +1,29 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+width = 3.487*2
+height = width/1.4
+one_col = (width,height)
+fig,ax = plt.subplots(figsize=one_col)
+
+x1,y1 = np.loadtxt('C2H-355nm.dat',unpack=True)
+x2,y2 = np.loadtxt('C2D-355nm.dat',unpack=True)
+
+plt.plot(x1,y1,label=r'C$_2$H$^-$')
+plt.plot(x2,-y2-0.1,label=r'C$_2$D$^-$')
+ax.spines['top'].set_visible(False)
+ax.spines['left'].set_visible(False)
+ax.spines['right'].set_visible(False)
+plt.yticks([])
+plt.xlim(23500,28300)
+plt.xticks([23000,24000,25000,26000,27000,28000])
+ax.set_xticklabels(['23000','24000','25000','26000','27000','28000'],fontsize=14)
+plt.minorticks_on()
+ax.tick_params(width=1.5)
+plt.setp(ax.spines.values(), linewidth=1.5)
+plt.legend(loc=1,fontsize=14,frameon=False)
+plt.subplots_adjust(top = 1, bottom = 0.1, right = 0.95, left = 0.05, 
+            hspace = 0, wspace = 0)
+
+plt.savefig('Fig1c.pdf',bbbox_inches='tight')
+plt.show()

### 2022-03-01 Stanton/c2h.tex
add Stanton

--- 2022-03-01 Letter.tex
@@
-\documentclass[journal=jpcafh,manuscript=article,layout=onecolumn, 12pt]{achemso}
-\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
-\usepackage[T1]{fontenc}       % Use modern font encodings
+\documentclass{article}
+\usepackage[utf8]{inputenc}
 \usepackage{amsmath}
-\usepackage[dvipsnames]{xcolor}
-% NB added command for in line cite
-\newcommand{\onlinecite}[1]{\hspace{-1 ex} \nocite{#1}\citenum{#1}} 
-%
-\author{Benjamin~A.~Laws}
-\email{b.laws@unsw.edu.au}
-\affiliation{School of Chemistry, University of New South Wales, Sydney NSW 2052, Australia}
-\alsoaffiliation{Research School of Physics, The Australian
-	National University, Canberra ACT 2601, Australia}
-\author{Zachariah~D.~Levey} 
-\affiliation{School of Chemistry, University of New South Wales, Sydney NSW 2052, Australia}
-\author{Timothy~W.~Schmidt} 
-\affiliation{School of Chemistry, University of New South Wales, Sydney NSW 2052, Australia}
-\author{Stephen~T.~Gibson}
-\affiliation{Research School of Physics, The Australian
-	National University, Canberra ACT 2601, Australia}
-\title{C2H-}
-\abbreviations{PES,PAD,EA,eKE,FWHM,VMI}
+
+\title{C2H}
+\author{z.levey }
+\date{October 2021}
+
 \begin{document}
-\begin{abstract}
 
-\end{abstract}
-\section{Introduction}
-Carbon monohydrides C$_{2n}$H, are a class of linear radicals that play an important role in combustion and interstellar chemistry.
-These carbon chains have been observed in many interstellar environments, including planetary atmospheres, comets, dark clouds, and during heavy star formation.
-Due to their relatively high abundance in a variety of astronomical conditions, they have been proposed to be promising candidates for Diffuse Interstellar Band carriers.
-The corresponding anions C$_{2n}$H$^-$ are also believed to play an important role in interstellar chemistry.
-C$_6$H$^-$ was the first negative ion detected in space, after it was observed in the circumstellar envelope of IRC+10216 in 2006.
-More recently, anions C$_4$H$^-$ and C$_8$H$^-$ have also been detected in a range of environments, include dark clouds, prestellar cores, and prostellar envelopes.
-
-Chain growth of the C$_{2n}$H radicals occurs predominately through acetylene addition,
-\begin{equation}
-\text{C}_{2n}\text{H} + \text{C}_2\text{H}_2 \rightarrow \text{C}_{2n+2}\text{H}+\text{H}_2.
-\end{equation}
-Conversely, the formation of anions in space is believed to be driven by radiative electron attachment, charge transfer, and dissociate electron attachment.
-However modelling these processes underestimates the abundance of C$_4$H$^-$ observed in IRC+10216.
-Therefore, ion-neutral reactions have been proposed as an additional chain growth mechanism that also needs to be considered,
- \begin{equation}
- \text{C}_{2n}\text{H}^- + \text{C}_2\text{H}_2 \rightarrow \text{C}_{2n+2}\text{H}^- + \text{H}_2.
- \end{equation}
-Modelling of the extraterrestrial planetary atmosphere of Saturn's moon Titan, suggests that both C$_2$H and C$_2$H$^-$ play an important role in the atmospheric chemistry.
-Multiple reaction pathways were included for the ion C$_2$H$^-$ including,
-\begin{align}
-\text{C}_2\text{H}^- &\xrightarrow[]{\text{H}^+} \text{C}_2\text{H}_2\\
-&\xrightarrow[]{\text{HCN}} \text{CN}^-+\text{H}_2\\
-&\xrightarrow[]{\text{C}_2\text{H}_2} \text{C}_4\text{H}^-+\text{H}_2\\
-&\xrightarrow[]{\text{C}_2\text{H}_2} \text{C}_4^-+\text{H}_3.
-\end{align}
-
-Understanding interstellar chemistry relies critically on theory, to provide a link between astronomical observations and terrestrial laboratory studies.
-Microwave spectroscopy has successfully been used in this fashion to identify a large number of molecules in the ISM.
-However for some species, particularly those with low abundances, UV/vis spectroscopic methods are required for identification.
-This creates a challenge for theory, as electronic spectra calculations are a lot more sensitive to the level of theory employed than pure rotational spectra.
-This becomes even more challenging when vibronic coupling effects are introduced, as they can be exceedingly difficult to model.
-
-These considerations may be explored by examining some of the smallest carbon monohydrides.
-The ethynyl radical C$_2$H may appear to be a simple linear triatomic molecule.
-However the electronic spectrum is complicated by the presence of the close-lying ground $^2\Sigma^+$ and first excited $^2\Pi$ surfaces, which are only separated by $\sim4,000~$cm$^{-1}$.
-The interaction of these surfaces produces a complex vibronic spectrum around the $\tilde{A}^2\Pi$ origin, where no single band corresponding to the $\tilde{X}-\tilde{A}$ origin has been observed.
-In C$_4$H the $^2\Sigma^+$ and $^2\Pi$ states are nearly degenerate, resulting in even stronger coupling, while in C$_6$H and C$_8$H the ordering of the states swaps, with a ground $^2\Pi$ state and a low lying excited $^2\Sigma^+$ state.
-Consequently, understanding these vibronic coupling interactions between the $^2\Sigma$ and $^2\Pi$ surfaces will be essential in order to accurately model the role these radicals (and their corresponding anions) are likely to play in the interstellar chemistry mentioned above, and to discern if they may be possible DIB carriers.
-
-In this paper we study the vibronic spectrum of the ethynyl radical C$_2$H by employing High-Resolution Photoelectron Imaging (HR-PEI) in order to benchmark CFOUR \emph{ab-initio} vibronic-coupling calculations.
-C$_2$H is reported to be one of the most abundant molecules in the universe, and is the most thoroughly studied of the C$_{2n}$H species.
-Many different experimental techniques have been employed to try and resolve the complex vibronic spectrum, including electron spin resonance, laser magnetic resonance, microwave and milli-meter wave spectroscopy, infrared (matrix isolation and Fourier Transform) spectroscopy, and photoelectron spectroscopy.
-Extensive theoretical work on C$_2$H has also been carried out, in order to try and decode the surprisingly complex spectra that are observed in the experimental studies, however this has proven to be far from straightforward.
-In this work we demonstrate how the procedures set out in CFOUR may be used to calculate the strength of the vibronic interaction between coupled surfaces near a conical intersection, in order to simulate electronic and vibronic spectra.
-By employing anion HR-PEI both the $^2\Sigma^+$ and $^2\Pi$ surfaces are mapped out on an equal footing from the anion $\tilde{X}^1\Sigma^+$ state, allowing for direct comparison to the \emph{ab-initio} modelling.
-
-\section{Results and Analysis}
-Ethynyl ions were produced in a pulsed-jet discharge of pure C$_2$H$_4$ gas, and subsequently mass isolated via time of flight.
-Electrons were detached using a tuneable Sunlite Optical Parametric Oscillator (OPO) pumped with the third harmonic of a Nd:YAG laser.
-High electron counts could also be obtained by using the third and fourth harmonics of the Nd:YAG laser directly.
-The detached electrons were then mapped onto a micro channel plate detector using a Velocity Map Imaging (VMI) lens.
-An illustrative VMI of $\sim$4 million electrons collected from 355~nm (3.49~eV) photodetachment of C$_2$H$^-$ is shown in Fig.~\ref{fig:1}(a).
-The electrons are distributed radially according to their speed, with slow electrons at the image center, and fast electrons located towards the outer edge.
-Due to the relatively large C$_2$H$^-$ electron affinity (EA) of 2.969~eV~\cite{erv91}, photodetachment at 355~nm occurs close to threshold.
-This yields slow electrons, allowing for a low repeller voltage ($-600$~V) on the VMI lens, and high velocity resolution.
-
-Despite being close to threshold, two electronic states of neutral C$_2$H are observed.
-The faster electrons on the outer edge correspond to C$_2$H$(\tilde{X}\,^2\Sigma^+)+e^- \leftarrow $C$_2$H$^-(\tilde{X}\,^1\Sigma^+)+h\nu$ photodetachment, and are preferentially distributed around the poles of the image, indicative of a positive anisotropy parameter.
-Conversely the angular distribution of the slower electrons near the center are skewed towards the equator, indicative of a negative anisotropy parameter.
-These electrons may be assigned to photodetachment to the first excited state C$_2$H$(\tilde{A}\,^2\Pi)+e^- \leftarrow $C$_2$H$^-(\tilde{X}\,^1\Sigma^+)+h\nu$.
-
-\begin{figure}
-	\includegraphics[width=0.8\textwidth]{figures/Fig1}
-	\caption{(a) A 3D-representation of the velocity-map image of $\sim$ 4 million photoelectrons detached from C$2$H$^-$ at 355~nm.
-The outer rings, distributed around the vertical laser polarisation axis, represents photodetachment to the ground $\tilde{X}\,^2\Sigma^+$ state.
-The inner rings reprsent detachment to the first excited state $\tilde{A}\,^2\Pi$.
-(b) Photoelectron spectra of C$_2$H$^-$ at a range of detachment wavelengths, illustrating the change in electron intensity profile and energy resolution.}
-	\label{fig:1}
-\end{figure}
-
-To investigate the vibronic coupling interaction between these two nearby $\Sigma^+$ and $\Pi$ surfaces, deuterated ethynyl C$_2$D$^-$ was also studied.
-C$_2$D$^-$ ions were produced in a discharge of pure C$_2$D$_4$ gas and measured under the same experimental conditions as C$_2$H$^-$.
-An illustrative VMI of photodetachment at 355~nm from C$_2$D$^-$ is shown in Fig.~\ref{fig:1}(b).
-Similarly to Fig~\ref{fig:1}(a) two electronic states are observed - fast electrons with a positive anisotropy corresponding to detachment to the $^2\Sigma^+$ surface, and slow electrons with a negative anisotropy corresponding to $^2\Pi$ detachment.
-While the fast electrons appear similar in both images, a striking difference is observed in the slow electrons near the detector center.
-In Fig.~\ref{fig:1}(a) a series of weak rings are observed, however in Fig.~\ref{fig:1}(b) two dominant rings are seen.
-
-The VMI in Fig.~\ref{fig:1} were inverted using the Abel inversion methods detailed in pyAbel, to extract the corresponding photoelectron spectra, which are presented in Fig.~\ref{fig:1}(c).
-Below $27,000~$cm$^{-1}$ the C$_2$H$^-$ and C$_2$D$^-$ spectra appear very similar.
-Both are dominated by the origin transition, shifted by $\sim10~$cm$^{-1}$ in the deuterated spectrum, and show a progression in the 2$^{n+1}_0$ and 3$^1_02^{n+1}_0$ vibrational modes.
-Within the harmonic oscillator approximation, transitions involving an odd quanta of vibrational excitation in the non-symmetric $v_2 (\pi)$ mode should be totally forbidden.
-However, their presence in the photoelectron spectrum in Fig.~\ref{fig:1}(c) is likely an indicator of Herzberg-Teller (HT) vibronic coupling between the ground $^2\Sigma^+$ and nearby excited $^2\Pi$ electronic surfaces, as
-\begin{equation}
-\Sigma^+ \otimes \pi = \Pi. 
-\end{equation}
-
-Above $27,000~$cm$^{-1}$, near the $\tilde{A}^2\Pi$ state origin, large differences are observed between the C$_2$H$^-$ and C$_2$D$^-$ photoelectron spectra in Fig.~\ref{fig:1}(c).
-In the C$_2$H$^-$ spectrum 5 sharp peaks are observed, spaced by $\sim95~$cm$^{-1}$.
-However in the deuterated spectrum, one dominant peak is observed at $27,792$~cm$^{-1}$, with 3 weaker peaks centred around $27,360~$cm$^{-1}$.
-Unlike the structure below $27,000$~cm$^{-1}$ none of these peaks are able to be readily assigned to vibronic transitions, due to the presence of strong coupling interactions between the nearby $\Sigma^+$ and $\Pi$ surfaces.
-
-%Discuss coupling now...
-
-\subsection{Vibronic Coupling Interactions}
-The surprisingly complex spectral structure observed near the $\tilde{A}^2\Pi$ state origin in the photoelectron spectra in Fig.~\ref{fig:1}(c), may be understood by considering the $v_2$ bending vibrational mode.
-To account for the degeneracy of this mode we may introduce the vibronic quantum number $\ell_i$, representing the angular momentum associated with the bending motion.
-This may take a value of $\ell_i = v_i, v_i-2, v_i-4,\dots,1$ or $0$, where $v_i$ is the quanta of bending excitation.
-In the Born-Oppenheimer approximation different vibronic energy levels $\ell_i$ are degenerate, however in cases with strong rovibronic coupling, this degeneracy in $\ell_i$ is lost.
-
-In C$_2$H this effect creates a Renner-Teller (RT) pair in the excited state, where the usually degenerate $\Pi$ surfaces separate to form two non-degenerate electronic states $\Pi^+ (2A')$ and $\Pi^-(1A'')$.
-This involves separating a single potential energy surface (V) into two distinct but connected surfaces (V$^+$) and (V$^-$).
-Due to the strong coupling along the linear axis between the electronic and vibration angular momenta of the $2A'$ and $1A''$ components of the $^2\Pi$ state, stationary states cannot be explicitly assigned to either of the $\Pi^+(2A')$ or $\Pi^-(1A'')$ electronic surfaces.
-Instead, they exist as a combination of both states.
-
-Due to the close lying nature of the ground {$\tilde{X} ^2\Sigma^+$} and excited {$\tilde{A} ^2\Pi$} electronic states, which are only separated by $\sim3700~$cm$^{-1}$, a pseudo Jahn-Teller effect is also observed.
-The Jahn-Teller theorem states that stability and degeneracy are not possible simultaneously unless the molecule is linear~\cite{jah37}, meaning that non-linear molecules with degenerate electronic states will undergo a symmetry breaking distortion in order to remove the degeneracy.
-However a similar effect has also been observed where coupling exists between a non-degenerate state and a nearby pair of degenerate states, even if a molecule is linear.
-
-In the case of ethynyl this is seen as coupling between the ground $\Sigma^+(1A')$ and excited $\Pi^+(2A')$ states, induced by the bending motion of $v_2$.
-The ground state only couples to one of the Renner-Teller pair $\Pi^+(2A')$, as the other state $\Pi^-(1A'')$ has incorrect symmetry.
-This results in a very complex vibronic structure for the $\tilde{A}^2\Pi$ electronic state, with contributions from three coupled surfaces $\Sigma^+(1A'),$ $\Pi^+(2A'),$ and $\Pi^-(1A'')$.
-
-These interactions spread the electronic orgin of the $\tilde{A}\,^2\Pi$ state over several vibronic levels.
-Therefore, instead of assigning a defined origin, the observed peaks in the spectrum may be assigned to coupled admixtures of vibronic transitions involving the three potential energy surfaces,
-\begin{equation}
-\Psi_f = \sum_\xi \psi_e^\xi \sum_k C_{fk}^\xi\phi_{fkm}^\xi,
-\label{eq:teller3} 
-\end{equation}
-where $\psi_e^\xi$ is the diabatic electronic wavefunction, and $\phi_{fkm}^\xi$ is the spin-rovibrational wavefunction.
-$\xi$ represents the electronic states used in the expansion, and in this case $\xi=\Sigma^+(1A'),~\Pi^+(2A'),~\Pi^-(1A'')$.
-A depiction of these three interacting surfaces is given in Fig.~\ref{fig:3}.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.5\textwidth]{figures/Fig3}
-	\caption{Adiabatic potential energy surfaces of $\tilde{X}^2\Sigma^+$, $\tilde{A}^2\Pi^-$, and $\tilde{A}^2\Pi^+$ states, calculated using the method developed by Tarroni and Carter~\cite{tar03} (E$_{1A'}$, E$_{2A'}$, and E$_{1A''}$ in Eq.~\ref{eq:teller3}).}
-	\label{fig:3}
-\end{figure}
-
-Tarroni and Carter~\cite{tar03} have demonstrated that a large number of admixed vibronic levels may be calculated using the potential energy surfaces in Fig.~\ref{fig:3}.
-In fact, over 100 vibronic levels have been calculated, upto 6,400~cm$^{-1}$ above the $\tilde{X}$ state origin.
-However assigning these levels to experimental spectra has remained a challenge, partly due to the large number of calculated vibronic levels, and partly due to the resolution of the experimental data in the literature.
-
-%The total number of vibronic levels that need to be considered may be reduced, by examining the symmetry of the level.
-Conservation of angular momentum dictates only transitions from the anion $\tilde{X}\,^1\Sigma^+$ origin to neutral states with $\Sigma^+$ or $\Pi$ symmetry will be allowed.
-
-\subsection{Photoelectron Angular Distributions}
-Symmetry considerations can be employed to help assign the admixed structure in the experimental photoelectron spectra around the $\tilde{A}^2\Pi$ origin.
-As the detachment laser is linearly polarized, the angular distribution of the electrons in Fig.~\ref{fig:1} may be linked to the symmetry of the detachment orbital.
-For polarised light, the differential cross section is given by
-\begin{equation}
-\frac{\text{d}\sigma}{\text{d}\Omega}=\frac{\sigma_{\text{total}}}{4\pi}[1+\beta P_{2}(\cos\theta)],
-\label{eq:beta1}
-\end{equation}
-where $\theta$ is the angle between the ejected electron and the (vertical) 
-laser polarization, and $P_2$ is the second-order Legendre polynomial.
-The anisotropy parameter $\beta$ provides a quantitative measure of the angular distribution, and can range from -1 to +2 for a pure parallel and perpendicular transition respectively.** From Eq.~(\ref{eq:beta1}), $\beta$ may be determined for each transition in a photoelectron spectrum from the slope of I($\theta$) vs $P_2(\cos\theta)$.
-Through conservation of angular momentum, it can be shown that $\beta$ may also be expressed in terms of partial waves and dipole matrix elements.
-Explicitly,
-	\begin{equation}
-\beta_{\ell} = \frac{[\ell(\ell-1)\chi_{\ell,\ell-1}^2+(\ell+1)(\ell+2)\chi_{\ell,\ell+1}^2-6\ell(\ell+1)\chi_{\ell,\ell-1}\chi_{\ell,\ell+1}\cos\delta_{\ell+1,\ell-1}]/(2\ell+1)}{\ell\chi_{\ell,\ell-1}^2+(\ell+1)\chi_{\ell,\ell+1}^2},
-\label{eq:cooper-zare}
-\end{equation}
-where $\ell$ is the electron orbital angular momentum of the parent anion 
-orbital, $\chi_{\ell,\ell\pm1}$ is the radial 
-dipole matrix element for the transition from an orbital $\ell$ to 
-each of the $\ell\pm1$ partial waves, and $\delta_{\ell+1,\ell-1}$ is 
-the phase shift between the two ($\ell\pm1$) partial waves.
-
-As the radial dipole matrix elements will vary with electron kinetic energy, so too will $\beta$.
-Therefore, measuring anisotropy parameters at a range of energies will reveal the character of the detachment orbital.
-Anisotropy parameters were calculated for all resolved transitions in the C$_2$H$^-$ photoelectron spectra from $266-355$~nm, and for C$_2$D$^-$ at 355~nm ,as shown in Fig.~\ref{fig:4}.
-
-\begin{figure}
-	\includegraphics[width=0.6\textwidth]{figures/PAD}
-	\caption{cat}
-	\label{fig:4}
-\end{figure}
-
-Photodetachment to the ground state of C$_2$H$^-$ $(\tilde{X}\,^1\Sigma^+)$ involves ejecting an electron from an $s-$like $5\sigma_g$ orbital, whereas detachment to the excited $(\tilde{A}\,^2\Pi)$ state occurs from a $p-$like $1\pi_u$ orbital.
-For a pure $s$ and $p$ orbital, the energy dependence of the anisotropy parameter may be described by Equations (\ref{eq:b-s}) and (\ref{eq:b-p}) respectively,
-\begin{equation}
-\beta_s = 2,
-\label{eq:b-s}
-\end{equation}
-and,
-\begin{equation}
-\beta_p = \frac{2\text{A}_1^2\epsilon^2-4\text{A}_1\epsilon\cos\delta_{2,0}}{1+2\text{A}_1^2\epsilon^2},
-\label{eq:b-p}
-\end{equation}
-where the Hanstorp coefficient A$_1$ relates to the ratio of radial matrix elements $\frac{\chi_{1,2}}{\chi_{1,0}}$ and $\delta_{2,0}$ represents the partial wave phase shift.
-As molecular orbitals may not be pure, we can describe the detachment from C$_2$H$^-$ using the mixed $sp$ model of Sanov~\cite{san14},
-\begin{equation}
-\beta(\epsilon)_{sp} = \frac{2Z\epsilon+2\text{A}_1\epsilon^2-4\epsilon\cos\delta_{\ell\pm 1}}{\frac{1}{\text{A}_1}+2\text{A}_1\epsilon^2+Z\epsilon}
-\label{eq:beta-sanov}
-\end{equation}  
-where $f$ is the percentage of $p$ character of the orbital,
-\begin{equation}
-Z = \frac{1-f}{f}\frac{8}{3}~~ \text{and} ~~ |\psi\rangle = \sqrt{1-f}|s\rangle + \sqrt{f}|p\rangle.
-\end{equation}
-
-Equation~(\ref{eq:beta-sanov}) may be fitted to the experimental anisotropy parameters in Fig.~\ref{fig:4} to determine the orbital character and Hanstorp coefficients.
-All transitions to the $\tilde{A}^2\Pi$ surface may be described by detachment from an orbital with 90\% $s$ character, and a Hanstorp coefficient of A=1.5(4)~eV$^{-1}$.
-However describing transitions to the $\tilde{X}^4\Sigma^+$ surface is complicated by the presence of HT coupling, which allows for the electronic character of two surfaces to be mixed via the promoting $v_2$ mode.
-The non-coupled allowed transitions may be described by detachment from an orbital with 90\% $p$ character, and a Hanstorp coefficient of A=0.66(4)~eV$^{-1}$.
-However the forbidden 2$^{2n+1}$ transitions follow the $s$-like detachment of the excited state.
-Therefore, measuring the anisotropy parameter of transitions near the conical intersection, where transitions to both surfaces overlap, will determine the symmetry of each level.
-This can then be compared to the calculated vibronic levels of Ref.** to help assign the transitions, as shown in Table~S1 and S2.
-
-\subsection{Coupling Calculations}
-In order to investigate the role of C$_{2n}$H and C$_{2n}$H$^-$ species in interstellar chemistry, theoretical approaches are required to link the terrestrial laboratory studies to astronomical observations.
-In particular, the ability to simulate electronic absorption spectra under interstellar conditions is required to survey potential DIB carriers.
-However the strong vibronic coupling in C$_{2n}$H species that has been explored in this study, makes these calculations exceedingly difficult.
-
-Here, we show how the photoelectron spectrum of C$_2$H$^-$, including vibronic coupling effects, may be simulated using a quasidiabatic Hamiltonian.
-Complications brought about by the vibronic interactions between the strongly coupled $\Sigma^+$ and $\Pi$ states in the adiabatic representation can be avoided - in principle - via a transformation to a diabatic model.
-A useful diabatic nuclear kinetic energy operator may be achieved by representing the wavefunction of the molecule as a product of the electronic wavefunction with electronic coordinates at a frozen reference geometry, and vibrational wavefunction
-\begin{equation}
-\Psi_{\text{diabatic}} = \psi_{0} \chi.
-\end{equation}
+The photoelectron spectrum of C2H -- including vibronic coupling effects -- is simulated using a quasidiabatic Hamiltonian, which has been described in detail elsewhere, and will only be briefly discussed below.
+Complications brought about by the vibronic interactions between strongly coupled electronic states in the adiabatic representation can be avoided -- in principle -- via a transformation to a diabatic model.
+A useful, diabatic nuclear kinetic energy operator is achieved by representing the wave function of the molecule as a product of electronic wave functions with electronic coordinates at a 'frozen' reference geometry, and vibrational wavefunctions.
 The electronic states responsible for the failure of the adiabatic model may be isolated (in the diabatic basis) from the rest of the electronic states (in the adiabatic basis).
 This mixing of states prevents the electronic Hamiltonian from being strictly diagonal.
-However, if the frozen electronic states are well-chosen, then the off-diagonal terms in the kinetic
-energy operator are small and can be effectively neglected. This resulting electronic basis is the quasidiabatic representation.
+However, if the frozen electronic states are well-chosen, then the off-diagonal terms in the kinetic energy operator are small and can be effectively neglected.
+This resulting electronic basis is the quasidiabatic representation.
+
+The potential energy matrix, V, that appropriately describes the low-lying vibronic states of C2H, can be written
 
@@
 
-The adiabatic potential energy surfaces were calculated using the coupled cluster
-method with single, double and triple excitations (CCSDT).
+The adiabatic potential energy surfaces were calculated using the coupled-cluster method with single, double and triple excitations (CCSDT).
 A restricted Hartree-Fock (RHF) reference function was used, along with the atomic natural orbital (ANO) basis set.
@@
 The quadratic force constants were calculated from harmonic frequency calculations based on analytic derivatives.
-The resulting coupling constants and force constants are presented in Table 1.
-
-The resulting simulated spectrum is presented in Fig.~\ref{fig:5} alongside the experimental photoelectron spectrum.
-
-Discuss difference in C2H and C2D...
-
-%--------------------------------------------
-%--Keep this for later (discussion or PAD)---
-%--------------------------------------------
-HT coupling allows for the electronic character of two surfaces to be mixed via a vibrational promoting mode.
-As shown in the Supplementary Materials, the transition dipole moment for a HT coupled transition may be rewritten as
-\begin{align}
-\mu_{\alpha}^{a-n} &= \langle \Psi_{\text{anion}}|\vec{\mu_{\alpha}}|\Psi_{\text{neutral}}\rangle\\
-&= \mu_{\alpha:0}^{\tilde{X}-\tilde{X}}\langle\chi_{ms}''|\chi_{jt}'\rangle+\gamma_{kr,jt}\mu_{a:0}^{\tilde{A}-\tilde{X}}\langle\chi_{ms}''|Q_n|\chi_{kr}'\rangle
-\label{eq:1}
-\end{align}  
-where $\mu_{\alpha:0}^{\tilde{X}-\tilde{X}}$ and $\mu_{a:0}^{\tilde{A}-\tilde{X}}$ are the electronic transition moments for the $\tilde{X}\leftarrow\tilde{X}$ and $\tilde{A}\leftarrow\tilde{X}$ transitions, $\chi_{ms}'',~\chi_{jt}',~$and$~\chi_{kr}'$ are the nuclear components of the anion and neutral respectively, and $\gamma_{kr,jt}$ is the vibronic coupling constant.
-By comparing Eq.~(\ref{eq:1}) to a Taylor series expansion of the transition dipole moment in $Q_n$ about the anion equilibrium geometry, one can see that the vibronic coupling constant may be defined as,
-\begin{equation}
-\left(\frac{\partial\mu_{\alpha}^{\tilde{X}-\tilde{X}}}{\partial Q_n}\right)_0 = \gamma_{kr,jt}\mu_{a:0}^{\tilde{A}-\tilde{X}}.
-\label{eq:2}
-\end{equation}
-Equation~(\ref{eq:2}) shows that information about the vibronic coupling interaction between the neutral $\tilde{A}-\tilde{X}$ states may be obtained from determining the slope of the $\tilde{X}-\tilde{X}$ electronic transition moment along the vibrational promoting mode coordinate $Q_n$.
-
-%--------------------------------------------------------------------------------
-%---------------------------------------------------------------------------------
-
-The resolution attainable using velocity-map imaging is dependent on the energy of the photoelectrons, $\Delta\epsilon\propto\epsilon$.
-Therefore, measurements close to threshold will provide the highest energy resolution, while shorter wavelength measurements will map a greater extent of the neutral vibrational structure.
-This variation is illustrated in Fig.~\ref{fig:1}(b), which shows the photoelectron spectra of C$_2$H$^-$ resulting from photodetachment at 266~nm, 300~nm, 310~nm, 320~nm, and 355~nm.
-In the shorter wavelength measurements, spectral structure related to the $\tilde{A}\,^2\Pi$ state is observed up to 6000~cm$^{-1}$ above the $\tilde{A}$ sate origin.
-A high resolution photoelectron spectrum of C$_2$H$^-$ detachment at 355~nm extracted from a 2048$\times$2048 image, similar to Fig.~\ref{fig:1}(a), via an inverse Abel transformation, is shown in Fig.~\ref{fig:C2H-355}
-
-\section{Conclusions}
-
-\section{Methods}
-Details of the HR-PEI spectrometer are given in Refs~\onlinecite{cav07} and~\onlinecite{dev17}.
-CH$_2$CN$^-$ ions are produced by passing a 1:1 C$_2$H$_4$:N$_2$O gas mixture through a pulse valve, which then undergoes supersonic expansion into a high-voltage discharge.
-Negative ions are extracted, accelerated to 500~eV, and focussed into a novel gating, bunching, and re-referencing unit~\cite{ded01}.
-Anions are mass separated over a 2m time-of-flight region, with the ion of interest isolated by an electrostatic gate.
-The ion packet is crossed with a tuneable detachment laser beam, generated from a Sunlite EX optical parametric oscillator pumped by the third harmonic of a Continuum Powerlite 9010 Nd:YAG laser.
-The laser produces between 10-50mJ per pulse at 10Hz, depending on whether the idler or signal beam is used.
-The wavelength of the laser light is measured using a HighFinesse WS7 UV wavemeter.
-
-A velocity-map imaging lens, a modified version of the original concept of Eppink and Parker, images the detached electrons to a 75mm diameter MCP/phosphor screen detector.
-Events are imaged by a 2014x2048 monochrome CCD camera (PCO 2000), with each frame transferred to a computer at a 10Hz repetition rate, and processed in real time to identify individual electron events.
-The electron positions are centroided to a sub-pixel accuracy, then written to a data file for subsequent analysis.
-The velocity-map image is centred and then circularized by an angular dependent-radial scaling determined by comparing adjacent radial slice intensity profiles~\cite{gas17}.
-An inverse Abel transformation of the VMI, based on the algorithm of Hansen and Law~\cite{han85,pya16}, returns a slice image of the 3D electron source distribution.
-Absolute energy calibration of the photoelectron spectra is achieved using published measurements of species, including O$^-$~\cite{cav07} and NO$_2^-$~\cite{law19}, that have been studied under similar conditions as used for the CH$_2$CN$^-$ measurements.
-
-In standard operation, the energy distribution of the detached electrons is obtained by recording the velocity-mapped positions from photodetachment at a fixed wavelength.
-However the HR-PEI spectrometer may also be reconfigured into an electron counting mode, where the number of events per laser shot is recorded, while the detachment laser wavelength is varied.
-
-%Hi~\cite{law17}
-
-\begin{acknowledgement}
-	This research was supported by the Australian Research Council Discovery
-	Project Grants DP160102585 and DP190103151.  
-\end{acknowledgement}
-
-% Create the reference section using BibTeX: 
-\bibliography{C2H.bib}
+Table 1 \& 2 presents all parameters that have been used in the Hamiltonians of this work ***to be completed by Zach***.
 
 \end{document}
-% ****** End of file apstemplate.tex ******

### 2022-03-01 Stanton/scripts/266-plot.py
add calculations

@@ -1,0 +1,37 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+def Gauss (E0,FWHM,E):
+    alpha = FWHM/2/np.sqrt(np.log(2.0))
+    return np.exp(-((E-E0)/alpha)**2)
+FWHM = 80
+amp = 1
+
+fn1 = '../C2H_all.dat'
+fn2 = '../C2H_ANU_PES/C2H-266nm.dat'
+
+EA = 23956.4
+ofs = 1220
+cut = 4534
+cut = 3471
+
+b,a = np.loadtxt(fn1,usecols=(1,2),unpack=True)
+x,y = np.loadtxt(fn2,unpack=True)
+
+x = x-EA
+
+Ev = np.arange(-630,12000,0.5)
+spec = np.zeros(np.size(Ev))
+
+for i in range(0,np.size(a)):
+    aa = a[i]
+    if a[i] > cut:
+        aa = a[i]-ofs
+    spec += b[i]*amp*Gauss(aa,FWHM,Ev)
+    #plt.plot((aa,aa),(0,-b[i]),'C0')
+
+plt.plot(Ev,-spec)
+plt.plot(x,y,'C2')
+plt.xlim(-630,12000)
+plt.show()
+

### 2022-03-01 Stanton/scripts/300-plot.py

@@ -1,0 +1,37 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+def Gauss (E0,FWHM,E):
+    alpha = FWHM/2/np.sqrt(np.log(2.0))
+    return np.exp(-((E-E0)/alpha)**2)
+FWHM = 50
+amp = 1
+
+fn1 = '../C2H_all.dat'
+fn2 = '../C2H_ANU_PES/C2H-300nm.dat'
+
+EA = 23956.4
+ofs = 1220
+cut = 4534
+cut = 3471
+
+b,a = np.loadtxt(fn1,usecols=(1,2),unpack=True)
+x,y = np.loadtxt(fn2,unpack=True)
+
+x = x-EA
+
+Ev = np.arange(-630,12000,0.5)
+spec = np.zeros(np.size(Ev))
+
+for i in range(0,np.size(a)):
+    aa = a[i]
+    if a[i] > cut:
+        aa = a[i]-ofs
+    spec += b[i]*amp*Gauss(aa,FWHM,Ev)
+    #plt.plot((aa,aa),(0,-b[i]),'C0')
+
+plt.plot(Ev,-spec)
+plt.plot(x,y,'C2')
+plt.xlim(-630,12000)
+plt.show()
+

### 2022-03-01 Stanton/scripts/C2D-plot.py

@@ -1,0 +1,36 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+fn1 = '../C2D_all.dat'
+fn2 = '../C2H_ANU_PES/C2D-355nm.dat'
+fn3 = '../C2D_sigma.dat'
+
+EA = 23956.4+36.4
+ofs = 1220
+ofs = 1500+36
+cut = 4534
+cut = 3471
+#cut = 100000
+
+b,a = np.loadtxt(fn1,usecols=(1,2),unpack=True)
+d,c = np.loadtxt(fn3,usecols=(1,2),unpack=True)
+x,y = np.loadtxt(fn2,unpack=True)
+
+x = x-EA
+
+for i in range(0,np.size(a)):
+    aa = a[i]
+    if a[i] > cut:
+        aa = a[i]-ofs
+    plt.plot((aa,aa),(0,-b[i]),'C0')
+
+for i in range(0,np.size(c)):
+    aa = c[i]
+    if c[i] > cut:
+        aa = c[i]-ofs
+    plt.plot((aa,aa),(0,-d[i]),'C1')
+
+plt.plot(x,y,'C2')
+plt.xlim(-630,4225)
+plt.show()
+

### 2022-03-01 Stanton/scripts/C2H-plot.py

@@ -1,0 +1,34 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+fn1 = '../C2H_all.dat'
+fn2 = '../C2H_ANU_PES/C2H-355nm.dat'
+fn3 = '../C2H_sigma.dat'
+
+EA = 23956.4
+ofs = 1220
+cut = 4534
+cut = 3471
+
+b,a = np.loadtxt(fn1,usecols=(1,2),unpack=True)
+d,c = np.loadtxt(fn3,usecols=(1,2),unpack=True)
+x,y = np.loadtxt(fn2,unpack=True)
+
+x = x-EA
+
+for i in range(0,np.size(a)):
+    aa = a[i]
+    if a[i] > cut:
+        aa = a[i]-ofs
+    plt.plot((aa,aa),(0,-b[i]),'C0')
+
+for i in range(0,np.size(c)):
+    aa = c[i]
+    if c[i] > cut:
+        aa = c[i]-ofs
+    plt.plot((aa,aa),(0,-d[i]),'C1')
+
+plt.plot(x,y,'C2')
+plt.xlim(-630,4225)
+plt.show()
+

### 2022-03-01 Stanton/scripts/beta/266-pyabel.py

@@ -1,0 +1,69 @@
+import numpy as np
+import abel
+import matplotlib.pyplot as plt
+
+sz = 1024
+sf = 1.19e-5
+zoom = sz/2048
+
+expt = np.loadtxt(f'../../C2H_ANU_PES/C2H-266nm.dat', unpack=True)
+
+#im = np.loadtxt(f'../../C2H_ANU_PES/C2H-266nm.txt')
+im = np.loadtxt(f'stg121/C2H-25M16CMb1024.txt')
+
+# inverse Abel transform
+aim = abel.Transform(im, method='basex', 
+                     transform_options=dict(reg=100),
+                     center='slice', angular_integration=True)
+
+I, beta = abel.tools.vmi.Ibeta(aim.transform, window=9)
+
+R, Iint = aim.angular_integration
+
+# convert radius, intensity to eBE, PES
+eBEbas, PESbas = abel.tools.vmi.toPES(R[:len(I)], I, 
+                           energy_cal_factor=sf,
+                           photon_energy=1.0e7/266, Vrep=-2000,
+                           zoom=zoom)
+
+eBEint, PESint = abel.tools.vmi.toPES(R, Iint, 
+                           energy_cal_factor=sf,
+                           photon_energy=1.0e7/266, Vrep=-2000,
+                           zoom=zoom)
+
+
+# plot ------------------
+fig, (ax0, ax1) = plt.subplots(1, 2, figsize=(12, 8))
+
+ax0.plot(eBEint, PESint/PESint.max(), label='basex angular', lw=1)
+ax0.plot(*expt, label='ANUVMI', lw=1)
+ax0.legend(labelspacing=0.5, fontsize='small')
+ax0.axis(xmin=11700, xmax=31400)
+ax0.set_xlabel(r'eBE (cm$^{-1}$)')
+
+ax1.plot(I*2/I.max(), label='basex PES', lw=1)
+ax1.plot(beta*I*2/I.max(), 'C3', label=r'basex $\beta$ $\times$ I', lw=1)
+ax1.axis(ymin=-1.5, ymax=2.5)
+ax1.set_xlabel(r'radius (pixels)')
+ax1.set_ylabel('anisotropy parameter')
+ax1.legend(labelspacing=0.5, fontsize='small')
+
+plt.savefig('266-pyabel.png', dpi=75, bb_inches='tight')
+plt.show()
+
+width=3.487
[…]

### 2022-03-01 Stanton/scripts/beta/C2D-pyabel.py

@@ -1,0 +1,111 @@
+import numpy as np
+import abel
+import matplotlib.pyplot as plt
+
+sz = 1024
+sf = 1.19e-5
+zoom = sz/2048
+
+expt = np.loadtxt(f'C2D-22M1CMI{sz}PESBE.dat', unpack=True)
+
+im = np.loadtxt(f'C2D-22M1CM{sz}.txt')
+
+# inverse Abel transform
+aim = abel.Transform(im, method='basex', 
+                     transform_options=dict(reg=100),
+                     center='slice', angular_integration=True)
+
+I, beta = abel.tools.vmi.Ibeta(aim.transform, window=9)
+
+R, Iint = aim.angular_integration
+
+# radial ranges for integration
+eBE_range = np.array([
+                   (18245,18600), (19020,19276), (19560,19740), (19740,20100),
+                   (20310,20500), (20500,20800), (21050,21240), (21240,21550),
+                   (21500,21760), (21760,21975), (21975,22152), (22348,22495),
+                   (22520,22708), (22740,22822), (23080,23240), (23250,23460),
+                   (23805,24003), (24005,24188), (24533,24755), (25273,25470)])
+
+eKE_range = 1e7/355 - eBE_range
+r_range = np.flip(np.sqrt(eKE_range/1.19e-5/600)*zoom)
+r_range = np.concatenate(
+            (np.array([(60, 98), (80, 143), (185, 240), (270, 303)])*zoom,
+                         r_range))
+
+# anisotropy parameter from image for each tuple r_range
+Beta, Amp, Rmid, Ivstheta, theta =\
+              abel.tools.vmi.radial_integration(aim.transform, r_range)
+
+BetaT = np.transpose(Beta)
+
+# convert radius, intensity to eBE, PES
+eBEbas, PESbas = abel.tools.vmi.toPES(R[:len(I)], I, 
+                           energy_cal_factor=sf,
+                           photon_energy=1.0e7/355, Vrep=-600,
+                           zoom=zoom)
+
+eBEint, PESint = abel.tools.vmi.toPES(R, Iint, 
+                           energy_cal_factor=sf,
[…]

### 2022-03-01 Stanton/scripts/beta/C2H-pyable.py

@@ -1,0 +1,111 @@
+import numpy as np
+import abel
+import matplotlib.pyplot as plt
+
+sz = 1024
+sf = 1.19e-5
+zoom = sz/2048
+
+expt = np.loadtxt(f'../../C2H_ANU_PES/C2H-355nm.dat', unpack=True)
+
+im = np.loadtxt(f'../../C2H_ANU_PES/C2H-355nm.txt')
+
+# inverse Abel transform
+aim = abel.Transform(im, method='basex', 
+                     transform_options=dict(reg=100),
+                     center='slice', angular_integration=True)
+
+I, beta = abel.tools.vmi.Ibeta(aim.transform, window=9)
+
+R, Iint = aim.angular_integration
+
+# radial ranges for integration
+eBE_range = np.array([
+                   (18245,18600), (19020,19276), (19560,19740), (19740,20100),
+                   (20310,20500), (20500,20800), (21050,21240), (21240,21550),
+                   (21500,21760), (21760,21975), (21975,22152), (22348,22495),
+                   (22520,22708), (22740,22822), (23080,23240), (23250,23460),
+                   (23805,24003), (24005,24188), (24533,24755), (25273,25470)])
+
+eKE_range = 1e7/355 - eBE_range
+r_range = np.flip(np.sqrt(eKE_range/1.19e-5/600)*zoom)
+r_range = np.concatenate(
+            (np.array([(60, 98), (80, 143), (185, 240), (270, 303)])*zoom,
+                         r_range))
+
+# anisotropy parameter from image for each tuple r_range
+Beta, Amp, Rmid, Ivstheta, theta =\
+              abel.tools.vmi.radial_integration(aim.transform, r_range)
+
+BetaT = np.transpose(Beta)
+
+# convert radius, intensity to eBE, PES
+eBEbas, PESbas = abel.tools.vmi.toPES(R[:len(I)], I, 
+                           energy_cal_factor=sf,
+                           photon_energy=1.0e7/355, Vrep=-600,
+                           zoom=zoom)
+
+eBEint, PESint = abel.tools.vmi.toPES(R, Iint, 
+                           energy_cal_factor=sf,
[…]

### 2022-03-01 Stanton/scripts/beta/beta-rbasex-PES.py

@@ -1,0 +1,54 @@
+import numpy as np
+import abel
+import matplotlib.pylab as plt
+
+imagefile = 'stg121/C2H-25M16CMb1024.txt' # 'NO2-001M1CM2048.txt'
+
+IM = np.loadtxt(imagefile)
+zoom = IM.shape[-1]/1024
+
+# radial range of peak X origin intensity used for image centering
+# rr = (int(1500*zoom), int(1700*zoom))
+rr = (int(710*zoom), int(810*zoom))
+
+# Abel transform - rbasex ------------------------------------------
+AIM = abel.Transform(IM, method='rbasex', origin='slice',
+                     transform_options=dict(reg=('diff', 10),
+                     basis_dir='./'),
+                     center_options=dict(radial_range=rr))
+
+r, I, beta = AIM.distr.rIbeta()   # I, beta directly from basis fit
+
+# convert intensity to PES
+eBE, PES = abel.tools.vmi.toPES(r, I,
+                                energy_cal_factor=1.20e-5,
+                                photon_energy=1.0e7/266, Vrep=-2000,
+                                zoom=zoom)
+sube = eBE < 39000
+EA = eBE[sube][(PES[sube]).argmax()]
+# eBE -= EA
+print(f'EA = {EA}')
+# normalize intensity to X origin
+PES /= PES.max()
+beta = beta[::-1]
+
+np.savetxt(f'{imagefile[:-4]}_rbasex.dat', np.column_stack((eBE, PES, beta)),
+           fmt='%8.3f   %10.5f    %10.5f',
+           header='eBE(cm-1)  int. (rel. X0)  beta')
+
+# plots ----------------------------
+fig, ax = plt.subplots(figsize=(12, 6))
+
+ax.plot(eBE, PES, lw=1, label=r'PES')
+ax.plot(eBE, PES*beta, lw=1, label=r'PES$\times\beta$')
+ax.plot((eBE[0], eBE[-1]), (0, 0), 'C7--')
+
+ax.legend()
+ax.set_xlabel(r'eBE (cm$^{-1}$)')
+ax.set_ylabel(r'intensity')
+ax.set_title(r'NO$_2^-$ photodetachment at 468.88 nm')
+#ax.axis(xmin=17500, xmax=21350, ymin=-0.05, ymax=1.8)
+
+#plt.subplots_adjust(left=0.15)
+plt.savefig('beta-rbasex-PES.png')
+plt.show()

### 2022-03-01 Stanton/scripts/beta1-plot.py

@@ -1,0 +1,34 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+fn1 = '../C2H_all.dat'
+fn2 = '../C2H_ANU_PES/C2H-266nm.dat'
+fn3 = '../C2H_sigma.dat'
+
+EA = 23956.4
+ofs = 1220
+cut = 4534
+cut = 3471
+
+b,a = np.loadtxt(fn1,usecols=(1,2),unpack=True)
+d,c = np.loadtxt(fn3,usecols=(1,2),unpack=True)
+x,y = np.loadtxt(fn2,unpack=True)
+
+x = x-EA
+
+for i in range(0,np.size(a)):
+    aa = a[i]
+    if a[i] > cut:
+        aa = a[i]-ofs
+    plt.plot((aa,aa),(0,-b[i]),'C0')
+
+for i in range(0,np.size(c)):
+    aa = c[i]
+    if c[i] > cut:
+        aa = c[i]-ofs
+    plt.plot((aa,aa),(0,-d[i]),'C1')
+
+plt.plot(x,y,'C2')
+plt.xlim(-630,12000)
+plt.show()
+

### 2022-03-03 Aug2021-CH2-.tex
update

@@
 Tarroni and Carter~\cite{tar03} have demonstrated that a large number of admixed vibronic levels may be calculated using the potential energy surfaces in Fig.~\ref{fig:3}.
-In fact, over 100 vibronic levels have been calculated, upto 6,400~cm$^{-1}$ above the $\tilde{X}$ state origin.
+In fact, over 100 vibronic levels have been calculated, up to 6,400~cm$^{-1}$ above the $\tilde{X}$ state origin.
 However assigning these levels to experimental spectra has remained a challenge, partly due to the large number of calculated vibronic levels, and partly due to the resolution of the experimental data in the literature.
@@
 
+\subsection{Coupling Calculations}
+In order to guide spectral assignment of C$_2$H and astronomical searches for other C$_n$H radicals, transition intensities are also needed.
+However, due to the strong vibronic coupling interactions, this can not be obtained via standard quantum chemistry methods.
+To account for these interactions, the photoelectron spectrum of the C$_2$H$^-$ anion was simulated using a quasidiabatic Hamiltonian of the type advocated by Koeppel, Domcke and Cederbaum (KDC, reference here).
+In this approach, the Hamiltonian is represented in a basis of quasidiabatic (slowly varying) electronic  states for which the kinetic energy operator can be assumed diagonal.
+For C$_2$H, the KDC Hamiltonian comprises three states - the two components of the $^2\Pi$ state and the ground $^2\Sigma$ state - and is then projected onto a vibrational basis, usually chosen as a direct product of harmonic oscillators.
+Diagonalization of the corresponding matrix yields the molecular states (which are given in terms of a Born-Huang expansion), and the squared projections of the corresponding eigenvectors onto the ground state of the anion yield the relative intensities.
+The latter is automatically true if the photodetachment cross sections for the $^2\Sigma$ and $^2\Pi$ states are assumed equal, but different cross sections of the two states can be incorporated by scaling the intensities of states according to their (vibronic) symmetry.
+
+Details of the construction and parametrization of KDC Hamiltonians can be found elsewhere in the literature (references), and the procedure followed will be discussed here only briefly.
+The present calculations use the so-called quadratic vibronic coupling (QVC) model.
+For the system at hand, the QVC model Hamiltonian  assumes the following form
+
+where the summations run over the dimensionless normal modes ($q_i$) that serve as the coordinate system for the problem.
+For convenience, the latter are chosen to be those of the anion, which considerably facilitates calculation of the spectral intensities.
+In Eq.
+1, the diagonal terms of V (excluding those that carry the Renner-Teller coupling constant $\eta$) represent the quasidiabatic potential energy surfaces of the $\Sigma$, and the two components of the $\Pi$ state, chosen here as those in which the unpaired electron lies within or is perpendicular to an arbitrarily chosen plane, designated as A(a') and A(a''), respectively.
+$\Delta_0^X$ is the separation of the anion and $\Sigma$ states at the origin of the coordinate system (the vertical electron detachment energy), and $\Delta_0^{Pi}$ is the gap between anion and $\Pi$ states at the same geometry.
+
+For the modes of $\sigma$ symmetry ($q_1$ and $q_3$), the diabatic forces ($F_i$) and force constants ($F_{ij}$) coincide with those of the adiabatic potential energy surfaces.
+However, for the bending mode, the diabatic (F22) and adiabatic (f22) force constants differ, and the parametrization is somewhat more involved.
+For each component of the $\Pi$ state, either the 2a or 2b component of the bending vibration will maintain the A' electronic symmetry that is needed to couple with the X state.
+Designating these as 2a for the A(a') state and 2b for the A(a'') state (as is implicit in Eq.
+1), the diabatic force constants for the bending mode in the X and A states can be written as
+
+where the Renner-Teller interaction strength ($\eta$) is determined from
+
+once the interstate coupling ($\lambda$ which is calculated analytically in this work, see below) is known.
+
+When the potential in Eq.
+1 is diagonalized, the adiabatic states that are used for its parametrization are precisely recovered through second order in displacement.
+To parametrize this Hamiltonian, the equation-of-motion coupled-cluster method known as EOMIP-CCSDT has been used … (Zach goes from here)…
+
+\begin{equation}
+V = \bordermatrix{ & X & A(a') & A(a'') \cr
+	X & {\Delta_0^X+F_1^Xq_1+F_3^Xq_3+   
+		\frac{1}{2} \Sigma_{ij}F^X_{ij}q_iq_j}& 0 & 1 \cr
+	A(a') & 1 & \Delta^A_0+F^A_1q_1+F^A_3q_3+\frac{1}{2}\sum_{ij}F^A_{ij}q_iq_j+\frac{1}{2}\eta(q_{3a}^2-q_{3b}^2) & 0 \cr
+	A(a'') & 0 & 1 & 0 } \qquad
+\end{equation}
+
+\subsection{Simulated Spectra}
+The above method was employed to simulate the photoelectron spectrum of C$_2$H$^-$, with the calculated transitions compared to the experimental data in Figure a.
+The positions of the $^2\Pi$ levels have been shifted by 1,220~cm$^{-1}$ to account for the EOMIP-CCSDT calculations overestimating the effective $^2\Pi$ Term energy.
+Excellent agreement is seen below the A state origin (xxx cm$^{-1}$) in both the position and intensity of the calculated transitions.
+This includes the Herzberg-Tellar coupled transitions, with $\Pi$ symmetry.
+
+The calculations also show good agreement near the conical intersection, correctly predicting that the A state origin is spread over 5 prominent transitions.
+The relative calculated intensities are also a good match to the experimental data.
+Peak e may appear overestimated in the calculations, however this may be explained by the Wigner threshold law reducing the intensity of the experimental peak as it is close to threshold at 355nm.
+The simulated spectrum slightly underestimates the splitting between the vibronic levels, however this may be linked to the overestimation of the gap between the $^2\Sigma$ and $^2\Pi$ surfaces.
+
+The deuterated spectrum of C$_2$D$^-$ was also simulated using the same approach, and is shown in Figure b.
+Again, there is excellent agreement in the intensity and calculated positions of the transitions on the X state surface.
+Near the A state origin, 3 strong transitions are calculated, which may be assigned to the 3 dominant peaks in the experimental spectrum (a,b,c).
+Two transitions are calculated at the position of peak a, however due to the small spacing this may not be resolved in the experimental data.
+The calculated transition for peak c appears to slightly underestimate both the intensity and splitting compared to the experimental data.
+
+The calculated transitions were used to simulate the photoelectron spectrum at 266~nm, as shown in Figure c.
+Gaussians were fitted to the transitions with a FWHM of 20~cm$^{-1}$ to match the resolution of the experimental data.
+This figure demonstrates that the method used in this work does in excellent job in qualitatively predicting the photoelectron spectrum of molecules involving complex vibronic coupling interactions.
+This result also confirms that the method is able to calculate the intensity and position of levels higher up the coupled A state surface.
+Near the $3^0$ transitions (5,000~cm$^1$) only peak f appears to be missing from the simulated spectrum.
+
+Overall, figures a-c show that the quasiadiabatic approach is a reliable method for simulating the spectra of molecules when strong vibornic coupling interactions are involved.
+This method may be expanded to other C$_n$H radicals that possess similar complexities, in order to help guide the search for new molecules to be found in space.
+
 \subsection{Photoelectron Angular Distributions}
+Symmetry considerations may be employed to help verify the assignments from the calculations above.
+The EOMIP-CCSDT calculations determine the symmetry of each transitions, either $\Sigma$ or $\Pi$.
+Experimentally, this may be compared directly to symmetries obtained from the corresponding photoelectron angular distributions.
+As the detachment laser is linearly polarized, the angular distribution of the electrons in Fig.~\ref{fig:1} may be linked to the symmetry of the detachment orbital.
+For polarised light, the differential cross section is given by
+\begin{equation}
+	\frac{\text{d}\sigma}{\text{d}\Omega}=\frac{\sigma_{\text{total}}}{4\pi}[1+\beta P_{2}(\cos\theta)],
+	\label{eq:beta1}
+\end{equation}
+where $\theta$ is the angle between the ejected electron and the (vertical) 
+laser polarization, and $P_2$ is the second-order Legendre polynomial.
+The anisotropy parameter $\beta$ provides a quantitative measure of the angular distribution, and can range from -1 to +2 for a pure parallel and perpendicular transition respectively.** From Eq.~(\ref{eq:beta1}), $\beta$ may be determined for each transition in a photoelectron spectrum from the slope of I($\theta$) vs $P_2(\cos\theta)$.
+
+Through conservation of angular momentum, it can be shown that $\beta$ may also be expressed in terms of partial waves and dipole matrix elements. Explicitly,
+\begin{equation}
+	\beta_{\ell} = \frac{[\ell(\ell-1)\chi_{\ell,\ell-1}^2+(\ell+1)(\ell+2)\chi_{\ell,\ell+1}^2-6\ell(\ell+1)\chi_{\ell,\ell-1}\chi_{\ell,\ell+1}\cos\delta_{\ell+1,\ell-1}]/(2\ell+1)}{\ell\chi_{\ell,\ell-1}^2+(\ell+1)\chi_{\ell,\ell+1}^2},
+	\label{eq:cooper-zare}
+\end{equation}
+where $\ell$ is the electron orbital angular momentum of the parent anion 
+orbital, $\chi_{\ell,\ell\pm1}$ is the radial 
+dipole matrix element for the transition from an orbital $\ell$ to 
+each of the $\ell\pm1$ partial waves, and $\delta_{\ell+1,\ell-1}$ is 
+the phase shift between the two ($\ell\pm1$) partial waves.
+
+ Photodetachment to the ground state of C$_2$H$^-$ $(\tilde{X}\,^1\Sigma^+)$ involves ejecting an electron from an $s-$like $5\sigma_g$ orbital, whereas detachment to the excited $(\tilde{A}\,^2\Pi)$ state occurs from a $p-$like $1\pi_u$ orbital.
+
 Symmetry considerations can be employed to help assign the admixed structure in the experimental photoelectron spectra around the $\tilde{A}^2\Pi$ origin.

### 2022-03-03 Stanton/scripts/C2H-plot.py

@@ -16,19 +16,60 @@ x,y = np.loadtxt(fn2,unpack=True)
 
 x = x-EA
 
+#Plotting Settings
+width = 3.487*2
+height = width/1.4
+one_col = (width,height)
+fig,ax = plt.subplots(figsize=one_col)
+
 for i in range(0,np.size(a)):
     aa = a[i]
     if a[i] > cut:
         aa = a[i]-ofs
-    plt.plot((aa,aa),(0,-b[i]),'C0')
+    plt.plot((aa,aa),(0,-b[i]),'C1')
 
 for i in range(0,np.size(c)):
     aa = c[i]
     if c[i] > cut:
         aa = c[i]-ofs
-    plt.plot((aa,aa),(0,-d[i]),'C1')
+    plt.plot((aa,aa),(0,-d[i]),'w',lw='2.5')
+    plt.plot((aa,aa),(0,-d[i]),'C0',lw='1.5')
 
-plt.plot(x,y,'C2')
+plt.plot(x,y,'k',label=r'C$_2$H$^-$ PES')
 plt.xlim(-630,4225)
+
+plt.plot((0,0),(0,0),'C0',label=r'$\Sigma$ Symmetry')
+plt.plot((0,0),(0,0),'C1',label=r'$\Pi$ Symmetry')
+plt.legend(loc=1,fontsize=10,frameon=False)
+
+ax.spines['top'].set_visible(False)
+ax.spines['left'].set_visible(False)
+ax.spines['right'].set_visible(False)
+
+plt.yticks([])
+plt.xticks([0,1000,2000,3000,4000])
+ax.set_xticklabels(['0','1000','2000','3000','4000'],fontsize=14)
+plt.minorticks_on()
+plt.xlabel('Wavenumber (cm$^{-1}$)',fontsize=14)
+ax.tick_params(width=1.5)
+plt.setp(ax.spines.values(), linewidth=1.5)
+
+
+#Annotating spectrum
+plt.annotate(r'$\tilde{X}$ $^2\Sigma^+$',(400,0.975),ha='center',fontsize=14)
+plt.annotate(r'$\tilde{A}$ $^2\Pi$',(3800,0.58),ha='center',fontsize=14)
+plt.annotate(r'$0^0_0$',(-137,0.955),ha='center')
+plt.annotate(r'$2^1_1$',(-137,0.17),ha='center')
+plt.annotate(r'$2^1_0$',(361,0.10),ha='center')
[…]

### 2022-03-03 Stanton/scripts/266-plot.py
update figures

@@ -5,12 +5,13 @@ def Gauss (E0,FWHM,E):
     alpha = FWHM/2/np.sqrt(np.log(2.0))
     return np.exp(-((E-E0)/alpha)**2)
 FWHM = 80
+#FWHM = 80
 amp = 1
 
 fn1 = '../C2H_all.dat'
 fn2 = '../C2H_ANU_PES/C2H-266nm.dat'
 
-EA = 23956.4
+EA = 23956.4-31
 ofs = 1220
 cut = 4534
 cut = 3471
@@ -19,6 +20,13 @@ b,a = np.loadtxt(fn1,usecols=(1,2),unpack=True)
 x,y = np.loadtxt(fn2,unpack=True)
 
 x = x-EA
+
+#Plotting Settings
+width = 3.487*2
+height = width/1.4
+one_col = (width,height)
+fig,ax = plt.subplots(figsize=one_col)
+
 
 Ev = np.arange(-630,12000,0.5)
 spec = np.zeros(np.size(Ev))
@@ -30,8 +38,48 @@ for i in range(0,np.size(a)):
     spec += b[i]*amp*Gauss(aa,FWHM,Ev)
     #plt.plot((aa,aa),(0,-b[i]),'C0')
 
-plt.plot(Ev,-spec)
-plt.plot(x,y,'C2')
-plt.xlim(-630,12000)
+#plt.plot(Ev,-spec,'C2',label=r'Simulates Spectrum')
+plt.plot(x,y,'k',label=r'C$_2$H$^-$ at 266 nm')
+plt.plot(Ev,-spec,'C2',label=r'Simulated Spectrum')
+plt.xlim(-630,8000)
+
+#Labelling
+#plt.plot((27320-EA,31000-EA),(0.215,0.215),color='k')
+#plt.plot((27320-EA,27320-EA),(0.22,0.21),color='k')
+#plt.plot((28060-EA,28060-EA),(0.22,0.21),color='k')
+#plt.plot((28960-EA,28960-EA),(0.22,0.21),color='k')
+#plt.plot((29620-EA,29620-EA),(0.22,0.21),color='k')
+
+plt.plot((3553,7000),(0.4,0.4),'k')
+plt.plot((3553,3553),(0.42,0.38),'k')
+plt.plot((4055,4055),(0.42,0.38),'k')
+plt.plot((5174,5174),(0.42,0.38),'k')
+plt.plot((5606,5606),(0.42,0.38),'k')
[…]

### 2022-03-03 Stanton/scripts/C2D-plot.py

@@ -12,25 +12,67 @@ cut = 4534
 cut = 3471
 #cut = 100000
 
+
 b,a = np.loadtxt(fn1,usecols=(1,2),unpack=True)
 d,c = np.loadtxt(fn3,usecols=(1,2),unpack=True)
 x,y = np.loadtxt(fn2,unpack=True)
 
 x = x-EA
 
+#Plotting Settings
+width = 3.487*2
+height = width/1.4
+one_col = (width,height)
+fig,ax = plt.subplots(figsize=one_col)
+
 for i in range(0,np.size(a)):
     aa = a[i]
     if a[i] > cut:
         aa = a[i]-ofs
-    plt.plot((aa,aa),(0,-b[i]),'C0')
+    plt.plot((aa,aa),(0,-b[i]),'C1')
 
 for i in range(0,np.size(c)):
     aa = c[i]
     if c[i] > cut:
         aa = c[i]-ofs
-    plt.plot((aa,aa),(0,-d[i]),'C1')
+    plt.plot((aa,aa),(0,-d[i]),'w',lw='2.5')
+    plt.plot((aa,aa),(0,-d[i]),'C0',lw='1.5')
 
-plt.plot(x,y,'C2')
+plt.plot(x,y,'k',label=r'C$_2$D$^-$ PES')
 plt.xlim(-630,4225)
+
+plt.plot((0,0),(0,0),'C0',label=r'$\Sigma$ Symmetry')
+plt.plot((0,0),(0,0),'C1',label=r'$\Pi$ Symmetry')
+plt.legend(loc=9,fontsize=10,frameon=False)
+
+ax.spines['top'].set_visible(False)
+ax.spines['left'].set_visible(False)
+ax.spines['right'].set_visible(False)
+
+plt.yticks([])
+plt.xticks([0,1000,2000,3000,4000])
+ax.set_xticklabels(['0','1000','2000','3000','4000'],fontsize=14)
+plt.minorticks_on()
+plt.xlabel('Wavenumber (cm$^{-1}$)',fontsize=14)
+ax.tick_params(width=1.5)
+plt.setp(ax.spines.values(), linewidth=1.5)
+
+
+#Annotating spectrum
+plt.annotate(r'$\tilde{X}$ $^2\Sigma^+$',(400,0.975),ha='center',fontsize=14)
+plt.annotate(r'$\tilde{A}$ $^2\Pi$',(3300,0.58),ha='center',fontsize=14)
[…]

### 2022-03-03 Stanton/scripts/C2H-plot.py

@@ -40,7 +40,7 @@ plt.xlim(-630,4225)
 
 plt.plot((0,0),(0,0),'C0',label=r'$\Sigma$ Symmetry')
 plt.plot((0,0),(0,0),'C1',label=r'$\Pi$ Symmetry')
-plt.legend(loc=1,fontsize=10,frameon=False)
+plt.legend(loc=9,fontsize=10,frameon=False)
 
 ax.spines['top'].set_visible(False)
 ax.spines['left'].set_visible(False)

### 2022-03-07 Aug2021-CH2-.tex
update figures
update

--- 2022-03-01 Aug2021-CH2-.tex
@@
 \affiliation{School of Chemistry, University of New South Wales, Sydney NSW 2052, Australia}
+\author{John F. Stanton}
+\affiliation{Department of Chemistry, University of Florida, Gainesville, Florida 32611, United States}
 \author{Timothy~W.~Schmidt} 
@@
 	National University, Canberra ACT 2601, Australia}
-\title{C2H-}
+\title{Vibronic coupling in C$_2$H: implications for astrochemistry}
 \abbreviations{PES,PAD,EA,eKE,FWHM,VMI}
@@
 These carbon chains have been observed in many interstellar environments, including planetary atmospheres, comets, dark clouds, and during heavy star formation.
-Due to their relatively high abundance in a variety of astronomical conditions, they have been proposed to be promising candidates for Diffuse Interstellar Band carriers.
+Due to their relatively high abundance in a variety of astronomical conditions, they are believed to be promising candidates for Diffuse Interstellar Band (DIB) carriers.
 The corresponding anions C$_{2n}$H$^-$ are also believed to play an important role in interstellar chemistry.
-C$_6$H$^-$ was the first negative ion detected in space, after it was observed in the circumstellar envelope of IRC+10216 in 2006.
+C$_6$H$^-$ was the first negative ion detected in space, after it was observed in two distinct interstellar molecular clouds IRC+10216 and TMC-1 in 2006.
 More recently, anions C$_4$H$^-$ and C$_8$H$^-$ have also been detected in a range of environments, include dark clouds, prestellar cores, and prostellar envelopes.
@@
 Conversely, the formation of anions in space is believed to be driven by radiative electron attachment, charge transfer, and dissociate electron attachment.
-However modelling these processes underestimates the abundance of C$_4$H$^-$ observed in IRC+10216.
-Therefore, ion-neutral reactions have been proposed as an additional chain growth mechanism that also needs to be considered,
+Current astrochemical modelling of interstellar clouds, such as IRC+1026, typically underestimate the observed abundances of CH$_4^-$.
+Therefore, it has been proposed that ion-neutral reactions
  \begin{equation}
@@
 \end{equation}
+may be significant chain growth mechanisms that also needs to be included.
 Modelling of the extraterrestrial planetary atmosphere of Saturn's moon Titan, suggests that both C$_2$H and C$_2$H$^-$ play an important role in the atmospheric chemistry.
-Multiple reaction pathways were included for the ion C$_2$H$^-$ including,
-\begin{align}
-\text{C}_2\text{H}^- &\xrightarrow[]{\text{H}^+} \text{C}_2\text{H}_2\\
-&\xrightarrow[]{\text{HCN}} \text{CN}^-+\text{H}_2\\
-&\xrightarrow[]{\text{C}_2\text{H}_2} \text{C}_4\text{H}^-+\text{H}_2\\
-&\xrightarrow[]{\text{C}_2\text{H}_2} \text{C}_4^-+\text{H}_3.
-\end{align}
+Multiple reaction pathways were included for the ion C$_2$H$^-$ including reactions with C$_2$H$_2$ and HCN.
 
 Understanding interstellar chemistry relies critically on theory, to provide a link between astronomical observations and terrestrial laboratory studies.
-Microwave spectroscopy has successfully been used in this fashion to identify a large number of molecules in the ISM.
-However for some species, particularly those with low abundances, UV/vis spectroscopic methods are required for identification.
-This creates a challenge for theory, as electronic spectra calculations are a lot more sensitive to the level of theory employed than pure rotational spectra.
+Microwave spectroscopy has successfully been used in this fashion to identify a large number of molecules in the interstellar medium (ISM).
+However for some species, particularly those with low abundances or no dipole moment, UV/vis spectroscopic methods are required for identification.
+This creates a challenge for theory, as electronic spectra calculations are more sensitive to the level of theory employed than pure rotational spectra.
 This becomes even more challenging when vibronic coupling effects are introduced, as they can be exceedingly difficult to model.
@@
 The ethynyl radical C$_2$H may appear to be a simple linear triatomic molecule.
-However the electronic spectrum is complicated by the presence of the close-lying ground $^2\Sigma^+$ and first excited $^2\Pi$ surfaces, which are only separated by $\sim4,000~$cm$^{-1}$.
-The interaction of these surfaces produces a complex vibronic spectrum around the $\tilde{A}^2\Pi$ origin, where no single band corresponding to the $\tilde{X}-\tilde{A}$ origin has been observed.
+However the electronic spectrum is complicated by the presence of the close-lying ground $^2\Sigma^+$ and first excited $^2\Pi$ surfaces, which are only separated by $\sim3,600~$cm$^{-1}$.
+The interaction of these surfaces produces a complex vibronic spectrum around the $\tilde{A}^2\Pi$ state, where the $\tilde{X}-\tilde{A}$ origin is spread over multiple admixed vibronic levels.
 In C$_4$H the $^2\Sigma^+$ and $^2\Pi$ states are nearly degenerate, resulting in even stronger coupling, while in C$_6$H and C$_8$H the ordering of the states swaps, with a ground $^2\Pi$ state and a low lying excited $^2\Sigma^+$ state.
-Consequently, understanding these vibronic coupling interactions between the $^2\Sigma$ and $^2\Pi$ surfaces will be essential in order to accurately model the role these radicals (and their corresponding anions) are likely to play in the interstellar chemistry mentioned above, and to discern if they may be possible DIB carriers.
+Consequently, understanding these vibronic coupling interactions between the $^2\Sigma$ and $^2\Pi$ surfaces will be essential in order to accurately model the role these radicals (and their corresponding anions) are likely to play in the interstellar chemistry mentioned above, and to guide the search for possible DIB carriers.
 
@@
 Many different experimental techniques have been employed to try and resolve the complex vibronic spectrum, including electron spin resonance, laser magnetic resonance, microwave and milli-meter wave spectroscopy, infrared (matrix isolation and Fourier Transform) spectroscopy, and photoelectron spectroscopy.
-Extensive theoretical work on C$_2$H has also been carried out, in order to try and decode the surprisingly complex spectra that are observed in the experimental studies, however this has proven to be far from straightforward.
-In this work we demonstrate how the procedures set out in CFOUR may be used to calculate the strength of the vibronic interaction between coupled surfaces near a conical intersection, in order to simulate electronic and vibronic spectra.
+C$_2$H has also received extensive theoretical attention to try and understand the experimental results, however the large number of possible vibronic levels means this has proven to be a challenge.
+In this work we demonstrate how construction of a quasiadiabatic Hamiltonian allows for the strength of vibronic interactions between coupled surfaces near a conical intersection to be calculated, in order to simulate electronic and vibronic spectra.
 By employing anion HR-PEI both the $^2\Sigma^+$ and $^2\Pi$ surfaces are mapped out on an equal footing from the anion $\tilde{X}^1\Sigma^+$ state, allowing for direct comparison to the \emph{ab-initio} modelling.
@@
 An illustrative VMI of photodetachment at 355~nm from C$_2$D$^-$ is shown in Fig.~\ref{fig:1}(b).
-Similarly to Fig~\ref{fig:1}(a) two electronic states are observed - fast electrons with a positive anisotropy corresponding to detachment to the $^2\Sigma^+$ surface, and slow electrons with a negative anisotropy corresponding to $^2\Pi$ detachment.
+Similarly to Fig~\ref{fig:1}(a) two electronic transitions are observed.
 While the fast electrons appear similar in both images, a striking difference is observed in the slow electrons near the detector center.
@@
 
-The VMI in Fig.~\ref{fig:1} were inverted using the Abel inversion methods detailed in pyAbel, to extract the corresponding photoelectron spectra, which are presented in Fig.~\ref{fig:1}(c).
-Below $27,000~$cm$^{-1}$ the C$_2$H$^-$ and C$_2$D$^-$ spectra appear very similar.
-Both are dominated by the origin transition, shifted by $\sim10~$cm$^{-1}$ in the deuterated spectrum, and show a progression in the 2$^{n+1}_0$ and 3$^1_02^{n+1}_0$ vibrational modes.
-Within the harmonic oscillator approximation, transitions involving an odd quanta of vibrational excitation in the non-symmetric $v_2 (\pi)$ mode should be totally forbidden.
-However, their presence in the photoelectron spectrum in Fig.~\ref{fig:1}(c) is likely an indicator of Herzberg-Teller (HT) vibronic coupling between the ground $^2\Sigma^+$ and nearby excited $^2\Pi$ electronic surfaces, as
+The VMIs in Fig.~\ref{fig:1} were inverted using the Abel inversion methods detailed in pyAbel, to extract the corresponding photoelectron spectra presented in Fig.~\ref{fig:1}(c).
+Below $27,000~$cm$^{-1}$ on the $\tilde{X} ^2\Sigma^+$ surface the C$_2$H$^-$ and C$_2$D$^-$ spectra are very similar.
+Both are dominated by the origin transition, shifted by $\sim10~$cm$^{-1}$ in the deuterated spectrum, with progressions involving the v$_2$($\pi$) bending and v$_3$($\sigma$) CC stretch vibrational normal modes.
+This includes transitions involving an odd quanta of v$_2$ bending excitation ($2^{n+1}$) which should be totally forbidden within the harmonic oscillator approximation.
+However, the presence of these transitions in the spectra is likely an indicator of Herzberg-Teller (HT) vibronic coupling between the ground $^2\Sigma^+$ and nearby excited $^2\Pi$ electronic surfaces, as
 \begin{equation}
@@
 
-Above $27,000~$cm$^{-1}$, near the $\tilde{A}^2\Pi$ state origin, large differences are observed between the C$_2$H$^-$ and C$_2$D$^-$ photoelectron spectra in Fig.~\ref{fig:1}(c).
+Above $27,000~$cm$^{-1}$, near the $\tilde{A}^2\Pi$ state origin, large differences are observed between the C$_2$H$^-$ and C$_2$D$^-$ photoelectron spectra.
 In the C$_2$H$^-$ spectrum 5 sharp peaks are observed, spaced by $\sim95~$cm$^{-1}$.
@@
 
-%Discuss coupling now...
-
 \subsection{Vibronic Coupling Interactions}
-The surprisingly complex spectral structure observed near the $\tilde{A}^2\Pi$ state origin in the photoelectron spectra in Fig.~\ref{fig:1}(c), may be understood by considering the $v_2$ bending vibrational mode.
-To account for the degeneracy of this mode we may introduce the vibronic quantum number $\ell_i$, representing the angular momentum associated with the bending motion.
+The complex spectral structure observed near the $\tilde{A}^2\Pi$ state origin in Fig.~\ref{fig:1}(c) may be understood by considering the $v_2$ bending vibrational mode.
+To account for the degeneracy of this mode, the vibronic quantum number $\ell_i$ may be introduced, representing the angular momentum associated with the bending motion.
 This may take a value of $\ell_i = v_i, v_i-2, v_i-4,\dots,1$ or $0$, where $v_i$ is the quanta of bending excitation.
@@
 Due to the close lying nature of the ground {$\tilde{X} ^2\Sigma^+$} and excited {$\tilde{A} ^2\Pi$} electronic states, which are only separated by $\sim3700~$cm$^{-1}$, a pseudo Jahn-Teller effect is also observed.
-The Jahn-Teller theorem states that stability and degeneracy are not possible simultaneously unless the molecule is linear~\cite{jah37}, meaning that non-linear molecules with degenerate electronic states will undergo a symmetry breaking distortion in order to remove the degeneracy.
+%The Jahn-Teller theorem states that stability and degeneracy are not possible simultaneously unless the molecule is linear~\cite{jah37}, meaning that non-linear molecules with degenerate electronic states will undergo a symmetry breaking distortion in order to remove the degeneracy.
 However a similar effect has also been observed where coupling exists between a non-degenerate state and a nearby pair of degenerate states, even if a molecule is linear.
-
-In the case of ethynyl this is seen as coupling between the ground $\Sigma^+(1A')$ and excited $\Pi^+(2A')$ states, induced by the bending motion of $v_2$.
+In the case of C$_2$H this is seen as coupling between the ground $\Sigma^+(1A')$ and excited $\Pi^+(2A')$ states, induced by the bending motion of $v_2$.
 The ground state only couples to one of the Renner-Teller pair $\Pi^+(2A')$, as the other state $\Pi^-(1A'')$ has incorrect symmetry.
-This results in a very complex vibronic structure for the $\tilde{A}^2\Pi$ electronic state, with contributions from three coupled surfaces $\Sigma^+(1A'),$ $\Pi^+(2A'),$ and $\Pi^-(1A'')$.
+This results in the complex vibronic structure observed for the $\tilde{A}^2\Pi$ electronic state, with contributions from three coupled surfaces $\Sigma^+(1A'),$ $\Pi^+(2A'),$ and $\Pi^-(1A'')$.
 
@@
 where $\psi_e^\xi$ is the diabatic electronic wavefunction, and $\phi_{fkm}^\xi$ is the spin-rovibrational wavefunction.
-$\xi$ represents the electronic states used in the expansion, and in this case $\xi=\Sigma^+(1A'),~\Pi^+(2A'),~\Pi^-(1A'')$.
+$\xi$ represents the electronic states used in the expansion ($\xi=\Sigma^+(1A'),~\Pi^+(2A'),~\Pi^-(1A'')$).
 A depiction of these three interacting surfaces is given in Fig.~\ref{fig:3}.
@@
 
-Tarroni and Carter~\cite{tar03} have demonstrated that a large number of admixed vibronic levels may be calculated using the potential energy surfaces in Fig.~\ref{fig:3}.
-In fact, over 100 vibronic levels have been calculated, upto 6,400~cm$^{-1}$ above the $\tilde{X}$ state origin.
-However assigning these levels to experimental spectra has remained a challenge, partly due to the large number of calculated vibronic levels, and partly due to the resolution of the experimental data in the literature.
+The adiabatic potential energy surfaces in Figure~\ref{fig:3} were calculated using the variational method of Tarroni and Carter.
+This has been used to calculate a multitude of admixed vibronic levels.
+In the literature, over 100 possible C$_2$H vibronic states have been calculated, up to 6,400~cm$^{-1}$ above the $\tilde{X} ^2\Sigma^+$ origin.
+However, assigning experimental spectra has remained a challenge, partly due to the large number of calculated levels providing multiple possible assignments for each experimentally observed transition.
 
-%The total number of vibronic levels that need to be considered may be reduced, by examining the symmetry of the level.
-Conservation of angular momentum dictates only transitions from the anion $\tilde{X}\,^1\Sigma^+$ origin to neutral states with $\Sigma^+$ or $\Pi$ symmetry will be allowed.
+\subsection{Coupling Calculations}
+In order to guide spectral assignment of C$_2$H and astronomical searches for other C$_n$H radicals, transition intensities are also needed.
+However, due to the strong vibronic coupling interactions, this can not be obtained via standard quantum chemistry methods.
+To account for these interactions, the photoelectron spectrum of the C$_2$H$^-$ anion was simulated using a quasidiabatic Hamiltonian of the type advocated by Koeppel, Domcke and Cederbaum (KDC, reference here).
+In this approach, the Hamiltonian is represented in a basis of quasidiabatic (slowly varying) electronic  states for which the kinetic energy operator can be assumed diagonal.
+For C$_2$H, the KDC Hamiltonian comprises three states - the two components of the $^2\Pi$ state and the ground $^2\Sigma$ state - and is then projected onto a vibrational basis, usually chosen as a direct product of harmonic oscillators.
+Diagonalization of the corresponding matrix yields the molecular states (which are given in terms of a Born-Huang expansion), and the squared projections of the corresponding eigenvectors onto the ground state of the anion yield the relative intensities.
+The latter is automatically true if the photodetachment cross sections for the $^2\Sigma$ and $^2\Pi$ states are assumed equal, but different cross sections of the two states can be incorporated by scaling the intensities of states according to their (vibronic) symmetry.
+
+Details of the construction and parametrization of KDC Hamiltonians can be found elsewhere in the literature (references), and the procedure followed will be discussed here only briefly.
+The present calculations use the so-called quadratic vibronic coupling (QVC) model.
+For the system at hand, the QVC model Hamiltonian  assumes the following form
+
+where the summations run over the dimensionless normal modes ($q_i$) that serve as the coordinate system for the problem.
+For convenience, the latter are chosen to be those of the anion, which considerably facilitates calculation of the spectral intensities.
+In Eq.
+1, the diagonal terms of V (excluding those that carry the Renner-Teller coupling constant $\eta$) represent the quasidiabatic potential energy surfaces of the $\Sigma$, and the two components of the $\Pi$ state, chosen here as those in which the unpaired electron lies within or is perpendicular to an arbitrarily chosen plane, designated as A(a$'$) and A(a$''$), respectively.
+$\Delta_0^X$ is the separation of the anion and $\Sigma$ states at the origin of the coordinate system (the vertical electron detachment energy), and $\Delta_0^{\Pi}$ is the gap between anion and $\Pi$ states at the same geometry.
+
+For the modes of $\sigma$ symmetry ($q_1$ and $q_3$), the diabatic forces ($F_i$) and force constants ($F_{ij}$) coincide with those of the adiabatic potential energy surfaces.
+However, for the bending mode, the diabatic (F$_{22}$) and adiabatic (f$_{22}$) force constants differ, and the parametrization is somewhat more involved.
+For each component of the $\Pi$ state, either the 2a or 2b component of the bending vibration will maintain the A$'$ electronic symmetry that is needed to couple with the X state.
+Designating these as 2a for the A(a$'$) state and 2b for the A(a$''$) state (as is implicit in Eq.
+1), the diabatic force constants for the bending mode in the X and A states can be written as
+
+where the Renner-Teller interaction strength ($\eta$) is determined from
+
+once the interstate coupling ($\lambda$ which is calculated analytically in this work, see below) is known.
+
+When the potential in Eq.
+1 is diagonalized, the adiabatic states that are used for its parametrization are precisely recovered through second order in displacement.
+To parametrize this Hamiltonian, the equation-of-motion coupled-cluster method known as EOMIP-CCSDT has been used … (Zach goes from here)…
+
+\begin{equation}
+V = \bordermatrix{ & X & A(a') & A(a'') \cr
+	X &{\Delta_0^X+F_1^Xq_1+F_3^Xq_3+ 
+		\frac{1}{2} \Sigma_{ij}F^X_{ij}q_iq_j}& 0 & 1 \cr
+	A(a') & 1 & \Delta^A_0+F^A_1q_1+F^A_3q_3+\frac{1}{2}\sum_{ij}F^A_{ij}q_iq_j+\frac{1}{2}\eta(q_{3a}^2-q_{3b}^2) & 0 \cr
+	A(a'') & 0 & 1 & 0 } \qquad
+\end{equation}
+
+\subsection{Simulated Spectra}
+The above method was employed to simulate the photoelectron spectrum of C$_2$H$^-$, with the calculated transitions shown in Figure~\ref{fig:C2H-plot}(a) alongside the experimental data at 355~nm.
+%Calculated transitions with $\Sigma$ symmetry are in blue, and transitions with $\Pi$ symmetry are in orange.
+On the $\tilde{X} ^2\Sigma^+$ surface, below 3,600~cm$^{-1}$, there is excellent agreement in both the transition positions and intensities between the simulated and experimental spectra.
+This includes the HT coupled (2$^{n+1}$) transitions with $\Pi$ symmetry, which would normally be missing from a simulation using standard \emph{ab-initio} approaches.
+
+The positions of the calculated levels for the $\tilde{A}^2\Pi$ state have been shifted by 1,220~cm$^{-1}$ to account for the EOMIP-CCSDT calculations overestimating the effective Term energy.
+The experimental data shows that the electronic coupling interactions induce a splitting of the $\tilde{A} ^2\Pi$ state origin over 5 vibronic levels, spaced by $\sim 95~$cm$^{-1}$ (a-e).
+This splitting is also observed in the calculated spectrum, which correctly predicts 5 prominent transitions in this region.
+The relative intensities between the calculated transitions are also in good agreement with the experimental data.
+Peak d is slightly underestimated, however the relative intensity difference between peaks d and e may be partly explained by the Wigner threshold law, which will reduce the intensity of peak e in the experimental spectrum as it is close to the detachment threshold.
+The simulated spectrum also slightly underestimates the splitting between the vibronic levels, which may be linked to the overestimation of the gap between the $^2\Sigma$ and $^2\Pi$ surfaces.
+
+\begin{figure}[th!]
+	\includegraphics[width=0.6\textwidth]{figures/Fig5.pdf}
+	\caption{cat}
+	\label{fig:C2H-plot}
+\end{figure}
+
+The photoelectron spectrum of C$_2$D$^-$ was also examined using the same approach, with the calculated transitions shown in Figure~\ref{fig:C2H-plot}(b) alongside the 355~nm experimental data.
+Again, there is excellent agreement in the intensity and calculated positions of the transitions on the $\tilde{X} ^2\Sigma^+$ state surface, including the HT coupled levels.
+Near the $\tilde{A} ^2\Pi$ state origin, deuteration has a large impact on the experimental photoelectron spectrum.
+Instead of the 5 evenly split levels observed in C$_2$H, a single dominant peak (d) is now observed at 3,844~cm$^{-1}$ alongside a collection of weaker peaks (a-c) centred around 3,400~cm$^{-1}$.
+Based on previous spin-orbit splitting measurements, peak d is expected to have significant $\tilde{A} ^2\Pi$ character, with peaks a-c commonly assigned to vibronic levels with predominantly HT coupled $\tilde{X} ^2\Sigma^+$ character.
+This suggests that deuteration effectively dampens the coupling interaction between the surfaces.
+
+Like the experimental spectra, a large change is observed in the simulated spectrum upon deuteration.
+The calculated intensity pattern of the vibronic levels around the $\tilde{A} ^2\Pi$ origin is a good match to the experimental data, with a single intense transition observed near peak d, and 3 prominent transitions predicted around the experimental peaks a-c.
+The calculated splitting between the levels is also similar, however the relative intensity of peak d appears to be slightly underestimated.
+%The results from Figure~\ref{fig:C2H-plot} confirm that the quasiadiabtic approach is able to accurately describe the vibronic interactions between the $\Sigma$ and $\Pi$ surfaces, including deuteration effects.
+
+\begin{figure}[th!]
+	\includegraphics[width=0.6\textwidth]{figures/266-plot.pdf}
+	\caption{cat}
+	\label{fig:266-plot}
+\end{figure}
+To investigate the effects of coupling on the higher excited vibronic levels on the$\tilde{A} ^2\Pi$ surface, the calculations were compared to the experimental photoelectron spectrum of C$_2$H$^-$ at 266~nm, as presented in Figure~\ref{fig:266-plot}.
+Gaussians were fitted to the transitions from Figure~\ref{fig:C2H-plot}(a) with a FWHM of 40~cm$^{-1}$ to match the resolution of the experimental data above threshold.
+Near 3,900~cm$^{-1}$ the electronic origin of the $\tilde{A} ^2\Pi$ state is split over 5 vibronic levels, as discussed above.
+A similar effect is also observed for the $3^1_0$ band, which becomes split over 3 vibronic levels labelled l, n, and o.
+The calculated spectrum correctly predicts the position and intensity of peaks n and o, but appears to strongly underestimate the intensity of peak l.
+Between the $0^0_0$ and $3^1_0$ bands a collection of weaker peaks are also observed (f,g,j,k).
+These are assigned to highly excited HT coupled $\tilde{X} ^2\Sigma^+$ transitions (j,k), and pure $\tilde{X} ^2\Sigma^+$ transitions (f,g).
+Consequently, peaks f and g will possess $\Sigma$ symmetry, and should have a different anisotropy to all of the other dominant transitions above 3,800~cm$^{-1}$.
+The position and intensity of these highly-excited coupled transitions are well described by the simulated spectrum.
+
+The results from Figures~\ref{fig:C2H-plot} and~\ref{fig:266-plot} confirm that the quasiadiabtic approach is able to accurately describe the vibronic interactions between the $\Sigma$ and $\Pi$ surfaces, including deuteration effects.
+This validates the proposed vibronic interactions, and demonstrates how this method can be employed to decode and assign even complex spectra.
+Applying this approach to similar less-studied systems will produce reliable predictions for the position and intensity of dominant transitions, which will help guide the search for these molecules in laboratory experiments and astronomical observations.
+
+%Overall, figures a-c show that the quasiadiabatic approach is a reliable method for simulating the spectra of molecules when strong vibornic coupling interactions are involved.
+This method may be expanded to other C$_n$H radicals that possess similar complexities, in order to help guide the search for new molecules to be found in space.
 
 \subsection{Photoelectron Angular Distributions}
+Symmetry considerations may be employed to help verify the assignments from the calculations above.
+The EOMIP-CCSDT calculations determine the symmetry of each transitions, either $\Sigma$ or $\Pi$.
+Experimentally, this may be compared directly to symmetries obtained from the corresponding photoelectron angular distributions.
+As the detachment laser is linearly polarized, the angular distribution of the electrons in Fig.~\ref{fig:1} may be linked to the symmetry of the detachment orbital.
+For polarised light, the differential cross section is given by
+\begin{equation}
+	\frac{\text{d}\sigma}{\text{d}\Omega}=\frac{\sigma_{\text{total}}}{4\pi}[1+\beta P_{2}(\cos\theta)],
+	\label{eq:beta1}
+\end{equation}
+where $\theta$ is the angle between the ejected electron and the (vertical) 
+laser polarization, and $P_2$ is the second-order Legendre polynomial.
+The anisotropy parameter $\beta$ provides a quantitative measure of the angular distribution, and can range from -1 to +2 for a pure parallel and perpendicular transition respectively.** From Eq.~(\ref{eq:beta1}), $\beta$ may be determined for each transition in a photoelectron spectrum from the slope of I($\theta$) vs $P_2(\cos\theta)$.
+
+Through conservation of angular momentum, it can be shown that $\beta$ may also be expressed in terms of partial waves and dipole matrix elements. Explicitly,
+\begin{equation}
+	\beta_{\ell} = \frac{[\ell(\ell-1)\chi_{\ell,\ell-1}^2+(\ell+1)(\ell+2)\chi_{\ell,\ell+1}^2-6\ell(\ell+1)\chi_{\ell,\ell-1}\chi_{\ell,\ell+1}\cos\delta_{\ell+1,\ell-1}]/(2\ell+1)}{\ell\chi_{\ell,\ell-1}^2+(\ell+1)\chi_{\ell,\ell+1}^2},
+	\label{eq:cooper-zare}
+\end{equation}
+where $\ell$ is the electron orbital angular momentum of the parent anion 
+orbital, $\chi_{\ell,\ell\pm1}$ is the radial 
+dipole matrix element for the transition from an orbital $\ell$ to 
+each of the $\ell\pm1$ partial waves, and $\delta_{\ell+1,\ell-1}$ is 
+the phase shift between the two ($\ell\pm1$) partial waves.
+
+ Photodetachment to the ground state of C$_2$H$^-$ $(\tilde{X}\,^1\Sigma^+)$ involves ejecting an electron from an $s-$like $5\sigma_g$ orbital, whereas detachment to the excited $(\tilde{A}\,^2\Pi)$ state occurs from a $p-$like $1\pi_u$ orbital.
+
 Symmetry considerations can be employed to help assign the admixed structure in the experimental photoelectron spectra around the $\tilde{A}^2\Pi$ origin.

### 2022-03-07 Stanton/scripts/beta/rbasex.py

@@ -1,0 +1,29 @@
+import numpy as np
+import abel
+import matplotlib.pyplot as plt
+
+imagefile = 'stg121/C2H-25M16CMb1024.txt'
+imagefile = '../../C2H_ANU_PES/C2H-300nm.txt'
+
+IM = np.loadtxt(imagefile)
+zoom = IM.shape[-1]/1024
+
+rr = (int(710*zoom), int(810*zoom))
+
+AIM = abel.Transform(IM, method='rbasex', origin='slice',
+                     transform_options=dict(reg=('diff', 10),
+                     basis_dir='./'),
+                     center_options=dict(radial_range=rr))
+
+r, I, beta = AIM.distr.rIbeta()
+
+eBE, PES = abel.tools.vmi.toPES(r, I,
+                                energy_cal_factor=1.20e-5,
+                                photon_energy=1.0e7/266, Vrep=-2000,
+                                zoom=zoom)
+
+fig, ax = plt.subplots(figsize=(12, 6))
+ax.plot(eBE, PES, lw=1, label=r'PES')
+ax.plot(eBE, PES*beta, lw=1, label=r'PES$\times\beta$')
+
+plt.show()

### 2022-03-09 Aug2021-CH2-.tex
update

@@
 \subsection{Photoelectron Angular Distributions}
-Symmetry considerations may be employed to help verify the assignments from the calculations above.
-The EOMIP-CCSDT calculations determine the symmetry of each transitions, either $\Sigma$ or $\Pi$.
-Experimentally, this may be compared directly to symmetries obtained from the corresponding photoelectron angular distributions.
-As the detachment laser is linearly polarized, the angular distribution of the electrons in Fig.~\ref{fig:1} may be linked to the symmetry of the detachment orbital.
-For polarised light, the differential cross section is given by
+Symmetry considerations may be employed to verify the spectral assignments from the calculations above.
+The quasiadiabatic Hamiltonian approach is able to determine the symmetry of each individual vibronic state, either $\Sigma$ or $\Pi$, which may be compared directly to the experimental electron anisotropy of each transition.
+The VMIs from this work (Figure~\ref{fig:1}) were obtained using a linearly polarized detachment laser.
+Therefore, the differential cross section of emitted electrons is given by
 \begin{equation}
@@
 laser polarization, and $P_2$ is the second-order Legendre polynomial.
-The anisotropy parameter $\beta$ provides a quantitative measure of the angular distribution, and can range from -1 to +2 for a pure parallel and perpendicular transition respectively.** From Eq.~(\ref{eq:beta1}), $\beta$ may be determined for each transition in a photoelectron spectrum from the slope of I($\theta$) vs $P_2(\cos\theta)$.
-
-Through conservation of angular momentum, it can be shown that $\beta$ may also be expressed in terms of partial waves and dipole matrix elements. Explicitly,
-\begin{equation}
-	\beta_{\ell} = \frac{[\ell(\ell-1)\chi_{\ell,\ell-1}^2+(\ell+1)(\ell+2)\chi_{\ell,\ell+1}^2-6\ell(\ell+1)\chi_{\ell,\ell-1}\chi_{\ell,\ell+1}\cos\delta_{\ell+1,\ell-1}]/(2\ell+1)}{\ell\chi_{\ell,\ell-1}^2+(\ell+1)\chi_{\ell,\ell+1}^2},
-	\label{eq:cooper-zare}
-\end{equation}
-where $\ell$ is the electron orbital angular momentum of the parent anion 
-orbital, $\chi_{\ell,\ell\pm1}$ is the radial 
-dipole matrix element for the transition from an orbital $\ell$ to 
-each of the $\ell\pm1$ partial waves, and $\delta_{\ell+1,\ell-1}$ is 
-the phase shift between the two ($\ell\pm1$) partial waves.
+The anisotropy parameter $\beta$ provides a quantitative measure of the anisotropy, and can range from -1 to +2 for purely perpendicular and parallel transition respectively.
+Through conservation of angular momentum, $\beta$ may be described in terms of the detachment partial waves, which are linked to the symmetry of the parent detachment orbital.
+This is discussed in detail elsewhere [cite], and will be only briefly described for the case of C$_2$H$^-$ here.
 
 Photodetachment to the ground state of C$_2$H$^-$ $(\tilde{X}\,^1\Sigma^+)$ involves ejecting an electron from an $s-$like $5\sigma_g$ orbital, whereas detachment to the excited $(\tilde{A}\,^2\Pi)$ state occurs from a $p-$like $1\pi_u$ orbital.
-
-Symmetry considerations can be employed to help assign the admixed structure in the experimental photoelectron spectra around the $\tilde{A}^2\Pi$ origin.
-As the detachment laser is linearly polarized, the angular distribution of the electrons in Fig.~\ref{fig:1} may be linked to the symmetry of the detachment orbital.
-For polarised light, the differential cross section is given by
-\begin{equation}
-\frac{\text{d}\sigma}{\text{d}\Omega}=\frac{\sigma_{\text{total}}}{4\pi}[1+\beta P_{2}(\cos\theta)],
-\label{eq:beta1}
-\end{equation}
-where $\theta$ is the angle between the ejected electron and the (vertical) 
-laser polarization, and $P_2$ is the second-order Legendre polynomial.
-The anisotropy parameter $\beta$ provides a quantitative measure of the angular distribution, and can range from -1 to +2 for a pure parallel and perpendicular transition respectively.** From Eq.~(\ref{eq:beta1}), $\beta$ may be determined for each transition in a photoelectron spectrum from the slope of I($\theta$) vs $P_2(\cos\theta)$.
-Through conservation of angular momentum, it can be shown that $\beta$ may also be expressed in terms of partial waves and dipole matrix elements.
-Explicitly,
-	\begin{equation}
-\beta_{\ell} = \frac{[\ell(\ell-1)\chi_{\ell,\ell-1}^2+(\ell+1)(\ell+2)\chi_{\ell,\ell+1}^2-6\ell(\ell+1)\chi_{\ell,\ell-1}\chi_{\ell,\ell+1}\cos\delta_{\ell+1,\ell-1}]/(2\ell+1)}{\ell\chi_{\ell,\ell-1}^2+(\ell+1)\chi_{\ell,\ell+1}^2},
-\label{eq:cooper-zare}
-\end{equation}
-where $\ell$ is the electron orbital angular momentum of the parent anion 
-orbital, $\chi_{\ell,\ell\pm1}$ is the radial 
-dipole matrix element for the transition from an orbital $\ell$ to 
-each of the $\ell\pm1$ partial waves, and $\delta_{\ell+1,\ell-1}$ is 
-the phase shift between the two ($\ell\pm1$) partial waves.
-
-As the radial dipole matrix elements will vary with electron kinetic energy, so too will $\beta$.
-Therefore, measuring anisotropy parameters at a range of energies will reveal the character of the detachment orbital.
-Anisotropy parameters were calculated for all resolved transitions in the C$_2$H$^-$ photoelectron spectra from $266-355$~nm, as shown in Fig.~\ref{fig:4}.
-
-Photodetachment to the ground state of C$_2$H$^-$ $(\tilde{X}\,^1\Sigma^+)$ involves ejecting an electron from an $s-$like $5\sigma_g$ orbital, whereas detachment to the excited $(\tilde{A}\,^2\Pi)$ state occurs from a $p-$like $1\pi_u$ orbital.
-For a pure $s$ and $p$ orbital, the energy dependence of the anisotropy parameter may be described by Equations (\ref{eq:b-s}) and (\ref{eq:b-p}) respectively,
-\begin{equation}
-\beta_s = 2,
-\label{eq:b-s}
-\end{equation}
-and,
-\begin{equation}
-\beta_p = \frac{2\text{A}_1^2\epsilon^2-4\text{A}_1\epsilon\cos\delta_{2,0}}{1+2\text{A}_1^2\epsilon^2},
-\label{eq:b-p}
-\end{equation}
-where the Hanstorp coefficient A$_1$ relates to the ratio of radial matrix elements $\frac{\chi_{1,2}}{\chi_{1,0}}$ and $\delta_{2,0}$ represents the partial wave phase shift.
-As molecular orbitals may not be pure, we can describe the detachment from C$_2$H$^-$ using the mixed $sp$ model of Sanov~\cite{san14},
+Therefore, the electron anisotropies may be described using the mixed $sp$ model,
 \begin{equation}
@@
 \end{equation}  
-where $f$ is the percentage of $p$ character of the orbital,
+where $\epsilon$ is the electron kinetic energy, $A_1$ is the $s\rightarrow p$ Hanstorp coefficient, $f$ is the percentage of $p$ orbital character,
 \begin{equation}
@@
 
-Therefore, calculating the anisotropy parameter for a given transition will reveal the symmetry of the state, which can be compared to the symmetry of the calculated vibronic levels.
-However this is complicated by the presence of HT coupling, which allows for the electronic character of two surfaces to be mixed via a vibrational promoting mode.
-As shown in the Supplementary Materials, the transition dipole moment for a HT coupled transition may be rewritten as
-\begin{align}
-\mu_{\alpha}^{a-n} &= \langle \Psi_{\text{anion}}|\vec{\mu_{\alpha}}|\Psi_{\text{neutral}}\rangle\\
-&= \mu_{\alpha:0}^{\tilde{X}-\tilde{X}}\langle\chi_{ms}''|\chi_{jt}'\rangle+\gamma_{kr,jt}\mu_{a:0}^{\tilde{A}-\tilde{X}}\langle\chi_{ms}''|Q_n|\chi_{kr}'\rangle
-\label{eq:1}
-\end{align}  
-where $\mu_{\alpha:0}^{\tilde{X}-\tilde{X}}$ and $\mu_{a:0}^{\tilde{A}-\tilde{X}}$ are the electronic transition moments for the $\tilde{X}\leftarrow\tilde{X}$ and $\tilde{A}\leftarrow\tilde{X}$ transitions, $\chi_{ms}'',~\chi_{jt}',~$and$~\chi_{kr}'$ are the nuclear components of the anion and neutral respectively, and $\gamma_{kr,jt}$ is the vibronic coupling constant.
-Therefore, HT coupled transitions on the $\tilde{X}^2\Sigma^+$ surface are expected to have anisotropy parameters that reflect the coupled $\tilde{A}^2\Pi$ surface.
+From Eq.~(\ref{eq:beta-sanov}) it can be seen that detachment from a pure $s$ orbital will have a positive anisotropy ($\beta=+2$), whereas detachment from a pure $p$ orbital will have a negative anisotropy for electron kinetic energies $\epsilon < 2/A_1$.
+Therefore, measuring the anisotropy will determine the electronic character of each individual transition, which may be compared to the calculated symmetries in Figure~\ref{fig:C2H-plot}.
+The anisotropy parameters were measured for every detachment wavelength and prominent transition in the C$_2$H$^-$ photoelectron spectra from this work, and are presented in Figure~S1.
+Fitting Eq.~(\ref{eq:beta-sanov}) to the $^2\Pi$ state detachment with f=0.9 produces a Hanstorp coefficient of $A_1$=0.66(4)~eV$^{-1}$.
 
-Anisotropy parameters were calculated for all strong transitions in the C$_2$H$^-$ photoelectron spectra from $355-266$~nm, as shown in Fig.~\ref{fig:4}.
+\begin{figure}[th!]
+	\includegraphics[width=0.5\textwidth]{figures/PAD.pdf}
+	\caption{cat}
+	\label{fig:S1}
+\end{figure}
 
-%--------------------------------------------
-%--Keep this for later (discussion or PAD)---
-%--------------------------------------------
-HT coupling allows for the electronic character of two surfaces to be mixed via a vibrational promoting mode.
-As shown in the Supplementary Materials, the transition dipole moment for a HT coupled transition may be rewritten as
-\begin{align}
-\mu_{\alpha}^{a-n} &= \langle \Psi_{\text{anion}}|\vec{\mu_{\alpha}}|\Psi_{\text{neutral}}\rangle\\
-&= \mu_{\alpha:0}^{\tilde{X}-\tilde{X}}\langle\chi_{ms}''|\chi_{jt}'\rangle+\gamma_{kr,jt}\mu_{a:0}^{\tilde{A}-\tilde{X}}\langle\chi_{ms}''|Q_n|\chi_{kr}'\rangle
-\label{eq:1}
-\end{align}  
-where $\mu_{\alpha:0}^{\tilde{X}-\tilde{X}}$ and $\mu_{a:0}^{\tilde{A}-\tilde{X}}$ are the electronic transition moments for the $\tilde{X}\leftarrow\tilde{X}$ and $\tilde{A}\leftarrow\tilde{X}$ transitions, $\chi_{ms}'',~\chi_{jt}',~$and$~\chi_{kr}'$ are the nuclear components of the anion and neutral respectively, and $\gamma_{kr,jt}$ is the vibronic coupling constant.
-By comparing Eq.~(\ref{eq:1}) to a Taylor series expansion of the transition dipole moment in $Q_n$ about the anion equilibrium geometry, one can see that the vibronic coupling constant may be defined as,
-\begin{equation}
-\left(\frac{\partial\mu_{\alpha}^{\tilde{X}-\tilde{X}}}{\partial Q_n}\right)_0 = \gamma_{kr,jt}\mu_{a:0}^{\tilde{A}-\tilde{X}}.
-\label{eq:2}
-\end{equation}
-Equation~(\ref{eq:2}) shows that information about the vibronic coupling interaction between the neutral $\tilde{A}-\tilde{X}$ states may be obtained from determining the slope of the $\tilde{X}-\tilde{X}$ electronic transition moment along the vibrational promoting mode coordinate $Q_n$.
+The sign (+/-) of $\beta$ can be used to assign each vibronic level to either the $^2\Sigma^+$ $\leftarrow^1\Sigma^+$ or $^2\Pi$ $\leftarrow^1\Sigma^+$ electronic transition respectively.
+This is particularly useful around the $\tilde{A} ^2\Pi$ origin, where the two states overlap.
+It is important to note that the HT coupled transitions on the $\tilde{X} ^2\Sigma^+$ surface have negative anisotropies and $\Pi$ symmetry.
+This is discussed in more detail in the Supplementary Materials.
 
-%--------------------------------------------------------------------------------
-%---------------------------------------------------------------------------------
+A plot of the anisotropy parameters for C$_2$H$^-$ detachment at 300~nm is presented in Figure~\ref{fig:beta}, alongside the experimental spectrum.
+By plotting $\beta\times I$ the sign (+/-) of each individual transition can be easily identified.
+All of the transitions above the $\tilde{A} ^2\Pi$ origin have a negative anisotropy, except for peak f.
+This confirms the assignment of this peak to the highly excited $\Sigma$ transition $\tilde{X}(0,6,1$).
+The nearby peak h is assigned to the admixed $\Pi$ transition $\tilde{X}(0,3,2)\tilde{A}(0,0,0)$.
+The other two peaks in this region j and k are assigned to highly excited HT coupled $\Pi$ transitions $\tilde{X}(0,7,1)$ and $\tilde{X}(0,11,0)$.
+The assignments for all peaks in the C$_2$H$^-$ and C$_2$D$^-$ photoelectron spectra are presented in the Supplementary Materials Table~S1.
 
-The resolution attainable using velocity-map imaging is dependent on the energy of the photoelectrons, $\Delta\epsilon\propto\epsilon$.
-Therefore, measurements close to threshold will provide the highest energy resolution, while shorter wavelength measurements will map a greater extent of the neutral vibrational structure.
-This variation is illustrated in Fig.~\ref{fig:1}(b), which shows the photoelectron spectra of C$_2$H$^-$ resulting from photodetachment at 266~nm, 300~nm, 310~nm, 320~nm, and 355~nm.
-In the shorter wavelength measurements, spectral structure related to the $\tilde{A}\,^2\Pi$ state is observed up to 6000~cm$^{-1}$ above the $\tilde{A}$ sate origin.
-A high resolution photoelectron spectrum of C$_2$H$^-$ detachment at 355~nm extracted from a 2048$\times$2048 image, similar to Fig.~\ref{fig:1}(a), via an inverse Abel transformation, is shown in Fig.~\ref{fig:C2H-355}
+\begin{figure}[th!]
+	\includegraphics[width=0.6\textwidth]{figures/plotBeta.pdf}
+	\caption{cat}
+	\label{fig:beta}
+\end{figure}
+
+This result demonstrates how experimental anisotropies and calculated transition intensities can be used to help assign and understand vibronically coupled spectra.
+This is particularly useful in regions where there a large number of potential vibronic states, making definitive assignments based on energetics alone difficult.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2022-03-09 Stanton/scripts/266-plot.py

@@ -59,7 +59,7 @@ plt.annotate(r'$0^0_0$',(3804,0.44),ha='center',color='k')
 plt.annotate(r'$3^1_0$',(5390,0.44),ha='center',color='k')
 plt.annotate(r'$\tilde{A}$ $^2\Pi$',(2870,0.40),va='center',fontsize=12)
 plt.annotate('f',(4396,0.105),ha='center')
-plt.annotate('g',(4566,0.12),ha='center')
+plt.annotate('h',(4566,0.12),ha='center')
 plt.annotate('j',(4812,0.1),ha='center')
 plt.annotate('k',(4944,0.11),ha='center')
 plt.annotate('l',(5184,0.173),ha='center')
@@ -75,7 +75,7 @@ plt.yticks([])
 plt.xticks([0,2000,4000,6000,8000])
 ax.set_xticklabels(['0','2000','4000','6000','8000'],fontsize=14)
 plt.minorticks_on()
-plt.xlabel('Wavenumber (cm$^{-1}$)',fontsize=14)
+plt.xlabel('Excitation Energy (cm$^{-1}$)',fontsize=14)
 ax.tick_params(width=1.5)
 plt.setp(ax.spines.values(), linewidth=1.5)
 

### 2022-03-09 Stanton/scripts/C2D-plot.py

@@ -53,7 +53,7 @@ plt.yticks([])
 plt.xticks([0,1000,2000,3000,4000])
 ax.set_xticklabels(['0','1000','2000','3000','4000'],fontsize=14)
 plt.minorticks_on()
-plt.xlabel('Wavenumber (cm$^{-1}$)',fontsize=14)
+plt.xlabel('Excitation Energy (cm$^{-1}$)',fontsize=14)
 ax.tick_params(width=1.5)
 plt.setp(ax.spines.values(), linewidth=1.5)
 

### 2022-03-09 Stanton/scripts/C2H-plot.py

@@ -50,7 +50,7 @@ plt.yticks([])
 plt.xticks([0,1000,2000,3000,4000])
 ax.set_xticklabels(['0','1000','2000','3000','4000'],fontsize=14)
 plt.minorticks_on()
-plt.xlabel('Wavenumber (cm$^{-1}$)',fontsize=14)
+plt.xlabel('Excitation Energy (cm$^{-1}$)',fontsize=14)
 ax.tick_params(width=1.5)
 plt.setp(ax.spines.values(), linewidth=1.5)
 

### 2022-03-09 Stanton/scripts/beta/PAD.py

@@ -1,0 +1,159 @@
+import json
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy.optimize import curve_fit
+from matplotlib.ticker import (MultipleLocator, FormatStrFormatter,
+                               AutoMinorLocator)
+
+
+
+def bet(E,A,f):
+    Z = (8*(1-f))/(3*f)
+    num = 2*Z*E+2*A*E**2-4*E
+    den = 1/A+2*A*E**2+Z*E
+    return num/den
+
+
+with open('beta-raw.json') as json_file:
+    data = json.load(json_file)
+    
+peaks = [211,0,210,310,210310,230310,'G','H','I','J','K','B1','B2','B3']
+col = ['C1','C1','C1','C1','C1','C1','C0','C0','C0','C0','C0','C3','C3','C3']
+
+width = 3.487
+height = width/1.4
+one_col = (2*width,2*height)
+
+fig = plt.figure(figsize=one_col)
+ax = plt.subplot(111)
+
+n = np.size(peaks)
+for j in range (0,n):
+    x = peaks[j]
+    eKE = []
+    b = []
+    err = []
+    c = col[j]
+    for i in data:
+        p = i['Peak']
+        if x != p: continue
+        pea = str(p)
+        b.append(i['Beta'])
+        eKE.append(i['eKE'])
+        err.append(i['Error'])
+    #plt.errorbar(eKE,b,yerr=err,fmt='o',markersize=8,color=c,label=pea)
+
+xeKE = []
+xb = []
+xerr = []
+xhteKE =[]
+xhtb = []
+xhterr = []
+aeKE = []
+ab = []
+aerr = []
+
+for i in data:
+    p = i['Peak']
+    if p in (211,0,310):
+        xeKE.append(i['eKE']/8065.74)
+        xb.append(i['Beta'])
+        xerr.append(i['Error'])
+    if p in (210,210310,230310):
+        xhteKE.append(i['eKE']/8065.74)
+        xhtb.append(i['Beta'])
+        xhterr.append(i['Error'])
+    if p in ('G','H','I','J','K','B1','B2','B3'):
+        aeKE.append(i['eKE']/8065.74)
[…]

### 2022-03-09 Stanton/scripts/beta/plotBeta.py

@@ -1,0 +1,82 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+def Gauss (E0,FWHM,E):
+    alpha = FWHM/2/np.sqrt(np.log(2.0))
+    return np.exp(-((E-E0)/alpha)**2)
+
+FWHM = 40
+amp = 1
+hv = 1e7/300
+
+#Plotting Settings
+width = 3.487*2
+height = width/1.4
+one_col = (width,height)
+fig,ax = plt.subplots(figsize=one_col)
+
+x,y = np.loadtxt('300nm.dat',unpack=True)
+
+b,em,ex,er,ep = np.loadtxt('300.dat',skiprows=1,unpack=True)
+ym = []
+by = []
+xx = []
+
+for i in range(0,np.size(b)):
+    subr = np.logical_and(x>em[i],x<ex[i])
+    suby = y[subr]
+    subx = x[subr]
+    yx = max(suby)
+    for j in range(0,np.size(suby)):
+        if suby[j] == yx:
+            xx.append(subx[j])
+    ym.append(max(suby))
+    by.append(b[i]*max(suby))
+
+fd = np.column_stack((ep,ym,b,by))
+np.savetxt('300BetaData.txt',fd)
+
+#Now we can plot the data
+
+Ev = np.arange(15000,30000,0.5)
+spec = np.zeros(np.size(Ev))
+
+for i in range(0,np.size(b)):
+    spec+= by[i]*amp*Gauss(xx[i],FWHM,Ev)
+
+plt.plot(hv-x,y,'k',label='C$_2$H$^-$ at 300nm')
+plt.plot(hv-Ev,spec,'C3',label = r'Anisotropy ($\beta\times$I)')
+
+#Plotting
+plt.xlim(hv-27000,hv-15000)
+#plt.ylim(-0.18,1.61)
+plt.ylim(-0.18,0.6)
+
+col = ['C0','C0','C1','C0','C0','C1','C1','C1','C1','C1','C1','C1','C0','C1','C1','C1','C1','C1','C1','C1']
+
+lab = ['$2^1_1$','0$^0_0$','$2^1_0$','$2^2_0$','$3^1_0$','$2^1_03^1_0$','$2^3_03^1_0$','a','b','c','d','e','f','h','i','j','k','l','n','o']
+for i in range(0,np.size(lab)):
+    if i == 1: continue
+    if i ==0:
[…]

### 2022-03-14 Aug2021-CH2-.tex
update

@@
 
+\begin{align}
+H &= T_n1+V\\
+V &= \bordermatrix{ & X & A(a') & A(a'') \cr
+	X &\substack{\Delta_0^X+F_1^Xq_1+F_3^Xq_3+\\ 
+		\frac{1}{2} \sum_{ij}F^X_{ij}q_iq_j}& \lambda q_{3a} & \lambda q_{3b} \cr
+	A(a') & \lambda q_{3a} & \substack{\Delta^A_0+F^A_1q_1+F^A_3q_3\\+\frac{1}{2}\sum_{ij}F^A_{ij}q_iq_j+\\\frac{1}{2}\eta(q_{3a}^2-q_{3b}^2)} & \eta q_{3a}q_{3b} \cr
+	A(a'') & \lambda q_{3b} & \eta q_{3a}q_{3b} & \substack{\Delta_0^A+F_1^Aq_1+F_3^Aq_3\\+\frac{1}{2}\sum_{ij}F_{ij}^Aq_iq_j\\-\frac{1}{2}\eta(q_{3a}^2-q_{3b}^2) } } \qquad
+\label{eq:calc1}
+\end{align}
+
 where the summations run over the dimensionless normal modes ($q_i$) that serve as the coordinate system for the problem.
 For convenience, the latter are chosen to be those of the anion, which considerably facilitates calculation of the spectral intensities.
-In Eq.
-1, the diagonal terms of V (excluding those that carry the Renner-Teller coupling constant $\eta$) represent the quasidiabatic potential energy surfaces of the $\Sigma$, and the two components of the $\Pi$ state, chosen here as those in which the unpaired electron lies within or is perpendicular to an arbitrarily chosen plane, designated as A(a$'$) and A(a$''$), respectively.
+In Eq.~(\ref{eq:calc1}), the diagonal terms of V (excluding those that carry the Renner-Teller coupling constant $\eta$) represent the quasidiabatic potential energy surfaces of the $\Sigma$, and the two components of the $\Pi$ state, chosen here as those in which the unpaired electron lies within or is perpendicular to an arbitrarily chosen plane, designated as A(a$'$) and A(a$''$), respectively.
 $\Delta_0^X$ is the separation of the anion and $\Sigma$ states at the origin of the coordinate system (the vertical electron detachment energy), and $\Delta_0^{\Pi}$ is the gap between anion and $\Pi$ states at the same geometry.
@@
 For each component of the $\Pi$ state, either the 2a or 2b component of the bending vibration will maintain the A$'$ electronic symmetry that is needed to couple with the X state.
-Designating these as 2a for the A(a$'$) state and 2b for the A(a$''$) state (as is implicit in Eq.
-1), the diabatic force constants for the bending mode in the X and A states can be written as
+Designating these as 2a for the A(a$'$) state and 2b for the A(a$''$) state (as is implicit in Eq.~\ref{eq:calc1}), the diabatic force constants for the bending mode in the X and A states can be written as
+
+\begin{align}
+F_{33}^X &= f_{33}^X+\frac{2\lambda^2}{(\Delta_0^A-\Delta_0^X)}\\
+F_{33}^A &= f_{3a3a}^{A(a')}-\frac{2\lambda^2}{(\Delta_0^A-\Delta_0^X)}-\eta
+\label{eq:calc2}
+\end{align}
 
 where the Renner-Teller interaction strength ($\eta$) is determined from
+
+\begin{equation}
+\eta = \frac{1}{2}\left[ f_{3a3a}^{A(a')}-f_{3b3b}^{A(a')}-\frac{2\lambda^2}{(\Delta_0^A-\Delta_0^X)}\right]
+\label{eq:calc3}
+\end{equation}
 
@@
 1 is diagonalized, the adiabatic states that are used for its parametrization are precisely recovered through second order in displacement.
-To parametrize this Hamiltonian, the equation-of-motion coupled-cluster method known as EOMIP-CCSDT has been used … (Zach goes from here)…
-
-\begin{equation}
-V = \bordermatrix{ & X & A(a') & A(a'') \cr
-	X &{\Delta_0^X+F_1^Xq_1+F_3^Xq_3+ 
-		\frac{1}{2} \Sigma_{ij}F^X_{ij}q_iq_j}& 0 & 1 \cr
-	A(a') & 1 & \Delta^A_0+F^A_1q_1+F^A_3q_3+\frac{1}{2}\sum_{ij}F^A_{ij}q_iq_j+\frac{1}{2}\eta(q_{3a}^2-q_{3b}^2) & 0 \cr
-	A(a'') & 0 & 1 & 0 } \qquad
-\end{equation}
+To parametrize this Hamiltonian, the equation-of-motion coupled-cluster method known as EOMIP-CCSDT has been used to optimise the geometry of the ground state anion, with an Atomic Natural Orbital (ANO) basis (ANO2).
+Adiabatic linear and quadratic force constants are calculated from the analytical derivatives of the \emph{ab-initio} potential energy surface with respect to the anion reduced normal coordinates, at the anion geometry Q$_0$.
+The interstate PJT coupling constant $\lambda$ is evaluated directly using the CFOUR package to employ the quasidiabatic ansatz described in refs.
+This allows for direct ab-initio evaluation of the linear diabatic interstate coupling constants that parametrize the KDC potential.
+The calculated parameters are presented in the Supplementary Materials, in Table S1.
 

### 2022-03-20 Aug2021-CH2-.tex
update

@@
 	X &\substack{\Delta_0^X+F_1^Xq_1+F_3^Xq_3+\\ 
-		\frac{1}{2} \sum_{ij}F^X_{ij}q_iq_j}& \lambda q_{3a} & \lambda q_{3b} \cr
-	A(a') & \lambda q_{3a} & \substack{\Delta^A_0+F^A_1q_1+F^A_3q_3\\+\frac{1}{2}\sum_{ij}F^A_{ij}q_iq_j+\\\frac{1}{2}\eta(q_{3a}^2-q_{3b}^2)} & \eta q_{3a}q_{3b} \cr
-	A(a'') & \lambda q_{3b} & \eta q_{3a}q_{3b} & \substack{\Delta_0^A+F_1^Aq_1+F_3^Aq_3\\+\frac{1}{2}\sum_{ij}F_{ij}^Aq_iq_j\\-\frac{1}{2}\eta(q_{3a}^2-q_{3b}^2) } } \qquad
+		\frac{1}{2} \sum_{ij}F^X_{ij}q_iq_j}& \lambda q_{2a} & \lambda q_{2b} \cr
+	A(a') & \lambda q_{2a} & \substack{\Delta^A_0+F^A_1q_1+F^A_3q_3\\+\frac{1}{2}\sum_{ij}F^A_{ij}q_iq_j+\\\frac{1}{2}\eta(q_{2a}^2-q_{2b}^2)} & \eta q_{2a}q_{2b} \cr
+	A(a'') & \lambda q_{2b} & \eta q_{2a}q_{2b} & \substack{\Delta_0^A+F_1^Aq_1+F_3^Aq_3\\+\frac{1}{2}\sum_{ij}F_{ij}^Aq_iq_j\\-\frac{1}{2}\eta(q_{2a}^2-q_{2b}^2) } } \qquad
 \label{eq:calc1}
@@
 In Eq.~(\ref{eq:calc1}), the diagonal terms of V (excluding those that carry the Renner-Teller coupling constant $\eta$) represent the quasidiabatic potential energy surfaces of the $\Sigma$, and the two components of the $\Pi$ state, chosen here as those in which the unpaired electron lies within or is perpendicular to an arbitrarily chosen plane, designated as A(a$'$) and A(a$''$), respectively.
-$\Delta_0^X$ is the separation of the anion and $\Sigma$ states at the origin of the coordinate system (the vertical electron detachment energy), and $\Delta_0^{\Pi}$ is the gap between anion and $\Pi$ states at the same geometry.
+$\Delta_0^X$ is the separation of the anion and $\Sigma$ states at the origin of the coordinate system (the vertical electron detachment energy), and $\Delta_0^{A}$ is the gap between anion and $\Pi$ states at the same geometry.
 
@@
 \begin{align}
-F_{33}^X &= f_{33}^X+\frac{2\lambda^2}{(\Delta_0^A-\Delta_0^X)}\\
-F_{33}^A &= f_{3a3a}^{A(a')}-\frac{2\lambda^2}{(\Delta_0^A-\Delta_0^X)}-\eta
+F_{22}^X &= f_{22}^X+\frac{2\lambda^2}{(\Delta_0^A-\Delta_0^X)}\\
+F_{22}^A &= f_{2a2a}^{A(a')}-\frac{2\lambda^2}{(\Delta_0^A-\Delta_0^X)}-\eta
 \label{eq:calc2}
@@
 \begin{equation}
-\eta = \frac{1}{2}\left[ f_{3a3a}^{A(a')}-f_{3b3b}^{A(a')}-\frac{2\lambda^2}{(\Delta_0^A-\Delta_0^X)}\right]
+\eta = \frac{1}{2}\left[ f_{2a2a}^{A(a')}-f_{2b2b}^{A(a')}-\frac{2\lambda^2}{(\Delta_0^A-\Delta_0^X)}\right]
 \label{eq:calc3}
@@
 % Create the reference section using BibTeX: 
-\bibliography{C2H.bib}
+\bibliography{2022C2H.bib}
 

### 2022-03-21 Aug2021-CH2-.tex
add ref

@@
 However, due to the strong vibronic coupling interactions, this can not be obtained via standard quantum chemistry methods.
-To account for these interactions, the photoelectron spectrum of the C$_2$H$^-$ anion was simulated using a quasidiabatic Hamiltonian of the type advocated by Koeppel, Domcke and Cederbaum (KDC, reference here).
-In this approach, the Hamiltonian is represented in a basis of quasidiabatic (slowly varying) electronic  states for which the kinetic energy operator can be assumed diagonal.
-For C$_2$H, the KDC Hamiltonian comprises three states - the two components of the $^2\Pi$ state and the ground $^2\Sigma$ state - and is then projected onto a vibrational basis, usually chosen as a direct product of harmonic oscillators.
+To account for these interactions, the photoelectron spectrum of the C$_2$H$^-$ anion was simulated using a quasidiabatic Hamiltonian of the type advocated by Koeppel, Domcke and Cederbaum (KDC).~\cite{kou84,dom81} In this approach, the Hamiltonian is represented in a basis of quasidiabatic (slowly varying) electronic  states for which the kinetic energy operator can be assumed diagonal.~\cite{pac93} For C$_2$H, the KDC Hamiltonian comprises three states - the two components of the $^2\Pi$ state and the ground $^2\Sigma^+$ state - and is then projected onto a vibrational basis, usually chosen as a direct product of harmonic oscillators.
 Diagonalization of the corresponding matrix yields the molecular states (which are given in terms of a Born-Huang expansion), and the squared projections of the corresponding eigenvectors onto the ground state of the anion yield the relative intensities.
-The latter is automatically true if the photodetachment cross sections for the $^2\Sigma$ and $^2\Pi$ states are assumed equal, but different cross sections of the two states can be incorporated by scaling the intensities of states according to their (vibronic) symmetry.
+The latter is automatically true if the photodetachment cross sections for the $^2\Sigma^+$ and $^2\Pi$ states are assumed equal, but different cross sections of the two states can be incorporated by scaling the intensities of states according to their (vibronic) symmetry.~\cite{sta11}
 
-Details of the construction and parametrization of KDC Hamiltonians can be found elsewhere in the literature (references), and the procedure followed will be discussed here only briefly.
-The present calculations use the so-called quadratic vibronic coupling (QVC) model.
-For the system at hand, the QVC model Hamiltonian  assumes the following form
+Details of the construction and parametrization of KDC Hamiltonians can be found elsewhere in the literature,~\cite{sta21,ich06,ich08,ich09,wei17} and the procedure followed will be discussed here only briefly.
+The present calculations use the so-called quadratic vibronic coupling (QVC) model.~\cite{ich06} For the system at hand, the QVC model Hamiltonian  assumes the following form
 
 \begin{align}
-H &= T_n1+V\\
+H &= T_n1+V,\\
 V &= \bordermatrix{ & X & A(a') & A(a'') \cr
@@
 
-where the summations run over the dimensionless normal modes ($q_i$) that serve as the coordinate system for the problem.
-For convenience, the latter are chosen to be those of the anion, which considerably facilitates calculation of the spectral intensities.
+where the summations run over the dimensionless normal modes ($q_i$) that serve as the coordinate system for the problem.~\cite{sta21,car00} For convenience, the latter are chosen to be those of the anion, which considerably facilitates calculation of the spectral intensities.
 In Eq.~(\ref{eq:calc1}), the diagonal terms of V (excluding those that carry the Renner-Teller coupling constant $\eta$) represent the quasidiabatic potential energy surfaces of the $\Sigma$, and the two components of the $\Pi$ state, chosen here as those in which the unpaired electron lies within or is perpendicular to an arbitrarily chosen plane, designated as A(a$'$) and A(a$''$), respectively.
-$\Delta_0^X$ is the separation of the anion and $\Sigma$ states at the origin of the coordinate system (the vertical electron detachment energy), and $\Delta_0^{A}$ is the gap between anion and $\Pi$ states at the same geometry.
+$\Delta_0^X$ is the separation of the anion and $^2\Sigma^+$ states at the origin of the coordinate system (the vertical electron detachment energy), and $\Delta_0^{A}$ is the gap between anion and $^2\Pi$ states at the same geometry.
 
@@
 For each component of the $\Pi$ state, either the 2a or 2b component of the bending vibration will maintain the A$'$ electronic symmetry that is needed to couple with the X state.
-Designating these as 2a for the A(a$'$) state and 2b for the A(a$''$) state (as is implicit in Eq.~\ref{eq:calc1}), the diabatic force constants for the bending mode in the X and A states can be written as
+Designating these as 2a for the A(a$'$) state and 2b for the A(a$''$) state (as is implicit in Eq.~\ref{eq:calc1}), the diabatic force constants for the bending mode in the $^2\Sigma^+$ and $^2\Pi$ states can be written as
 
@@
 
-When the potential in Eq.
-1 is diagonalized, the adiabatic states that are used for its parametrization are precisely recovered through second order in displacement.
-To parametrize this Hamiltonian, the equation-of-motion coupled-cluster method known as EOMIP-CCSDT has been used to optimise the geometry of the ground state anion, with an Atomic Natural Orbital (ANO) basis (ANO2).
-Adiabatic linear and quadratic force constants are calculated from the analytical derivatives of the \emph{ab-initio} potential energy surface with respect to the anion reduced normal coordinates, at the anion geometry Q$_0$.
+When the potential in Eq.~(\ref{eq:calc1}) is diagonalized, the adiabatic states that are used for its parametrization are precisely recovered through terms second order in displacement.
+The linear diabatic coupling constants between the electronic states of interest were calculated analytically at the EOM-CCSDT/AN02 level of theory, using the CFOUR computational package and the quasidiabatic ansatz of Ichino~\emph{et al.}~\cite{ich09} Briefly, the EOM procedure is used to operationally define quasidiabatic states (those that relax according to a well-behaved reference state wavefunction) and the coupling constants are then evaluated as the first derivative of the off-diagonal elements of the electronic Hamiltonian in the basis defined by this representation.
+The diabatic force and coupling constants calculated to parametrize the KDC potential in Eq.~(\ref{eq:calc1}) are presented in Table~1.
+
+%To parametrize this Hamiltonian, the equation-of-motion coupled-cluster method known as EOMIP-CCSDT has been used to optimise the geometry of the ground state anion, with an Atomic Natural Orbital (ANO) basis (ANO2), using the CFOUR computational package.
+
+%Adiabatic linear and quadratic force constants are calculated from the analytical derivatives of the \emph{ab-initio} potential energy surface with respect to the anion reduced normal coordinates, at the anion geometry Q$_0$.
 The interstate PJT coupling constant $\lambda$ is evaluated directly using the CFOUR package to employ the quasidiabatic ansatz described in refs.

### 2022-03-31 Aug2021-CH2-.tex
update references

@@
 \section{Introduction}
-Carbon monohydrides C$_{2n}$H, are a class of linear radicals that play an important role in combustion and interstellar chemistry.
-These carbon chains have been observed in many interstellar environments, including planetary atmospheres, comets, dark clouds, and during heavy star formation.
-Due to their relatively high abundance in a variety of astronomical conditions, they are believed to be promising candidates for Diffuse Interstellar Band (DIB) carriers.
-The corresponding anions C$_{2n}$H$^-$ are also believed to play an important role in interstellar chemistry.
-C$_6$H$^-$ was the first negative ion detected in space, after it was observed in two distinct interstellar molecular clouds IRC+10216 and TMC-1 in 2006.
-More recently, anions C$_4$H$^-$ and C$_8$H$^-$ have also been detected in a range of environments, include dark clouds, prestellar cores, and prostellar envelopes.
+Carbon monohydrides C$_{2n}$H, are a class of linear radicals that play an important role in combustion and interstellar chemistry~\cite{fre85,bou96,wil91,vui01}.
+These carbon chains have been observed in many interstellar environments, including planetary atmospheres~\cite{vui01,wil03,dob16}, comets~\cite{jac96}, dark clouds~\cite{ziu82,wil91,gup09}, and during heavy star formation~\cite{beu08,jia15}.
+Due to their relatively high abundance in a variety of astronomical conditions, they are believed to be promising candidates for Diffuse Interstellar Band (DIB) carriers~\cite{dou97,ful93,wat94,ful00,sch05,gup09}.
+The corresponding anions C$_{2n}$H$^-$ are also believed to play an important role in interstellar chemistry~\cite{mil17,gup09}.
+C$_6$H$^-$ was the first negative ion detected in space, after it was observed in two distinct interstellar molecular clouds IRC+10216 and TMC-1 in 2006~\cite{mcc06}.
+More recently, anions C$_4$H$^-$~\cite{cer07} and C$_8$H$^-$~\cite{bru07,rem07} have also been detected in a range of environments, include dark clouds~\cite{cor13}, prestellar cores,~\cite{sak10} and prostellar envelopes~\cite{sak07}.
 
@@
 Conversely, the formation of anions in space is believed to be driven by radiative electron attachment, charge transfer, and dissociate electron attachment.
-Current astrochemical modelling of interstellar clouds, such as IRC+1026, typically underestimate the observed abundances of CH$_4^-$.
+Current astrochemical modelling of interstellar clouds, such as IRC+1026, typically underestimate the observed abundances of CH$_4^-$~\cite{mil17,cor13,her08}.
 Therefore, it has been proposed that ion-neutral reactions
@@
 \end{equation}
-may be significant chain growth mechanisms that also needs to be included.
-Modelling of the extraterrestrial planetary atmosphere of Saturn's moon Titan, suggests that both C$_2$H and C$_2$H$^-$ play an important role in the atmospheric chemistry.
+may be significant chain growth mechanisms that also needs to be included~\cite{mil17,bas19}.
+Modelling of the extraterrestrial planetary atmosphere of Saturn's moon Titan, suggests that both C$_2$H and C$_2$H$^-$ play an important role in the atmospheric chemistry~\cite{dob16,vui09,des17,vri18}.
 Multiple reaction pathways were included for the ion C$_2$H$^-$ including reactions with C$_2$H$_2$ and HCN.
@@
 Microwave spectroscopy has successfully been used in this fashion to identify a large number of molecules in the interstellar medium (ISM).
-However for some species, particularly those with low abundances or no dipole moment, UV/vis spectroscopic methods are required for identification.
-This creates a challenge for theory, as electronic spectra calculations are more sensitive to the level of theory employed than pure rotational spectra.
+However for some species, particularly those with low abundances or no dipole moment, UV/vis spectroscopic methods are required for identification~\cite{mai97}.
+This creates a challenge for theory, as electronic spectra calculations are more sensitive to the level of theory employed than pure rotational spectra~\cite{for10}.
 This becomes even more challenging when vibronic coupling effects are introduced, as they can be exceedingly difficult to model.
@@
 The ethynyl radical C$_2$H may appear to be a simple linear triatomic molecule.
-However the electronic spectrum is complicated by the presence of the close-lying ground $^2\Sigma^+$ and first excited $^2\Pi$ surfaces, which are only separated by $\sim3,600~$cm$^{-1}$.
+However the electronic spectrum is complicated by the presence of the close-lying ground $^2\Sigma^+$ and first excited $^2\Pi$ surfaces, which are only separated by $\sim3,700~$cm$^{-1}$~\cite{cur85,tar03}.
 The interaction of these surfaces produces a complex vibronic spectrum around the $\tilde{A}^2\Pi$ state, where the $\tilde{X}-\tilde{A}$ origin is spread over multiple admixed vibronic levels.
-In C$_4$H the $^2\Sigma^+$ and $^2\Pi$ states are nearly degenerate, resulting in even stronger coupling, while in C$_6$H and C$_8$H the ordering of the states swaps, with a ground $^2\Pi$ state and a low lying excited $^2\Sigma^+$ state.
+In C$_4$H the $^2\Sigma^+$ and $^2\Pi$ states are nearly degenerate, resulting in even stronger coupling~\cite{zho07}, while in C$_6$H and C$_8$H the ordering of the states swaps, with a ground $^2\Pi$ state and a low lying excited $^2\Sigma^+$ state~\cite{lin99,tay98}.
 Consequently, understanding these vibronic coupling interactions between the $^2\Sigma$ and $^2\Pi$ surfaces will be essential in order to accurately model the role these radicals (and their corresponding anions) are likely to play in the interstellar chemistry mentioned above, and to guide the search for possible DIB carriers.
@@
 In this paper we study the vibronic spectrum of the ethynyl radical C$_2$H by employing High-Resolution Photoelectron Imaging (HR-PEI) in order to benchmark CFOUR \emph{ab-initio} vibronic-coupling calculations.
-C$_2$H is reported to be one of the most abundant molecules in the universe, and is the most thoroughly studied of the C$_{2n}$H species.
-Many different experimental techniques have been employed to try and resolve the complex vibronic spectrum, including electron spin resonance, laser magnetic resonance, microwave and milli-meter wave spectroscopy, infrared (matrix isolation and Fourier Transform) spectroscopy, and photoelectron spectroscopy.
-C$_2$H has also received extensive theoretical attention to try and understand the experimental results, however the large number of possible vibronic levels means this has proven to be a challenge.
+C$_2$H is reported to be one of the most abundant molecules in the universe, and is the most thoroughly studied of the C$_{2n}$H species~\cite{wil91,hei99,for10}.
+Many different experimental techniques have been employed to try and resolve the complex vibronic spectrum, including electron spin resonance~\cite{coc64,jin85}, laser magnetic resonance~\cite{bro88,pfe96,sch98}, microwave and milli-meter wave spectroscopy~\cite{sas81,got83,end89,mul00}, infrared (matrix isolation~\cite{she87,jac87,for95} and Fourier Transform emission~\cite{ver88}) spectroscopy, laser induced fluorescence spectroscopy~\cite{hsu93,hsu95,chi99} and photoelectron spectroscopy~\cite{erv91,tay98,zho07}.
+C$_2$H has also received extensive theoretical attention to try and understand the experimental results, however the large number of possible vibronic levels means this has proven to be a challenge~\cite{per90,per91,per91b,per91c,per92,car00,tar03.tar04,for10,sta21}.
 In this work we demonstrate how construction of a quasiadiabatic Hamiltonian allows for the strength of vibronic interactions between coupled surfaces near a conical intersection to be calculated, in order to simulate electronic and vibronic spectra.

### 2022-04-05 Aug2021-CH2-.tex
draft complete

@@
 	National University, Canberra ACT 2601, Australia}
-\title{Vibronic coupling in C$_2$H: implications for astrochemistry}
+\title{Velocity Map Imaging Spectroscopy of C$_2$H$^-$ and C$_2$D$^-$: a benchmark study of vibronic coupling interactions}
 \abbreviations{PES,PAD,EA,eKE,FWHM,VMI}
@@
 \end{abstract}
+High-resolution velocity map imaged photoelectron spectra of the ethynyl anions C$_2$H$^-$ and C$_2$D$^-$ are measured over a range of photodetachment wavelengths, to investigate the complex interactions between the close lying $\tilde{X}^2\Sigma^+$ and $\tilde{A}^2\Pi$ electronic states.
+Vibronic coupling calculations are performed by transforming to a quasidiabatic representation, parametrised by \emph{ab-initio} CFOUR calculations, to model the interplay between psuedo Jahn-Teller and Renner-Teller coupling.
+This approach is combined with electron anisotropy measurements to assign all of the observed vibronic structure, providing a framework that may be used to accurately simulate spectra of larger C$_{2n}$H monohydride carbon chains.
+
 \section{Introduction}
 Carbon monohydrides C$_{2n}$H, are a class of linear radicals that play an important role in combustion and interstellar chemistry~\cite{fre85,bou96,wil91,vui01}.
-These carbon chains have been observed in many interstellar environments, including planetary atmospheres~\cite{vui01,wil03,dob16}, comets~\cite{jac96}, dark clouds~\cite{ziu82,wil91,gup09}, and during heavy star formation~\cite{beu08,jia15}.
-Due to their relatively high abundance in a variety of astronomical conditions, they are believed to be promising candidates for Diffuse Interstellar Band (DIB) carriers~\cite{dou97,ful93,wat94,ful00,sch05,gup09}.
+These carbon chains have been observed in many interstellar environments, including planetary atmospheres~\cite{vui01,wil03,dob16}, comets~\cite{jac96}, dark clouds~\cite{ziu82,gup09}, and during heavy star formation~\cite{beu08,jia15}.
+Due to their relatively high abundance in a variety of astronomical conditions, they are believed to be promising candidates for Diffuse Interstellar Band (DIB) carriers~\cite{dou77,ful93,wat94,ful00,sch05,gup09}.
 The corresponding anions C$_{2n}$H$^-$ are also believed to play an important role in interstellar chemistry~\cite{mil17,gup09}.
@@
 \end{equation}
-may be significant chain growth mechanisms that also needs to be included~\cite{mil17,bas19}.
-Modelling of the extraterrestrial planetary atmosphere of Saturn's moon Titan, suggests that both C$_2$H and C$_2$H$^-$ play an important role in the atmospheric chemistry~\cite{dob16,vui09,des17,vri18}.
-Multiple reaction pathways were included for the ion C$_2$H$^-$ including reactions with C$_2$H$_2$ and HCN.
+may be significant chain growth mechanisms that also needs to be included in astrochemical models~\cite{mil17,bas19}.
+Studies of the extraterrestrial planetary atmosphere of Saturn's moon Titan, suggest that both C$_2$H and C$_2$H$^-$ play an important role in the atmospheric chemistry~\cite{dob16,vui09,des17,vri18}.
+Multiple reaction pathways involving the C$_2$H$^-$ have been proposed, including reactions with C$_2$H$_2$ and HCN.
 
-Understanding interstellar chemistry relies critically on theory, to provide a link between astronomical observations and terrestrial laboratory studies.
+Our knowledge of interstellar chemistry relies critically on theory, to provide a link between astronomical observations and terrestrial laboratory studies.
 Microwave spectroscopy has successfully been used in this fashion to identify a large number of molecules in the interstellar medium (ISM).
@@
 
-In this paper we study the vibronic spectrum of the ethynyl radical C$_2$H by employing High-Resolution Photoelectron Imaging (HR-PEI) in order to benchmark CFOUR \emph{ab-initio} vibronic-coupling calculations.
+In this paper we study the vibronic spectrum of the ethynyl radical C$_2$H by employing High-Resolution Photoelectron Imaging (HR-PEI) in order to benchmark CFOUR~\cite{dev20}  \emph{ab-initio} vibronic-coupling calculations.
 C$_2$H is reported to be one of the most abundant molecules in the universe, and is the most thoroughly studied of the C$_{2n}$H species~\cite{wil91,hei99,for10}.
 Many different experimental techniques have been employed to try and resolve the complex vibronic spectrum, including electron spin resonance~\cite{coc64,jin85}, laser magnetic resonance~\cite{bro88,pfe96,sch98}, microwave and milli-meter wave spectroscopy~\cite{sas81,got83,end89,mul00}, infrared (matrix isolation~\cite{she87,jac87,for95} and Fourier Transform emission~\cite{ver88}) spectroscopy, laser induced fluorescence spectroscopy~\cite{hsu93,hsu95,chi99} and photoelectron spectroscopy~\cite{erv91,tay98,zho07}.
-C$_2$H has also received extensive theoretical attention to try and understand the experimental results, however the large number of possible vibronic levels means this has proven to be a challenge~\cite{per90,per91,per91b,per91c,per92,car00,tar03.tar04,for10,sta21}.
-In this work we demonstrate how construction of a quasiadiabatic Hamiltonian allows for the strength of vibronic interactions between coupled surfaces near a conical intersection to be calculated, in order to simulate electronic and vibronic spectra.
+C$_2$H has also received extensive theoretical attention to try and understand the experimental results, however the large number of possible vibronic levels means this has proven to be a challenge~\cite{per90,per91,per91b,per91c,per92,car00,tar03,tar04,for10,sta21}.
+In this work we demonstrate how construction of a quasidiabatic Hamiltonian allows for the strength of vibronic interactions between coupled surfaces near a conical intersection to be calculated, in order to simulate electronic and vibronic spectra.
 By employing anion HR-PEI both the $^2\Sigma^+$ and $^2\Pi$ surfaces are mapped out on an equal footing from the anion $\tilde{X}^1\Sigma^+$ state, allowing for direct comparison to the \emph{ab-initio} modelling.
@@
 While the fast electrons appear similar in both images, a striking difference is observed in the slow electrons near the detector center.
-In Fig.~\ref{fig:1}(a) a series of weak rings are observed, however in Fig.~\ref{fig:1}(b) two dominant rings are seen.
+In Fig.~\ref{fig:1}(a) a series of weak rings are observed, however in Fig.~\ref{fig:1}(b) the image is dominated by two distinct rings.
 
-The VMIs in Fig.~\ref{fig:1} were inverted using the Abel inversion methods detailed in pyAbel, to extract the corresponding photoelectron spectra presented in Fig.~\ref{fig:1}(c).
-Below $27,000~$cm$^{-1}$ on the $\tilde{X} ^2\Sigma^+$ surface the C$_2$H$^-$ and C$_2$D$^-$ spectra are very similar.
+The VMIs in Fig.~\ref{fig:1} were inverted using the Abel inversion methods detailed in pyAbel~\cite{hic19}, to extract the corresponding photoelectron spectra presented in Fig.~\ref{fig:1}(c).
+Below $27,000~$cm$^{-1}$ on the $\tilde{X} ^2\Sigma^+$ surface the C$_2$H$^-$ and C$_2$D$^-$ spectra are a close match.
 Both are dominated by the origin transition, shifted by $\sim10~$cm$^{-1}$ in the deuterated spectrum, with progressions involving the v$_2$($\pi$) bending and v$_3$($\sigma$) CC stretch vibrational normal modes.
@@
 $\xi$ represents the electronic states used in the expansion ($\xi=\Sigma^+(1A'),~\Pi^+(2A'),~\Pi^-(1A'')$).
-A depiction of these three interacting surfaces is given in Fig.~\ref{fig:3}.
+A depiction of these three interacting surfaces is given in Fig.~\ref{fig:2}.
 
@@
 	\caption{Adiabatic potential energy surfaces of $\tilde{X}^2\Sigma^+$, $\tilde{A}^2\Pi^-$, and $\tilde{A}^2\Pi^+$ states, calculated using the method developed by Tarroni and Carter~\cite{tar03} (E$_{1A'}$, E$_{2A'}$, and E$_{1A''}$ in Eq.~\ref{eq:teller3}).}
-	\label{fig:3}
+	\label{fig:2}
 \end{figure}
 
-The adiabatic potential energy surfaces in Figure~\ref{fig:3} were calculated using the variational method of Tarroni and Carter.
+The adiabatic potential energy surfaces in Figure~\ref{fig:2} were calculated using the variational method of Tarroni and Carter~\cite{car00}.
 This has been used to calculate a multitude of admixed vibronic levels.
-In the literature, over 100 possible C$_2$H vibronic states have been calculated, up to 6,400~cm$^{-1}$ above the $\tilde{X} ^2\Sigma^+$ origin.
+In the literature, over 100 possible C$_2$H vibronic states have been calculated, up to 10,000~cm$^{-1}$ above the $\tilde{X} ^2\Sigma^+$ origin.
 However, assigning experimental spectra has remained a challenge, partly due to the large number of calculated levels providing multiple possible assignments for each experimentally observed transition.
@@
 where the summations run over the dimensionless normal modes ($q_i$) that serve as the coordinate system for the problem.~\cite{sta21,car00} For convenience, the latter are chosen to be those of the anion, which considerably facilitates calculation of the spectral intensities.
-In Eq.~(\ref{eq:calc1}), the diagonal terms of V (excluding those that carry the Renner-Teller coupling constant $\eta$) represent the quasidiabatic potential energy surfaces of the $\Sigma$, and the two components of the $\Pi$ state, chosen here as those in which the unpaired electron lies within or is perpendicular to an arbitrarily chosen plane, designated as A(a$'$) and A(a$''$), respectively.
+In Eq.~(\ref{eq:calc1}), the diagonal terms of V (excluding those that carry the Renner-Teller coupling constant $\eta$) represent the quasidiabatic potential energy surfaces of the $^2\Sigma^+$, and the two components of the $^2\Pi$ state, chosen here as those in which the unpaired electron lies within or is perpendicular to an arbitrarily chosen plane, designated as A(a$'$) and A(a$''$), respectively.
 $\Delta_0^X$ is the separation of the anion and $^2\Sigma^+$ states at the origin of the coordinate system (the vertical electron detachment energy), and $\Delta_0^{A}$ is the gap between anion and $^2\Pi$ states at the same geometry.
@@
 However, for the bending mode, the diabatic (F$_{22}$) and adiabatic (f$_{22}$) force constants differ, and the parametrization is somewhat more involved.
-For each component of the $\Pi$ state, either the 2a or 2b component of the bending vibration will maintain the A$'$ electronic symmetry that is needed to couple with the X state.
+For each component of the $^2\Pi$ state, either the 2a or 2b component of the bending vibration will maintain the A$'$ electronic symmetry that is needed to couple with the $^2\Sigma^+$ state.
 Designating these as 2a for the A(a$'$) state and 2b for the A(a$''$) state (as is implicit in Eq.~\ref{eq:calc1}), the diabatic force constants for the bending mode in the $^2\Sigma^+$ and $^2\Pi$ states can be written as
@@
 When the potential in Eq.~(\ref{eq:calc1}) is diagonalized, the adiabatic states that are used for its parametrization are precisely recovered through terms second order in displacement.
-The linear diabatic coupling constants between the electronic states of interest were calculated analytically at the EOM-CCSDT/AN02 level of theory, using the CFOUR computational package and the quasidiabatic ansatz of Ichino~\emph{et al.}~\cite{ich09} Briefly, the EOM procedure is used to operationally define quasidiabatic states (those that relax according to a well-behaved reference state wavefunction) and the coupling constants are then evaluated as the first derivative of the off-diagonal elements of the electronic Hamiltonian in the basis defined by this representation.
-The diabatic force and coupling constants calculated to parametrize the KDC potential in Eq.~(\ref{eq:calc1}) are presented in Table~1.
+The linear diabatic coupling constants between the electronic states of interest were calculated analytically at the EOM-CCSDT/AN02 level of theory, using the CFOUR computational package~\cite{dev20} and the quasidiabatic ansatz of Ichino~\emph{et al.}~\cite{ich09} Briefly, the EOM procedure is used to operationally define quasidiabatic states (those that relax according to a well-behaved reference state wavefunction) and the coupling constants are then evaluated as the first derivative of the off-diagonal elements of the electronic Hamiltonian in the basis defined by this representation.
+The diabatic force and coupling constants calculated to parametrize the KDC potential in Eq.~(\ref{eq:calc1}) are presented in Table~\ref{tab:1}.
 
@@
 
+\begin{table}
+	\caption{Parameters for the quasidiabatic Hamiltonian Eq.~(\ref{eq:calc1}) determined using CFOUR and the quasidiabatic ansatz.}
+	\label{tab:1}
+	\begin{tabular}{c |c c c c| c c c c }
+		 & C$_2$H & &  & & C$_2$D & & & \\
+		 parameter & Anion & $\tilde{X}^2\Sigma^+$ & $\tilde{A}^2\Pi (a')$ & $\tilde{A}^2\Pi (a'')$ & Anion & $\tilde{X}^2\Sigma^+$ & $\tilde{A}^2\Pi (a')$ & $\tilde{A}^2\Pi (a'')$ \\
+		 \hline\hline
+		 Energy & 0 & 22431.21 &  26543.67 & 26543.67 & 0&	22431.21 & 26543.67	& 26543.67\\
+		 f1 & 0	& -596.04 & 641.6 &	641.6 & 0& -596.04& 641.6 & 641.6\\
+		 f2 & 0 & -1515.21 & 1257.07 & 1257.07 & 0 & -1401.53 & 1115.17 & 1115.17\\
+		 f3 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+		 f4 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+         f11 & 3424.32 & 3487.03 & 3482.16 & 3482.16 & 2611.42 & 2636.57 & 2681.25 & 2681.25\\
+         f12 & 0.00 & -28.32 & 31.46 & 31.46 & 0.00 & -48.38 & 55.40 & 55.40\\
+         f22 & 1894.71 & 1830.83 & 2099.57 & 2042.21 & 1792.49 & 1747.62 & 1914.39 & 1914.39\\
+         f33 & 607.09 & 87.57 & 1883.48 & 658.96 & 481.89 & 120.09 & 1503.88 & 473.55\\
+         f44 & 607.09 & 87.57 & 658.96 & 1883.48 & 481.89 & 120.09 & 473.55 & 1503.88\\
+         $\lambda$ & -1185.26 & & 770.77991 & -429.49481 & -1014.58 & & 620.701579 & -382.57 \\
+         \end{tabular}
+\end{table}
+
 \subsection{Simulated Spectra}
-The above method was employed to simulate the photoelectron spectrum of C$_2$H$^-$, with the calculated transitions shown in Figure~\ref{fig:C2H-plot}(a) alongside the experimental data at 355~nm.
+The above method was employed to simulate the photoelectron spectrum of C$_2$H$^-$, with the calculated transitions shown in Figure~\ref{fig:3}(a) alongside the experimental data at 355~nm.
 %Calculated transitions with $\Sigma$ symmetry are in blue, and transitions with $\Pi$ symmetry are in orange.
@@
 The positions of the calculated levels for the $\tilde{A}^2\Pi$ state have been shifted by 1,220~cm$^{-1}$ to account for the EOMIP-CCSDT calculations overestimating the effective Term energy.
-The experimental data shows that the electronic coupling interactions induce a splitting of the $\tilde{A} ^2\Pi$ state origin over 5 vibronic levels, spaced by $\sim 95~$cm$^{-1}$ (a-e).
+The experimental data shows that the electronic coupling interactions induce a splitting of the $\tilde{A} ^2\Pi$ state origin over 5 vibronic levels, spaced by $\sim 95~$cm$^{-1}$ ($a-e$).
 This splitting is also observed in the calculated spectrum, which correctly predicts 5 prominent transitions in this region.
 The relative intensities between the calculated transitions are also in good agreement with the experimental data.
-Peak d is slightly underestimated, however the relative intensity difference between peaks d and e may be partly explained by the Wigner threshold law, which will reduce the intensity of peak e in the experimental spectrum as it is close to the detachment threshold.
+Peak $d$ is slightly underestimated, however the relative intensity difference between peaks $d$ and $e$ may be partly explained by the Wigner threshold law~\cite{wig48}, which will reduce the intensity of peak e in the experimental spectrum as it is close to the detachment threshold.
 The simulated spectrum also slightly underestimates the splitting between the vibronic levels, which may be linked to the overestimation of the gap between the $^2\Sigma$ and $^2\Pi$ surfaces.
@@
 	\includegraphics[width=0.6\textwidth]{figures/Fig5.pdf}
-	\caption{cat}
-	\label{fig:C2H-plot}
+	\caption{(a) Experimental photoelectron spectrum of C$_2$H$^-$ at 355~nm, compared to the simulated spectrum calculated using the quasidiabatic ansatz.
+Transitions with $\Sigma$ symmetry are shown in blue, transitions with $\Pi$ symmetry are shown in orange.
+(b) Experimental photoelectron spectrum of C$_2$D$^-$ at 355~nm, compared to the simulated spectrum.
+The labelling of peaks near the $\tilde{A}$ origin correspond to Table~S1.}
+	\label{fig:3}
 \end{figure}
 
-The photoelectron spectrum of C$_2$D$^-$ was also examined using the same approach, with the calculated transitions shown in Figure~\ref{fig:C2H-plot}(b) alongside the 355~nm experimental data.
+The photoelectron spectrum of C$_2$D$^-$ was also examined using the same approach, with the calculated transitions shown in Figure~\ref{fig:3}(b) alongside the 355~nm experimental data.
 Again, there is excellent agreement in the intensity and calculated positions of the transitions on the $\tilde{X} ^2\Sigma^+$ state surface, including the HT coupled levels.
 Near the $\tilde{A} ^2\Pi$ state origin, deuteration has a large impact on the experimental photoelectron spectrum.
-Instead of the 5 evenly split levels observed in C$_2$H, a single dominant peak (d) is now observed at 3,844~cm$^{-1}$ alongside a collection of weaker peaks (a-c) centred around 3,400~cm$^{-1}$.
-Based on previous spin-orbit splitting measurements, peak d is expected to have significant $\tilde{A} ^2\Pi$ character, with peaks a-c commonly assigned to vibronic levels with predominantly HT coupled $\tilde{X} ^2\Sigma^+$ character.
+Instead of the 5 evenly split levels observed in C$_2$H, a single dominant peak ($d$) is now observed at 3,844~cm$^{-1}$ alongside a collection of weaker peaks ($a-c$) centred around 3,400~cm$^{-1}$.
+Based on previous spin-orbit splitting measurements, peak d is expected to have significant $\tilde{A} ^2\Pi$ character, with peaks a-c commonly assigned to vibronic levels with predominantly HT coupled $\tilde{X} ^2\Sigma^+$ character~\cite{yan87,hsu95,chi99,wil11}.
 This suggests that deuteration effectively dampens the coupling interaction between the surfaces.
@@
 Like the experimental spectra, a large change is observed in the simulated spectrum upon deuteration.
-The calculated intensity pattern of the vibronic levels around the $\tilde{A} ^2\Pi$ origin is a good match to the experimental data, with a single intense transition observed near peak d, and 3 prominent transitions predicted around the experimental peaks a-c.
-The calculated splitting between the levels is also similar, however the relative intensity of peak d appears to be slightly underestimated.
+The calculated intensity pattern of the vibronic levels around the $\tilde{A} ^2\Pi$ origin is a good match to the experimental data, with a single intense transition observed near peak d, and 3 prominent transitions predicted around the experimental peaks $a-c$.
+The calculated splitting between the levels is also similar, however the relative intensity of peak $d$ appears to be slightly underestimated.
 %The results from Figure~\ref{fig:C2H-plot} confirm that the quasiadiabtic approach is able to accurately describe the vibronic interactions between the $\Sigma$ and $\Pi$ surfaces, including deuteration effects.
@@
 	\includegraphics[width=0.6\textwidth]{figures/266-plot.pdf}
-	\caption{cat}
-	\label{fig:266-plot}
+	\caption{Photoelectron spectrum of C$_2$H$^-$ at 266~nm, showing vibrationally excited $\tilde{A}$ state structure.
+The simulated spectra shown in green is calculated using the quasidiabatic ansatz, and convolved with Gaussians with a FWHM of 40~cm$^{-1}$ to match the lower VMI resolution at large electron kinetic energies.}
+	\label{fig:4}
 \end{figure}
-To investigate the effects of coupling on the higher excited vibronic levels on the$\tilde{A} ^2\Pi$ surface, the calculations were compared to the experimental photoelectron spectrum of C$_2$H$^-$ at 266~nm, as presented in Figure~\ref{fig:266-plot}.
-Gaussians were fitted to the transitions from Figure~\ref{fig:C2H-plot}(a) with a FWHM of 40~cm$^{-1}$ to match the resolution of the experimental data above threshold.
+To investigate the effects of coupling on the higher excited vibronic levels on the$\tilde{A} ^2\Pi$ surface, the calculations were also compared to the experimental photoelectron spectrum of C$_2$H$^-$ at 266~nm, presented in Figure~\ref{fig:4}.
+Gaussians were fit to the transitions from Figure~\ref{fig:3}(a) with a FWHM of 40~cm$^{-1}$ to match the lower resolution of the experimental data at high electron kinetic energies.
 Near 3,900~cm$^{-1}$ the electronic origin of the $\tilde{A} ^2\Pi$ state is split over 5 vibronic levels, as discussed above.
-A similar effect is also observed for the $3^1_0$ band, which becomes split over 3 vibronic levels labelled l, n, and o.
-The calculated spectrum correctly predicts the position and intensity of peaks n and o, but appears to strongly underestimate the intensity of peak l.
-Between the $0^0_0$ and $3^1_0$ bands a collection of weaker peaks are also observed (f,g,j,k).
-These are assigned to highly excited HT coupled $\tilde{X} ^2\Sigma^+$ transitions (j,k), and pure $\tilde{X} ^2\Sigma^+$ transitions (f,g).
-Consequently, peaks f and g will possess $\Sigma$ symmetry, and should have a different anisotropy to all of the other dominant transitions above 3,800~cm$^{-1}$.
+A similar effect is also observed for the $3^1_0$ band, which becomes split over 3 vibronic levels labelled $l$, $n$, and $o$.
+The calculated spectrum correctly predicts the position and intensity of peaks $n$ and $o$, but appears to strongly underestimate the intensity of peak $l$.
+Between the $0^0_0$ and $3^1_0$ bands a collection of weaker peaks are also observed ($f-k$).
+These are assigned to highly excited HT coupled $\tilde{X} ^2\Sigma^+$ transitions ($j,k$), admixed $\tilde{X}-\tilde{A}$ transitions ($h,i$) and pure $\tilde{X} ^2\Sigma^+$ transitions ($f$).
+Consequently, peak $f$ will possess $\Sigma$ symmetry, and should have a different anisotropy to all of the other dominant transitions above 3,800~cm$^{-1}$.
 The position and intensity of these highly-excited coupled transitions are well described by the simulated spectrum.
 
-The results from Figures~\ref{fig:C2H-plot} and~\ref{fig:266-plot} confirm that the quasiadiabtic approach is able to accurately describe the vibronic interactions between the $\Sigma$ and $\Pi$ surfaces, including deuteration effects.
+The results from Figures~\ref{fig:3} and~\ref{fig:4} confirm that the quasiadiabtic approach is able to accurately describe the vibronic interactions between the $^2\Sigma^+$ and $^2\Pi$ surfaces, including deuteration effects.
 This validates the proposed vibronic interactions, and demonstrates how this method can be employed to decode and assign even complex spectra.
@@
 
-%Overall, figures a-c show that the quasiadiabatic approach is a reliable method for simulating the spectra of molecules when strong vibornic coupling interactions are involved.
+%Overall, figures a-c show that the quasidiabatic approach is a reliable method for simulating the spectra of molecules when strong vibornic coupling interactions are involved.
 This method may be expanded to other C$_n$H radicals that possess similar complexities, in order to help guide the search for new molecules to be found in space.
@@
 Symmetry considerations may be employed to verify the spectral assignments from the calculations above.
-The quasiadiabatic Hamiltonian approach is able to determine the symmetry of each individual vibronic state, either $\Sigma$ or $\Pi$, which may be compared directly to the experimental electron anisotropy of each transition.
+The quasidiabatic Hamiltonian approach is able to determine the symmetry of each individual vibronic state, either $\Sigma$ or $\Pi$, which may be compared directly to the experimental electron anisotropy of each transition.
 The VMIs from this work (Figure~\ref{fig:1}) were obtained using a linearly polarized detachment laser.
@@
 Through conservation of angular momentum, $\beta$ may be described in terms of the detachment partial waves, which are linked to the symmetry of the parent detachment orbital.
-This is discussed in detail elsewhere [cite], and will be only briefly described for the case of C$_2$H$^-$ here.
+This is discussed in detail elsewhere~\cite{khu14,law19}, and will be only briefly described for the case of C$_2$H$^-$ here.
 
-Photodetachment to the ground state of C$_2$H$^-$ $(\tilde{X}\,^1\Sigma^+)$ involves ejecting an electron from an $s-$like $5\sigma_g$ orbital, whereas detachment to the excited $(\tilde{A}\,^2\Pi)$ state occurs from a $p-$like $1\pi_u$ orbital.
-Therefore, the electron anisotropies may be described using the mixed $sp$ model,
+Photodetachment to the ground state of C$_2$H $(\tilde{X}\,^2\Sigma^+)$ involves ejecting an electron from an $s-$like $5\sigma_g$ orbital, whereas detachment to the excited $\tilde{A}\,^2\Pi$ state occurs from a $p-$like $1\pi_u$ orbital.
+Therefore, the electron anisotropies may be described using the mixed $sp$ model\cite{khu14},
 \begin{equation}
@@
 From Eq.~(\ref{eq:beta-sanov}) it can be seen that detachment from a pure $s$ orbital will have a positive anisotropy ($\beta=+2$), whereas detachment from a pure $p$ orbital will have a negative anisotropy for electron kinetic energies $\epsilon < 2/A_1$.
-Therefore, measuring the anisotropy will determine the electronic character of each individual transition, which may be compared to the calculated symmetries in Figure~\ref{fig:C2H-plot}.
-The anisotropy parameters were measured for every detachment wavelength and prominent transition in the C$_2$H$^-$ photoelectron spectra from this work, and are presented in Figure~S1.
-Fitting Eq.~(\ref{eq:beta-sanov}) to the $^2\Pi$ state detachment with f=0.9 produces a Hanstorp coefficient of $A_1$=0.66(4)~eV$^{-1}$.
+Therefore, measuring the anisotropy will determine the electronic character of each individual transition, which may be compared to the calculated symmetries in Figure~\ref{fig:3}.
+The anisotropy parameters were measured for every detachment wavelength and prominent transition in the C$_2$H$^-$ photoelectron spectra from this work, and are presented in Figure~\ref{fig:5}.
+Fitting Eq.~(\ref{eq:beta-sanov}) to the anisotropy parameters from $^2\Pi$ state detachment, with f=0.9 produces a Hanstorp coefficient of $A_1$=0.66(4)~eV$^{-1}$.
 
@@
 	\includegraphics[width=0.5\textwidth]{figures/PAD.pdf}
-	\caption{cat}
-	\label{fig:S1}
+	\caption{Photoelectron anisotropy parameters, measured for each resolved C$_2$H$^-$ transition, across a range of detachment wavelengths.
+Allowed ground state transitions $\tilde{X}$ are shown in orange, Herzberg-Teller coupled transitions are shown in purple, and excited state transitions $\tilde{A}$ are shown in blue.
+Anisotropy curves for a mixed-$sp$ model (Eq.~\ref{eq:beta-sanov}) are shown for f=0.1 and f=0.9.}
+	\label{fig:5}
 \end{figure}
@@
 
-A plot of the anisotropy parameters for C$_2$H$^-$ detachment at 300~nm is presented in Figure~\ref{fig:beta}, alongside the experimental spectrum.
-By plotting $\beta\times I$ the sign (+/-) of each individual transition can be easily identified.
-All of the transitions above the $\tilde{A} ^2\Pi$ origin have a negative anisotropy, except for peak f.
-This confirms the assignment of this peak to the highly excited $\Sigma$ transition $\tilde{X}(0,6,1$).
-The nearby peak h is assigned to the admixed $\Pi$ transition $\tilde{X}(0,3,2)\tilde{A}(0,0,0)$.
-The other two peaks in this region j and k are assigned to highly excited HT coupled $\Pi$ transitions $\tilde{X}(0,7,1)$ and $\tilde{X}(0,11,0)$.
+A plot of the anisotropy parameters for C$_2$H$^-$ detachment at 300~nm is presented in Figure~\ref{fig:6}, alongside the experimental spectrum.
+By plotting $\beta\times I$ the sign (+/-) of each individual transition can be easily identified, even for partially resolved peaks.
+All of the transitions above the $\tilde{A} ^2\Pi$ origin have a negative anisotropy, except for peak $f$.
+This confirms the assignment of this peak to the highly excited $\Sigma$ transition $\tilde{X}(0,6,1$), where $\tilde{X}(v_1,v_2,v_3)$.
+The nearby peaks $h$ and $i$  are assigned to the admixed $\Pi$ transitions $\tilde{X}(0,3,2)\tilde{A}(0,0,0)$ and $\tilde{X}(0,7,1)\tilde{A}(010)$.
+The other two peaks in this region $j$ and $k$ are assigned to highly excited HT coupled $\Pi$ transitions $\tilde{X}(0,7,1)$ and $\tilde{X}(0,11,0)$.
 The assignments for all peaks in the C$_2$H$^-$ and C$_2$D$^-$ photoelectron spectra are presented in the Supplementary Materials Table~S1.
@@
 	\includegraphics[width=0.6\textwidth]{figures/plotBeta.pdf}
-	\caption{cat}
-	\label{fig:beta}
+	\caption{Photoelectron spectrum of C$_2$H$^-$ at 300~nm, compared to anisotropy measurements ($\beta\times I$).
+For each resolved transition the anisotropy parameter was determined from Eq.~(\ref{eq:beta1}) and multiplied by the corresponding photoelectron intensity.
+This allows for the sign (+/-) of each transitions to be readily determined.}
+	\label{fig:6}
 \end{figure}
@@
 \section{Conclusions} 
+High-resolution photoelectron images of C$_2$H$^-$ and C$_2$D$^-$ were recorded both at and above threshold, to investigate vibronic coupling effects in C$_{2n}$H carbon monohydride chains.
+The interplay of pseudo Jahn-Teller and Renner Teller coupling between the close lying $\tilde{X}^2\Sigma^+$ and $\tilde{A}^2\Pi$ states results in a complex vibronic spectrum near the $\tilde{A}$ state surface, with the electronic origin split over multiple admixed levels.We have shown that by transforming to a quasidiabatic representation, the effect of these coupling interactions may be simulated.
+A KDC Hamiltonian was constructed, and parametrised using the CFOUR \emph{ab-initio} computational package and the quasidiabatic ansatz.
+This resulted in simulated photoelectron spectra of C$_2$H$^-$ and C$_2$D$^-$ which closely resembled the experimental data, even near the complex $\tilde{A}$ state origin.
+Photoelectron anisotropy parameters were also calculated for each observed transition, across multiple wavelengths.
+Comparing the sign (+/-) of the anisotropy to the calculated vibronic symmetry allowed for even weak or partially resolved transitions to be assigned.
+
+The excellent agreement between the experimental and calculated spectra in this work
+demonstrates that electronic spectra complicated by vibronic coupling effects may still be accurately simulated using outputs from standard \emph{ab-initio} techniques, by transforming to a quasidiabatic representation.
+This approach may be extended to larger, less well known, C$_{2n}$H chains, which may help guide the search for these molecules in astronomical studies, and help identify potential DIB carriers.
 
@@
 Details of the HR-PEI spectrometer are given in Refs~\onlinecite{cav07} and~\onlinecite{dev17}.
-CH$_2$CN$^-$ ions are produced by passing a 1:1 C$_2$H$_4$:N$_2$O gas mixture through a pulse valve, which then undergoes supersonic expansion into a high-voltage discharge.
+C$_2$H$^-$ ions are produced by passing a 1:1 C$_2$H$_4$:O$_2$ gas mixture through a pulse valve, which then undergoes supersonic expansion into a high-voltage discharge.
 Negative ions are extracted, accelerated to 500~eV, and focussed into a novel gating, bunching, and re-referencing unit~\cite{ded01}.
@@
 An inverse Abel transformation of the VMI, based on the algorithm of Hansen and Law~\cite{han85,pya16}, returns a slice image of the 3D electron source distribution.
-Absolute energy calibration of the photoelectron spectra is achieved using published measurements of species, including O$^-$~\cite{cav07} and NO$_2^-$~\cite{law19}, that have been studied under similar conditions as used for the CH$_2$CN$^-$ measurements.
+Absolute energy calibration of the photoelectron spectra is achieved using published measurements of species, including O$^-$~\cite{cav07} and NO$_2^-$~\cite{law19}, that have been studied under similar conditions as used for the C$_2$H$^-$ measurements.
 

### 2022-04-05 Stanton/scripts/C2D-plot.py

@@ -69,7 +69,7 @@ plt.annotate(r'$2^1_03^1_0$',(1952,0.125),ha='center')
 plt.annotate(r'$2^3_03^1_0$',(2607,0.125),ha='center')
 plt.annotate(r'a',(3376,0.201),ha='center')
 plt.annotate(r'b',(3468,0.320),ha='center')
-plt.annotate(r'c',(3798,0.859),ha='center')
+plt.annotate(r'd',(3798,0.859),ha='center')
 #plt.annotate(r'd',(4028,0.228),ha='center')
 #plt.annotate(r'e',(4118,0.287),ha='center')
 

### 2022-04-05 Stanton/scripts/C2H-plot.py

@@ -38,8 +38,8 @@ for i in range(0,np.size(c)):
 plt.plot(x,y,'k',label=r'C$_2$H$^-$ PES')
 plt.xlim(-630,4225)
 
-plt.plot((0,0),(0,0),'C0',label=r'$\Sigma$ Symmetry')
-plt.plot((0,0),(0,0),'C1',label=r'$\Pi$ Symmetry')
+plt.plot((0,0),(0,0),'C1',label=r'$\Sigma$ Symmetry')
+plt.plot((0,0),(0,0),'C0',label=r'$\Pi$ Symmetry')
 plt.legend(loc=9,fontsize=10,frameon=False)
 
 ax.spines['top'].set_visible(False)

### 2022-04-05 Stanton/scripts/beta/PAD.py

@@ -18,7 +18,7 @@ with open('beta-raw.json') as json_file:
     data = json.load(json_file)
     
 peaks = [211,0,210,310,210310,230310,'G','H','I','J','K','B1','B2','B3']
-col = ['C1','C1','C1','C1','C1','C1','C0','C0','C0','C0','C0','C3','C3','C3']
+col = ['C0','C0','C0','C0','C0','C0','C1','C1','C1','C1','C1','C3','C3','C3']
 
 width = 3.487
 height = width/1.4
@@ -112,9 +112,9 @@ for k in data:
         ddba.append(k['Error'])
 
 
-plt.errorbar(xeKE,xb,yerr=xerr,fmt='o',markersize=6,color='C1',elinewidth=0.5,mfc='white',label=r'$\tilde{X}\,^2\Sigma^+$')
-plt.errorbar(xhteKE,xhtb,yerr=xhterr,fmt='d',markersize=6,color='C2',elinewidth=0.5,mfc='white',label=r'$\tilde{X}\,^2\Sigma^+ - $HT')
-plt.errorbar(aeKE,ab,yerr=aerr,fmt='s',markersize=6,color='C0',elinewidth=0.5,mfc='white',label=r'$\tilde{A}\,^2\Pi$')
+plt.errorbar(xeKE,xb,yerr=xerr,fmt='o',markersize=6,color='C0',elinewidth=0.5,mfc='white',label=r'$\tilde{X}\,^2\Sigma^+$')
+plt.errorbar(xhteKE,xhtb,yerr=xhterr,fmt='d',markersize=6,color='C4',elinewidth=0.5,mfc='white',label=r'$\tilde{X}\,^2\Sigma^+ - $HT')
+plt.errorbar(aeKE,ab,yerr=aerr,fmt='s',markersize=6,color='C1',elinewidth=0.5,mfc='white',label=r'$\tilde{A}\,^2\Pi$')
 
 grid = np.arange(0,1.7,0.01)
 
@@ -131,7 +131,7 @@ A2 = grid[-1]
 #plt.errorbar(dea,dba,yerr=ddba,fmt='s',markersize=8,color='C0',mfc='white',label=r'C$_2$D $^2\Pi$')
 
 #plt.annotate(r'$A$ = 1.5(4) eV$^{-1}$',(1.15,1.200),color='C1',fontsize=13)
[…]

### 2022-04-05 scripts/plotPES.py

@@ -20,9 +20,12 @@ plt.xticks([23000,24000,25000,26000,27000,28000])
 ax.set_xticklabels(['23000','24000','25000','26000','27000','28000'],fontsize=14)
 plt.minorticks_on()
 ax.tick_params(width=1.5)
+plt.xlabel('Binding Energy (cm$^{-1}$)',fontsize=14)
+plt.annotate(r'$\tilde{X}$ $^2\Sigma^+$',(24400,0.825),ha='center',fontsize=14)
+plt.annotate(r'$\tilde{A}$ $^2\Pi$',(27800,0.43),ha='center',fontsize=14)
 plt.setp(ax.spines.values(), linewidth=1.5)
 plt.legend(loc=1,fontsize=14,frameon=False)
-plt.subplots_adjust(top = 1, bottom = 0.1, right = 0.95, left = 0.05, 
+plt.subplots_adjust(top = 1, bottom = 0.12, right = 0.95, left = 0.05, 
             hspace = 0, wspace = 0)
 
 plt.savefig('Fig1c.pdf',bbbox_inches='tight')

### 2022-04-07 Aug2021-CH2-.tex
sanov update

@@
 \affiliation{School of Chemistry, University of New South Wales, Sydney NSW 2052, Australia}
+\author{Andrei M. Sanov}
+\affiliation{Department of Chemistry and Biochemistry, The University of Arizona, Tucson, Arizona 85721, United States}
 \author{John F. Stanton}
@@
 
-In this paper we study the vibronic spectrum of the ethynyl radical C$_2$H by employing High-Resolution Photoelectron Imaging (HR-PEI) in order to benchmark CFOUR~\cite{dev20}  \emph{ab-initio} vibronic-coupling calculations.
+In this work the vibronic spectrum of the ethynyl radical C$_2$H is examined by employing High-Resolution Photoelectron Imaging (HR-PEI) in order to benchmark CFOUR~\cite{dev20}  \emph{ab-initio} vibronic-coupling calculations.
 C$_2$H is reported to be one of the most abundant molecules in the universe, and is the most thoroughly studied of the C$_{2n}$H species~\cite{wil91,hei99,for10}.
@@
 In this work we demonstrate how construction of a quasidiabatic Hamiltonian allows for the strength of vibronic interactions between coupled surfaces near a conical intersection to be calculated, in order to simulate electronic and vibronic spectra.
-By employing anion HR-PEI both the $^2\Sigma^+$ and $^2\Pi$ surfaces are mapped out on an equal footing from the anion $\tilde{X}^1\Sigma^+$ state, allowing for direct comparison to the \emph{ab-initio} modelling.
+By employing anion HR-PEI both the $^2\Sigma^+$ and $^2\Pi$ surfaces are mapped out on an equal footing from the anion $\tilde{X}^1\Sigma^+$ state, allowing a direct comparison with \emph{ab-initio} modelling.
 
@@
 Ethynyl ions were produced in a pulsed-jet discharge of pure C$_2$H$_4$ gas, and subsequently mass isolated via time of flight.
-Electrons were detached using a tuneable Sunlite Optical Parametric Oscillator (OPO) pumped with the third harmonic of a Nd:YAG laser.
+Electrons were detached using a tuneable Continuum Sunlite Ex Optical Parametric Oscillator (OPO) pumped with the third harmonic of a Nd:YAG laser.
 High electron counts could also be obtained by using the third and fourth harmonics of the Nd:YAG laser directly.
-The detached electrons were then mapped onto a micro channel plate detector using a Velocity Map Imaging (VMI) lens.
+Detached electrons are mapped onto a micro channel plate detector using a Velocity Map Imaging (VMI) lens.
 An illustrative VMI of $\sim$4 million electrons collected from 355~nm (3.49~eV) photodetachment of C$_2$H$^-$ is shown in Fig.~\ref{fig:1}(a).
@@
 
-The VMIs in Fig.~\ref{fig:1} were inverted using the Abel inversion methods detailed in pyAbel~\cite{hic19}, to extract the corresponding photoelectron spectra presented in Fig.~\ref{fig:1}(c).
+The VMIs in Fig.~\ref{fig:1} were inverted using the Abel inversion methods detailed in PyAbel~\cite{hic19}, to extract the corresponding photoelectron spectra presented in Fig.~\ref{fig:1}(c).
 Below $27,000~$cm$^{-1}$ on the $\tilde{X} ^2\Sigma^+$ surface the C$_2$H$^-$ and C$_2$D$^-$ spectra are a close match.
@@
 
-Above $27,000~$cm$^{-1}$, near the $\tilde{A}^2\Pi$ state origin, large differences are observed between the C$_2$H$^-$ and C$_2$D$^-$ photoelectron spectra.
+Above $27,000~$cm$^{-1}$, near the $\tilde{A}^2\Pi$ state origin, significant differences are observed between the C$_2$H$^-$ and C$_2$D$^-$ photoelectron spectra.
 In the C$_2$H$^-$ spectrum 5 sharp peaks are observed, spaced by $\sim95~$cm$^{-1}$.
@@
 In C$_2$H this effect creates a Renner-Teller (RT) pair in the excited state, where the usually degenerate $\Pi$ surfaces separate to form two non-degenerate electronic states $\Pi^+ (2A')$ and $\Pi^-(1A'')$.
-This involves separating a single potential energy surface (V) into two distinct but connected surfaces (V$^+$) and (V$^-$).
+This involves separating a single potential energy surface (V) into two distinct but coupled surfaces (V$^+$) and (V$^-$).
 Due to the strong coupling along the linear axis between the electronic and vibration angular momenta of the $2A'$ and $1A''$ components of the $^2\Pi$ state, stationary states cannot be explicitly assigned to either of the $\Pi^+(2A')$ or $\Pi^-(1A'')$ electronic surfaces.
@@
 	\includegraphics[width=0.5\textwidth]{figures/Fig3}
-	\caption{Adiabatic potential energy surfaces of $\tilde{X}^2\Sigma^+$, $\tilde{A}^2\Pi^-$, and $\tilde{A}^2\Pi^+$ states, calculated using the method developed by Tarroni and Carter~\cite{tar03} (E$_{1A'}$, E$_{2A'}$, and E$_{1A''}$ in Eq.~\ref{eq:teller3}).}
+	\caption{Adiabatic potential energy surfaces of $\tilde{X}^2\Sigma^+$, $\tilde{A}^2\Pi^-$, and $\tilde{A}^2\Pi^+$ states, calculated using the parameters calculated by Tarroni and Carter~\cite{tar03} (E$_{1A'}$, E$_{2A'}$, and E$_{1A''}$ in Eq.~\ref{eq:teller3}).}
 	\label{fig:2}
@@
 
-The adiabatic potential energy surfaces in Figure~\ref{fig:2} were calculated using the variational method of Tarroni and Carter~\cite{car00}.
-This has been used to calculate a multitude of admixed vibronic levels.
+The adiabatic potential energy surfaces in Figure~\ref{fig:2} were evaluated from the variational parameters of Tarroni and Carter~\cite{car00}.
+Their technique calculates a multitude of admixed vibronic levels.
 In the literature, over 100 possible C$_2$H vibronic states have been calculated, up to 10,000~cm$^{-1}$ above the $\tilde{X} ^2\Sigma^+$ origin.
@@
 Based on previous spin-orbit splitting measurements, peak d is expected to have significant $\tilde{A} ^2\Pi$ character, with peaks a-c commonly assigned to vibronic levels with predominantly HT coupled $\tilde{X} ^2\Sigma^+$ character~\cite{yan87,hsu95,chi99,wil11}.
-This suggests that deuteration effectively dampens the coupling interaction between the surfaces.
+This suggests that deuteration effectively dampens the coupling interaction between the surfaces, as has been observed for HCCH~\cite{dev17}.
 
-Like the experimental spectra, a large change is observed in the simulated spectrum upon deuteration.
-The calculated intensity pattern of the vibronic levels around the $\tilde{A} ^2\Pi$ origin is a good match to the experimental data, with a single intense transition observed near peak d, and 3 prominent transitions predicted around the experimental peaks $a-c$.
+In agreement with the experimental spectra, a large change is observed in the simulated spectrum upon deuteration.
+The calculated intensity pattern of the vibronic levels around the $\tilde{A} ^2\Pi$ origin is also a good match to the experimental data, with a single intense transition observed near peak d, and 3 prominent transitions predicted around the experimental peaks $a-c$.
 The calculated splitting between the levels is also similar, however the relative intensity of peak $d$ appears to be slightly underestimated.
@@
 \end{figure}
-To investigate the effects of coupling on the higher excited vibronic levels on the$\tilde{A} ^2\Pi$ surface, the calculations were also compared to the experimental photoelectron spectrum of C$_2$H$^-$ at 266~nm, presented in Figure~\ref{fig:4}.
+To investigate the effects of coupling on the higher excited vibronic levels on the $\tilde{A} ^2\Pi$ surface, the calculations were also compared to the experimental photoelectron spectrum of C$_2$H$^-$ at 266~nm, presented in Figure~\ref{fig:4}.
 Gaussians were fit to the transitions from Figure~\ref{fig:3}(a) with a FWHM of 40~cm$^{-1}$ to match the lower resolution of the experimental data at high electron kinetic energies.
@@
 
-Photodetachment to the ground state of C$_2$H $(\tilde{X}\,^2\Sigma^+)$ involves ejecting an electron from an $s-$like $5\sigma_g$ orbital, whereas detachment to the excited $\tilde{A}\,^2\Pi$ state occurs from a $p-$like $1\pi_u$ orbital.
-Therefore, the electron anisotropies may be described using the mixed $sp$ model\cite{khu14},
+Photodetachment to the ground state of C$_2$H $(\tilde{X}\,^2\Sigma^+)$ involves ejecting an electron from an $s-$like $\sigma$ orbital (approximately $5\sigma_g$ in symmetry character), whereas detachment to the excited $\tilde{A}\,^2\Pi$ state occurs from a $p-$like $\pi$ orbital (approximately $1\pi_u$ in character).
+Therefore, the electron anisotropies may be described using the mixed $s-p$ model\cite{khu14},
 \begin{equation}
-\beta(\epsilon)_{sp} = \frac{2Z\epsilon+2\text{A}_1\epsilon^2-4\epsilon\cos\delta_{\ell\pm 1}}{\frac{1}{\text{A}_1}+2\text{A}_1\epsilon^2+Z\epsilon}
-\label{eq:beta-sanov}
+\beta_{sp}(\epsilon) = \frac{2(1-\gamma_p)B_1\epsilon + \gamma_p(2A_1^2\epsilon^2-4A_1\epsilon\cos\delta_{2,0})}
+{(1-\gamma_p)B_1\epsilon+\gamma_p(1+2A_1^2\epsilon^2)}
+\label{eq:beta-sp}
 \end{equation}
-where $\epsilon$ is the electron kinetic energy, $A_1$ is the $s\rightarrow p$ Hanstorp coefficient, $f$ is the percentage of $p$ orbital character,
+where $\epsilon$ is the electron kinetic energy and $\gamma_p$ is the fraction of $p$ character of the detachment orbital described as
 \begin{equation}
-Z = \frac{1-f}{f}\frac{8}{3}~~ \text{and} ~~ |\psi\rangle = \sqrt{1-f}|s\rangle + \sqrt{f}|p\rangle.
+|\psi\rangle = \sqrt{1-\gamma_p}|s\rangle + \sqrt{\gamma_p}|p\rangle.
 \end{equation}
+$A_1$ and $B_1$ in Eq.~(\ref{eq:beta-sp}) are the generalised Hanstorp~\cite{han89} coefficients describing the assumed Wigner-like~\cite{wig48} relative scalings of the radial transition dipole matrix elements for different allowed detachment channels.
+Specifically, $A_1\epsilon$ describes the energy-dependent ratio of the $p\rightarrow d$ and $p\rightarrow s$ transition amplitudes, while $B_1\epsilon$ corresponds to the $s\rightarrow p$ and $p\rightarrow s$ cross-section ratio~\cite{khu14}.
+It can be shown that under certain approximations $B_1/A_1 = 8/3$~\cite{san13}.
+Finally, $\delta_{2,0}$ in Eq.~(\ref{eq:beta-sp}) is the phase shift between the $s$ and $d$ partial waves, which in most cases of anion photodetachment is assumed to be small, corresponding to $\cos\delta_{2,0}\approx1$.
 
-From Eq.~(\ref{eq:beta-sanov}) it can be seen that detachment from a pure $s$ orbital will have a positive anisotropy ($\beta=+2$), whereas detachment from a pure $p$ orbital will have a negative anisotropy for electron kinetic energies $\epsilon < 2/A_1$.
+From Eq.~(\ref{eq:beta-sp}) it can be seen that detachment from a pure $s$ orbital ($\gamma_p=0$) will have a positive anisotropy ($\beta = +2$), whereas detachment from a pure $p$ orbital ($\gamma_p=1$) will have a negative anisotropy for electron kinetic energies $\epsilon < 2/A_1$.
+Therefore, measuring the anisotropy can help determine the electronic character of each individual transition, which may be compared to the calculated symmetries in Figure~\ref{fig:3}.
+The anisotropy parameters were measured at every detachment wavelength for prominent transitions in the C$_2$H$^-$ photoelectron spectra from this work, and are presented in Figure~\ref{fig:5}.
+Fitting Eq.~(\ref{eq:beta-sp}) to the anisotropy parameters from $^2\Pi$ state detachment, with $\gamma_p = 0.9$ produces a Hanstorp coefficient of $A_1=0.66(4)~$eV$^{-1}$.
+
+%\begin{equation}
+%\beta(\epsilon)_{sp} = \frac{2Z\epsilon+2\text{A}_1\epsilon^2-4\epsilon\cos\delta_{\ell\pm 1}}{\frac{1}{\text{A}_1}+2\text{A}_1\epsilon^2+Z\epsilon}
+%\label{eq:beta-sanov}
+%\end{equation}  
+%where $\epsilon$ is the electron kinetic energy, $A_1$ is the $s\rightarrow p$ Hanstorp coefficient, $f$ is the percentage of $p$ orbital character,
+%\begin{equation}
+%Z = \frac{1-f}{f}\frac{8}{3}~~ \text{and} ~~ |\psi\rangle = \sqrt{1-f}|s\rangle + \sqrt{f}|p\rangle.
+%\end{equation}
+
+%From Eq.~(\ref{eq:beta-sanov}) it can be seen that detachment from a pure $s$ orbital will have a positive anisotropy ($\beta=+2$), whereas detachment from a pure $p$ orbital will have a negative anisotropy for electron kinetic energies $\epsilon < 2/A_1$.
 Therefore, measuring the anisotropy will determine the electronic character of each individual transition, which may be compared to the calculated symmetries in Figure~\ref{fig:3}.
@@
 	\caption{Photoelectron anisotropy parameters, measured for each resolved C$_2$H$^-$ transition, across a range of detachment wavelengths.
-Allowed ground state transitions $\tilde{X}$ are shown in orange, Herzberg-Teller coupled transitions are shown in purple, and excited state transitions $\tilde{A}$ are shown in blue.
-Anisotropy curves for a mixed-$sp$ model (Eq.~\ref{eq:beta-sanov}) are shown for f=0.1 and f=0.9.}
+Allowed ground state transitions $\tilde{X}^2\Sigma^+$ are shown in orange, Herzberg-Teller coupled transitions are shown in purple, and excited state transitions $\tilde{A} ^2\Pi$ are shown in blue.
+Anisotropy curves for a mixed-$sp$ model (Eq.~\ref{eq:beta-sp}) are shown for $\gamma_p=0.1$ and $\gamma_p=0.9$.}
 	\label{fig:5}
@@
 Anions are mass separated over a 2m time-of-flight region, with the ion of interest isolated by an electrostatic gate.
-The ion packet is crossed with a tuneable detachment laser beam, generated from a Sunlite EX optical parametric oscillator pumped by the third harmonic of a Continuum Powerlite 9010 Nd:YAG laser.
+The ion packet is crossed with a tuneable detachment laser beam, generated from a Continuum Sunlite EX optical parametric oscillator pumped by the third harmonic of a Continuum Powerlite 9010 Nd:YAG laser.
 The laser produces between 10-50mJ per pulse at 10Hz, depending on whether the idler or signal beam is used.
@@
 
-A velocity-map imaging lens, a modified version of the original concept of Eppink and Parker, images the detached electrons to a 75mm diameter MCP/phosphor screen detector.
-Events are imaged by a 2014x2048 monochrome CCD camera (PCO 2000), with each frame transferred to a computer at a 10Hz repetition rate, and processed in real time to identify individual electron events.
+A velocity-map imaging lens (modified version of the original concept of Eppink and Parker) images the detached electrons to a 75mm diameter MCP/phosphor screen detector.
+Events are imaged by a 2048x2048 monochrome CCD camera (PCO 2000), with each frame transferred to a computer at a 10Hz repetition rate, and processed in real time to identify individual electron events.
 The electron positions are centroided to a sub-pixel accuracy, then written to a data file for subsequent analysis.
 The velocity-map image is centred and then circularized by an angular dependent-radial scaling determined by comparing adjacent radial slice intensity profiles~\cite{gas17}.
-An inverse Abel transformation of the VMI, based on the algorithm of Hansen and Law~\cite{han85,pya16}, returns a slice image of the 3D electron source distribution.
+An inverse Abel transformation of the VMI, based on the algorithm of Hansen and Law~\cite{han85,hic19}, returns a slice image of the 3D electron source distribution.
 Absolute energy calibration of the photoelectron spectra is achieved using published measurements of species, including O$^-$~\cite{cav07} and NO$_2^-$~\cite{law19}, that have been studied under similar conditions as used for the C$_2$H$^-$ measurements.

### 2022-04-12 Aug2021-CH2-.tex
fix figures

@@
 Many different experimental techniques have been employed to try and resolve the complex vibronic spectrum, including electron spin resonance~\cite{coc64,jin85}, laser magnetic resonance~\cite{bro88,pfe96,sch98}, microwave and milli-meter wave spectroscopy~\cite{sas81,got83,end89,mul00}, infrared (matrix isolation~\cite{she87,jac87,for95} and Fourier Transform emission~\cite{ver88}) spectroscopy, laser induced fluorescence spectroscopy~\cite{hsu93,hsu95,chi99} and photoelectron spectroscopy~\cite{erv91,tay98,zho07}.
-C$_2$H has also received extensive theoretical attention to try and understand the experimental results, however the large number of possible vibronic levels means this has proven to be a challenge~\cite{per90,per91,per91b,per91c,per92,car00,tar03,tar04,for10,sta21}.
+C$_2$H has also received extensive theoretical attention to try and understand the experimental results, however the large number of possible vibronic levels means this has proven to be a challenge~\cite{per90,per91,per91b,per91c,per92,car00,tar03,tar04,for10,sta21,gul21}.
 In this work we demonstrate how construction of a quasidiabatic Hamiltonian allows for the strength of vibronic interactions between coupled surfaces near a conical intersection to be calculated, in order to simulate electronic and vibronic spectra.
@@
 		 & C$_2$H & &  & & C$_2$D & & & \\
-		 parameter & Anion & $\tilde{X}^2\Sigma^+$ & $\tilde{A}^2\Pi (a')$ & $\tilde{A}^2\Pi (a'')$ & Anion & $\tilde{X}^2\Sigma^+$ & $\tilde{A}^2\Pi (a')$ & $\tilde{A}^2\Pi (a'')$ \\
+		  & Anion & $\tilde{X}^2\Sigma^+$ & $\tilde{A}^2\Pi (a')$ & $\tilde{A}^2\Pi (a'')$ & Anion & $\tilde{X}^2\Sigma^+$ & $\tilde{A}^2\Pi (a')$ & $\tilde{A}^2\Pi (a'')$ \\
 		 \hline\hline
-		 Energy & 0 & 22431.21 &  26543.67 & 26543.67 & 0&	22431.21 & 26543.67	& 26543.67\\
-		 f1 & 0	& -596.04 & 641.6 &	641.6 & 0& -596.04& 641.6 & 641.6\\
+		 $\Delta$E & 0 & 22431.21 &  26543.67 & 26543.67 & 0&	22431.21 & 26543.67	& 26543.67\\
+		 f1 & 0	& -211.28 & 286.9 &	286.9 & 0& -596.04& 641.6 & 641.6\\
 		 f2 & 0 & -1515.21 & 1257.07 & 1257.07 & 0 & -1401.53 & 1115.17 & 1115.17\\
@@
          f44 & 607.09 & 87.57 & 658.96 & 1883.48 & 481.89 & 120.09 & 473.55 & 1503.88\\
-         $\lambda$ & -1185.26 & & 770.77991 & -429.49481 & -1014.58 & & 620.701579 & -382.57 \\
+         $\lambda$ &  & & -1185.26 &  &  & & -1014.58 &  \\
          \end{tabular}
@@
 	\caption{Photoelectron spectrum of C$_2$H$^-$ at 266~nm, showing vibrationally excited $\tilde{A}$ state structure.
-The simulated spectra shown in green is calculated using the quasidiabatic ansatz, and convolved with Gaussians with a FWHM of 40~cm$^{-1}$ to match the lower VMI resolution at large electron kinetic energies.}
+The simulated spectra shown in green is calculated using the quasidiabatic ansatz, and convolved with Gaussians with a kinetic energy dependent FWHM of $\Delta\text{E}/\text{E} = 0.04\%$ ($\Gamma=55-30$~cm$^{-1}$) to match the lower VMI resolution at large electron kinetic energies.}
 	\label{fig:4}
@@
 
-Photodetachment to the ground state of C$_2$H $(\tilde{X}\,^2\Sigma^+)$ involves ejecting an electron from an $s-$like $\sigma$ orbital (approximately $5\sigma_g$ in symmetry character), whereas detachment to the excited $\tilde{A}\,^2\Pi$ state occurs from a $p-$like $\pi$ orbital (approximately $1\pi_u$ in character).
+Photodetachment to the ground state of C$_2$H $(\tilde{X}\,^2\Sigma^+)$ involves ejecting an electron from an $s-$like $\sigma$ orbital (approximately $5\sigma_g$ in symmetry character), whereas detachment to the excited $\tilde{A}\,^2\Pi$ state occurs from a $p-$like $\pi$ orbital (approximately $1\pi_u$ in character)~\cite{gul21}.
 Therefore, the electron anisotropies may be described using the mixed $s-p$ model\cite{khu14},

### 2022-04-12 Stanton/scripts/266-plot.py

@@ -7,6 +7,7 @@ def Gauss (E0,FWHM,E):
 FWHM = 80
 #FWHM = 80
 amp = 1
+e0 = 1e7/266-2.969*8065.74
 
 fn1 = '../C2H_all.dat'
 fn2 = '../C2H_ANU_PES/C2H-266nm.dat'
@@ -33,8 +34,12 @@ spec = np.zeros(np.size(Ev))
 
 for i in range(0,np.size(a)):
     aa = a[i]
+    KEw = e0 - aa
+    FWHM = KEw*0.004*2
     if a[i] > cut:
         aa = a[i]-ofs
+    if a[i] < 1700:
+        FWHMa = 120
     spec += b[i]*amp*Gauss(aa,FWHM,Ev)
     #plt.plot((aa,aa),(0,-b[i]),'C0')
 

### 2022-04-12 Stanton/scripts/beta/PAD.py

@@ -134,8 +134,8 @@ A2 = grid[-1]
 plt.annotate(r'$A_1$ = 0.66(4) eV$^{-1}$',(1.15,0.18),color='C1',fontsize=13)
 #plt.annotate(r'$A$ = 0.66(4) eV$^{-1}$',(1.45,-0.68),color='C0',fontsize=10)
 
-plt.annotate(r'f = 0.9',(A2+0.05,A1),va='center',fontsize=12)
-plt.annotate(r'f = 0.1',(A2+0.05,A2-0.1),va='center',fontsize=12)
+plt.annotate(r'$\gamma_p$ = 0.9',(A2+0.05,A1),va='center',fontsize=12)
+plt.annotate(r'$\gamma_p$ = 0.1',(A2+0.05,A2-0.1),va='center',fontsize=12)
 
 plt.xlabel('Electron Kinetic Energy (eV)',fontsize=14)
 plt.ylabel(r'Anisotropy ($\beta$)',fontsize=14)

### 2022-04-14 Aug2021-CH2-.tex
fix table
cse

@@
 	\includegraphics[width=0.8\textwidth]{figures/Fig1}
-	\caption{(a) A 3D-representation of the velocity-map image of $\sim$ 4 million photoelectrons detached from C$2$H$^-$ at 355~nm.
-The outer rings, distributed around the vertical laser polarisation axis, represents photodetachment to the ground $\tilde{X}\,^2\Sigma^+$ state.
-The inner rings reprsent detachment to the first excited state $\tilde{A}\,^2\Pi$.
-(b) Photoelectron spectra of C$_2$H$^-$ at a range of detachment wavelengths, illustrating the change in electron intensity profile and energy resolution.}
+	\caption{(a) Velocity map image of C$_2$H$^-$ photodetachment at 355~nm.
+(b) Velocity map image of C$_2$D$^-$ at 355~nm.
+(c) Comparison of 355~nm photoelectron spectra from C$_2$H$^-$ and C$_2$D$^-$.
+Structure below $\sim 27,000~$cm$^{-1}$ is assigned to the ground state $\tilde{X} ^2\Sigma^+$, and structure above  $\sim 27,000~$cm$^{-1}$ is assigned to the excited $\tilde{A} ^2\Pi$ state.}
 	\label{fig:1}
@@
 	\begin{tabular}{c |c c c c| c c c c }
-		 & C$_2$H & &  & & C$_2$D & & & \\
+		 & \multicolumn{4}{c}{C$_2$H}     & \multicolumn{4}{c}{C$_2$D}  \\ \hline
 		  & Anion & $\tilde{X}^2\Sigma^+$ & $\tilde{A}^2\Pi (a')$ & $\tilde{A}^2\Pi (a'')$ & Anion & $\tilde{X}^2\Sigma^+$ & $\tilde{A}^2\Pi (a')$ & $\tilde{A}^2\Pi (a'')$ \\

### 2022-04-14 Gibson/potentialsurf.py

@@ -1,0 +1,81 @@
+import numpy as np
+import cse
+from mpl_toolkits.mplot3d import axes3d
+import matplotlib.pyplot as plt
+import matplotlib as mpl
+
+def adiabatic(VSp, VPp, V12):
+     W = np.array([[VSp, V12], [V12, VPp]])
+
+     Ae, Av = np.linalg.eigh(W.T)
+
+     return Ae.T, Av.T
+
+def Va(q1, q2, q3, Ca):
+    s = 0
+    for ii, jj, kk, C in Ca:
+        s += C*(q1**ii)*(q2**jj)*(q3**kk)
+
+    return s
+
+def V12(q1, q2, q3, C12):
+    s = 0
+    for ii, jj, kk, C in C12:
+        s += C*q1**ii*q2**jj*q3**kk
+
+    return np.sin(q3)*(1-np.tanh(q1))*(1-np.tanh(q2))*s
+
+H2cm = 27.2*8065.541
+
+# Expansion coefficients Tarroni & Carter JCP 119, 12878 (2003)
+i, j, k, CSp, CPp, CPm, C12 = np.loadtxt('Cijk', unpack=True)
+# restructure for easy transport to generating function
+CSp = np.column_stack((i, j, k, CSp))
+CPm = np.column_stack((i, j, k, CPm))
+CPp = np.column_stack((i, j, k, CPp))
+C12 = np.column_stack((i, j, k, C12))
+
+# Rcc, RCH, bond angle - equilibrium values
+eq = {'Sp':(2.283737, 2.00787, np.pi), 'Pp':(2.432753, 2.021043, np.pi),
+      'Pm':(2.432753, 2.021043, np.pi), '12':(2.5, 2.0, np.pi)}
+
+# coordinates, relative to quilibrium values, in Angstroms
+cc = np.linspace(-0.2, 0.2, 101)
+ch = np.linspace(-0.2, 0.2, 101)
+bar = np.linspace(-1, 1, 101)
+
+CC, BAR = np.meshgrid(cc, bar, indexing='ij')
+
+CH = 0 # equilibrium
+
+
+Vsp = Va(CC, CH, BAR, CSp)*H2cm
+Vpm = Va(CC, CH, BAR, CPm)*H2cm
+Vpp = Va(CC, CH, BAR, CPp)*H2cm
+VV = V12(CC, CH, BAR, C12)*H2cm
+
+# diagonalize
[…]

### 2022-04-27 Aug2021-CH2-.tex
make edits

@@
 \end{equation}
-Conversely, the formation of anions in space is believed to be driven by radiative electron attachment, charge transfer, and dissociate electron attachment.
+Conversely, the formation of anions in space is believed to be driven by radiative electron attachment, charge transfer, and dissociative electron attachment.
 Current astrochemical modelling of interstellar clouds, such as IRC+1026, typically underestimate the observed abundances of CH$_4^-$~\cite{mil17,cor13,her08}.
@@
 may be significant chain growth mechanisms that also needs to be included in astrochemical models~\cite{mil17,bas19}.
-Studies of the extraterrestrial planetary atmosphere of Saturn's moon Titan, suggest that both C$_2$H and C$_2$H$^-$ play an important role in the atmospheric chemistry~\cite{dob16,vui09,des17,vri18}.
+Studies of the extraterrestrial planetary atmosphere of Saturn's moon Titan suggest that both C$_2$H and C$_2$H$^-$ play an important role in the atmospheric chemistry~\cite{dob16,vui09,des17,vri18}.
 Multiple reaction pathways involving the C$_2$H$^-$ have been proposed, including reactions with C$_2$H$_2$ and HCN.
@@
 However for some species, particularly those with low abundances or no dipole moment, UV/vis spectroscopic methods are required for identification~\cite{mai97}.
-This creates a challenge for theory, as electronic spectra calculations are more sensitive to the level of theory employed than pure rotational spectra~\cite{for10}.
+This creates a challenge for theory, as electronic spectra calculations are more difficult than those employed for pure rotational spectra~\cite{for10}.
 This becomes even more challenging when vibronic coupling effects are introduced, as they can be exceedingly difficult to model.
@@
 In C$_4$H the $^2\Sigma^+$ and $^2\Pi$ states are nearly degenerate, resulting in even stronger coupling~\cite{zho07}, while in C$_6$H and C$_8$H the ordering of the states swaps, with a ground $^2\Pi$ state and a low lying excited $^2\Sigma^+$ state~\cite{lin99,tay98}.
-Consequently, understanding these vibronic coupling interactions between the $^2\Sigma$ and $^2\Pi$ surfaces will be essential in order to accurately model the role these radicals (and their corresponding anions) are likely to play in the interstellar chemistry mentioned above, and to guide the search for possible DIB carriers.
+Consequently, understanding the vibronic coupling interactions between the $^2\Sigma$ and $^2\Pi$ surfaces is essential in order to accurately model the role these radicals (and their corresponding anions) are likely to play in the interstellar chemistry discussed above, and to guide the search for possible DIB carriers.
 
-In this work the vibronic spectrum of the ethynyl radical C$_2$H is examined by employing High-Resolution Photoelectron Imaging (HR-PEI) in order to benchmark CFOUR~\cite{dev20}  \emph{ab-initio} vibronic-coupling calculations.
+In this work the vibronic spectrum of the ethynyl radical C$_2$H is examined with High-Resolution Photoelectron Imaging (HR-PEI) together with CFOUR~\cite{dev20}  \emph{ab-initio} vibronic-coupling calculations.
 C$_2$H is reported to be one of the most abundant molecules in the universe, and is the most thoroughly studied of the C$_{2n}$H species~\cite{wil91,hei99,for10}.
-Many different experimental techniques have been employed to try and resolve the complex vibronic spectrum, including electron spin resonance~\cite{coc64,jin85}, laser magnetic resonance~\cite{bro88,pfe96,sch98}, microwave and milli-meter wave spectroscopy~\cite{sas81,got83,end89,mul00}, infrared (matrix isolation~\cite{she87,jac87,for95} and Fourier Transform emission~\cite{ver88}) spectroscopy, laser induced fluorescence spectroscopy~\cite{hsu93,hsu95,chi99} and photoelectron spectroscopy~\cite{erv91,tay98,zho07}.
-C$_2$H has also received extensive theoretical attention to try and understand the experimental results, however the large number of possible vibronic levels means this has proven to be a challenge~\cite{per90,per91,per91b,per91c,per92,car00,tar03,tar04,for10,sta21,gul21}.
-In this work we demonstrate how construction of a quasidiabatic Hamiltonian allows for the strength of vibronic interactions between coupled surfaces near a conical intersection to be calculated, in order to simulate electronic and vibronic spectra.
-By employing anion HR-PEI both the $^2\Sigma^+$ and $^2\Pi$ surfaces are mapped out on an equal footing from the anion $\tilde{X}^1\Sigma^+$ state, allowing a direct comparison with \emph{ab-initio} modelling.
+Many different experimental techniques have been employed to help understand the complexities of the vibronic spectrum, including electron spin resonance~\cite{coc64,jin85}, laser magnetic resonance~\cite{bro88,pfe96,sch98}, microwave and milli-meter wave spectroscopy~\cite{sas81,got83,end89,mul00}, infrared (matrix isolation~\cite{she87,jac87,for95} and Fourier Transform emission~\cite{ver88}) spectroscopy, laser induced fluorescence spectroscopy~\cite{hsu93,hsu95,chi99} and photoelectron spectroscopy of the negative ion~\cite{erv91,tay98,zho07}.
+C$_2$H has also received extensive theoretical attention to interpret the experimental results, however the large number of possible vibronic levels means this has proven to be a challenge~\cite{per90,per91,per91b,per91c,per92,car00,tar03,tar04,for10,sta21,gul21}.
+In this work we demonstrate how the construction of a quasidiabatic Hamiltonian allows the strength of vibronic interactions between coupled surfaces near a conical intersection to be estimated, sufficient to accurately simulate electronic and vibronic spectra.
+Anion HR-PEI spectroscopy maps both of the $^2\Sigma^+$ and $^2\Pi$ surfaces on an equal footing from the anion $\tilde{X}^1\Sigma^+$ state, allowing a direct comparison with \emph{ab-initio} modelling.
 
@@
 Electrons were detached using a tuneable Continuum Sunlite Ex Optical Parametric Oscillator (OPO) pumped with the third harmonic of a Nd:YAG laser.
-High electron counts could also be obtained by using the third and fourth harmonics of the Nd:YAG laser directly.
+Higher electron counts were also obtained with the direct use of the third and fourth harmonics of the Nd:YAG laser.
 Detached electrons are mapped onto a micro channel plate detector using a Velocity Map Imaging (VMI) lens.
-An illustrative VMI of $\sim$4 million electrons collected from 355~nm (3.49~eV) photodetachment of C$_2$H$^-$ is shown in Fig.~\ref{fig:1}(a).
-The electrons are distributed radially according to their speed, with slow electrons at the image center, and fast electrons located towards the outer edge.
-Due to the relatively large C$_2$H$^-$ electron affinity (EA) of 2.969~eV~\cite{erv91}, photodetachment at 355~nm occurs close to threshold.
-This yields slow electrons, allowing for a low repeller voltage ($-600$~V) on the VMI lens, and high velocity resolution.
+An illustrative velocity map image containing $\sim$4 million electrons, collected from 355~nm (3.49~eV) photodetachment of C$_2$H$^-$ is shown in Fig.~\ref{fig:1}(a).
+The electrons are distributed radially according to their speed, with slow electrons near the image center, and fast electrons located towards the outer edge.
+Due to the relatively large C$_2$H electron affinity (EA) of 2.969~eV~\cite{erv91}, photodetachment at 355~nm occurs close to threshold.
+This yields slow electrons, allowing the use of a low repeller voltage ($-600$~V) for the VMI lens, to spread the electron velocity distribution across the whole detector, giving high velocity resolution.
 
-Despite being close to threshold, two electronic states of neutral C$_2$H are observed.
-The faster electrons on the outer edge correspond to C$_2$H$(\tilde{X}\,^2\Sigma^+)+e^- \leftarrow $C$_2$H$^-(\tilde{X}\,^1\Sigma^+)+h\nu$ photodetachment, and are preferentially distributed around the poles of the image, indicative of a positive anisotropy parameter.
+Despite the photodetachment being close to threshold, two electronic states of neutral C$_2$H are observed.
+The faster electrons on the outer edge correspond to C$_2$H$(\tilde{X}\,^2\Sigma^+)+e^- \leftarrow $C$_2$H$^-(\tilde{X}\,^1\Sigma^+)+h\nu$ photodetachment, and these are preferentially distributed around the poles of the image, indicative of a positive anisotropy parameter.
 Conversely the angular distribution of the slower electrons near the center are skewed towards the equator, indicative of a negative anisotropy parameter.
@@
 (b) Velocity map image of C$_2$D$^-$ at 355~nm.
+Both images contain $\sim4$ million electrons.
 (c) Comparison of 355~nm photoelectron spectra from C$_2$H$^-$ and C$_2$D$^-$.
-Structure below $\sim 27,000~$cm$^{-1}$ is assigned to the ground state $\tilde{X} ^2\Sigma^+$, and structure above  $\sim 27,000~$cm$^{-1}$ is assigned to the excited $\tilde{A} ^2\Pi$ state.}
+Structure below $\sim 27,000~$cm$^{-1}$ is associated with the ground state $\tilde{X} ^2\Sigma^+$, while structure above  $\sim 27,000~$cm$^{-1}$ is due to the excited neutral $\tilde{A} ^2\Pi$ state.}
 	\label{fig:1}
@@
 To investigate the vibronic coupling interaction between these two nearby $\Sigma^+$ and $\Pi$ surfaces, deuterated ethynyl C$_2$D$^-$ was also studied.
-C$_2$D$^-$ ions were produced in a discharge of pure C$_2$D$_4$ gas and measured under the same experimental conditions as C$_2$H$^-$.
+The C$_2$D$^-$ ions were produced in a discharge of pure C$_2$D$_4$ gas and measured under the same experimental conditions as for C$_2$H$^-$.
 An illustrative VMI of photodetachment at 355~nm from C$_2$D$^-$ is shown in Fig.~\ref{fig:1}(b).
@@
 The VMIs in Fig.~\ref{fig:1} were inverted using the Abel inversion methods detailed in PyAbel~\cite{hic19}, to extract the corresponding photoelectron spectra presented in Fig.~\ref{fig:1}(c).
-Below $27,000~$cm$^{-1}$ on the $\tilde{X} ^2\Sigma^+$ surface the C$_2$H$^-$ and C$_2$D$^-$ spectra are a close match.
+Below $27,000~$cm$^{-1}$ on the $\tilde{X} ^2\Sigma^+$ surface the C$_2$H$^-$ and C$_2$D$^-$ spectra are similar in structure.
 Both are dominated by the origin transition, shifted by $\sim10~$cm$^{-1}$ in the deuterated spectrum, with progressions involving the v$_2$($\pi$) bending and v$_3$($\sigma$) CC stretch vibrational normal modes.
-This includes transitions involving an odd quanta of v$_2$ bending excitation ($2^{n+1}$) which should be totally forbidden within the harmonic oscillator approximation.
-However, the presence of these transitions in the spectra is likely an indicator of Herzberg-Teller (HT) vibronic coupling between the ground $^2\Sigma^+$ and nearby excited $^2\Pi$ electronic surfaces, as
+This structure includes transitions involving an odd quanta of v$_2$ bending excitation ($2^{n+1}$) which should be totally forbidden within the Franck-Condon approximation.
+However, the presence of these transitions in the spectra is an indicator of Herzberg-Teller (HT) vibronic coupling between the ground $^2\Sigma^+$ and nearby excited $^2\Pi$ electronic surfaces, as
 \begin{equation}
@@
 Above $27,000~$cm$^{-1}$, near the $\tilde{A}^2\Pi$ state origin, significant differences are observed between the C$_2$H$^-$ and C$_2$D$^-$ photoelectron spectra.
-In the C$_2$H$^-$ spectrum 5 sharp peaks are observed, spaced by $\sim95~$cm$^{-1}$.
+In C$_2$H$^-$, 5 sharp peaks are observed, spaced by $\sim95~$cm$^{-1}$.
 However in the deuterated spectrum, one dominant peak is observed at $27,792$~cm$^{-1}$, with 3 weaker peaks centred around $27,360~$cm$^{-1}$.
@@
 This may take a value of $\ell_i = v_i, v_i-2, v_i-4,\dots,1$ or $0$, where $v_i$ is the quanta of bending excitation.
-In the Born-Oppenheimer approximation different vibronic energy levels $\ell_i$ are degenerate, however in cases with strong rovibronic coupling, this degeneracy in $\ell_i$ is lost.
+In the Born-Oppenheimer approximation, different vibronic energy levels $\ell_i$ are degenerate, however in cases with strong rovibronic coupling, this degeneracy in $\ell_i$ is lost.
 
-In C$_2$H this effect creates a Renner-Teller (RT) pair in the excited state, where the usually degenerate $\Pi$ surfaces separate to form two non-degenerate electronic states $\Pi^+ (2A')$ and $\Pi^-(1A'')$.
+In C$_2$H the loss of degeneracy creates a Renner-Teller (RT) pair in the excited state, where the usually degenerate $\Pi$ surfaces separate to form two non-degenerate electronic states $\Pi^+ (2A')$ and $\Pi^-(1A'')$.
 This involves separating a single potential energy surface (V) into two distinct but coupled surfaces (V$^+$) and (V$^-$).
@@
 Instead, they exist as a combination of both states.
-
 Due to the close lying nature of the ground {$\tilde{X} ^2\Sigma^+$} and excited {$\tilde{A} ^2\Pi$} electronic states, which are only separated by $\sim3700~$cm$^{-1}$, a pseudo Jahn-Teller effect is also observed.
@@
 In the case of C$_2$H this is seen as coupling between the ground $\Sigma^+(1A')$ and excited $\Pi^+(2A')$ states, induced by the bending motion of $v_2$.
-The ground state only couples to one of the Renner-Teller pair $\Pi^+(2A')$, as the other state $\Pi^-(1A'')$ has incorrect symmetry.
+The ground state only couples to one member of the Renner-Teller pair $\Pi^+(2A')$, as the other state $\Pi^-(1A'')$ has incorrect symmetry.
 This results in the complex vibronic structure observed for the $\tilde{A}^2\Pi$ electronic state, with contributions from three coupled surfaces $\Sigma^+(1A'),$ $\Pi^+(2A'),$ and $\Pi^-(1A'')$.
@@
 $\xi$ represents the electronic states used in the expansion ($\xi=\Sigma^+(1A'),~\Pi^+(2A'),~\Pi^-(1A'')$).
-A depiction of these three interacting surfaces is given in Fig.~\ref{fig:2}.
+A depiction of these three interacting surfaces, generated from the parameters in Ref.~[\onlinecite{tar03}], is given in Fig.~\ref{fig:2}.
 
@@
 
-The adiabatic potential energy surfaces in Figure~\ref{fig:2} were evaluated from the variational parameters of Tarroni and Carter~\cite{car00}.
+The adiabatic potential energy surfaces in Figure~\ref{fig:2} were evaluated from the variational parameters of Tarroni and Carter~\cite{tar03}.
 Their technique calculates a multitude of admixed vibronic levels.
@@
 In order to guide spectral assignment of C$_2$H and astronomical searches for other C$_n$H radicals, transition intensities are also needed.
-However, due to the strong vibronic coupling interactions, this can not be obtained via standard quantum chemistry methods.
+However, due to the strong vibronic coupling interactions, this can not be obtained via simple Franck-Condon calculations based on quantum chemistry methods.
 To account for these interactions, the photoelectron spectrum of the C$_2$H$^-$ anion was simulated using a quasidiabatic Hamiltonian of the type advocated by Koeppel, Domcke and Cederbaum (KDC).~\cite{kou84,dom81} In this approach, the Hamiltonian is represented in a basis of quasidiabatic (slowly varying) electronic  states for which the kinetic energy operator can be assumed diagonal.~\cite{pac93} For C$_2$H, the KDC Hamiltonian comprises three states - the two components of the $^2\Pi$ state and the ground $^2\Sigma^+$ state - and is then projected onto a vibrational basis, usually chosen as a direct product of harmonic oscillators.
 Diagonalization of the corresponding matrix yields the molecular states (which are given in terms of a Born-Huang expansion), and the squared projections of the corresponding eigenvectors onto the ground state of the anion yield the relative intensities.
-The latter is automatically true if the photodetachment cross sections for the $^2\Sigma^+$ and $^2\Pi$ states are assumed equal, but different cross sections of the two states can be incorporated by scaling the intensities of states according to their (vibronic) symmetry.~\cite{sta11}
+The latter is true only if the photodetachment cross sections for the $^2\Sigma^+$ and $^2\Pi$ states are assumed equal, but different cross sections of the two states can be incorporated by scaling the intensities of states according to their (vibronic) symmetry.~\cite{sta11}
 
@@
 where the summations run over the dimensionless normal modes ($q_i$) that serve as the coordinate system for the problem.~\cite{sta21,car00} For convenience, the latter are chosen to be those of the anion, which considerably facilitates calculation of the spectral intensities.
-In Eq.~(\ref{eq:calc1}), the diagonal terms of V (excluding those that carry the Renner-Teller coupling constant $\eta$) represent the quasidiabatic potential energy surfaces of the $^2\Sigma^+$, and the two components of the $^2\Pi$ state, chosen here as those in which the unpaired electron lies within or is perpendicular to an arbitrarily chosen plane, designated as A(a$'$) and A(a$''$), respectively.
+In Eq.~(\ref{eq:calc1}), the diagonal terms of V (excluding those that carry the Renner-Teller coupling constant $\eta$) represent the quasidiabatic potential energy surfaces of the $^2\Sigma^+$ state, and the two components of the $^2\Pi$ state, chosen here as those in which the unpaired electron lies within or is perpendicular to an arbitrarily chosen plane, designated as A(a$'$) and A(a$''$), respectively.
 $\Delta_0^X$ is the separation of the anion and $^2\Sigma^+$ states at the origin of the coordinate system (the vertical electron detachment energy), and $\Delta_0^{A}$ is the gap between anion and $^2\Pi$ states at the same geometry.
@@
 When the potential in Eq.~(\ref{eq:calc1}) is diagonalized, the adiabatic states that are used for its parametrization are precisely recovered through terms second order in displacement.
-The linear diabatic coupling constants between the electronic states of interest were calculated analytically at the EOM-CCSDT/AN02 level of theory, using the CFOUR computational package~\cite{dev20} and the quasidiabatic ansatz of Ichino~\emph{et al.}~\cite{ich09} Briefly, the EOM procedure is used to operationally define quasidiabatic states (those that relax according to a well-behaved reference state wavefunction) and the coupling constants are then evaluated as the first derivative of the off-diagonal elements of the electronic Hamiltonian in the basis defined by this representation.
-The diabatic force and coupling constants calculated to parametrize the KDC potential in Eq.~(\ref{eq:calc1}) are presented in Table~\ref{tab:1}.
+The linear diabatic coupling constants between the electronic states of interest were calculated analytically at the EOM-CCSD/ANO2 level of theory, using the CFOUR computational package~\cite{dev20} and the quasidiabatic ansatz of Ichino~\emph{et al.}~\cite{ich09} Briefly, the EOM procedure is used to operationally define quasidiabatic states (those that relax according to a well-behaved reference state wavefunction, which is that of the anion level) and the coupling constants are then evaluated as the first derivative of the off-diagonal elements of the electronic Hamiltonian in the basis defined by this representation.
+The diabatic force and coupling constants calculated to parametrize the KDC potential in Eq.~(\ref{eq:calc1}) were calculated at the CCSDT/ANO2 level of theory, and are presented in Table~\ref{tab:1}.
 
@@
 \begin{table}
-	\caption{Parameters for the quasidiabatic Hamiltonian Eq.~(\ref{eq:calc1}) determined using CFOUR and the quasidiabatic ansatz.}
+	\caption{Parameters for the quasidiabatic Hamiltonian Eq.~(\ref{eq:calc1}) determined using CFOUR and the quasidiabatic ansatz. Units are in cm$^{-1}$.}
 	\label{tab:1}
@@
 On the $\tilde{X} ^2\Sigma^+$ surface, below 3,600~cm$^{-1}$, there is excellent agreement in both the transition positions and intensities between the simulated and experimental spectra.
-This includes the HT coupled (2$^{n+1}$) transitions with $\Pi$ symmetry, which would normally be missing from a simulation using standard \emph{ab-initio} approaches.
+This includes the HT coupled (2$^{n+1}$) transitions with $\Pi$ symmetry, which would normally be missing from a simulation using the standard \emph{ab-initio} approaches.
 
 The positions of the calculated levels for the $\tilde{A}^2\Pi$ state have been shifted by 1,220~cm$^{-1}$ to account for the EOMIP-CCSDT calculations overestimating the effective Term energy.
-The experimental data shows that the electronic coupling interactions induce a splitting of the $\tilde{A} ^2\Pi$ state origin over 5 vibronic levels, spaced by $\sim 95~$cm$^{-1}$ ($a-e$).
+The experimental data show that the electronic coupling interactions induce a splitting of the $\tilde{A} ^2\Pi$ state origin over 5 vibronic levels, spaced by $\sim 95~$cm$^{-1}$ ($a-e$).
 This splitting is also observed in the calculated spectrum, which correctly predicts 5 prominent transitions in this region.
 The relative intensities between the calculated transitions are also in good agreement with the experimental data.
-Peak $d$ is slightly underestimated, however the relative intensity difference between peaks $d$ and $e$ may be partly explained by the Wigner threshold law~\cite{wig48}, which will reduce the intensity of peak e in the experimental spectrum as it is close to the detachment threshold.
-The simulated spectrum also slightly underestimates the splitting between the vibronic levels, which may be linked to the overestimation of the gap between the $^2\Sigma$ and $^2\Pi$ surfaces.
+Peak $d$ is slightly underestimated; however the relative intensity difference between peaks $d$ and $e$ may be partly explained by the Wigner threshold law~\cite{wig48}, which will reduce the intensity of peak e in the experimental spectrum due to its proximity to the detachment threshold.
+The simulated spectrum also slightly underestimates the splitting between the vibronic levels, which may be linked to the overestimation of the calculated gap between the $^2\Sigma$ and $^2\Pi$ surfaces.
 
@@
 	\includegraphics[width=0.6\textwidth]{figures/Fig5.pdf}
-	\caption{(a) Experimental photoelectron spectrum of C$_2$H$^-$ at 355~nm, compared to the simulated spectrum calculated using the quasidiabatic ansatz.
-Transitions with $\Sigma$ symmetry are shown in blue, transitions with $\Pi$ symmetry are shown in orange.
+	\caption{(a) Experimental photoelectron spectrum of C$_2$H$^-$ at 355~nm, compared with the simulated spectrum, calculated using the quasidiabatic ansatz.
+Transitions with $\Sigma$ symmetry are shown in blue, and those with $\Pi$ symmetry are shown in orange.
 (b) Experimental photoelectron spectrum of C$_2$D$^-$ at 355~nm, compared to the simulated spectrum.
-The labelling of peaks near the $\tilde{A}$ origin correspond to Table~S1.}
+The labelling of peaks near the $\tilde{A}$ origin correspond to transitions identified in Table~S1.}
 	\label{fig:3}
@@
 Near the $\tilde{A} ^2\Pi$ state origin, deuteration has a large impact on the experimental photoelectron spectrum.
-Instead of the 5 evenly split levels observed in C$_2$H, a single dominant peak ($d$) is now observed at 3,844~cm$^{-1}$ alongside a collection of weaker peaks ($a-c$) centred around 3,400~cm$^{-1}$.
+Instead of the 5 evenly split levels observed in C$_2$H, a single dominant peak ($d$) is now observed near $\sim3,845$~cm$^{-1}$ alongside a collection of weaker peaks ($a-c$) centred around 3,400~cm$^{-1}$.
 Based on previous spin-orbit splitting measurements, peak d is expected to have significant $\tilde{A} ^2\Pi$ character, with peaks a-c commonly assigned to vibronic levels with predominantly HT coupled $\tilde{X} ^2\Sigma^+$ character~\cite{yan87,hsu95,chi99,wil11}.
-This suggests that deuteration effectively dampens the coupling interaction between the surfaces, as has been observed for HCCH~\cite{dev17}.
+This suggests that deuteration effectively dampens the coupling interaction between the surfaces, as has been observed in the vinylidene photoelectron spectrum~\cite{dev17}.
 
-In agreement with the experimental spectra, a large change is observed in the simulated spectrum upon deuteration.
+The simulated spectrum reproduces the large change observed for the deuterated species.
 The calculated intensity pattern of the vibronic levels around the $\tilde{A} ^2\Pi$ origin is also a good match to the experimental data, with a single intense transition observed near peak d, and 3 prominent transitions predicted around the experimental peaks $a-c$.
-The calculated splitting between the levels is also similar, however the relative intensity of peak $d$ appears to be slightly underestimated.
+The calculated splitting between the levels is also similar, however the relative intensity of peak $d$ appears to be underestimated.
 %The results from Figure~\ref{fig:C2H-plot} confirm that the quasiadiabtic approach is able to accurately describe the vibronic interactions between the $\Sigma$ and $\Pi$ surfaces, including deuteration effects.
@@
 	\caption{Photoelectron spectrum of C$_2$H$^-$ at 266~nm, showing vibrationally excited $\tilde{A}$ state structure.
-The simulated spectra shown in green is calculated using the quasidiabatic ansatz, and convolved with Gaussians with a kinetic energy dependent FWHM of $\Delta\text{E}/\text{E} = 0.04\%$ ($\Gamma=55-30$~cm$^{-1}$) to match the lower VMI resolution at large electron kinetic energies.}
+The simulated spectrum, shown in green, is calculated using the quasidiabatic ansatz, and convolved with Gaussians with a kinetic energy dependent FWHM of $\Delta\text{E}/\text{E} = 0.4\%$ ($\Gamma=55-30$~cm$^{-1}$) to match the VMI resolution characteristics.}
 	\label{fig:4}
 \end{figure}
-To investigate the effects of coupling on the higher excited vibronic levels on the $\tilde{A} ^2\Pi$ surface, the calculations were also compared to the experimental photoelectron spectrum of C$_2$H$^-$ at 266~nm, presented in Figure~\ref{fig:4}.
-Gaussians were fit to the transitions from Figure~\ref{fig:3}(a) with a FWHM of 40~cm$^{-1}$ to match the lower resolution of the experimental data at high electron kinetic energies.
-Near 3,900~cm$^{-1}$ the electronic origin of the $\tilde{A} ^2\Pi$ state is split over 5 vibronic levels, as discussed above.
+To investigate the effects of coupling on the higher excited vibronic levels on the~$\tilde{A} ^2\Pi$ surface, the calculations were also compared to the experimental photoelectron spectrum of C$_2$H$^-$ at 266~nm, presented in Figure~\ref{fig:4}.
+Gaussian functions were fitted to the transitions from Figure~\ref{fig:3}(a) with a kinetic energy dependent FWHM of $\Delta\text{E}/\text{E} = 0.4\%$ ($\Gamma=55-30$~cm$^{-1}$) to match the lower resolution of the experimental data at high electron kinetic energies.
+Near 3,900~cm$^{-1}$ excitation energy the electronic origin of the $\tilde{A} ^2\Pi$ state is split over 5 vibronic levels, as has been discussed above.
 A similar effect is also observed for the $3^1_0$ band, which becomes split over 3 vibronic levels labelled $l$, $n$, and $o$.
@@
 
-The results from Figures~\ref{fig:3} and~\ref{fig:4} confirm that the quasiadiabtic approach is able to accurately describe the vibronic interactions between the $^2\Sigma^+$ and $^2\Pi$ surfaces, including deuteration effects.
+The results from Figures~\ref{fig:3} and~\ref{fig:4} confirm that the quasidiabatic approach is able to accurately describe the vibronic interactions between the $^2\Sigma^+$ and $^2\Pi$ surfaces, including deuteration effects.
 This validates the proposed vibronic interactions, and demonstrates how this method can be employed to decode and assign even complex spectra.
+While the present calculations invoke a high level of \emph{ab-initio} theory (EOM-CCSDT), the level of parametrization of the vibronic Hamiltonian is relatively simple (QVC model).
+The approach could be systematically improved with a more elaborate expansion, such as that used in Ref.~[\onlinecite{sim12}] for the NO$_3$ radical.
 Applying this approach to similar less-studied systems will produce reliable predictions for the position and intensity of dominant transitions, which will help guide the search for these molecules in laboratory experiments and astronomical observations.
@@
 Symmetry considerations may be employed to verify the spectral assignments from the calculations above.
-The quasidiabatic Hamiltonian approach is able to determine the symmetry of each individual vibronic state, either $\Sigma$ or $\Pi$, which may be compared directly to the experimental electron anisotropy of each transition.
+The quasidiabatic Hamiltonian approach is able to determine the symmetry of each individual vibronic state, either $\Sigma$ or $\Pi$, which may be compared directly to the observed anisotropy of each transition.
 The VMIs from this work (Figure~\ref{fig:1}) were obtained using a linearly polarized detachment laser.
@@
 laser polarization, and $P_2$ is the second-order Legendre polynomial.
-The anisotropy parameter $\beta$ provides a quantitative measure of the anisotropy, and can range from -1 to +2 for purely perpendicular and parallel transition respectively.
-Through conservation of angular momentum, $\beta$ may be described in terms of the detachment partial waves, which are linked to the symmetry of the parent detachment orbital.
-This is discussed in detail elsewhere~\cite{khu14,law19}, and will be only briefly described for the case of C$_2$H$^-$ here.
+The anisotropy parameter $\beta$ provides a quantitative measure of the electron anisotropy, which ranges from -1 to +2, the limits representing purely perpendicular and parallel transitions respectively.
+Through conservation of angular momentum, $\beta$ may be described in terms of the detachment partial waves, which are linked to the symmetry of the state accessed by photodetachment.
+This is discussed in detail elsewhere\cite{khu14,law19}, and is only briefly described for the case of C$_2$H$^-$ here.
 
@@
 Therefore, measuring the anisotropy can help determine the electronic character of each individual transition, which may be compared to the calculated symmetries in Figure~\ref{fig:3}.
-The anisotropy parameters were measured at every detachment wavelength for prominent transitions in the C$_2$H$^-$ photoelectron spectra from this work, and are presented in Figure~\ref{fig:5}.
+The anisotropy parameters were measured at a range of detachment wavelengths for prominent transitions in the C$_2$H$^-$ photoelectron spectra from this work, and are presented in Figure~\ref{fig:5}.
 Fitting Eq.~(\ref{eq:beta-sp}) to the anisotropy parameters from $^2\Pi$ state detachment, with $\gamma_p = 0.9$ produces a Hanstorp coefficient of $A_1=0.66(4)~$eV$^{-1}$.
@@
 
-The sign (+/-) of $\beta$ can be used to assign each vibronic level to either the $^2\Sigma^+$ $\leftarrow^1\Sigma^+$ or $^2\Pi$ $\leftarrow^1\Sigma^+$ electronic transition respectively.
+The sign (+/-) of $\beta$ can be used to assign each accessed vibronic level to either the $^2\Sigma^+$ or $^2\Pi$ vibronic symmetry respectively.
 This is particularly useful around the $\tilde{A} ^2\Pi$ origin, where the two states overlap.
@@
 
-A plot of the anisotropy parameters for C$_2$H$^-$ detachment at 300~nm is presented in Figure~\ref{fig:6}, alongside the experimental spectrum.
-By plotting $\beta\times I$ the sign (+/-) of each individual transition can be easily identified, even for partially resolved peaks.
+A plot of the anisotropy parameters for C$_2$H$^-$ detachment at 300~nm, represented as $\beta\times I$, is presented in Figure~\ref{fig:6}, alongside the experimental spectrum.
+Plotting $\beta\times I$ allows the sign (+/-) of each individual transition to be easily identified, even for partially resolved peaks.
 All of the transitions above the $\tilde{A} ^2\Pi$ origin have a negative anisotropy, except for peak $f$.
@@
 
-This result demonstrates how experimental anisotropies and calculated transition intensities can be used to help assign and understand vibronically coupled spectra.
+This result demonstrates how experimental anisotropies and calculated transition intensities can be combined to help assign and understand vibronically coupled spectra.
 This is particularly useful in regions where there a large number of potential vibronic states, making definitive assignments based on energetics alone difficult.
@@
 \section{Conclusions} 
-High-resolution photoelectron images of C$_2$H$^-$ and C$_2$D$^-$ were recorded both at and above threshold, to investigate vibronic coupling effects in C$_{2n}$H carbon monohydride chains.
-The interplay of pseudo Jahn-Teller and Renner Teller coupling between the close lying $\tilde{X}^2\Sigma^+$ and $\tilde{A}^2\Pi$ states results in a complex vibronic spectrum near the $\tilde{A}$ state surface, with the electronic origin split over multiple admixed levels.We have shown that by transforming to a quasidiabatic representation, the effect of these coupling interactions may be simulated.
-A KDC Hamiltonian was constructed, and parametrised using the CFOUR \emph{ab-initio} computational package and the quasidiabatic ansatz.
-This resulted in simulated photoelectron spectra of C$_2$H$^-$ and C$_2$D$^-$ which closely resembled the experimental data, even near the complex $\tilde{A}$ state origin.
-Photoelectron anisotropy parameters were also calculated for each observed transition, across multiple wavelengths.
+High-resolution photoelectron images of C$_2$H$^-$ and C$_2$D$^-$ were recorded both near and above threshold, to investigate vibronic coupling effects in the simplest C$_{2n}$H carbon monohydride chain.
+The interplay of pseudo Jahn-Teller and Renner Teller coupling between the close lying $\tilde{X}^2\Sigma^+$ and $\tilde{A}^2\Pi$ states results in a complex vibronic spectrum near the $\tilde{A}$ state surface, with the electronic origin split over multiple admixed levels.We have shown that by transforming to a quasidiabatic representation, the effect of these coupling interactions may be accurately simulated.
+A KDC Hamiltonian was constructed, and parametrised using the high-level EOMIP-CCSDT quantum chemical approach and the quasidiabatic ansatz.
+The resulting simulated photoelectron spectra of C$_2$H$^-$ and C$_2$D$^-$ closely resemble the experimental data, even in the energy region of the complicated $\tilde{A}$ state origin.
+Photoelectron anisotropy parameters were also measured for each dominant transition, at a range of wavelengths.
 Comparing the sign (+/-) of the anisotropy to the calculated vibronic symmetry allowed for even weak or partially resolved transitions to be assigned.
@@
 The excellent agreement between the experimental and calculated spectra in this work
-demonstrates that electronic spectra complicated by vibronic coupling effects may still be accurately simulated using outputs from standard \emph{ab-initio} techniques, by transforming to a quasidiabatic representation.
-This approach may be extended to larger, less well known, C$_{2n}$H chains, which may help guide the search for these molecules in astronomical studies, and help identify potential DIB carriers.
+demonstrates that electronic spectra complicated by vibronic coupling effects may still be accurately simulated using a quasidiabatic treatment, as parametrised by appropriate quantum chemical methodology.
+This approach may be applied to larger, less well known, C$_{2n}$H chains, which may help guide the search for these molecules in astronomical studies, and help identify potential DIB carriers.
+It is especially encouraging that the fairly modest parametrisation used here works so well for C$_2$H, as this bodes well for its extension to larger systems.
 
@@
 Details of the HR-PEI spectrometer are given in Refs~\onlinecite{cav07} and~\onlinecite{dev17}.
-C$_2$H$^-$ ions are produced by passing a 1:1 C$_2$H$_4$:O$_2$ gas mixture through a pulse valve, which then undergoes supersonic expansion into a high-voltage discharge.
-Negative ions are extracted, accelerated to 500~eV, and focussed into a novel gating, bunching, and re-referencing unit~\cite{ded01}.
-Anions are mass separated over a 2m time-of-flight region, with the ion of interest isolated by an electrostatic gate.
+C$_2$H$^-$ and C$_2$D$^-$ anions are produced by passing pure C$_2$H$_4$ or C$_2$D$_4$ gas at $\sim2$ bar pressure through a pulsed solenoid valve, into the source vacuum chamber.
+The gas undergoes adiabatic supersonic expansion into a high-voltage discharge which generates negative ions.
+The anions are extracted, accelerated to 500~eV, and focussed into a novel gating, bunching, and re-referencing unit~\cite{ded01}, before being mass separated over a 2m time-of-flight region.
+The anion of interest (C$_2$H$^-$ or C$_2$D$^-$) is then isolated by an electrostatic gate.
 The ion packet is crossed with a tuneable detachment laser beam, generated from a Continuum Sunlite EX optical parametric oscillator pumped by the third harmonic of a Continuum Powerlite 9010 Nd:YAG laser.
-The laser produces between 10-50mJ per pulse at 10Hz, depending on whether the idler or signal beam is used.
+The laser output is then doubled by passing through a BBO crystal, to produce UV laser pulse energies between 2-10mJ at 10Hz.
 The wavelength of the laser light is measured using a HighFinesse WS7 UV wavemeter.
 
-A velocity-map imaging lens (modified version of the original concept of Eppink and Parker) images the detached electrons to a 75mm diameter MCP/phosphor screen detector.
+A modified velocity-map imaging lens images the detached photoelectrons to a 75mm diameter MCP/phosphor screen detector.
 Events are imaged by a 2048x2048 monochrome CCD camera (PCO 2000), with each frame transferred to a computer at a 10Hz repetition rate, and processed in real time to identify individual electron events.
@@
 Absolute energy calibration of the photoelectron spectra is achieved using published measurements of species, including O$^-$~\cite{cav07} and NO$_2^-$~\cite{law19}, that have been studied under similar conditions as used for the C$_2$H$^-$ measurements.
-
-In standard operation, the energy distribution of the detached electrons is obtained by recording the velocity-mapped positions from photodetachment at a fixed wavelength.
-However the HR-PEI spectrometer may also be reconfigured into an electron counting mode, where the number of events per laser shot is recorded, while the detachment laser wavelength is varied.
 

### 2022-04-27 Gibson/potential-adiab.py

@@ -1,0 +1,93 @@
+import numpy as np
+import cse
+from mpl_toolkits.mplot3d import axes3d
+import matplotlib.pyplot as plt
+import matplotlib as mpl
+
+def adiabatic(VSp, VPp, V12):
+     W = np.array([[VSp, V12], [V12, VPp]])
+
+     Ae, Av = np.linalg.eigh(W.T)
+
+     return Ae.T, Av.T
+
+def Va(q1, q2, q3, Ca):
+    s = 0
+    for ii, jj, kk, C in Ca:
+        s += C*(q1**ii)*(q2**jj)*(q3**kk)
+
+    return s
+
+def V12(q1, q2, q3, C12):
+    s = 0
+    for ii, jj, kk, C in C12:
+        s += C*q1**ii*q2**jj*q3**kk
+
+    return np.sin(q3)*(1-np.tanh(q1))*(1-np.tanh(q2))*s
+
+H2cm = 27.2*8065.541
+
+# Expansion coefficients Tarroni & Carter JCP 119, 12878 (2003)
+i, j, k, CSp, CPp, CPm, C12 = np.loadtxt('Cijk', unpack=True)
+# restructure for easy transport to generating function
+CSp = np.column_stack((i, j, k, CSp))
+CPm = np.column_stack((i, j, k, CPm))
+CPp = np.column_stack((i, j, k, CPp))
+C12 = np.column_stack((i, j, k, C12))
+
+# Rcc, RCH, bond angle - equilibrium values
+eq = {'Sp':(2.283737, 2.00787, np.pi), 'Pp':(2.432753, 2.021043, np.pi),
+      'Pm':(2.432753, 2.021043, np.pi), '12':(2.5, 2.0, np.pi)}
+
+# coordinates, relative to quilibrium values, in Angstroms
+cc = np.linspace(-0.2, 0.2, 101)
+ch = np.linspace(-0.2, 0.2, 101)
+bar = np.linspace(-1, 1, 101)
+
+CC, BAR = np.meshgrid(cc, bar, indexing='ij')
+
+CH = 0 # equilibrium
+
+
+Vsp = Va(CC, CH, BAR, CSp)*H2cm
+Vpm = Va(CC, CH, BAR, CPm)*H2cm
+Vpp = Va(CC, CH, BAR, CPp)*H2cm
+VV = V12(CC, CH, BAR, C12)*H2cm
[…]

### 2022-04-27 Gibson/potential-couple.py

@@ -1,0 +1,84 @@
+import numpy as np
+import cse
+from mpl_toolkits.mplot3d import axes3d
+import matplotlib.pyplot as plt
+import matplotlib as mpl
+
+def adiabatic(VSp, VPp, V12):
+     W = np.array([[VSp, V12], [V12, VPp]])
+
+     Ae, Av = np.linalg.eigh(W.T)
+
+     return Ae.T, Av.T
+
+def Va(q1, q2, q3, Ca):
+    s = 0
+    for ii, jj, kk, C in Ca:
+        s += C*(q1**ii)*(q2**jj)*(q3**kk)
+
+    return s
+
+def V12(q1, q2, q3, C12):
+    s = 0
+    for ii, jj, kk, C in C12:
+        s += C*q1**ii*q2**jj*q3**kk
+
+    return np.sin(q3)*(1-np.tanh(q1))*(1-np.tanh(q2))*s
+
+H2cm = 27.2*8065.541
+
+# Expansion coefficients Tarroni & Carter JCP 119, 12878 (2003)
+i, j, k, CSp, CPp, CPm, C12 = np.loadtxt('Cijk', unpack=True)
+# restructure for easy transport to generating function
+CSp = np.column_stack((i, j, k, CSp))
+CPm = np.column_stack((i, j, k, CPm))
+CPp = np.column_stack((i, j, k, CPp))
+C12 = np.column_stack((i, j, k, C12))
+
+# Rcc, RCH, bond angle - equilibrium values
+eq = {'Sp':(2.283737, 2.00787, np.pi), 'Pp':(2.432753, 2.021043, np.pi),
+      'Pm':(2.432753, 2.021043, np.pi), '12':(2.5, 2.0, np.pi)}
+
+# coordinates, relative to quilibrium values, in Angstroms
+cc = np.linspace(-0.2, 0.2, 101)
+ch = np.linspace(-0.2, 0.2, 101)
+bar = np.linspace(-1, 1, 101)
+
+CC, BAR = np.meshgrid(cc, bar, indexing='ij')
+
+CH = 0 # equilibrium
+
+
+Vsp = Va(CC, CH, BAR, CSp)*H2cm
+Vpm = Va(CC, CH, BAR, CPm)*H2cm
+Vpp = Va(CC, CH, BAR, CPp)*H2cm
+VV = V12(CC, CH, BAR, C12)*H2cm
+
+# diagonalize
[…]

### 2022-04-27 Gibson/potentialsurf-diab.py

@@ -1,0 +1,81 @@
+import numpy as np
+import cse
+from mpl_toolkits.mplot3d import axes3d
+import matplotlib.pyplot as plt
+import matplotlib as mpl
+
+def adiabatic(VSp, VPp, V12):
+     W = np.array([[VSp, V12], [V12, VPp]])
+
+     Ae, Av = np.linalg.eigh(W.T)
+
+     return Ae.T, Av.T
+
+def Va(q1, q2, q3, Ca):
+    s = 0
+    for ii, jj, kk, C in Ca:
+        s += C*(q1**ii)*(q2**jj)*(q3**kk)
+
+    return s
+
+def V12(q1, q2, q3, C12):
+    s = 0
+    for ii, jj, kk, C in C12:
+        s += C*q1**ii*q2**jj*q3**kk
+
+    return np.sin(q3)*(1-np.tanh(q1))*(1-np.tanh(q2))*s
+
+H2cm = 27.2*8065.541
+
+# Expansion coefficients Tarroni & Carter JCP 119, 12878 (2003)
+i, j, k, CSp, CPp, CPm, C12 = np.loadtxt('Cijk', unpack=True)
+# restructure for easy transport to generating function
+CSp = np.column_stack((i, j, k, CSp))
+CPm = np.column_stack((i, j, k, CPm))
+CPp = np.column_stack((i, j, k, CPp))
+C12 = np.column_stack((i, j, k, C12))
+
+# Rcc, RCH, bond angle - equilibrium values
+eq = {'Sp':(2.283737, 2.00787, np.pi), 'Pp':(2.432753, 2.021043, np.pi),
+      'Pm':(2.432753, 2.021043, np.pi), '12':(2.5, 2.0, np.pi)}
+
+# coordinates, relative to quilibrium values, in Angstroms
+cc = np.linspace(-0.2, 0.2, 101)
+ch = np.linspace(-0.2, 0.2, 101)
+bar = np.linspace(-1, 1, 101)
+
+CC, BAR = np.meshgrid(cc, bar, indexing='ij')
+
+CH = 0 # equilibrium
+
+
+Vsp = Va(CC, CH, BAR, CSp)*H2cm
+Vpm = Va(CC, CH, BAR, CPm)*H2cm
+Vpp = Va(CC, CH, BAR, CPp)*H2cm
+VV = V12(CC, CH, BAR, C12)*H2cm
+
+# diagonalize
[…]

### 2022-04-27 Gibson/potentialsurfx.py

@@ -1,0 +1,86 @@
+import numpy as np
+import cse
+from mpl_toolkits.mplot3d import axes3d
+import matplotlib.pyplot as plt
+import matplotlib as mpl
+
+def adiabatic(VSp, VPp, V12):
+     W = np.array([[VSp, V12], [V12, VPp]])
+
+     Ae, Av = np.linalg.eigh(W.T)
+
+     return Ae.T, Av.T
+
+def Va(q1, q2, q3, Ca):
+    s = 0
+    for ii, jj, kk, C in Ca:
+        s += C*(q1**ii)*(q2**jj)*(q3**kk)
+
+    return s
+
+def V12(q1, q2, q3, C12):
+    s = 0
+    for ii, jj, kk, C in C12:
+        s += C*q1**ii*q2**jj*q3**kk
+
+    return np.sin(q3)*(1-np.tanh(q1))*(1-np.tanh(q2))*s
+
+H2cm = 27.2*8065.541
+
+# Expansion coefficients Tarroni & Carter JCP 119, 12878 (2003)
+i, j, k, CSp, CPp, CPm, C12 = np.loadtxt('Cijk', unpack=True)
+# restructure for easy transport to generating function
+CSp = np.column_stack((i, j, k, CSp))
+CPm = np.column_stack((i, j, k, CPm))
+CPp = np.column_stack((i, j, k, CPp))
+C12 = np.column_stack((i, j, k, C12))
+
+# Rcc, RCH, bond angle - equilibrium values
+eq = {'Sp':(2.283737, 2.00787, np.pi), 'Pp':(2.432753, 2.021043, np.pi),
+      'Pm':(2.432753, 2.021043, np.pi), '12':(2.5, 2.0, np.pi)}
+
+# coordinates, relative to quilibrium values, in Angstroms
+cc = np.linspace(-0.2, 0.2, 101)
+ch = np.linspace(-0.2, 0.2, 101)
+bar = np.linspace(-1, 1, 101)
+
+CC, BAR = np.meshgrid(cc, bar, indexing='ij')
+
+CH = 0 # equilibrium
+
+
+Vsp = Va(CC, CH, BAR, CSp)*H2cm
+Vpm = Va(CC, CH, BAR, CPm)*H2cm
+Vpp = Va(CC, CH, BAR, CPp)*H2cm
+VV = V12(CC, CH, BAR, C12)*H2cm
+
+# diagonalize
[…]

### 2022-05-05 suppInfo.tex
update

\documentclass[journal=jacsat,manuscript=suppinfo]{achemso}
%\usepackage{scicite}
\usepackage[sort&compress, numbers]{natbib}
\usepackage{times}
\usepackage{amssymb}
\usepackage{subfigure}
\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{upgreek}
\usepackage{gensymb}
\usepackage[colorlinks]{hyperref}
%\newcommand{\hah}[1]{\textcolor{magenta}{#1}}
\newcommand{\tws}[1]{\textcolor{red}{#1}}
\usepackage[version=4]{mhchem}
\usepackage{amsmath,amsfonts,amssymb,dcolumn,lscape,alltt,graphicx,chemarr}
\usepackage[english]{babel}
\SectionNumbersOn
\usepackage{bm}
\usepackage[T1]{fontenc}
\usepackage{chemstyle}
% NB added command for in line cite
\newcommand{\onlinecite}[1]{\hspace{-1 ex} \nocite{#1}\citenum{#1}}
% 2 column equations
%\usepackage{widetext, widetable}
%
\author{Benjamin~A.~Laws}
\email{b.laws@unsw.edu.au}
\affiliation{School of Chemistry, University of New South Wales, Sydney NSW 2052, Australia}
\alsoaffiliation{Research School of Physics, The Australian
	National University, Canberra ACT 2601, Australia}
\author{Zachariah~D.~Levey} 
\affiliation{School of Chemistry, University of New South Wales, Sydney NSW 2052, Australia}
\author{Andrei M. Sanov}
\affiliation{Department of Chemistry and Biochemistry, The University of Arizona, Tucson, Arizona 85721, United States}
\author{John F. Stanton}
\affiliation{Department of Chemistry, University of Florida, Gainesville, Florida 32611, United States}
\author{Timothy~W.~Schmidt} 
\affiliation{School of Chemistry, University of New South Wales, Sydney NSW 2052, Australia}
\author{Stephen~T.~Gibson}
\affiliation{Research School of Physics, The Australian
	National University, Canberra ACT 2601, Australia}
\title{Velocity Map Imaging Spectroscopy of C$_2$H$^-$ and C$_2$D$^-$: a benchmark study of vibronic coupling interactions}
\abbreviations{PES,PAD,EA,eKE,FWHM,VMI}
%\DeclareUnicodeCharacter{2192}{-}

\begin{document}

\tableofcontents

\section{C$_2$H$^-$ Spectral Assignments}
Spectral assignments for all peaks resolved in the photoelectron spectra of C$_2$H$^-$ from this work are presented in Table~\ref{tab:1}. Peaks are labelled with respect to the photoelectron spectrum of C$_2$H$^-$ at 300~nm in Figure~\ref{fig:1}. The experimental binding energy of each transition is given, alongside the anisotropy ($+/-$), the corresponding vibronic symmetry, the calculated energy from Ref.~\onlinecite{tar03}. Assignments are given as $\tilde{X}(v_1,v_2,v_3)\tilde{A}(v_1,v_2,v_3)$ where superscripts represent hot-band transitions.

\begin{table*}
	\caption{Peak positions (cm$^{-1}$), and assignments for the C$_2$H$^-$ photoelectron spectra from this work. The sign of the anisotropy parameter is shown for each transition, along with it's vibronic symmetry, and the calculated position from Ref.~\cite{tar03}.} \label{tab:1}
	\begin{tabular}{c c c c c c c c c}
		\hline Peak & eBE (cm$^{-1}$) & $v$ (cm$^{-1}$) & $\beta$ & Symmetry & $A_{\text{SO}}\,^a$ & $v_{\text{calc}}\,^b$ & \multicolumn{2}{c}{Assignment}  \\ 
		& & & & & & & $\tilde{X}$ &$\tilde{A}$ \\ \hline \hline
		& 23 591 & -231 & + & $\Sigma^+$ & & & $2^2_2$ & --\\
		& 23 685 & -137 &  + & $\Sigma^+$ & & & $2^1_1$ & --\\
		& 23 823 & 0 & + & $\Sigma^+$ & -- & 0 & $0^0_0$ & --\\
		& 24 184 & 361 & $-$ & $\Pi$ & -0.35$^{c}$&371 & $2^1_0$ & -- \\
		& 24 630 & 807 & $+$ & $\Sigma^+$ & -- & 794 & $2^2_0$ & --\\
		& 25 663 & 1840 & $+$ & $\Sigma^+$ & -- & 1838 & $3^1_0$ & -- \\
		& 25 916 & 2093 & $-$ & $\Pi$ & -1.02$^{d}$ & 2096 & $2^1_03^10$ & -- \\
		& 25 993 & 2170 & $-$ & $\Pi$ & -0.66 & 2166 & $2^5_0$ & -- \\
		& 26 362 & 2539 & $+$ & $\Sigma^+$ & & 2536 & $2^203^1_0$ & -- \\
		& 26 757 &  2934 & $-$ & $\Pi$ & -1.52$^{e}$ & 2933 & $2^3_03^10$ &-- \\
		& 26 929 & 3106 & $-$ & $\Pi$ & -0.52 & 3104 & $2^7_0$ & -- \\
		& 27 175 & 3352 & + & $\Sigma^+$ & -- & 3371 & $2^43^1$ & --\\
		a & 27 430 & 3607 & $-$ & $\Pi$ & -7.22$^{f}$ & 3604 & $2^1_03^2_0/1^1_02^1_0$ & $0^0_0$ \\
		b & 27 515 & 3692 & $-$ & $\Pi$ & -5.41$^{g}$ & 3690 & $1^1_02^1_0/2^1_03^2_0$ & $0^0_0$ \\
		c & 27 612 & 3788 & $-$ & $\Pi$ & -2.51 & 3790 & $2^5_03^1_0$ & $0^0_0$ \\
		d & 27 851 & 4028 & $-$ & $\Pi$ & -2.22 & 4011 & $2^9_0/2^5_03^1_0$ & $0^0_0$ \\
		e & 27 941 & 4118 & $-$ & $\Pi$ & -3.28 & 4093 & $2^9_0$ & $0^0_0$ \\
		f & 28 200 & 4377 & $+$ & $\Sigma^+$ & & 4375 & $2^603^1_0$ & -- \\
		g & 28 349 & 4526 & $+$ & $\Sigma^+$ & -- & 4524 & $2^{10}_0$ & -- \\
		h  & 28 423 & 4600 & $-$ & $\Pi$ & & 4593 & $2^33^2$ & $0^0_0$ \\
		i & 28 562 & 4739 & $-$ & $\Pi$ & & 4702 & $2^73^1$ & $2^10$ \\
		j & 28 714 & 4891 & $-$ & $\Pi$ & & 4879 & $2^73^1$ & -- \\
		k   & 28 834 & 5011 & $-$ & $\Pi$ & & 5004 &$2^{11}$ & -- \\  
		l & 29 049 & 5226 & $-$ & $\Pi$ & & 5222 & $2^1_03^3_0$ & $3^1_0$ \\
		m* & 29 227 & 5404 & + & $\Sigma^+$ & -- & 5406 & $2^{12}$ & $2^1_0$\\
		n & 29 283 & 5460 & $-$ & $\Pi$ & & 5445  & $2^5_03^2_0$ & $3^1_0$ \\
		o & 29 465 & 5642 & $-$ & $\Pi$ & & 5630  & $2^9_03^1_0$ & $3^1_0$ \\
		p  & 29 740 & 5917 & $-$ & $\Pi$ & & 5914 & $2^{13}$ & --\\
		q & 29 844 & 6021 & + & $\Sigma^+$ & & 6054 & $2^63^2/2^23^3$ & --\\
		r & 30 021 & 6198 & $-$ & $\Pi$ & & 6200 & $2^33^3$ & $2^2$\\
		s & 30 086 & 6263 & $-$ & $\Pi$ & & 6266 & $1^12^7$ & --\\
	\end{tabular}

	\raggedright
	$^*$ transition only partially resolved in photoelectron spectrum. \\
	$^a$ from infra-red measurements of Refs.~\onlinecite{chi99} and~\onlinecite{yen95}, onless otherwise indicated.\\
	$^b$ from calculations of Ref.~\onlinecite{tar03}\\
	$^c$ Ref.~\onlinecite{kan88}\\
	$^d$ Ref.~\onlinecite{yen93}\\
	$^e$ Ref.~\onlinecite{yan93}\\
	$^f$ Ref.~\onlinecite{yan87}\\
	$^g$ Ref.~\onlinecite{cur85}
\end{table*}

Additional mass spectra are presented in Fig.~\ref{fig:S1}, to highlight the role of the CH radical in the formation of phenalenyl. Fig.~\ref{fig:S1}(a) and (b) show the mass spectrum (on and off resonance) when neat Ar gas is passed through the high voltage discharge. from a 1\% mixture of CH$_4$ in Ar gas passed through the HV discharge. The bottom plots, Fig.~\ref{fig:S1} (c) and (d) show the resulting mass spectrum when a 1\% mixture of CH$_4$ in Ar gas is used instead. A clear increase in both the resonant and non-resonant signal is observed when CH$_4$ is included in the gas mixture, confirming that the CH radicals formed in the discharge are involved in the formation of phenalenyl.

%\newpage
%\bibliography{sup-PhenRad}

\end{document}

### 2022-05-05 scripts/plotBeta.py

@@ -1,0 +1,84 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+def Gauss (E0,FWHM,E):
+    alpha = FWHM/2/np.sqrt(np.log(2.0))
+    return np.exp(-((E-E0)/alpha)**2)
+
+FWHM = 40
+amp = 1
+hv = 1e7/300
+
+#Plotting Settings
+width = 3.487*2
+height = width/1.4
+one_col = (width,height)
+fig,ax = plt.subplots(figsize=one_col)
+
+x,y = np.loadtxt('300nm.dat',unpack=True)
+
+b,em,ex,er,ep = np.loadtxt('300.dat',skiprows=1,unpack=True)
+ym = []
+by = []
+xx = []
+
+for i in range(0,np.size(b)):
+    subr = np.logical_and(x>em[i],x<ex[i])
+    suby = y[subr]
+    subx = x[subr]
+    yx = max(suby)
+    for j in range(0,np.size(suby)):
+        if suby[j] == yx:
+            xx.append(subx[j])
+    ym.append(max(suby))
+    by.append(b[i]*max(suby))
+
+fd = np.column_stack((ep,ym,b,by))
+np.savetxt('300BetaData.txt',fd)
+
+#Now we can plot the data
+
+Ev = np.arange(15000,30000,0.5)
+spec = np.zeros(np.size(Ev))
+
+for i in range(0,np.size(b)):
+    spec+= by[i]*amp*Gauss(xx[i],FWHM,Ev)
+
+plt.plot(x,y,'k',label='C$_2$H$^-$ at 300nm')
+plt.plot(Ev,spec,'C3',label = r'Anisotropy ($\beta\times$I)')
+
+#Plotting
+plt.xlim(15000,27000)
+#plt.ylim(-0.18,1.61)
+plt.ylim(-0.18,0.6)
+
+col = ['C0','C0','C1','C0','C0','C1','C1','C1','C1','C1','C1','C1','C0','C1','C1','C1','C1','C1','C1','C1']
+
+lab = ['$2^1_1$','0$^0_0$','$2^1_0$','$2^2_0$','$3^1_0$','$2^1_03^1_0$','$2^3_03^1_0$','a','b','c','d','e','f','h','i','j','k','l','n','o']
+for i in range(0,np.size(lab)):
+    if i == 1: continue
+    if i ==0:
+        plt.annotate(lab[i],(xx[i]-100,max(ym[i],by[i])+0.03),ha='center',color=col[i])
[…]

### 2022-05-05 testC2H/scripts/266-plot.py
add new images

@@ -1,0 +1,93 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+def Gauss (E0,FWHM,E):
+    alpha = FWHM/2/np.sqrt(np.log(2.0))
+    return np.exp(-((E-E0)/alpha)**2)
+FWHM = 80
+#FWHM = 80
+amp = 1
+e0 = 1e7/266-2.969*8065.74
+
+fn1 = '../C2H.dat'
+fn2 = '../C2H-266nm.dat'
+
+EA = 23956.4-31
+ofs = 1220
+cut = 4534
+cut = 3471
+
+b,a = np.loadtxt(fn1,usecols=(1,2),unpack=True)
+x,y = np.loadtxt(fn2,unpack=True)
+
+x = x-EA
+
+#Plotting Settings
+width = 3.487*2
+height = width/1.4
+one_col = (width,height)
+fig,ax = plt.subplots(figsize=one_col)
+
+
+Ev = np.arange(-630,12000,0.5)
+spec = np.zeros(np.size(Ev))
+
+for i in range(0,np.size(a)):
+    aa = a[i]
+    bb = b[i]
+    if aa == 4821.77350602297:
+        bb *=0.5
+    KEw = e0 - aa
+    FWHM = KEw*0.004*2
+    if a[i] > cut:
+        aa = a[i]-ofs
+    if a[i] < 1700:
+        FWHMa = 120
+    spec += bb*amp*Gauss(aa,FWHM,Ev)
+    #plt.plot((aa,aa),(0,-b[i]),'C0')
+
+#plt.plot(Ev,-spec,'C2',label=r'Simulates Spectrum')
+plt.plot(x,y,'k',label=r'C$_2$H$^-$ at 266 nm')
+plt.plot(Ev,-spec,'C2',label=r'Simulated Spectrum')
+plt.xlim(-630,8000)
+
+#Labelling
+#plt.plot((27320-EA,31000-EA),(0.215,0.215),color='k')
+#plt.plot((27320-EA,27320-EA),(0.22,0.21),color='k')
+#plt.plot((28060-EA,28060-EA),(0.22,0.21),color='k')
+#plt.plot((28960-EA,28960-EA),(0.22,0.21),color='k')
+#plt.plot((29620-EA,29620-EA),(0.22,0.21),color='k')
+
+plt.plot((3553,7000),(0.4,0.4),'k')
+plt.plot((3553,3553),(0.42,0.38),'k')
+plt.plot((4055,4055),(0.42,0.38),'k')
[…]

### 2022-05-05 testC2H/scripts/C2D-plot.py

@@ -1,0 +1,90 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+fn1 = '../C2D.dat'
+fn2 = '../C2D-355nm.dat'
+fn3 = '../C2D.dat'
+
+EA = 23956.4+36.4
+ofs = 1220
+#ofs = 1500+36
+ofs = 1030.3352249+50
+cut = 4534
+cut = 3471
+#cut = 100000
+
+
+b,a = np.loadtxt(fn1,usecols=(1,2),unpack=True)
+d,c = np.loadtxt(fn3,usecols=(1,2),unpack=True)
+x,y = np.loadtxt(fn2,unpack=True)
+
+x = x-EA
+
+#Plotting Settings
+width = 3.487*2
+height = width/1.4
+one_col = (width,height)
+fig,ax = plt.subplots(figsize=one_col)
+
+for i in range(0,np.size(a)):
+    aa = a[i]
+    if b[i] < 5e-3: continue
+    if a[i] > cut:
+        aa = a[i]-ofs
+    plt.plot((aa,aa),(0,-b[i]),'C1')
+    if aa == 0:
+        plt.plot((aa,aa),(0,-b[i]),'C0')
+    if aa == 1744.01312140007:
+        plt.plot((aa,aa),(0,-b[i]),'w',lw='1.5')
+        plt.plot((aa-20,aa-20),(0,-b[i]),'C0')
+    if aa == 2102.65224819867:
+        plt.plot((aa,aa),(0,-b[i]),'w',lw='1.5')
+        plt.plot((aa-60,aa-60),(0,-b[i]),'C1')
+    if aa == 3474.77973502800-ofs:
+        plt.plot((aa,aa),(0,-b[i]),'C0')
+
+for i in range(0,np.size(c)):
+    aa = c[i]
+    if c[i] > cut:
+        aa = c[i]-ofs
+#    plt.plot((aa,aa),(0,-d[i]),'w',lw='2.5')
+#    plt.plot((aa,aa),(0,-d[i]),'C0',lw='1.5')
+
+plt.plot(x,y,'k',label=r'C$_2$D$^-$ PES')
+plt.xlim(-630,4225)
+
+plt.plot((0,0),(0,0),'C0',label=r'$\Sigma$ Symmetry')
+plt.plot((0,0),(0,0),'C1',label=r'$\Pi$ Symmetry')
+plt.legend(loc=9,fontsize=10,frameon=False)
+
+ax.spines['top'].set_visible(False)
[…]

### 2022-05-05 testC2H/scripts/C2H-plot.py

@@ -1,0 +1,96 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+fn1 = '../C2H.dat'
+fn2 = '../C2H-355nm.dat'
+fn3 = '../C2H.dat'
+
+EA = 23956.4
+ofs = 1220
+cut = 4534
+cut = 3471
+
+b,a = np.loadtxt(fn1,usecols=(1,2),unpack=True)
+d,c = np.loadtxt(fn3,usecols=(1,2),unpack=True)
+x,y = np.loadtxt(fn2,unpack=True)
+
+x = x-EA
+
+#Plotting Settings
+width = 3.487*2
+height = width/1.4
+one_col = (width,height)
+fig,ax = plt.subplots(figsize=one_col)
+
+for i in range(0,np.size(a)):
+    if b[i] < 1e-3: continue
+    aa = a[i]
+    if a[i] > cut:
+        aa = a[i]-ofs
+    plt.plot((aa,aa),(0,-b[i]),'C1')
+    if aa == 0:
+        plt.plot((aa,aa),(0,-b[i]),'C0')
+    if aa == 1825.5990272609:
+        plt.plot((aa,aa),(0,-b[i]),'C0')
+    if aa == 3630.02149701572-ofs:
+        plt.plot((aa,aa),(0,-b[i]),'C0')
+    if aa == 2081.86799942435:
+        plt.plot((aa,aa),(0,-b[i]),'C0')
+    if aa == 4821.77350602297-ofs:
+        plt.plot((aa,aa),(0,-b[i]),'w',lw='2.5')
+        plt.plot((aa,aa),(0,-b[i]*0.6),'C1')
+    if aa == 5117.34572422576-ofs:
+        plt.plot((aa,aa),(0,-b[i]),'w',lw='2.5')
+        plt.plot((aa,aa),(0,-b[i]*0.8),'C1')
+    if aa == 5136.79551715929-ofs:
+        plt.plot((aa,aa),(0,-b[i]*3),'C1')
+    if aa == 4909.67040664068-ofs:
+        plt.plot((aa,aa),(0,-b[i]*1.5),'C1')
+    #plt.plot((aa,aa),(0,-b[i]),'C1')
+
+for i in range(0,np.size(c)):
+    aa = c[i]
+    if c[i] > cut:
+        aa = c[i]-ofs
+    #plt.plot((aa,aa),(0,-d[i]),'w',lw='2.5')
[…]

### 2022-05-05 C2Hpaper.tex
include figs

--- 2022-04-27 Aug2021-CH2-.tex
@@
 \section{Introduction}
-Carbon monohydrides C$_{2n}$H, are a class of linear radicals that play an important role in combustion and interstellar chemistry~\cite{fre85,bou96,wil91,vui01}.
+Carbon monohydrides C$_{2n}$H, are a class of linear radicals that play an important role in combustion and interstellar chemistry~\cite{kie90,kie92,bou96,wil91,vui01}.
 These carbon chains have been observed in many interstellar environments, including planetary atmospheres~\cite{vui01,wil03,dob16}, comets~\cite{jac96}, dark clouds~\cite{ziu82,gup09}, and during heavy star formation~\cite{beu08,jia15}.
@@
 In C$_4$H the $^2\Sigma^+$ and $^2\Pi$ states are nearly degenerate, resulting in even stronger coupling~\cite{zho07}, while in C$_6$H and C$_8$H the ordering of the states swaps, with a ground $^2\Pi$ state and a low lying excited $^2\Sigma^+$ state~\cite{lin99,tay98}.
-Consequently, understanding the vibronic coupling interactions between the $^2\Sigma$ and $^2\Pi$ surfaces is essential in order to accurately model the role these radicals (and their corresponding anions) are likely to play in the interstellar chemistry discussed above, and to guide the search for possible DIB carriers.
+Consequently, understanding the vibronic coupling interactions between the $^2\Sigma^+$ and $^2\Pi$ surfaces is essential in order to accurately model the role these radicals (and their corresponding anions) are likely to play in the interstellar chemistry discussed above, and to guide the search for possible DIB carriers.
 
@@
 $\xi$ represents the electronic states used in the expansion ($\xi=\Sigma^+(1A'),~\Pi^+(2A'),~\Pi^-(1A'')$).
-A depiction of these three interacting surfaces, generated from the parameters in Ref.~[\onlinecite{tar03}], is given in Fig.~\ref{fig:2}.
+A depiction of these three interacting surfaces, generated from the parameters in Ref.~\onlinecite{tar03}, is given in Fig.~\ref{fig:2}.
 
@@
 \begin{equation}
-\eta = \frac{1}{2}\left[ f_{2a2a}^{A(a')}-f_{2b2b}^{A(a')}-\frac{2\lambda^2}{(\Delta_0^A-\Delta_0^X)}\right]
+\eta = \frac{1}{2}\left[ f_{2a2a}^{A(a')}-f_{2b2b}^{A(a'')}-\frac{2\lambda^2}{(\Delta_0^A-\Delta_0^X)}\right]
 \label{eq:calc3}
@@
 		 $\Delta$E & 0 & 22431.21 &  26543.67 & 26543.67 & 0&	22431.21 & 26543.67	& 26543.67\\
-		 f1 & 0	& -211.28 & 286.9 &	286.9 & 0& -596.04& 641.6 & 641.6\\
-		 f2 & 0 & -1515.21 & 1257.07 & 1257.07 & 0 & -1401.53 & 1115.17 & 1115.17\\
-		 f3 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-		 f4 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-         f11 & 3424.32 & 3487.03 & 3482.16 & 3482.16 & 2611.42 & 2636.57 & 2681.25 & 2681.25\\
-         f12 & 0.00 & -28.32 & 31.46 & 31.46 & 0.00 & -48.38 & 55.40 & 55.40\\
-         f22 & 1894.71 & 1830.83 & 2099.57 & 2042.21 & 1792.49 & 1747.62 & 1914.39 & 1914.39\\
-         f33 & 607.09 & 87.57 & 1883.48 & 658.96 & 481.89 & 120.09 & 1503.88 & 473.55\\
-         f44 & 607.09 & 87.57 & 658.96 & 1883.48 & 481.89 & 120.09 & 473.55 & 1503.88\\
+		 F$_1$ & 0	& -211.28 & 286.9 &	286.9 & 0& -596.04& 641.6 & 641.6\\
+		 F$_3$ & 0 & -1515.21 & 1257.07 & 1257.07 & 0 & -1401.53 & 1115.17 & 1115.17\\
+		 F$_{2a}$ & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+		 F$_{2b}$ & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+         F$_{11}$ & 3424.32 & 3487.03 & 3482.16 & 3482.16 & 2611.42 & 2636.57 & 2681.25 & 2681.25\\
+         F$_{13}$ & 0.00 & -28.32 & 31.46 & 31.46 & 0.00 & -48.38 & 55.40 & 55.40\\
+         F$_{33}$ & 1894.71 & 1830.83 & 2099.57 & 2042.21 & 1792.49 & 1747.62 & 1914.39 & 1914.39\\
+         F$_{2a2a}$ & 607.09 & 87.57 & 1883.48 & 658.96 & 481.89 & 120.09 & 1503.88 & 473.55\\
+         F$_{2b2b}$ & 607.09 & 87.57 & 658.96 & 1883.48 & 481.89 & 120.09 & 473.55 & 1503.88\\
          $\lambda$ &  & & -1185.26 &  &  & & -1014.58 &  \\
@@
 While the present calculations invoke a high level of \emph{ab-initio} theory (EOM-CCSDT), the level of parametrization of the vibronic Hamiltonian is relatively simple (QVC model).
-The approach could be systematically improved with a more elaborate expansion, such as that used in Ref.~[\onlinecite{sim12}] for the NO$_3$ radical.
+The approach could be systematically improved with a more elaborate expansion, such as that used in Ref.~\onlinecite{sim12} for the NO$_3$ radical.
 Applying this approach to similar less-studied systems will produce reliable predictions for the position and intensity of dominant transitions, which will help guide the search for these molecules in laboratory experiments and astronomical observations.
@@
 It is important to note that the HT coupled transitions on the $\tilde{X} ^2\Sigma^+$ surface have negative anisotropies and $\Pi$ symmetry.
-This is discussed in more detail in the Supplementary Materials.
 
@@
 Plotting $\beta\times I$ allows the sign (+/-) of each individual transition to be easily identified, even for partially resolved peaks.
-All of the transitions above the $\tilde{A} ^2\Pi$ origin have a negative anisotropy, except for peak $f$.
-This confirms the assignment of this peak to the highly excited $\Sigma$ transition $\tilde{X}(0,6,1$), where $\tilde{X}(v_1,v_2,v_3)$.
-The nearby peaks $h$ and $i$  are assigned to the admixed $\Pi$ transitions $\tilde{X}(0,3,2)\tilde{A}(0,0,0)$ and $\tilde{X}(0,7,1)\tilde{A}(010)$.
-The other two peaks in this region $j$ and $k$ are assigned to highly excited HT coupled $\Pi$ transitions $\tilde{X}(0,7,1)$ and $\tilde{X}(0,11,0)$.
-The assignments for all peaks in the C$_2$H$^-$ and C$_2$D$^-$ photoelectron spectra are presented in the Supplementary Materials Table~S1.
+All of the transitions above the $\tilde{A} ^2\Pi$ origin have a negative anisotropy, except for peak $f$, which was not assigned in previous experiments.
+The positive anisotropy supports our assignment of this peak to the highly excited $\Sigma$ transition $\tilde{X}(0,6,1$), where $\tilde{X}(v_1,v_2,v_3)$.
+The nearby peaks $h$ and $i$  are assigned to the admixed $\Pi$ transitions $\tilde{X}(0,3,2)\tilde{A}(0,0,0)$ and $\tilde{X}(0,7,1)\tilde{A}(010)$, which agrees with previous assignments~\cite{zho07,tar03}.
+Peak $j$ was tentatively assigned to the $\Sigma$ transition $\tilde{X}(1,4,0$) previously~\cite{zho07}, however Figure~\ref{fig:6} shows peak $j$ has $\Pi$ symmetry.
+Therefore, we assign $j$ to the highly excited HT coupled $\Pi$ transition $\tilde{X}(0,7,1)$.
+The other dominant peaks in this region, $l$, $n$, and $o$, represent admixed $\Pi$ transitions involving the $\tilde{A}(0,0,1)$ vibrational level of the excited state.
+The complete assignments for all resolved peaks in the C$_2$H$^-$ and C$_2$D$^-$ photoelectron spectra from this work are presented in the Supplementary Materials Table~S1.
 
@@
 The resulting simulated photoelectron spectra of C$_2$H$^-$ and C$_2$D$^-$ closely resemble the experimental data, even in the energy region of the complicated $\tilde{A}$ state origin.
-Photoelectron anisotropy parameters were also measured for each dominant transition, at a range of wavelengths.
+Photoelectron anisotropy parameters were also measured for dominant transitions, at a range of wavelengths.
 Comparing the sign (+/-) of the anisotropy to the calculated vibronic symmetry allowed for even weak or partially resolved transitions to be assigned.
@@
 demonstrates that electronic spectra complicated by vibronic coupling effects may still be accurately simulated using a quasidiabatic treatment, as parametrised by appropriate quantum chemical methodology.
-This approach may be applied to larger, less well known, C$_{2n}$H chains, which may help guide the search for these molecules in astronomical studies, and help identify potential DIB carriers.
+This approach may be applied to larger, less well known, C$_{2n}$H species, which may help guide the search for these molecules in astronomical studies, and help identify potential DIB carriers.
 It is especially encouraging that the fairly modest parametrisation used here works so well for C$_2$H, as this bodes well for its extension to larger systems.
@@
 A modified velocity-map imaging lens images the detached photoelectrons to a 75mm diameter MCP/phosphor screen detector.
-Events are imaged by a 2048x2048 monochrome CCD camera (PCO 2000), with each frame transferred to a computer at a 10Hz repetition rate, and processed in real time to identify individual electron events.
-The electron positions are centroided to a sub-pixel accuracy, then written to a data file for subsequent analysis.
+Events are imaged by a 2048x2048 monochrome CCD camera (PCO 2000), with each frame transferred to a computer at a 10Hz repetition rate, and processed in real time to identify the electron events, centroiding the position to
+a subpixel accuracy.
+The electron positions are then written to a data file for subsequent analysis.
 The velocity-map image is centred and then circularized by an angular dependent-radial scaling determined by comparing adjacent radial slice intensity profiles~\cite{gas17}.
 An inverse Abel transformation of the VMI, based on the algorithm of Hansen and Law~\cite{han85,hic19}, returns a slice image of the 3D electron source distribution.
-Absolute energy calibration of the photoelectron spectra is achieved using published measurements of species, including O$^-$~\cite{cav07} and NO$_2^-$~\cite{law19}, that have been studied under similar conditions as used for the C$_2$H$^-$ measurements.
+Absolute energy calibration of the photoelectron spectra is achieved using published measurements of species, including C$_2^-$~\cite{law19b} and NO$_2^-$~\cite{law19}, that have been studied under similar conditions and photon energies as those used for the C$_2$H$^-$ measurements.
 

### 2022-05-05 C2Hpaper.tex
updates

@@
 	\label{tab:1}
-	\begin{tabular}{c |c c c c| c c c c }
-		 & \multicolumn{4}{c}{C$_2$H}     & \multicolumn{4}{c}{C$_2$D}  \\ \hline
+%	\begin{tabular}{c |c c c c| c c c c }
+%		 & \multicolumn{4}{c}{C$_2$H}     & \multicolumn{4}{c}{C$_2$D}  \\ \hline
+%		  & Anion & $\tilde{X}^2\Sigma^+$ & $\tilde{A}^2\Pi (a')$ & $\tilde{A}^2\Pi (a'')$ & Anion & $\tilde{X}^2\Sigma^+$ & $\tilde{A}^2\Pi (a')$ & $\tilde{A}^2\Pi (a'')$ \\
+%		 \hline\hline
+%		 $\Delta$E & 0 & 22431.21 &  26543.67 & 26543.67 & 0&	22431.21 & 26543.67	& 26543.67\\
+%		 F$_1$ & 0	& -211.28 & 286.9 &	286.9 & 0& -596.04& 641.6 & 641.6\\
+%		 F$_3$ & 0 & -1515.21 & 1257.07 & 1257.07 & 0 & -1401.53 & 1115.17 & 1115.17\\
+%		 F$_{2a}$ & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+%		 F$_{2b}$ & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+ %        F$_{11}$ & 3424.32 & 3487.03 & 3482.16 & 3482.16 & 2611.42 & 2636.57 & 2681.25 & 2681.25\\
+%         F$_{13}$ & 0.00 & -28.32 & 31.46 & 31.46 & 0.00 & -48.38 & 55.40 & 55.40\\
+ %        F$_{33}$ & 1894.71 & 1830.83 & 2099.57 & 2042.21 & 1792.49 & 1747.62 & 1914.39 & 1914.39\\
+  %       F$_{2a2a}$ & 607.09 & 87.57 & 1883.48 & 658.96 & 481.89 & 120.09 & 1503.88 & 473.55\\
+   %      F$_{2b2b}$ & 607.09 & 87.57 & 658.96 & 1883.48 & 481.89 & 120.09 & 473.55 & 1503.88\\
+    %     $\lambda$ &  & & -1185.26 &  &  & & -1014.58 &  \\
+     %    \end{tabular}
+     \begin{tabular}{c | c c c c | c c c c} 
+     	\hline
+     	& \multicolumn{4}{c}{C2H} & \multicolumn{4}{c}{C2D}\\
+     	\hline
      	& Anion & $\tilde{X}^2\Sigma^+$ & $\tilde{A}^2\Pi (a')$ & $\tilde{A}^2\Pi (a'')$ & Anion & $\tilde{X}^2\Sigma^+$ & $\tilde{A}^2\Pi (a')$ & $\tilde{A}^2\Pi (a'')$  \\
-		 \hline\hline
-		 $\Delta$E & 0 & 22431.21 &  26543.67 & 26543.67 & 0&	22431.21 & 26543.67	& 26543.67\\
-		 F$_1$ & 0	& -211.28 & 286.9 &	286.9 & 0& -596.04& 641.6 & 641.6\\
-		 F$_3$ & 0 & -1515.21 & 1257.07 & 1257.07 & 0 & -1401.53 & 1115.17 & 1115.17\\
-		 F$_{2a}$ & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-		 F$_{2b}$ & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-         F$_{11}$ & 3424.32 & 3487.03 & 3482.16 & 3482.16 & 2611.42 & 2636.57 & 2681.25 & 2681.25\\
-         F$_{13}$ & 0.00 & -28.32 & 31.46 & 31.46 & 0.00 & -48.38 & 55.40 & 55.40\\
-         F$_{33}$ & 1894.71 & 1830.83 & 2099.57 & 2042.21 & 1792.49 & 1747.62 & 1914.39 & 1914.39\\
-         F$_{2a2a}$ & 607.09 & 87.57 & 1883.48 & 658.96 & 481.89 & 120.09 & 1503.88 & 473.55\\
-         F$_{2b2b}$ & 607.09 & 87.57 & 658.96 & 1883.48 & 481.89 & 120.09 & 473.55 & 1503.88\\
-         $\lambda$ &  & & -1185.26 &  &  & & -1014.58 &  \\
+     	\hline
+     	$\Delta_0$ & 0& 22431.21&  26543.67& 26543.67& 0 & 22431.21& 26543.67& 26543.67 \\
+     	F$_1$ &  0& -211.28& 286.90& 286.90& 0& -596.04& 641.6& 641.6\\
+     	F$_3$ &  0& -1515.21&  1257.07& 1257.07& 0& -1401.53& 1115.17& 1115.17\\
+     	F$_{2a}$& 0 & 0& 0& 0& 0& 0& 0&0 \\
+     	F$_{2b}$&  0& 0& 0& 0& 0& 0& 0&0 \\
+     	F$_{11}$& 3424.32 &  3487.03& 3482.16& 3482.16& 2611.42&  2636.57& 2681.25& 2681.25\\
+     	F$_{13}$&  0 & -28.32& 31.46& 31.46& 0& -48.38& 55.40& 55.40\\
+     	F$_{33}$& 1894.71 & 1830.83& 2042.21& 2042.21& 1792.49&  1747.62& 1914.39& 1914.39\\
+     	f$_{22}$& 607.09&  87.57& -& -& 481.89&  120.09& -& -\\
+     	F$_{22}$& 607.09 & 770.78& -& -& 481.89& 620.70& -& -\\
+     	f$_{2a2a}$& - &- & 1883.48& 658.96& -& -& 1503.88& 473.55\\
+     	f$_{2b2b}$& - &- & 658.96& 1883.48& -& -& 473.55& 1503.88\\
+     	F$_{2a2a}$& -& -& 1200.27& 658.96& -& -& 1003.27& 473.55\\
+     	F$_{2b2b}$& -& -& 658.96& 1200.27& -& -& 473.55& 1003.27\\
+     	&&&&&&&& \\
+     	$\lambda$& & & -1185.26& & & & -1014.58& \\
+     	$\eta$ & & & -270.66& & & & -264.86& \\
+
      \end{tabular}
@@
 The relative intensities between the calculated transitions are also in good agreement with the experimental data.
-Peak $d$ is slightly underestimated; however the relative intensity difference between peaks $d$ and $e$ may be partly explained by the Wigner threshold law~\cite{wig48}, which will reduce the intensity of peak e in the experimental spectrum due to its proximity to the detachment threshold.
+Peak $d$ is slightly overestimated; however the relative intensity difference between peaks may be partly explained by the Wigner threshold law~\cite{wig48}, which will reduce the intensity of peaks $d$ and $e$ in the experimental spectrum due to their proximity to the detachment threshold.
 The simulated spectrum also slightly underestimates the splitting between the vibronic levels, which may be linked to the overestimation of the calculated gap between the $^2\Sigma$ and $^2\Pi$ surfaces.
@@
 (b) Experimental photoelectron spectrum of C$_2$D$^-$ at 355~nm, compared to the simulated spectrum.
-The labelling of peaks near the $\tilde{A}$ origin correspond to transitions identified in Table~S1.}
+The labelling of peaks near the $\tilde{A}$ origin correspond to transitions identified in Tables~S1 and~S2.}
 	\label{fig:3}
@@
 Near the $\tilde{A} ^2\Pi$ state origin, deuteration has a large impact on the experimental photoelectron spectrum.
-Instead of the 5 evenly split levels observed in C$_2$H, a single dominant peak ($d$) is now observed near $\sim3,845$~cm$^{-1}$ alongside a collection of weaker peaks ($a-c$) centred around 3,400~cm$^{-1}$.
-Based on previous spin-orbit splitting measurements, peak d is expected to have significant $\tilde{A} ^2\Pi$ character, with peaks a-c commonly assigned to vibronic levels with predominantly HT coupled $\tilde{X} ^2\Sigma^+$ character~\cite{yan87,hsu95,chi99,wil11}.
+Instead of the 5 evenly split levels observed in C$_2$H, a single dominant peak ($e$) is now observed near $\sim3,845$~cm$^{-1}$ alongside a collection of weaker peaks ($a-d$) centred around 3,400~cm$^{-1}$.
+Based on previous spin-orbit splitting measurements, peak d is expected to have significant $\tilde{A} ^2\Pi$ character, with peaks $a-d$ commonly assigned to vibronic levels with predominantly HT coupled $\tilde{X} ^2\Sigma^+$ character~\cite{yan87,hsu95,chi99,wil11}.
 This suggests that deuteration effectively dampens the coupling interaction between the surfaces, as has been observed in the vinylidene photoelectron spectrum~\cite{dev17}.
@@
 The simulated spectrum reproduces the large change observed for the deuterated species.
-The calculated intensity pattern of the vibronic levels around the $\tilde{A} ^2\Pi$ origin is also a good match to the experimental data, with a single intense transition observed near peak d, and 3 prominent transitions predicted around the experimental peaks $a-c$.
-The calculated splitting between the levels is also similar, however the relative intensity of peak $d$ appears to be underestimated.
+The calculated intensity pattern of the vibronic levels around the $\tilde{A} ^2\Pi$ origin is also a good match to the experimental data, with a single intense transition observed near peak $e$, and 3 prominent transitions predicted around the experimental peaks $a-d$.
+The calculated splitting between the levels is also similar.
+%however the relative intensity of peak $d$ appears to be underestimated.
 %The results from Figure~\ref{fig:C2H-plot} confirm that the quasiadiabtic approach is able to accurately describe the vibronic interactions between the $\Sigma$ and $\Pi$ surfaces, including deuteration effects.
@@
 The positive anisotropy supports our assignment of this peak to the highly excited $\Sigma$ transition $\tilde{X}(0,6,1$), where $\tilde{X}(v_1,v_2,v_3)$.
-The nearby peaks $h$ and $i$  are assigned to the admixed $\Pi$ transitions $\tilde{X}(0,3,2)\tilde{A}(0,0,0)$ and $\tilde{X}(0,7,1)\tilde{A}(010)$, which agrees with previous assignments~\cite{zho07,tar03}.
+The nearby peaks $h$ and $i$  are assigned to the admixed $\Pi$ transitions $\tilde{X}(0,3,2)\tilde{A}(0,0,0)$ and $\tilde{X}(0,7,1)\tilde{A}(0,1,0)$, which agrees with previous assignments~\cite{zho07,tar03}.
 Peak $j$ was tentatively assigned to the $\Sigma$ transition $\tilde{X}(1,4,0$) previously~\cite{zho07}, however Figure~\ref{fig:6} shows peak $j$ has $\Pi$ symmetry.

### 2022-05-05 suppInfo.tex
updates

@@
 \usepackage{gensymb}
-\usepackage[colorlinks]{hyperref}
+%\usepackage[colorlinks]{hyperref}
 %\newcommand{\hah}[1]{\textcolor{magenta}{#1}}
@@
 Peaks are labelled with respect to the photoelectron spectrum of C$_2$H$^-$ at 300~nm in Figure~\ref{fig:1}.
-The experimental binding energy of each transition is given, alongside the anisotropy ($+/-$), the corresponding vibronic symmetry, the calculated energy from Ref.~\onlinecite{tar03}.
+The experimental binding energy of each transition is given, alongside the anisotropy ($+/-$), the corresponding vibronic symmetry, and the calculated energy from Ref.~\onlinecite{tar03}.
 Assignments are given as $\tilde{X}(v_1,v_2,v_3)\tilde{A}(v_1,v_2,v_3)$ where superscripts represent hot-band transitions.
+
+\begin{figure}[th!]
+	\includegraphics[width=0.6\textwidth]{figures/FigS1.pdf}
+	\caption{Photoelectron spectrum of C$_2$H$^-$ at 300~nm, showing the labelling of peaks used in this work.}
+	\label{fig:1}
+\end{figure}
 
@@
 The sign of the anisotropy parameter is shown for each transition, along with it's vibronic symmetry, and the calculated position from Ref.~\cite{tar03}.} \label{tab:1}
-	\begin{tabular}{c c c c c c c c c}
-		\hline Peak & eBE (cm$^{-1}$) & $v$ (cm$^{-1}$) & $\beta$ & Symmetry & $A_{\text{SO}}\,^a$ & $v_{\text{calc}}\,^b$ & \multicolumn{2}{c}{Assignment}  \\ 
-		& & & & & & & $\tilde{X}$ &$\tilde{A}$ \\ \hline \hline
-		& 23 591 & -231 & + & $\Sigma^+$ & & & $2^2_2$ & --\\
-		& 23 685 & -137 &  + & $\Sigma^+$ & & & $2^1_1$ & --\\
-		& 23 823 & 0 & + & $\Sigma^+$ & -- & 0 & $0^0_0$ & --\\
-		& 24 184 & 361 & $-$ & $\Pi$ & -0.35$^{c}$&371 & $2^1_0$ & -- \\
-		& 24 630 & 807 & $+$ & $\Sigma^+$ & -- & 794 & $2^2_0$ & --\\
-		& 25 663 & 1840 & $+$ & $\Sigma^+$ & -- & 1838 & $3^1_0$ & -- \\
-		& 25 916 & 2093 & $-$ & $\Pi$ & -1.02$^{d}$ & 2096 & $2^1_03^10$ & -- \\
-		& 25 993 & 2170 & $-$ & $\Pi$ & -0.66 & 2166 & $2^5_0$ & -- \\
-		& 26 362 & 2539 & $+$ & $\Sigma^+$ & & 2536 & $2^203^1_0$ & -- \\
-		& 26 757 &  2934 & $-$ & $\Pi$ & -1.52$^{e}$ & 2933 & $2^3_03^10$ &-- \\
-		& 26 929 & 3106 & $-$ & $\Pi$ & -0.52 & 3104 & $2^7_0$ & -- \\
-		& 27 175 & 3352 & + & $\Sigma^+$ & -- & 3371 & $2^43^1$ & --\\
-		a & 27 430 & 3607 & $-$ & $\Pi$ & -7.22$^{f}$ & 3604 & $2^1_03^2_0/1^1_02^1_0$ & $0^0_0$ \\
-		b & 27 515 & 3692 & $-$ & $\Pi$ & -5.41$^{g}$ & 3690 & $1^1_02^1_0/2^1_03^2_0$ & $0^0_0$ \\
-		c & 27 612 & 3788 & $-$ & $\Pi$ & -2.51 & 3790 & $2^5_03^1_0$ & $0^0_0$ \\
-		d & 27 851 & 4028 & $-$ & $\Pi$ & -2.22 & 4011 & $2^9_0/2^5_03^1_0$ & $0^0_0$ \\
-		e & 27 941 & 4118 & $-$ & $\Pi$ & -3.28 & 4093 & $2^9_0$ & $0^0_0$ \\
-		f & 28 200 & 4377 & $+$ & $\Sigma^+$ & & 4375 & $2^603^1_0$ & -- \\
-		g & 28 349 & 4526 & $+$ & $\Sigma^+$ & -- & 4524 & $2^{10}_0$ & -- \\
-		h  & 28 423 & 4600 & $-$ & $\Pi$ & & 4593 & $2^33^2$ & $0^0_0$ \\
-		i & 28 562 & 4739 & $-$ & $\Pi$ & & 4702 & $2^73^1$ & $2^10$ \\
-		j & 28 714 & 4891 & $-$ & $\Pi$ & & 4879 & $2^73^1$ & -- \\
-		k   & 28 834 & 5011 & $-$ & $\Pi$ & & 5004 &$2^{11}$ & -- \\  
-		l & 29 049 & 5226 & $-$ & $\Pi$ & & 5222 & $2^1_03^3_0$ & $3^1_0$ \\
-		m* & 29 227 & 5404 & + & $\Sigma^+$ & -- & 5406 & $2^{12}$ & $2^1_0$\\
-		n & 29 283 & 5460 & $-$ & $\Pi$ & & 5445  & $2^5_03^2_0$ & $3^1_0$ \\
-		o & 29 465 & 5642 & $-$ & $\Pi$ & & 5630  & $2^9_03^1_0$ & $3^1_0$ \\
-		p  & 29 740 & 5917 & $-$ & $\Pi$ & & 5914 & $2^{13}$ & --\\
-		q & 29 844 & 6021 & + & $\Sigma^+$ & & 6054 & $2^63^2/2^23^3$ & --\\
-		r & 30 021 & 6198 & $-$ & $\Pi$ & & 6200 & $2^33^3$ & $2^2$\\
-		s & 30 086 & 6263 & $-$ & $\Pi$ & & 6266 & $1^12^7$ & --\\
+	\begin{tabular}{c c c c c c l}
+		\hline Peak & eBE (cm$^{-1}$) & $v$ (cm$^{-1}$) & $\beta$ & Symmetry &  $v_{\text{calc}}\,^a$ & {Assignment}  \\ 
+		 \hline \hline
+		& 23 591 & -231 & + & $\Sigma^+$ & & $\tilde{X}(0,2^2,0)$ \\
+		& 23 685 & -137 &  + & $\Sigma^+$ & & $\tilde{X}(0,1^1,0)$ \\
+		& 23 823 & 0 & + & $\Sigma^+$ &  0 & $\tilde{X}(0,0,0)$ \\
+		& 24 184 & 361 & $-$ & $\Pi$ & 371 & $\tilde{X}(0,1,0)$  \\
+		& 24 630 & 807 & $+$ & $\Sigma^+$ & 794 & $\tilde{X}(0,2,0)$ \\
+		& 25 663 & 1840 & $+$ & $\Sigma^+$ & 1838 & $\tilde{X}(0,0,1)$  \\
+		& 25 916 & 2093 & $-$ & $\Pi$ & 2096 & $\tilde{X}(0,1,1)$  \\
+		& 25 993 & 2170 & $-$ & $\Pi$ & 2166 & $\tilde{X}(0,5,0)$  \\
+		& 26 362 & 2539 & $+$ & $\Sigma^+$ & 2536 & $\tilde{X}(0,2,1)$  \\
+		& 26 757 &  2934 & $-$ & $\Pi$ & 2933 & $\tilde{X}(0,3,1)$  \\
+		& 26 929 & 3106 & $-$ & $\Pi$ & 3104 & $\tilde{X}(0,7,0)$  \\
+		& 27 175 & 3352 & + & $\Sigma^+$ & 3371 & $\tilde{X}(0,4,1)$ \\
+		a & 27 430 & 3607 & $-$ & $\Pi$ & 3604 & $\tilde{X}(0,1,2)\tilde{X}(1,1,0)\tilde{A}(0,0,0)$  \\
+		b & 27 515 & 3692 & $-$ & $\Pi$ & 3690 & $\tilde{X}(1,1,0)\tilde{X}(0,1,2)\tilde{A}(0,0,0)$   \\
+		c & 27 612 & 3788 & $-$ & $\Pi$ & 3790 & $\tilde{X}(0,5,1)\tilde{A}(0,0,0)$  \\
+		d & 27 851 & 4028 & $-$ & $\Pi$ & 4011 & $\tilde{X}(0,9,0)\tilde{X}(0,5,1)\tilde{A}(0,0,0)$  \\
+		e & 27 941 & 4118 & $-$ & $\Pi$ & 4093 & $\tilde{X}(0,9,0)\tilde{A}(0,0,0)$  \\
+		f & 28 200 & 4377 & $+$ & $\Sigma^+$ & 4375 & $\tilde{X}(0,6,1)$  \\
+		g & 28 349 & 4526 & $+$ & $\Sigma^+$ & 4524 & $\tilde{X}(0,10,0)$  \\
+		h  & 28 423 & 4600 & $-$ & $\Pi$ & 4593 & $\tilde{X}(0,3,2)\tilde{A}(0,0,0)$  \\
+		i & 28 562 & 4739 & $-$ & $\Pi$ & 4702 & $\tilde{X}(0,7,1)\tilde{A}(0,1,0)$  \\
+		j & 28 714 & 4891 & $-$ & $\Pi$ & 4879 & $\tilde{X}(0,7,1)$  \\
+		k   & 28 834 & 5011 & $-$ & $\Pi$ & 5004 & $\tilde{X}(0,11,0)$  \\  
+		l & 29 049 & 5226 & $-$ & $\Pi$ & 5222 & $\tilde{X}(0,1,3)\tilde{A}(0,0,1)$  \\
+		m & 29 227 & 5404 & + & $\Sigma^+$ & 5406 & $\tilde{X}(0,12,0)\tilde{A}(0,1,0)$ \\
+		n & 29 283 & 5460 & $-$ & $\Pi$ & 5445  & $\tilde{X}(0,5,2)\tilde{A}(0,0,1)$  \\
+		o & 29 465 & 5642 & $-$ & $\Pi$ & 5630  & $\tilde{X}(0,9,1)\tilde{A}(0,0,1)$  \\
+		p  & 29 740 & 5917 & $-$ & $\Pi$ & 5914 & $\tilde{X}(0,13,0)$ \\
+		q & 29 844 & 6021 & + & $\Sigma^+$ & 6054 & $\tilde{X}(0,6,2)\tilde{X}(0,2,3)$ \\
+		r & 30 021 & 6198 & $-$ & $\Pi$ & 6200 & $\tilde{X}(0,3,3)\tilde{A}(0,2,0)$ \\
+		s & 30 086 & 6263 & $-$ & $\Pi$ & 6266 & $\tilde{X}(1,7,0)$ \\
+	\end{tabular}
+	\raggedright
+
+$^a$ from calculations of Ref.~\onlinecite{tar03}
+
+\end{table*}
+
+\section{C$_2$D$^-$ Spectral Assignments}
+Spectral assignments for all peaks resolved in C$_2$D$^-$ from this work are presented in Table~\ref{tab:2}.
+Peaks are labelled with respect to the photoelectron spectrum of C$_2$D$^-$ at 355~nm in Figure~\ref{fig:2}.
+The experimental binding energy of each transition is given, alongside the anisotropy ($+/-$), the corresponding vibronic symmetry, and the calculated energy from Ref.~\onlinecite{tar03}.
+
+\begin{figure}[th!]
+	\includegraphics[width=0.6\textwidth]{figures/FigS2.pdf}
+	\caption{Photoelectron spectrum of C$_2$D$^-$ at 266~nm, showing the labelling of peaks used in this work.}
+	\label{fig:2}
+\end{figure}
+
+\begin{table*}
+	\caption{Peak positions (cm$^{-1}$) and assignments for the C$_2$D$^-$ photoelectron spectra from this work.
+The sign of the anisotropy parameter is shown for each transition, along with it's vibronic symmerty, and calculated position from Ref.~\cite{tar03}.} \label{tab:2}
+	\begin{tabular}{c c c c c c c }
+		\hline Peak & eBE (cm$^{-1}$) & $v$ (cm$^{-1}$) & $\beta$ & Symmetry &  $v_{\text{calc}}\,^a$ &{Assignment}  \\ 
+		 \hline \hline
+		& 23 751 & -197 & + & $\Sigma{+}$ & & $\tilde{X}(0,2^2,0)$ \\
+		& 23829 & -120 & + & $\Sigma^+$ & & $\tilde{X}(0,2^1,0)$  \\
+		& 23 949 & 0 & + & $\Sigma^+$ & 0 & $\tilde{X}(0,0,0)$ \\
+		& 24 227 & 278 & $-$ & $\Pi$ & 287 & $\tilde{X}(0,1,0)$ \\
+		& 24 577 & 629  & + & $\Sigma^+$ & 615 & $\tilde{X}(0,2,0)$ \\
+		& 24 906 & 957 & $-$ & $\Pi$ & 953 & $\tilde{X}(0,3,0)$ \\ 
+		& 25 506 & 1557 & + &  &  &  \\
+		& 25 688 & 1740 & + & $\Sigma^+$ & 1744 & $\tilde{X}(0,0,1)$ \\
+		& 25 901 & 1952 & $-$ & $\Pi$ & 1962 & $\tilde{X}(0,1,1)$ \\
+		& 26 245 & 2297 & + & $\Sigma^+$ & 2302 & $\tilde{X}(0,2,1)$ \\
+		& 26 556 & 2607 & $-$ & $\Pi$ & 2612 & $\tilde{X}(0,3,1)$ \\
+		& 26 747 & 2798 & $-$ & $\Pi$ & 2796 & $\tilde{X}(1,1,0)$ \\
+		a & 27 253 & 3304 & $-$ & $\Pi$ & 3309 & $\tilde{X}(0,5,1)$ \\
+		b & 27 369 & 3420 & $-$ & $\Pi$ & 3426 & $\tilde{X}(1,3,0)$ \\
+		c & 27 450 & 3501 & $-$ & $\Pi$ & 3511 & $\tilde{X}(0,1,2)$ \\
+		d & 27 552 & 3603 & $-$ &  &  &  \\
+		e & 27 793 & 3844 & $-$ & $\Pi$ & 3838 & $\tilde{A}(0,0,0)$\\
+		f & 27 906 & 3957 & $+$ & $\Sigma^+$ & 3967 & $\tilde{X}(0,2,2)$ \\
 	\end{tabular}
@@
 	\raggedright
-	$^*$ transition only partially resolved in photoelectron spectrum. \\
-	$^a$ from infra-red measurements of Refs.~\onlinecite{chi99} and~\onlinecite{yen95}, onless otherwise indicated.\\
-	$^b$ from calculations of Ref.~\onlinecite{tar03}\\
-	$^c$ Ref.~\onlinecite{kan88}\\
-	$^d$ Ref.~\onlinecite{yen93}\\
-	$^e$ Ref.~\onlinecite{yan93}\\
-	$^f$ Ref.~\onlinecite{yan87}\\
-	$^g$ Ref.~\onlinecite{cur85}
+
+	$^a$ from calculations of Ref.~\onlinecite{tar03}
 \end{table*}
 
-Additional mass spectra are presented in Fig.~\ref{fig:S1}, to highlight the role of the CH radical in the formation of phenalenyl.
-Fig.~\ref{fig:S1}(a) and (b) show the mass spectrum (on and off resonance) when neat Ar gas is passed through the high voltage discharge.
-from a 1\% mixture of CH$_4$ in Ar gas passed through the HV discharge.
-The bottom plots, Fig.~\ref{fig:S1} (c) and (d) show the resulting mass spectrum when a 1\% mixture of CH$_4$ in Ar gas is used instead.
-A clear increase in both the resonant and non-resonant signal is observed when CH$_4$ is included in the gas mixture, confirming that the CH radicals formed in the discharge are involved in the formation of phenalenyl.
-
-%\newpage
-%\bibliography{sup-PhenRad}
+\newpage
+\bibliography{sup-C2H}
 

### 2022-05-05 testC2H/scripts/C2D-plot.py

@@ -34,6 +34,8 @@ for i in range(0,np.size(a)):
     plt.plot((aa,aa),(0,-b[i]),'C1')
     if aa == 0:
         plt.plot((aa,aa),(0,-b[i]),'C0')
+    #if aa == 4745.70365733937-ofs:
+    #    plt.plot((aa,aa),(0,-b[i]),'C0')
     if aa == 1744.01312140007:
         plt.plot((aa,aa),(0,-b[i]),'w',lw='1.5')
         plt.plot((aa-20,aa-20),(0,-b[i]),'C0')
@@ -79,9 +81,12 @@ plt.annotate(r'$2^1_0$',(278,0.10),ha='center')
 plt.annotate(r'$3^1_0$',(1740,0.19),ha='center')
 plt.annotate(r'$2^1_03^1_0$',(1952,0.125),ha='center')
 plt.annotate(r'$2^3_03^1_0$',(2607,0.125),ha='center')
-plt.annotate(r'a',(3376,0.201),ha='center')
-plt.annotate(r'b',(3468,0.320),ha='center')
-plt.annotate(r'd',(3798,0.859),ha='center')
+plt.annotate(r'a',(27253-EA,0.11),ha='center')
+plt.annotate(r'b',(3376,0.201),ha='center')
+plt.annotate(r'c',(3468,0.320),ha='center')
+plt.annotate(r'e',(3798,0.859),ha='center')
+plt.annotate(r'd',(27571-EA,0.0859),ha='center')
+plt.annotate(r'f',(27898-EA,0.159),ha='center')
 #plt.annotate(r'd',(4028,0.228),ha='center')
 #plt.annotate(r'e',(4118,0.287),ha='center')
 

### 2022-05-05 testC2H/scripts/Fig6-C2H-UV.py

@@ -1,0 +1,63 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+x,y = np.loadtxt("C2H-6S1CMbI1024PESBE.dat",unpack=True)
+
+#Plotting Settings
+width = 3.487*2
+height = width/1.4
+one_col = (width,height)
+fig,ax = plt.subplots(figsize=one_col)
+
+
+plt.plot(x,y,color='k')
+
+plt.axis(xmin=27000,xmax=30500,ymin=-0.02,ymax=0.25)
+
+plt.annotate(r'$\tilde{A}\,^2\Pi$ $0^0_0$',(27750,0.225),ha='center',color='k',fontsize=14)
+plt.annotate(r'$\tilde{X}\,^2\Sigma^+$',(28600,0.225),ha='center',color='k',fontsize=14)
+plt.annotate(r'$\tilde{A}\,^2\Pi$ $3^1_0$',(29250,0.225),ha='center',color='k',fontsize=14)
+plt.plot((27320,31000),(0.215,0.215),color='k')
+plt.plot((27320,27320),(0.22,0.21),color='k')
+plt.plot((28060,28060),(0.22,0.21),color='k')
+plt.plot((28960,28960),(0.22,0.21),color='k')
+plt.plot((29620,29620),(0.22,0.21),color='k')
+
+plt.annotate('a', (27460,0.181), ha = 'center', color='k', fontsize=12)
+plt.annotate('b', (27565,0.105), ha = 'center', color='k', fontsize=12)
+plt.annotate('c', (27642,0.080), ha = 'center', color='k', fontsize=12)
+plt.annotate('d', (27851,0.114), ha = 'center', color='k', fontsize=12)
+plt.annotate('e', (27941,0.167), ha = 'center', color='k', fontsize=12)
+plt.annotate('f', (28200,0.025), ha = 'center', color='k', fontsize=12)
+plt.annotate('g', (28349,0.035), ha = 'center', color='k', fontsize=12)
+plt.annotate('h', (28423,0.044), ha = 'center', color='k', fontsize=12)
+plt.annotate('i', (28562,0.031), ha = 'center', color='k', fontsize=12)
+plt.annotate('j', (28714,0.047), ha = 'center', color='k', fontsize=12)
+plt.annotate('k', (28834,0.048), ha = 'center', color='k', fontsize=12)
+plt.annotate('l', (29049,0.085), ha = 'center', color='k', fontsize=12)
[…]

### 2022-05-05 testC2H/scripts/Fig9-C2H-slices.py

@@ -1,0 +1,83 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.image as image
+
+width = 3.487
+height = 2*width/1.4
+one_col = (2*width, 2*height)
+
+x1, y1 = np.loadtxt("C2H-6S1CMbI1024PESBE.dat", unpack=True)
+x2, y2  = np.loadtxt("C2H-6S1CMI512PESBE.dat", unpack=True)
+x3, y3  = np.loadtxt("C2H-6S1CMI512Am0Ax30PESBE.dat", unpack=True)
+x4, y4  = np.loadtxt("C2H-6S1CMI512Am60Ax90PESBE.dat", unpack=True)
+VMI1 = np.loadtxt("C2H-12D1CMb512.txt")
+VMI2 = np.loadtxt("C2D-22M1CM1024.txt")
+
+fig=plt.figure(figsize=one_col)
+ax1 = plt.subplot(211)
+ax2 = plt.subplot(212, sharex=ax1)
+
+ax1.plot(x1,y1,color='k')
+ax2.plot(x2,y2*3.2,color='k',label='512x512 PES')
+ax2.plot(x3,y3*3,color='C2',label = r'$\theta=0^{\circ}-30^{\circ}$')
+ax2.plot(x4,y4,color='C0',label=r'$\theta=60^{\circ}-90^{\circ}$')
+
+ax1.annotate('a', (27460,0.181), ha = 'center', color='k', fontsize=12)
+ax1.annotate('b', (27565,0.105), ha = 'center', color='k', fontsize=12)
+ax1.annotate('c', (27642,0.080), ha = 'center', color='k', fontsize=12)
+ax1.annotate('d', (27851,0.114), ha = 'center', color='k', fontsize=12)
+ax1.annotate('e', (27941,0.167), ha = 'center', color='k', fontsize=12)
+ax1.annotate('f', (28200,0.025), ha = 'center', color='k', fontsize=12)
+ax1.annotate('g', (28349,0.035), ha = 'center', color='k', fontsize=12)
+ax1.annotate('h', (28423,0.044), ha = 'center', color='k', fontsize=12)
+ax1.annotate('i', (28562,0.031), ha = 'center', color='k', fontsize=12)
+ax1.annotate('j', (28714,0.047), ha = 'center', color='k', fontsize=12)
+ax1.annotate('k', (28834,0.048), ha = 'center', color='k', fontsize=12)
[…]

### 2022-05-05 testC2H/scripts/SM-C2D.py

@@ -1,0 +1,77 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+fn1 = '../C2D.dat'
+fn2 = '../C2D-355nm.dat'
+fn3 = '../C2D.dat'
+
+EA = 23956.4+36.4
+ofs = 1220
+#ofs = 1500+36
+ofs = 1030.3352249+50
+cut = 4534
+cut = 3471
+#cut = 100000
+
+
+b,a = np.loadtxt(fn1,usecols=(1,2),unpack=True)
+d,c = np.loadtxt(fn3,usecols=(1,2),unpack=True)
+x,y = np.loadtxt(fn2,unpack=True)
+
+x = x#-EA
+
+#Plotting Settings
+width = 3.487*2
+height = width/1.4
+one_col = (width,height)
+fig,ax = plt.subplots(figsize=one_col)
+
+
+for i in range(0,np.size(c)):
+    aa = c[i]
+    if c[i] > cut:
+        aa = c[i]-ofs
+#    plt.plot((aa,aa),(0,-d[i]),'w',lw='2.5')
+#    plt.plot((aa,aa),(0,-d[i]),'C0',lw='1.5')
+
+plt.plot(x,y,'k',label=r'C$_2$D$^-$ PES')
+plt.xlim(23000,28400)
+
+#plt.plot((0,0),(0,0),'C0',label=r'$\Sigma$ Symmetry')
+#plt.plot((0,0),(0,0),'C1',label=r'$\Pi$ Symmetry')
+#plt.legend(loc=9,fontsize=10,frameon=False)
+
+ax.spines['top'].set_visible(False)
+ax.spines['left'].set_visible(False)
+ax.spines['right'].set_visible(False)
+
+plt.yticks([])
+plt.xticks([23000,24000,25000,26000,27000,28000])
+ax.set_xticklabels(['23000','24000','25000','26000','27000','28000'],fontsize=14)
+plt.minorticks_on()
+plt.xlabel('Excitation Energy (cm$^{-1}$)',fontsize=14)
+ax.tick_params(width=1.5)
+plt.setp(ax.spines.values(), linewidth=1.5)
+
+
+#Annotating spectrum
+plt.annotate(r'$\tilde{X}$ $^2\Sigma^+$',(400+EA,0.975),ha='center',fontsize=14)
+plt.annotate(r'$\tilde{A}$ $^2\Pi$',(3300+EA,0.58),ha='center',fontsize=14)
[…]

### 2022-06-24 Resubmission/ResponseLetter.tex
update resubmission

\documentclass[a4paper,12pt]{letter}
\usepackage{fancyhdr,color,graphicx,afterpage,enumitem}
\usepackage[top=50mm,head=40mm,bottom=40mm,foot=30mm,left=20mm,right=20mm]{geometry}
\usepackage{tabularx}
\usepackage{sansmathfonts}
\usepackage[scaled]{helvet}
\renewcommand\familydefault{\sfdefault} 
\usepackage[T1]{fontenc}
\renewcommand{\headrule}{
\vskip-13ex \hrule width\headwidth height\headrulewidth \vskip-\headrulewidth}
%== adjust line position -13.ex by trial an error, if # of lines in 
%== the header boxes below is changed 
\rhead{
 \begin{minipage}[t]{.4\textwidth}
  \raggedleft
   \includegraphics[width=.5\textwidth]{unsw}\vspace*{1ex}\ \\
   \begin{footnotesize}
   \begin{sf}
   \begin{tabular}{l@{\ :\ }l}
    T& +61 2 9065 4259\\
    E& B.Laws@unsw.edu.au\\
    \multicolumn{2}{l}{research.unsw.edu.au/people/dr-ben-laws}
   \end{tabular}
  \end{sf}
  \end{footnotesize}
 \end{minipage}
}
\lhead{
 \begin{minipage}[t]{.6\textwidth}
  \begin{footnotesize}
  \begin{sf}
  \raggedright
  {\textsc\textbf{UNSW FACULTY OF SCIENCE}}
  \vspace*{2ex}\ \\
          \textbf{Dr Benjamin A. Laws}\\
          Postdoctoral Fellow\\
          Molecular Photonics Laboratories\\
          School of Chemistry\\
          The University of New South Wales\\
          Sydney NSW 2052 Australia\\
  \end{sf}
  \end{footnotesize}
 \end{minipage}
}
\cfoot{}
\lfoot{}
\rfoot{}
\setlength{\parskip}{1em}
\pagestyle{plain}
% =============== Add your input below =================================
\address{\vspace*{-5ex}\ \\
} 
\signature{\sf \vspace*{-8ex}Dr Benjamin A. Laws.}
\begin{document}
\begin{sf}
%\date{ }                  % comment this line to specify today's date
\begin{letter}{%
Prof. Xueming Yang\\
The Journal of Chemical Physics
}
\opening{Dear Editor,}
\thispagestyle{fancy}

The following manuscript was submitted on 23rd May 2022 to be considered for publication in
The Journal of Chemical Physics:

\begin{tabularx}{.95\textwidth}{ll}
	Title: & \hspace*{.4em}\mbox{\it Velocity-Map Imaging Spectroscopy of C$_2$H$^-$ and C$_2$D$^-$: a benchmark study} \\ & \hspace*{.4em}\mbox{\it of vibronic coupling interactions}\\
\end{tabularx}

\vspace*{-5ex}\ \\

Thank you for considering our work for publication in The Journal of Chemical Physics. We would also like to thank the reviewers for their positive and constructive feedback. We have made all of the requested changes to our manuscript based on the reviewers comments, as outlined below. The key changes have been to reorder the structure of the manuscript, as requested by Reviewer \#2, to highlight the new and important results from this work. We have also included Dyson orbital calculations as requested by Reviewer \#1 to enhance our discussion of the photoelectron anisotropies.

Below are our responses to the comments made by each Reviewer:

\begin{verbatim}
----------------------------------------------------------------------
Reviewer #1  
----------------------------------------------------------------------
\end{verbatim}
\vspace*{-2ex}
\emph{This is a nice study illustrating spectroscopic signatures of vibronic couplings in photodetachment spectroscopy. The experiment is carefully analyzed and supported by high-level electronic structure calculations. The paper is well written and suitable to the JCP readership. The agreement between theory and experiment is inspiring!}

\emph{I have only minor optimal suggestions:}

\emph{1. I would comment on recent photodetachment studies of isolelectronic (or similar) species, i.e., CN- and CH2CN- by Mabbs and coworkers.}

The paper on the photoelectron anisotropy of isoelectronic CN$^-$ by Mabbs and coworkers is now cited on page 18 of the manuscript. We comment on the similarities between C$_2$H$^-$ and CN$^-$ with the statement `This makes the near threshold anisotropy behaviour highly sensitive to the exact amount of $p$ orbital character included in the orbital, an effect that has also been observed in NO$_2^-$ and the isoelectronic CN$^-$.'

\emph{2. To illustrate the nature of the electronic states, it would be useful to add a figure with the respective Dyson orbitals, such as those from Ref. 66 (can even borrow the figure from this work). The orbitals will be particularly relevant for the discussion of PADs on pages 15-16. 	Also, the authors may want to comment that relative positions of Sigma and Pi states depend on the chain length. This has been extensively discussed for the isolectronic HCxN- species.}

We have included new Dyson orbital calculations, with the Dyson orbitals representing each transition now included in Figure 5 on page 17. We have added a discussion of these orbitals on page 17-18. `The Dyson orbital representation of the C$_2$H$^-$ $\tilde{X}^1\Sigma^+\rightarrow\tilde{X}^2\Sigma^+$ transition, calculated at the EOM-CCSD/aug-cc-pVTZ level, is shown in Fig.5(b)' $\dots$ `the cylindrical symmetry of the molecule introduces some $p$ character into the predominantly $s-$like Dyson orbital (Fig.~5(b)) which becomes significant near threshold due to the centrifugal detachment barrier.'

The relative position of Sigma and Pi states for different chain lengths is discussed in the introduction on page 3: `In C$_4$H the $^2\Sigma^+$ and $^2\Pi$ states are nearly degenerate, resulting in even stronger coupling, while in C$_6$H and C$_8$H the ordering of the states swaps, with a ground $^2\Pi$ state and a low lying excited $^2\Sigma^+$ state.'

\emph{3. Line above Eq. 2: do you mean CH4- or is it a typo?}

This should be C$_4$H$^-$. We have included a space between the $^-$ and the following citation to make this clear.

\emph{4. Comp. details and below (e.g., p.14): please specify that it is EOM-IP-CCSDT with closed-shell anionic reference that was used and say a few words why it is a good method. Also, please specify which level of excitation was used in the EOM part -- 1h and 2h1p or also 3h2p. Also, adding a coupe of references to EOM theory would be useful for the readers.}

We have included these details on page 6: `The equation-of-motion ionised-potential coupled-cluster singles, doubles, and triples (EOM-IP-CCSDT) level of theory with an atomic natural orbital basis set of quadruple-zeta quality (ANO2) was used on a closed-shell anionic reference to perform geometry optimisations and frequency calculations (including 1h + 2h1p + 3h2p excitations).'

We have also added a statement on why EOM is a good method for this problem, along with references on EOM theory: `EOM is a highly accurate and robust framework that provides access to different types of target electronic states, including ionised states, making it well suited to the study of photodetachment.' (J. Chem Phys. {\bf154} 114115 (2021), J. Chem. Theory Comput. {\bf18} 1748 (2022), and Rev. Mod. Phys. {\bf79} 291 (2007))

\emph{5. Page 9 'introduced' or 'developed' would be a better word than 'advocated'.}

We have replaced the word `advocated' with `introduced' on page 7.

\emph{6. Discussion of s\&p model can be enhanced by calculating beta from the respective Dyson orbitals.}

We have included new Dyson orbital calculations, with the resulting anisotropy curves included in Figure 5 on page 17. These results are discussed alongside the s\&p model on page 18: `The corresponding anisotropy curve was calculated using ezDyson software, and is shown in blue in Fig.~5(a) alongside the experimental data. Figure~5 shows that above threshold there is excellent agreement between the experimental anisotropies, the mixed $sp$ model (Eq.~11), and the calculated anisotropies (Eq.~14)' $\dots$ `Again the calculated anisotropy curve (shown in orange in Fig.~5(a)) appears a good match to the $sp$ model (Eq.~11) and the experimental data, however it underestimates the amount of $s$ orbital character.'

\emph{7. I understand the vibronic Hamiltonian part and state mixing, but it was no clear how electronic factors entering the photodetachment cross-sections were computed. Did the authors used Dyson orbitals and plane waves? Please clarify. Also, a brief explanation of what xsim module of CFOUR does.}

In this simulation the transition moment of the two ionisation processes are assumed to be equal, they are not calculated from the Dyson orbitals. We have added this explanation along with a description of the xsim module on page 10: `The xsim module projects the Hamiltonian (Eq.~5) onto a vibrational basis, which is then diagonalised using Lanczos algorithm to calculate transition energies and intensities that map to the measured photoelectron spectrum. In this simulation the transition moments for the two ionisation processes are assumed to be equal.'

\emph{8. I am confused how Fig. 5 was generated. Some explanations are needed.}

Figure 5 includes the experimental anisotropy parameters, for each prominent transition and at each wavelength measured. Each data point is obtained by plotting the integrated radial intensity of each peak against P$_2(\cos\theta)$ for 5$^\circ$ slices around the velocity-mapped image. This explanation is now included on page 16: `For each prominent transition in the photoelectron spectrum of C$_2$H$^-$ in Fig.~1 the corresponding anisotropy parameter may be calculated by fitting Eq.~(10) to a plot of the integrated radial intensity (across the peak) versus angle, as (for a single quadrant of the electron image) the intensity variation is linear in $P_2(\cos\theta)$ with a slope equal to $\beta\times$intercept.'
\vspace*{1ex}
\begin{verbatim}
----------------------------------------------------------------------
Reviewer #2  
----------------------------------------------------------------------
\end{verbatim}
\vspace*{-2ex}
\emph{The work by Laws and coworkers has some highly-useful results for the classification of the problematic C2H radical's vibronic spectrum. The agreement between theory and experiment is exceptional. Hence, the science is sound, but I have some concerns about the presentation. Most notably, the paper is thin on discussion of results unique to this work. I have outlined this in more detail below, there are really only 2ish pages (out of 18) with useful discussion about the novel results from this study. Yes, this molecule has been examined in detail for years, but the new data have vital information in there that is not clearly communicated. Frankly, the entire purpose of the manuscript is summarized with Figure 4. I strongly support the science, but the sophomoric writing needs to be tightened up for this to be publishable.}

We have restructured the manuscript based on the comments from Reviewer \#2 below. We have tightened up the writing as suggested, to focus on the new results arising from this work. This includes expanding on the discussion on the electron anisotropy (pages 16-18) following from  recommendations by Reviewer \#1.

\emph{The abstract contents are poor. It gives no data about what was learned only about what was done. It's methodology and not results. Ultimately, the most important findings need to be what the abstract gives the reader.}

This is a good point. We have rewritten the abstract to discuss the key results from this work instead of the methodology: `High-resolution velocity-map imaged photoelectron spectra of the ethynyl anions C$_2$H$^-$ and C$_2$D$^-$ are measured at photon wavelengths between $355-266$~nm, to investigate the complex interactions between the close lying $\tilde{X} ^2\Sigma^+$ and $\tilde{A} ^2\Pi$ electronic states. An indicative kinetic energy resolution of 0.4\%, together with full angular dependence of the fast electrons, provides a detailed description of the vibronically coupled structure. It is demonstrated that a modest quadratic vibronic coupling model, parametrized by the quasidiabatic ansatz, is sufficient to accurately recreate all of the observed vibronic interactions. Simulated spectra are shown to be in excellent agreement with the experimental data, verifying the proposed model, providing a framework that may be used to accurately simulate spectra of larger C$_{2n}$H monohydride carbon chains. New spectral assignments are supported by experimental electron anisotropy measurements and Dyson orbital calculations.'

\emph{The authors should also note that C2H is one of the most abundant molecules observed in the ISM or CSM.}

This statement is included on page 3: `C$_2$H is reported to be one of the most abundant molecules in the ISM, and is the most thoroughly studied of the C$_{2n}$H species.'

\emph{There are a few typos in the text such as the following sentence on p. 6: "Below 27,000 cm-1 binding energy, corresponding to the X $^2\Sigma^+$ surface ,the C2H-". There should be a "the" in front of 27,000 and the comma should be shifted in "surface, the" towards the end. On p. 7, "is the quanta of bending excitation" should be either "are the quanta" or "is the quantum" not the mixed form currently given. In the sentence immediately after, "however" is not a conjunction but should be used to start a new sentence. Additionally, the tab spacing after equations should be removed as these are not new paragraphs, not even new sentences. Top of p. 15, "Applying this approach to similar systems will produce reliable predictions. . ." should be "will likely produce. . ." Also, remove the comma before the and as the following text in that sentence is a phrase and not a clause. Remove the comma in the first sentence of Section IV. Also, remove the comma on p. 18 in the sentence "Photoelectron anisotropy parameters were also measured for dominant transitions, at a range of wavelengths."}

All of the above typos have been fixed.

\emph{Section III is arranged strangely. The first subsection is largely a rehash of the experimental methodology with a mention of what the spectrum looks like. Section III.A does not introduce any new information but is a restatement of what is already known about C2H and is more fitting for the introduction. Section III.B has a few results sprinkled in, but this is more computational and theoretical approach explanations. Besides Figure 1 and Table 1, there are almost no results given in Section III until the first full paragraph of p. 12.}

We have made all of the restructuring recommendations above, which has helped tighten up the writing and put the emphasis back onto the new results. The first subsection of III has been removed from the Results, and combined with a condensed description of the experimental methodology on page 5.

Section III.A has been moved to the introduction on page 3 and integrated into the literature review. This is preceded by the new statement: `Zhou~\emph{et al.} measured photodetachment of C$_2$H$^-$ and C$_2$D$^-$ to both the $\tilde{X} ^2\Sigma^+$ and $\tilde{A} ^2\Pi$ surfaces using slow electron velocity-map imaging (SEVI), which revealed detailed structure around the $\tilde{A} ^2\Pi$ state origin. Comparison with calculations by Tarroni and Carter resulted in detailed spectral assignments, however this was limited by the suppression of $p-$wave structure near threshold.' These changes help define what work has previously been done.

The first 3 paragraphs of Section III.B have been moved to the Methods section, to describe the theory behind the quasidiabatic ansatz. This allows the section on vibronic coupling calculations in the Results and Analysis to go directly into the parametrization, and the new values calculated in this work (Table 1). This helps put the focus back on the new results from this work.

Due to the recommended changes from Reviewer \#2 the first results from this work are now given in the first paragraph of the Results and Analysis section. This restructuring has helped make a clear distinction between the past work, and the unique results from this study.

\emph{Additionally, this paragraph (first full on p. 12) does little to tie the experimental and computational results together in a tangible way. I don't disagree with any of the statements, but they do not reference data that the reader can easily find in order to verify the statements given. This should be cleaned up. The same is true for the next paragraph after involving C2D-.}

These paragraphs have been rewritten to link the discussion back to the data/figures, so the reader can follow the discussion more clearly. The discussion of each feature (pages 12-13) now includes a reference to the corresponding figure, with detail on what part of the spectrum is being analysed. For example: `Figure~3(a) shows excellent agreement in both the transition positions and intensities between the calculated and experimental C$_2$H$^-$ photodetachment spectra on the $\tilde{X} ^2\Sigma^+$ surface, below $3,600~$cm$^{-1}$.' $\dots$ `Near the excited state surface (peaks $a-e$ in Fig.~3(a)) the experimental data shows that the electronic coupling interactions induce a splitting of the $\tilde{A} ^2\Pi$ state origin over 5 vibronic levels, spaced by $\sim 95~$cm$^{-1}$. This splitting is also observed in the calculated spectrum, which reproduces the 5 prominent transitions in this region. Fig.~3(a) shows that the relative intensities between the calculated transitions near $3,700~$cm$^{-1}$ are also in agreement with the experimental data.' $\dots$ `This is supported by the reduction in the calculated coupling constants $\lambda$ and $\eta$ for C$_2$D$^-$ in Table~1.'

\emph{The third full paragraph on p. 12 also has necessary data but no means of pointing the reader to where they may be able to verify these statements through either tables or figures. This connection must be given.}

Similar changes have been made to this paragraph (page 13) to link the discussion back to the results/figures: `The calculated transitions in Fig.~3(b) reproduce the large change observed experimentally for the deuterated species. The calculated intensity pattern of the vibronic levels around the $\tilde{A} ^2\Pi$ origin also mirrors the experimental data, with a single intense transition observed near peak $e$, and 3 prominent transitions predicted around the experimental peaks $a-d$.' Similar edits have been made throughout the transcript to ensure that the discussion of results is always linked back to the data and figures.

\emph{Along this same vein, why are the data then rehashed on pp. 13-14 with new figures? This seems redundant or confusing.}

We have separated Figure 3 (page 12) and Figure 4 (page 15) into separate subsections, to clarify the different information each figure portrays. Figure 3 shows the individual calculated transitions and their corresponding vibronic symmetry. This is compared to photoelectron spectra at 355~nm, close to the $\tilde{A} ^2\Pi$ origin, where high velocity resolution may be obtained. This is important for discussing the vibronic interactions, and for comparison to the electron anisotropy in section III.C. Figure 4 shows a simulated spectrum (convolved with Gaussian functions) of the excited vibronic levels of the $\tilde{A} ^2\Pi$ state. This is compared to a photoelectron spectrum at 266~nm, where more of the $\tilde{A} ^2\Pi$ surface is accessible, at the cost of lower energy resolution. This is important, to highlight the vibronic splitting also occurs away from the origin (ie the $3^1_0$ band). Showing the convolved spectrum also highlights that the discrepancies between the experiment and model are negligible compared to the experimental resolution, confirming that the accuracy of the QVC model is sufficient for direct comparisons to experimental and astronomical data.

We have included statements on page 14 to highlight these points, including: `Photodetachment at 266~nm (4.66~eV) maps out more of the $\tilde{A} ^2\Pi$ potential energy surface, at the cost of lower electron velocity resolution.' $\dots$ `By showing the convolved spectrum, the suitability of the QVC model to simulate spectra capable of direct comparison to experimental or astronomical data can be examined.' 
\vspace*{-2ex}
\begin{verbatim}
----------------------------------------------------------------------
Reviewer #3  
----------------------------------------------------------------------
\end{verbatim}
\vspace*{-2ex}
\emph{This work presents a study of C2H and C2D via photodetachment of the associated anions. These are important astophysical species but represent a spectroscopic challenge with their attendant Herzberg-Teller coupling making simple harmonic assignment impractical. The interaction between the neutral sigma and pi states also represents a challenge for theory and therefore full understanding of spectra.
	The authors present a very nice, combined theoretical and experimental study which (in addition to everything else) represents how science is supposed to work. The spectra are well presented, at good resolution (for photoelectron spectroscopy) and the simulations (at a high level of theory) nicely explain/highlight the effect of the HT coupling. The work is supported by an analysis of the photoelectron angular distributions associated with each transition, vindicating the spectral assignments.
	Overall this is a very nice piece of work which will be an important contribution - it should be published as is (and forthwith)}

We thank Reviewer \#3 for their comments.

\vspace*{-2ex}\ \\ 
\textbf{Statement}\\[.5ex]
This manuscript is not being considered by any other journal.

%\closing{Regards,\\
\   
\includegraphics[width=.2\textwidth,clip]{signatureXX}
               \closing{Regards,}
\end{letter}
\end{sf}
\end{document}

### 2022-06-24 C2Hpaper.tex
update resubmission

@@
 \affiliation{School of Chemistry, University of New South Wales, Sydney NSW 2052, Australia}
-\author{Andrei M. Sanov}
+\author{Andrei Sanov}
 \affiliation{Department of Chemistry and Biochemistry, The University of Arizona, Tucson, Arizona 85721, United States}
@@
 High-resolution velocity map imaged photoelectron spectra of the ethynyl anions C$_2$H$^-$ and C$_2$D$^-$ are measured over a range of photodetachment wavelengths, to investigate the complex interactions between the close lying $\tilde{X}^2\Sigma^+$ and $\tilde{A}^2\Pi$ electronic states.
-Vibronic coupling calculations are performed by transforming to a quasidiabatic representation, parametrised by \emph{ab-initio} CFOUR calculations, to model the interplay between psuedo Jahn-Teller and Renner-Teller coupling.
+Vibronic coupling calculations are performed by transforming to a quasidiabatic representation, parametrised by \emph{ab-initio} CFOUR calculations, to model the interplay between pseudo Jahn-Teller and Renner-Teller coupling.
 This approach is combined with electron anisotropy measurements to assign all of the observed vibronic structure, providing a framework that may be used to accurately simulate spectra of larger C$_{2n}$H monohydride carbon chains.
@@
 
-Chain growth of the C$_{2n}$H radicals occurs predominately through acetylene addition,
+Chain growth of the C$_{2n}$H radicals occurs predominately through acetylene addition,~\cite{wil03}
 \begin{equation}
@@
 Conversely, the formation of anions in space is believed to be driven by radiative electron attachment, charge transfer, and dissociative electron attachment.
-Current astrochemical modelling of interstellar clouds, such as IRC+1026, typically underestimate the observed abundances of CH$_4^-$~\cite{mil17,cor13,her08}.
+Current astrochemical modelling of interstellar clouds, such as IRC+10216, typically underestimate the observed abundances of CH$_4^-$~\cite{mil17,cor13,her08}.
 Therefore, it has been proposed that ion-neutral reactions
@@
 However for some species, particularly those with low abundances or no dipole moment, UV/vis spectroscopic methods are required for identification~\cite{mai97}.
-This creates a challenge for theory, as electronic spectra calculations are more difficult than those employed for pure rotational spectra~\cite{for10}.
+This creates a challenge for theory, as electronic spectral calculations are more difficult than those employed for pure rotational spectra~\cite{for10}.
 This becomes even more challenging when vibronic coupling effects are introduced, as they can be exceedingly difficult to model.
@@
 The interaction of these surfaces produces a complex vibronic spectrum around the $\tilde{A}^2\Pi$ state, where the $\tilde{X}-\tilde{A}$ origin is spread over multiple admixed vibronic levels.
-In C$_4$H the $^2\Sigma^+$ and $^2\Pi$ states are nearly degenerate, resulting in even stronger coupling~\cite{zho07}, while in C$_6$H and C$_8$H the ordering of the states swaps, with a ground $^2\Pi$ state and a low lying excited $^2\Sigma^+$ state~\cite{lin99,tay98}.
+In C$_4$H the $^2\Sigma^+$ and $^2\Pi$ states are nearly degenerate, resulting in even stronger coupling~\cite{zho07b}, while in C$_6$H and C$_8$H the ordering of the states swaps, with a ground $^2\Pi$ state and a low lying excited $^2\Sigma^+$ state~\cite{lin99,tay98}.
 Consequently, understanding the vibronic coupling interactions between the $^2\Sigma^+$ and $^2\Pi$ surfaces is essential in order to accurately model the role these radicals (and their corresponding anions) are likely to play in the interstellar chemistry discussed above, and to guide the search for possible DIB carriers.
@@
 C$_2$H is reported to be one of the most abundant molecules in the universe, and is the most thoroughly studied of the C$_{2n}$H species~\cite{wil91,hei99,for10}.
-Many different experimental techniques have been employed to help understand the complexities of the vibronic spectrum, including electron spin resonance~\cite{coc64,jin85}, laser magnetic resonance~\cite{bro88,pfe96,sch98}, microwave and milli-meter wave spectroscopy~\cite{sas81,got83,end89,mul00}, infrared (matrix isolation~\cite{she87,jac87,for95} and Fourier Transform emission~\cite{ver88}) spectroscopy, laser induced fluorescence spectroscopy~\cite{hsu93,hsu95,chi99} and photoelectron spectroscopy of the negative ion~\cite{erv91,tay98,zho07}.
+Many different experimental techniques have been employed to help understand the complexities of the vibronic spectrum, including electron spin resonance~\cite{coc64,jin85}, laser magnetic resonance~\cite{bro88,pfe96,sch98}, microwave and millimeter wave spectroscopy~\cite{sas81,got83,end89,mul00}, infrared (matrix isolation~\cite{she87,jac87,for95} and Fourier Transform emission~\cite{ver88}) spectroscopy, laser induced fluorescence spectroscopy~\cite{hsu93,hsu95,chi99} and photoelectron spectroscopy of the negative ion~\cite{erv91,tay98,zho07}.
 C$_2$H has also received extensive theoretical attention to interpret the experimental results, however the large number of possible vibronic levels means this has proven to be a challenge~\cite{per90,per91,per91b,per91c,per92,car00,tar03,tar04,for10,sta21,gul21}.
 In this work we demonstrate how the construction of a quasidiabatic Hamiltonian allows the strength of vibronic interactions between coupled surfaces near a conical intersection to be estimated, sufficient to accurately simulate electronic and vibronic spectra.
+%The quadratic vibronic coupling model employed can be readily scaled to larger molecules (such as longer C$_n$H chains) which quickly become too complex to study using full variational approaches.
 Anion HR-PEI spectroscopy maps both of the $^2\Sigma^+$ and $^2\Pi$ surfaces on an equal footing from the anion $\tilde{X}^1\Sigma^+$ state, allowing a direct comparison with \emph{ab-initio} modelling.
+%The electron anisotropy allows transitions with $\sigma$ and $\pi$ symmetry to be distinguished, providing definitive assignments of calculated transitions.
 
 \section{Results and Analysis}
-Ethynyl ions were produced in a pulsed-jet discharge of pure C$_2$H$_4$ gas, and subsequently mass isolated via time of flight.
-Electrons were detached using a tuneable Continuum Sunlite Ex Optical Parametric Oscillator (OPO) pumped with the third harmonic of a Nd:YAG laser.
-Higher electron counts were also obtained with the direct use of the third and fourth harmonics of the Nd:YAG laser.
+Ethynyl ions were produced in a pulsed-jet discharge of pure ethylene (C$_2$H$_4$) gas, and subsequently mass isolated via time of flight.
+Electrons were detached using a tuneable Continuum Sunlite Ex Optical Parametric Oscillator (OPO) pumped with the third harmonic (355~nm) of a Nd:YAG laser.
+Higher electron counts were also obtained with the direct use of the third and fourth harmonics (266~nm) of the Nd:YAG laser.
 Detached electrons are mapped onto a micro channel plate detector using a Velocity Map Imaging (VMI) lens.
@@
 The electrons are distributed radially according to their speed, with slow electrons near the image center, and fast electrons located towards the outer edge.
-Due to the relatively large C$_2$H electron affinity (EA) of 2.969~eV~\cite{erv91}, photodetachment at 355~nm occurs close to threshold.
-This yields slow electrons, allowing the use of a low repeller voltage ($-600$~V) for the VMI lens, to spread the electron velocity distribution across the whole detector, giving high velocity resolution.
+Due to the relatively large C$_2$H electron affinity (EA) of 2.969~eV~\cite{erv91}, photodetachment at 355~nm produces photoelectrons with small (< 0.5~eV) kinetic energies.
+These slow electrons allow the use of a low repeller voltage ($-600$~V) for the VMI lens, spreading the electron velocity distribution across the whole detector to give a high electron velocity resolution.
 
-Despite the photodetachment being close to threshold, two electronic states of neutral C$_2$H are observed.
-The faster electrons on the outer edge correspond to C$_2$H$(\tilde{X}\,^2\Sigma^+)+e^- \leftarrow $C$_2$H$^-(\tilde{X}\,^1\Sigma^+)+h\nu$ photodetachment, and these are preferentially distributed around the poles of the image, indicative of a positive anisotropy parameter.
-Conversely the angular distribution of the slower electrons near the center are skewed towards the equator, indicative of a negative anisotropy parameter.
+Despite the photodetachment energy being close to threshold, two electronic states of neutral C$_2$H are observed.
+The faster electrons, on the outer edge, correspond to C$_2$H$(\tilde{X}\,^2\Sigma^+)+e^- \leftarrow $C$_2$H$^-(\tilde{X}\,^1\Sigma^+)+h\nu$ photodetachment, and these are preferentially distributed around the poles of the image, indicative of a positive anisotropy parameter.
+Conversely the angular distribution of the slower electrons near the center is skewed towards the equator, indicative of a negative anisotropy parameter~\cite{buc70}.
 These electrons may be assigned to photodetachment to the first excited state C$_2$H$(\tilde{A}\,^2\Pi)+e^- \leftarrow $C$_2$H$^-(\tilde{X}\,^1\Sigma^+)+h\nu$.
@@
 	\includegraphics[width=0.8\textwidth]{figures/Fig1}
-	\caption{(a) Velocity map image of C$_2$H$^-$ photodetachment at 355~nm.
+	\caption{(a) Velocity map image of electrons from C$_2$H$^-$ photodetachment at 355~nm.
 (b) Velocity map image of C$_2$D$^-$ at 355~nm.
 Both images contain $\sim4$ million electrons.
-(c) Comparison of 355~nm photoelectron spectra from C$_2$H$^-$ and C$_2$D$^-$.
-Structure below $\sim 27,000~$cm$^{-1}$ is associated with the ground state $\tilde{X} ^2\Sigma^+$, while structure above  $\sim 27,000~$cm$^{-1}$ is due to the excited neutral $\tilde{A} ^2\Pi$ state.}
+(c) Comparison of the corresponding 355~nm photoelectron spectra for C$_2$H$^-$ and C$_2$D$^-$.
+Structure below $\sim 27,000~$cm$^{-1}$ is associated with the ground state $\tilde{X} ^2\Sigma^+$, while structure above  $\sim 27,000~$cm$^{-1}$ is largely due to the excited neutral $\tilde{A} ^2\Pi$ state.}
 	\label{fig:1}
@@
 To investigate the vibronic coupling interaction between these two nearby $\Sigma^+$ and $\Pi$ surfaces, deuterated ethynyl C$_2$D$^-$ was also studied.
-The C$_2$D$^-$ ions were produced in a discharge of pure C$_2$D$_4$ gas and measured under the same experimental conditions as for C$_2$H$^-$.
-An illustrative VMI of photodetachment at 355~nm from C$_2$D$^-$ is shown in Fig.~\ref{fig:1}(b).
+The C$_2$D$^-$ ions were produced in a discharge of pure C$_2$D$_4$ gas and measurements were performed under the same experimental conditions as those for C$_2$H$^-$.
+An illustrative velocity-map image of photodetachment at 355~nm from C$_2$D$^-$ is shown in Fig.~\ref{fig:1}(b).
 Similarly to Fig~\ref{fig:1}(a) two electronic transitions are observed.
-While the fast electrons appear similar in both images, a striking difference is observed in the slow electrons near the detector center.
+While the distribution of fast electrons is similar in both images, a striking difference is observed for the slow electrons, near the detector center.
 In Fig.~\ref{fig:1}(a) a series of weak rings are observed, however in Fig.~\ref{fig:1}(b) the image is dominated by two distinct rings.
 
-The VMIs in Fig.~\ref{fig:1} were inverted using the Abel inversion methods detailed in PyAbel~\cite{hic19}, to extract the corresponding photoelectron spectra presented in Fig.~\ref{fig:1}(c).
-Below $27,000~$cm$^{-1}$ on the $\tilde{X} ^2\Sigma^+$ surface the C$_2$H$^-$ and C$_2$D$^-$ spectra are similar in structure.
+The velocity-map images of Fig.~\ref{fig:1} were inverted using the Abel inversion methods detailed in PyAbel~\cite{hic19} to extract the corresponding photoelectron spectra, presented in Fig.~\ref{fig:1}(c).
+Below $27,000~$cm$^{-1}$ binding energy, corresponding to the $\tilde{X} ^2\Sigma^+$ surface ,the C$_2$H$^-$ and C$_2$D$^-$ spectra are similar in structure.
 Both are dominated by the origin transition, shifted by $\sim10~$cm$^{-1}$ in the deuterated spectrum, with progressions involving the v$_2$($\pi$) bending and v$_3$($\sigma$) CC stretch vibrational normal modes.
-This structure includes transitions involving an odd quanta of v$_2$ bending excitation ($2^{n+1}$) which should be totally forbidden within the Franck-Condon approximation.
-However, the presence of these transitions in the spectra is an indicator of Herzberg-Teller (HT) vibronic coupling between the ground $^2\Sigma^+$ and nearby excited $^2\Pi$ electronic surfaces, as
+This structure also includes transitions involving an odd quanta of v$_2$ bending excitation ($2^{n+1}$) which are totally forbidden within the Franck-Condon approximation.
+The presence of these transitions in the spectra is an indicator of Herzberg-Teller (HT) vibronic coupling between the ground $^2\Sigma^+$ and nearby excited $^2\Pi$ electronic surfaces, as
 \begin{equation}
@@
 In the case of C$_2$H this is seen as coupling between the ground $\Sigma^+(1A')$ and excited $\Pi^+(2A')$ states, induced by the bending motion of $v_2$.
-The ground state only couples to one member of the Renner-Teller pair $\Pi^+(2A')$, as the other state $\Pi^-(1A'')$ has incorrect symmetry.
+The ground state only couples to one member of the Renner-Teller pair $\Pi^+(2A')$, as the other state $\Pi^-(1A'')$ has incompatible symmetry.
 This results in the complex vibronic structure observed for the $\tilde{A}^2\Pi$ electronic state, with contributions from three coupled surfaces $\Sigma^+(1A'),$ $\Pi^+(2A'),$ and $\Pi^-(1A'')$.
@@
 	\includegraphics[width=0.5\textwidth]{figures/Fig3}
-	\caption{Adiabatic potential energy surfaces of $\tilde{X}^2\Sigma^+$, $\tilde{A}^2\Pi^-$, and $\tilde{A}^2\Pi^+$ states, calculated using the parameters calculated by Tarroni and Carter~\cite{tar03} (E$_{1A'}$, E$_{2A'}$, and E$_{1A''}$ in Eq.~\ref{eq:teller3}).}
+	\caption{Adiabatic potential energy surfaces of $\tilde{X}^2\Sigma^+$, $\tilde{A}^2\Pi^-$, and $\tilde{A}^2\Pi^+$ states, calculated using the parameters calculated by Tarroni and Carter~\cite{tar03}.}
 	\label{fig:2}
@@
 
-The adiabatic potential energy surfaces in Figure~\ref{fig:2} were evaluated from the variational parameters of Tarroni and Carter~\cite{tar03}.
-Their technique calculates a multitude of admixed vibronic levels.
-In the literature, over 100 possible C$_2$H vibronic states have been calculated, up to 10,000~cm$^{-1}$ above the $\tilde{X} ^2\Sigma^+$ origin.
-However, assigning experimental spectra has remained a challenge, partly due to the large number of calculated levels providing multiple possible assignments for each experimentally observed transition.
+The adiabatic potential energy surfaces in Figure~\ref{fig:2} were evaluated from the variational parameters of Tarroni and Carter~\cite{tar03}, illustrating the loss of degeneracy for the doublet $\Pi$ surfaces, due to the Renner-Teller and pseudo Jahn-Teller interactions.
+This technique has been used to calculate a multitude of admixed vibronic levels.
+More than 100 possible C$_2$H vibronic states have been calculated, up to 10,000~cm$^{-1}$ above the $\tilde{X} ^2\Sigma^+$ origin.
+However, assigning experimental spectra has remained a challenge, partly due to the large number of calculated levels providing for multiple possible assignments for each experimentally observed transition.
 
 \subsection{Coupling Calculations}
-In order to guide spectral assignment of C$_2$H and astronomical searches for other C$_n$H radicals, transition intensities are also needed.
-However, due to the strong vibronic coupling interactions, this can not be obtained via simple Franck-Condon calculations based on quantum chemistry methods.
-To account for these interactions, the photoelectron spectrum of the C$_2$H$^-$ anion was simulated using a quasidiabatic Hamiltonian of the type advocated by Koeppel, Domcke and Cederbaum (KDC).~\cite{kou84,dom81} In this approach, the Hamiltonian is represented in a basis of quasidiabatic (slowly varying) electronic  states for which the kinetic energy operator can be assumed diagonal.~\cite{pac93} For C$_2$H, the KDC Hamiltonian comprises three states - the two components of the $^2\Pi$ state and the ground $^2\Sigma^+$ state - and is then projected onto a vibrational basis, usually chosen as a direct product of harmonic oscillators.
+In order to guide spectral assignment of C$_2$H and future astronomical searches for other C$_n$H radicals, transition intensities are also needed.
+However, due to the strong vibronic coupling interactions, transition intensities can not be obtained via simple Franck-Condon calculations based on quantum chemistry methods.
+To account for these interactions, the photoelectron spectrum of the C$_2$H$^-$ anion is simulated using a quasidiabatic Hamiltonian of the type advocated by Koeppel, Domcke and Cederbaum (KDC).~\cite{kou84,dom81} In this approach, the Hamiltonian is represented in a basis of quasidiabatic (slowly varying) electronic  states for which the kinetic energy operator can be assumed diagonal.~\cite{pac93} For C$_2$H, the KDC Hamiltonian comprises three states - the two components of the $^2\Pi$ state and the ground $^2\Sigma^+$ state - and is then projected onto a vibrational basis, usually chosen as a direct product of harmonic oscillators.
 Diagonalization of the corresponding matrix yields the molecular states (which are given in terms of a Born-Huang expansion), and the squared projections of the corresponding eigenvectors onto the ground state of the anion yield the relative intensities.
@@
 \begin{equation}
-\eta = \frac{1}{2}\left[ f_{2a2a}^{A(a')}-f_{2b2b}^{A(a'')}-\frac{2\lambda^2}{(\Delta_0^A-\Delta_0^X)}\right]
+\eta = \frac{1}{2}\left[ f_{2a2a}^{A(a')}-f_{2b2b}^{A(a')}-\frac{2\lambda^2}{(\Delta_0^A-\Delta_0^X)}\right]
 \label{eq:calc3}
@@
 The above method was employed to simulate the photoelectron spectrum of C$_2$H$^-$, with the calculated transitions shown in Figure~\ref{fig:3}(a) alongside the experimental data at 355~nm.
+Photoelectron spectra are simulated using the xsim package of CFOUR and the model Hamiltonian generated above.
+The Hamiltonian is diagonalised using the Lanczos algorithm, to calculate transition energies and intensities that map to the measured photoelectron spectrum.
 %Calculated transitions with $\Sigma$ symmetry are in blue, and transitions with $\Pi$ symmetry are in orange.
@@
 The experimental data show that the electronic coupling interactions induce a splitting of the $\tilde{A} ^2\Pi$ state origin over 5 vibronic levels, spaced by $\sim 95~$cm$^{-1}$ ($a-e$).
-This splitting is also observed in the calculated spectrum, which correctly predicts 5 prominent transitions in this region.
-The relative intensities between the calculated transitions are also in good agreement with the experimental data.
-Peak $d$ is slightly overestimated; however the relative intensity difference between peaks may be partly explained by the Wigner threshold law~\cite{wig48}, which will reduce the intensity of peaks $d$ and $e$ in the experimental spectrum due to their proximity to the detachment threshold.
+This splitting is also observed in the calculated spectrum, which reproduces the 5 prominent transitions in this region.
+The relative intensities between the calculated transitions are also in agreement with the experimental data.
+Peak $d$ is slightly overestimated in intensity, which may in part be due to the variation of photodetachment cross section near threshold, as described by the Wigner threshold law~\cite{wig48}.
 The simulated spectrum also slightly underestimates the splitting between the vibronic levels, which may be linked to the overestimation of the calculated gap between the $^2\Sigma$ and $^2\Pi$ surfaces.
@@
 Instead of the 5 evenly split levels observed in C$_2$H, a single dominant peak ($e$) is now observed near $\sim3,845$~cm$^{-1}$ alongside a collection of weaker peaks ($a-d$) centred around 3,400~cm$^{-1}$.
-Based on previous spin-orbit splitting measurements, peak d is expected to have significant $\tilde{A} ^2\Pi$ character, with peaks $a-d$ commonly assigned to vibronic levels with predominantly HT coupled $\tilde{X} ^2\Sigma^+$ character~\cite{yan87,hsu95,chi99,wil11}.
+Based on the observed spin-orbit splitting measurements from rotationally resolved IR spectra~\cite{yan87,sch98,ste88}, peak $e$ is expected to have significant $\tilde{A} ^2\Pi$ character, with peaks $a-d$ commonly assigned to vibronic levels with predominantly HT coupled $\tilde{X} ^2\Sigma^+$ character~\cite{yan87,hsu95,chi99,wil11}.
 This suggests that deuteration effectively dampens the coupling interaction between the surfaces, as has been observed in the vinylidene photoelectron spectrum~\cite{dev17}.
@@
 The simulated spectrum reproduces the large change observed for the deuterated species.
-The calculated intensity pattern of the vibronic levels around the $\tilde{A} ^2\Pi$ origin is also a good match to the experimental data, with a single intense transition observed near peak $e$, and 3 prominent transitions predicted around the experimental peaks $a-d$.
+The calculated intensity pattern of the vibronic levels around the $\tilde{A} ^2\Pi$ origin also mirrors the experimental data, with a single intense transition observed near peak $e$, and 3 prominent transitions predicted around the experimental peaks $a-d$.
 The calculated splitting between the levels is also similar.
@@
 
-\begin{figure}[th!]
-	\includegraphics[width=0.6\textwidth]{figures/266-plot.pdf}
-	\caption{Photoelectron spectrum of C$_2$H$^-$ at 266~nm, showing vibrationally excited $\tilde{A}$ state structure.
-The simulated spectrum, shown in green, is calculated using the quasidiabatic ansatz, and convolved with Gaussians with a kinetic energy dependent FWHM of $\Delta\text{E}/\text{E} = 0.4\%$ ($\Gamma=55-30$~cm$^{-1}$) to match the VMI resolution characteristics.}
-	\label{fig:4}
-\end{figure}
-To investigate the effects of coupling on the higher excited vibronic levels on the~$\tilde{A} ^2\Pi$ surface, the calculations were also compared to the experimental photoelectron spectrum of C$_2$H$^-$ at 266~nm, presented in Figure~\ref{fig:4}.
+To investigate the effects of coupling on the higher excited vibronic levels on the~$\tilde{A} ^2\Pi$ surface, the calculations were compared with the experimental photoelectron spectrum of C$_2$H$^-$ at 266~nm, as presented in Figure~\ref{fig:4}.
 Gaussian functions were fitted to the transitions from Figure~\ref{fig:3}(a) with a kinetic energy dependent FWHM of $\Delta\text{E}/\text{E} = 0.4\%$ ($\Gamma=55-30$~cm$^{-1}$) to match the lower resolution of the experimental data at high electron kinetic energies.
@@
 
+\begin{figure}[th!]
+	\includegraphics[width=0.6\textwidth]{figures/266-plot.pdf}
+	\caption{Photoelectron spectrum of C$_2$H$^-$ at 266~nm, showing vibrationally excited $\tilde{A}$ state structure.
+The simulated spectrum, shown in green, is calculated using the quasidiabatic ansatz, and convolved with a Gaussian function with a kinetic energy dependent FWHM of $\Delta\text{E}/\text{E} = 0.4\%$ ($\Gamma=55-30$~cm$^{-1}$) to match the VMI resolution characteristics.}
+	\label{fig:4}
+\end{figure}
+
 The results from Figures~\ref{fig:3} and~\ref{fig:4} confirm that the quasidiabatic approach is able to accurately describe the vibronic interactions between the $^2\Sigma^+$ and $^2\Pi$ surfaces, including deuteration effects.
@@
 The approach could be systematically improved with a more elaborate expansion, such as that used in Ref.~\onlinecite{sim12} for the NO$_3$ radical.
-Applying this approach to similar less-studied systems will produce reliable predictions for the position and intensity of dominant transitions, which will help guide the search for these molecules in laboratory experiments and astronomical observations.
+Applying this approach to similar systems will produce reliable predictions for the position and intensity of dominant transitions, and help guide the search for these molecules in laboratory experiments and astronomical observations.
 
@@
 The quasidiabatic Hamiltonian approach is able to determine the symmetry of each individual vibronic state, either $\Sigma$ or $\Pi$, which may be compared directly to the observed anisotropy of each transition.
-The VMIs from this work (Figure~\ref{fig:1}) were obtained using a linearly polarized detachment laser.
-Therefore, the differential cross section of emitted electrons is given by
+The velocity-map images from this work (Fig~\ref{fig:1}) were obtained using a linearly polarized detachment laser.
+Therefore, the differential cross section of emitted electrons is given by,
 \begin{equation}
@@
 \end{equation}
-where $\epsilon$ is the electron kinetic energy and $\gamma_p$ is the fraction of $p$ character of the detachment orbital described as
+where $\epsilon$ is the electron kinetic energy and $\gamma_p$ is the fraction of $p$ character of the detachment orbital described as,
 \begin{equation}
@@
 Therefore, measuring the anisotropy can help determine the electronic character of each individual transition, which may be compared to the calculated symmetries in Figure~\ref{fig:3}.
-The anisotropy parameters were measured at a range of detachment wavelengths for prominent transitions in the C$_2$H$^-$ photoelectron spectra from this work, and are presented in Figure~\ref{fig:5}.
+Anisotropy parameters were measured over a range of detachment wavelengths for prominent transitions in the C$_2$H$^-$ photoelectron spectra, and are presented in Figure~\ref{fig:5}.
 Fitting Eq.~(\ref{eq:beta-sp}) to the anisotropy parameters from $^2\Pi$ state detachment, with $\gamma_p = 0.9$ produces a Hanstorp coefficient of $A_1=0.66(4)~$eV$^{-1}$.
@@
 
-The sign (+/-) of $\beta$ can be used to assign each accessed vibronic level to either the $^2\Sigma^+$ or $^2\Pi$ vibronic symmetry respectively.
+The sign $(+/-)$ of $\beta$ can be used to assign each accessed vibronic level to either the $^2\Sigma^+$ or $^2\Pi$ vibronic symmetry respectively.
 This is particularly useful around the $\tilde{A} ^2\Pi$ origin, where the two states overlap.
@@
 
-A plot of the anisotropy parameters for C$_2$H$^-$ detachment at 300~nm, represented as $\beta\times I$, is presented in Figure~\ref{fig:6}, alongside the experimental spectrum.
-Plotting $\beta\times I$ allows the sign (+/-) of each individual transition to be easily identified, even for partially resolved peaks.
-All of the transitions above the $\tilde{A} ^2\Pi$ origin have a negative anisotropy, except for peak $f$, which was not assigned in previous experiments.
-The positive anisotropy supports our assignment of this peak to the highly excited $\Sigma$ transition $\tilde{X}(0,6,1$), where $\tilde{X}(v_1,v_2,v_3)$.
-The nearby peaks $h$ and $i$  are assigned to the admixed $\Pi$ transitions $\tilde{X}(0,3,2)\tilde{A}(0,0,0)$ and $\tilde{X}(0,7,1)\tilde{A}(0,1,0)$, which agrees with previous assignments~\cite{zho07,tar03}.
+A plot of the anisotropy parameters for C$_2$H$^-$ detachment at 300~nm, represented as $\beta\times I$, is presented in Figure~\ref{fig:6}, alongside the photoelectron spectrum.
+Plotting $\beta\times I$ allows the sign $(+/-)$ of each individual transition to be easily identified, even for partially resolved peaks.
+All of the transitions above the $\tilde{A} ^2\Pi$ origin have a negative anisotropy parameter, except for peak $f$, which was not assigned in previous experiments.
+The positive anisotropy supports our assignment of this peak to the excited $\Sigma$ transition $\tilde{X}(0,6,1$), where $\tilde{X}(v_1,v_2,v_3)$.
+The nearby peaks $h$ and $i$  are assigned to the admixed $\Pi$ transitions $\tilde{X}(0,3,2)\tilde{A}(0,0,0)$ and $\tilde{X}(0,7,1)\tilde{A}(0,1,0)$, in agreement with previous assignments~\cite{zho07,tar03}.
 Peak $j$ was tentatively assigned to the $\Sigma$ transition $\tilde{X}(1,4,0$) previously~\cite{zho07}, however Figure~\ref{fig:6} shows peak $j$ has $\Pi$ symmetry.
-Therefore, we assign $j$ to the highly excited HT coupled $\Pi$ transition $\tilde{X}(0,7,1)$.
+Therefore, we assign $j$ to the excited HT coupled $\Pi$ transition $\tilde{X}(0,7,1)$.
 The other dominant peaks in this region, $l$, $n$, and $o$, represent admixed $\Pi$ transitions involving the $\tilde{A}(0,0,1)$ vibrational level of the excited state.
 The complete assignments for all resolved peaks in the C$_2$H$^-$ and C$_2$D$^-$ photoelectron spectra from this work are presented in the Supplementary Materials Table~S1.
+Transition assignments are based on a combination of the previous works of Tarroni and Carter~\cite{tar03} and Zhou~\emph{et al.}~\cite{zho07}, the transition position and symmetry outputs from the QVC calculations (Fig.~\ref{fig:3}), and the experimental electron anisotropies which define the vibronic symmetry.
 
@@
 	\includegraphics[width=0.6\textwidth]{figures/plotBeta.pdf}
-	\caption{Photoelectron spectrum of C$_2$H$^-$ at 300~nm, compared to anisotropy measurements ($\beta\times I$).
+	\caption{Photoelectron spectrum of C$_2$H$^-$ at 300~nm, compared to anisotropy measurements, presented as $\beta\times I$.
 For each resolved transition the anisotropy parameter was determined from Eq.~(\ref{eq:beta1}) and multiplied by the corresponding photoelectron intensity.
-This allows for the sign (+/-) of each transitions to be readily determined.}
+This allows for the sign $(+/-)$ of each transitions to be readily determined.}
 	\label{fig:6}
@@
 This result demonstrates how experimental anisotropies and calculated transition intensities can be combined to help assign and understand vibronically coupled spectra.
-This is particularly useful in regions where there a large number of potential vibronic states, making definitive assignments based on energetics alone difficult.
+This is particularly useful in spectral regions where there a large number of potential vibronic transitions, making definitive assignments based on energetics alone difficult.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 High-resolution photoelectron images of C$_2$H$^-$ and C$_2$D$^-$ were recorded both near and above threshold, to investigate vibronic coupling effects in the simplest C$_{2n}$H carbon monohydride chain.
-The interplay of pseudo Jahn-Teller and Renner Teller coupling between the close lying $\tilde{X}^2\Sigma^+$ and $\tilde{A}^2\Pi$ states results in a complex vibronic spectrum near the $\tilde{A}$ state surface, with the electronic origin split over multiple admixed levels.We have shown that by transforming to a quasidiabatic representation, the effect of these coupling interactions may be accurately simulated.
+The interplay of pseudo Jahn-Teller and Renner Teller coupling between the close lying $\tilde{X}^2\Sigma^+$ and $\tilde{A}^2\Pi$ states results in a complex vibronic spectrum near the $\tilde{A}$ state surface, with the electronic origin split over multiple admixed levels.
+By transforming to a quasidiabatic representation, the effect of these coupling interactions may be accurately simulated.
 A KDC Hamiltonian was constructed, and parametrised using the high-level EOMIP-CCSDT quantum chemical approach and the quasidiabatic ansatz.
-The resulting simulated photoelectron spectra of C$_2$H$^-$ and C$_2$D$^-$ closely resemble the experimental data, even in the energy region of the complicated $\tilde{A}$ state origin.
+The resulting simulated photoelectron spectra of C$_2$H$^-$ and C$_2$D$^-$ resemble the experimental data, particularly in the complex energy region of the $\tilde{A}$ state origin.
 Photoelectron anisotropy parameters were also measured for dominant transitions, at a range of wavelengths.
-Comparing the sign (+/-) of the anisotropy to the calculated vibronic symmetry allowed for even weak or partially resolved transitions to be assigned.
+The sign $(+/-)$ of the anisotropy parameter, when compared to the calculated vibronic symmetry, allowed even weak or partially resolved transitions to be assigned.
 
@@
 A modified velocity-map imaging lens images the detached photoelectrons to a 75mm diameter MCP/phosphor screen detector.
-Events are imaged by a 2048x2048 monochrome CCD camera (PCO 2000), with each frame transferred to a computer at a 10Hz repetition rate, and processed in real time to identify the electron events, centroiding the position to
+Events are imaged by a 2048x2048 monochrome CCD camera (PCO 2000), with each frame transferred to a computer at a 10Hz repetition rate, and processed in real time to identify electron events, centroiding each position to
 a subpixel accuracy.
@@
 
+\section*{Supplementary Materials}
+See supplementary material for the complete list of C$_2$H and C$_2$D photoelectron transitions and assignments.
 %Hi~\cite{law17}
@@
 
+\section*{Data Availability}
+
 % Create the reference section using BibTeX: 

### 2022-06-24 Resubmission/Laws_C2H.tex
update resubmission

--- 2022-06-24 C2Hpaper.tex
@@
-\documentclass[journal=jpcafh,manuscript=article,layout=onecolumn, 12pt]{achemso}
+%% ****** Start of file aiptemplate.tex ****** %
+%%
+%%   This file is part of the files in the distribution of AIP substyles for REVTeX4.
+%%   Version 4.1 of 9 October 2009.
+%%
+%
+% This is a template for producing documents for use with 
+% the REVTEX 4.1 document class and the AIP substyles.
+%
+
+\documentclass[aip,graphicx]{revtex4-1}
+\usepackage{graphicx}
+\usepackage{longtable}
 \usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
@@
 % NB added command for in line cite
-\newcommand{\onlinecite}[1]{\hspace{-1 ex} \nocite{#1}\citenum{#1}} 
-%
+%\newcommand{\onlinecite}[1]{\hspace{-1 ex} \nocite{#1}\citenum{#1}} 
+%\documentclass[aip,reprint]{revtex4-1}
+
+\draft % marks overfull lines with a black rule on the right
+
+\begin{document}
+
+% Use the \preprint command to place your local institutional report number 
+% on the title page in preprint mode.
+% Multiple \preprint commands are allowed.
+%\preprint{}
+
+\title{Velocity Map Imaging Spectroscopy of C$_2$H$^-$ and C$_2$D$^-$: a benchmark study of vibronic coupling interactions}
+
 \author{Benjamin~A.~Laws}
@@
 \affiliation{School of Chemistry, University of New South Wales, Sydney NSW 2052, Australia}
-\alsoaffiliation{Research School of Physics, The Australian
+\affiliation{Research School of Physics, The Australian
 	National University, Canberra ACT 2601, Australia}
@@
 	National University, Canberra ACT 2601, Australia}
-\title{Velocity Map Imaging Spectroscopy of C$_2$H$^-$ and C$_2$D$^-$: a benchmark study of vibronic coupling interactions}
-\abbreviations{PES,PAD,EA,eKE,FWHM,VMI}
-\begin{document} 
+
+\date{\today}
+
 \begin{abstract}
-
-\end{abstract}
-High-resolution velocity map imaged photoelectron spectra of the ethynyl anions C$_2$H$^-$ and C$_2$D$^-$ are measured over a range of photodetachment wavelengths, to investigate the complex interactions between the close lying $\tilde{X}^2\Sigma^+$ and $\tilde{A}^2\Pi$ electronic states.
+High-resolution velocity-map imaged photoelectron spectra of the ethynyl anions C$_2$H$^-$ and C$_2$D$^-$ are measured over a range of photodetachment wavelengths, to investigate the complex interactions between the close lying $\tilde{X}^2\Sigma^+$ and $\tilde{A}^2\Pi$ electronic states.
 Vibronic coupling calculations are performed by transforming to a quasidiabatic representation, parametrised by \emph{ab-initio} CFOUR calculations, to model the interplay between pseudo Jahn-Teller and Renner-Teller coupling.
 This approach is combined with electron anisotropy measurements to assign all of the observed vibronic structure, providing a framework that may be used to accurately simulate spectra of larger C$_{2n}$H monohydride carbon chains.
+\end{abstract}
+
+\pacs{}
+
+\maketitle
 
@@
 Conversely, the formation of anions in space is believed to be driven by radiative electron attachment, charge transfer, and dissociative electron attachment.
-Current astrochemical modelling of interstellar clouds, such as IRC+10216, typically underestimate the observed abundances of CH$_4^-$~\cite{mil17,cor13,her08}.
+Current astrochemical modelling of interstellar clouds, such as IRC+10216, typically underestimate the observed abundances of CH$_4^-$ ~\cite{mil17,cor13,her08}.
 Therefore, it has been proposed that ion-neutral reactions
@@
 In this work we demonstrate how the construction of a quasidiabatic Hamiltonian allows the strength of vibronic interactions between coupled surfaces near a conical intersection to be estimated, sufficient to accurately simulate electronic and vibronic spectra.
-%The quadratic vibronic coupling model employed can be readily scaled to larger molecules (such as longer C$_n$H chains) which quickly become too complex to study using full variational approaches.
 Anion HR-PEI spectroscopy maps both of the $^2\Sigma^+$ and $^2\Pi$ surfaces on an equal footing from the anion $\tilde{X}^1\Sigma^+$ state, allowing a direct comparison with \emph{ab-initio} modelling.
-%The electron anisotropy allows transitions with $\sigma$ and $\pi$ symmetry to be distinguished, providing definitive assignments of calculated transitions.
+
+\section{Methods}
+\subsection{Experimental Procedure}
+Details of the HR-PEI spectrometer are given in Refs~\onlinecite{cav07} and~\onlinecite{dev17}.
+Briefly, C$_2$H$^-$ and C$_2$D$^-$ anions are produced by passing pure ethylene (C$_2$H$_4$ or C$_2$D$_4$) gas at $\sim2$ bar pressure through a pulsed solenoid valve, into the source vacuum chamber.
+The gas undergoes adiabatic supersonic expansion into a high-voltage discharge which generates negative ions.
+The anions are extracted, accelerated to 500~eV, and focussed into a novel gating, bunching, and re-referencing unit~\cite{ded01}, before being mass separated over a 2m time-of-flight region.
+The anion of interest (C$_2$H$^-$ or C$_2$D$^-$) is then isolated by an electrostatic gate.
+The ion packet is crossed with a tuneable detachment laser beam, generated from a Continuum Sunlite EX optical parametric oscillator pumped by the third harmonic of a Continuum Powerlite 9010 Nd:YAG laser.
+The laser output is then doubled by passing through a BBO crystal, to produce UV laser pulse energies between 1-5mJ at 10Hz.
+The wavelength of the laser light is measured using a HighFinesse WS7 UV wavemeter.
+
+A modified velocity-map imaging lens images the detached photoelectrons to a 75mm diameter MCP/phosphor screen detector.
+Events are imaged by a 2048x2048 monochrome CCD camera (PCO 2000), with each frame transferred to a computer at a 10Hz repetition rate, and processed in real time to identify electron events, centroiding each position to
+a subpixel accuracy.
+The electron positions are then written to a data file for subsequent analysis.
+The velocity-map image is centred and then circularized by an angular dependent-radial scaling determined by comparing adjacent radial slice intensity profiles~\cite{gas17}.
+An inverse Abel transformation of the VMI, based on the algorithm of Hansen and Law~\cite{han85,hic19}, returns a slice image of the 3D electron source distribution.
+Absolute energy calibration of the photoelectron spectra is achieved using published measurements of species, including C$_2^-$~\cite{law19b} and NO$_2^-$~\cite{law19}, that have been studied under similar conditions and photon energies as those used for the C$_2$H$^-$ measurements.
+
+\subsection{Computational Details}
+Quantum chemical computations were preformed using the CFOUR computational package~\cite{dev20}.
+The equation-of-motion ionised-potential coupled-cluster singles, doubles, and triples (EOM-IP-CCSDT) level of theory with an atomic natural orbital basis set of quadruple-zeta quality (ANO2) was used on a closed-shell anionic reference to perform geometry optimisations and frequency calculations (including 1h + 2h1p + 3h2p excitations~\cite{mat16}).
+EOM is a highly accurate and robust framework that provides access to different types of target electronic states, including ionised states~\cite{gul21b,and22,bar07}.
+The linear diabatic coupling constants were calculated analytically at the EOM-IP-CCSD/ANO2 level.
 
@@
 Due to the close lying nature of the ground {$\tilde{X} ^2\Sigma^+$} and excited {$\tilde{A} ^2\Pi$} electronic states, which are only separated by $\sim3700~$cm$^{-1}$, a pseudo Jahn-Teller effect is also observed.
-%The Jahn-Teller theorem states that stability and degeneracy are not possible simultaneously unless the molecule is linear~\cite{jah37}, meaning that non-linear molecules with degenerate electronic states will undergo a symmetry breaking distortion in order to remove the degeneracy.
-However a similar effect has also been observed where coupling exists between a non-degenerate state and a nearby pair of degenerate states, even if a molecule is linear.
 In the case of C$_2$H this is seen as coupling between the ground $\Sigma^+(1A')$ and excited $\Pi^+(2A')$ states, induced by the bending motion of $v_2$.
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{figures/Fig3}
+	\includegraphics[width=0.5\textwidth]{figures/Fig2}
 	\caption{Adiabatic potential energy surfaces of $\tilde{X}^2\Sigma^+$, $\tilde{A}^2\Pi^-$, and $\tilde{A}^2\Pi^+$ states, calculated using the parameters calculated by Tarroni and Carter~\cite{tar03}.}
@@
 
-The adiabatic potential energy surfaces in Figure~\ref{fig:2} were evaluated from the variational parameters of Tarroni and Carter~\cite{tar03}, illustrating the loss of degeneracy for the doublet $\Pi$ surfaces, due to the Renner-Teller and pseudo Jahn-Teller interactions.
+The adiabatic potential energy surfaces in Figure~\ref{fig:2} were evaluated from the variational parameters of Tarroni and Carter~\cite{tar03}, illustrating the loss of degeneracy for the doublet $^2\Pi$ surfaces, due to the Renner-Teller and pseudo Jahn-Teller interactions.
 This technique has been used to calculate a multitude of admixed vibronic levels.
@@
 However, due to the strong vibronic coupling interactions, transition intensities can not be obtained via simple Franck-Condon calculations based on quantum chemistry methods.
-To account for these interactions, the photoelectron spectrum of the C$_2$H$^-$ anion is simulated using a quasidiabatic Hamiltonian of the type advocated by Koeppel, Domcke and Cederbaum (KDC).~\cite{kou84,dom81} In this approach, the Hamiltonian is represented in a basis of quasidiabatic (slowly varying) electronic  states for which the kinetic energy operator can be assumed diagonal.~\cite{pac93} For C$_2$H, the KDC Hamiltonian comprises three states - the two components of the $^2\Pi$ state and the ground $^2\Sigma^+$ state - and is then projected onto a vibrational basis, usually chosen as a direct product of harmonic oscillators.
+To account for these interactions, the photoelectron spectrum of the C$_2$H$^-$ anion is simulated using a quasidiabatic Hamiltonian of the type introduced by Koeppel, Domcke and Cederbaum (KDC).~\cite{kou84,dom81} In this approach, the Hamiltonian is represented in a basis of quasidiabatic (slowly varying) electronic  states for which the kinetic energy operator can be assumed diagonal.~\cite{pac93} For C$_2$H, the KDC Hamiltonian comprises three states - the two components of the $^2\Pi$ state and the ground $^2\Sigma^+$ state - and is then projected onto a vibrational basis, usually chosen as a direct product of harmonic oscillators.
 Diagonalization of the corresponding matrix yields the molecular states (which are given in terms of a Born-Huang expansion), and the squared projections of the corresponding eigenvectors onto the ground state of the anion yield the relative intensities.
@@
 When the potential in Eq.~(\ref{eq:calc1}) is diagonalized, the adiabatic states that are used for its parametrization are precisely recovered through terms second order in displacement.
-The linear diabatic coupling constants between the electronic states of interest were calculated analytically at the EOM-CCSD/ANO2 level of theory, using the CFOUR computational package~\cite{dev20} and the quasidiabatic ansatz of Ichino~\emph{et al.}~\cite{ich09} Briefly, the EOM procedure is used to operationally define quasidiabatic states (those that relax according to a well-behaved reference state wavefunction, which is that of the anion level) and the coupling constants are then evaluated as the first derivative of the off-diagonal elements of the electronic Hamiltonian in the basis defined by this representation.
-The diabatic force and coupling constants calculated to parametrize the KDC potential in Eq.~(\ref{eq:calc1}) were calculated at the CCSDT/ANO2 level of theory, and are presented in Table~\ref{tab:1}.
-
-%To parametrize this Hamiltonian, the equation-of-motion coupled-cluster method known as EOMIP-CCSDT has been used to optimise the geometry of the ground state anion, with an Atomic Natural Orbital (ANO) basis (ANO2), using the CFOUR computational package.
-
-%Adiabatic linear and quadratic force constants are calculated from the analytical derivatives of the \emph{ab-initio} potential energy surface with respect to the anion reduced normal coordinates, at the anion geometry Q$_0$.
-The interstate PJT coupling constant $\lambda$ is evaluated directly using the CFOUR package to employ the quasidiabatic ansatz described in refs.
-This allows for direct ab-initio evaluation of the linear diabatic interstate coupling constants that parametrize the KDC potential.
-The calculated parameters are presented in the Supplementary Materials, in Table S1.
+The parametrization of the potential in this work was completed using the CFOUR computational package~\cite{dev20} and the quasidiabatic ansatz of Ichino~\emph{et al.}~\cite{ich09} Briefly,the EOM procedure is used to operationally define quasidiabatic states (those that relax according to a well-behaved reference state wavefunction, which is that of the anion level) and the coupling constants are then evaluated as the first derivative of the off-diagonal elements of the electronic Hamiltonian in the basis defined by this representation.
+Vertical excitation energies ($\Delta_0$), and linear diabatic force and coupling constants between the electronic states of interest were calculated analytically using the highly accurate EOM-IP-CCSDT/ANO2 procedure.
+The interstate coupling constants ($\lambda$) were calculated analytically at the EOM-IP-CCSD/ANO2 level.
+All calculated values used to parametrize the KDC potential in Eq.~(\ref{eq:calc1}) are presented in Table~\ref{tab:1}.
 
@@
 	\label{tab:1}
-%	\begin{tabular}{c |c c c c| c c c c }
-%		 & \multicolumn{4}{c}{C$_2$H}     & \multicolumn{4}{c}{C$_2$D}  \\ \hline
-%		  & Anion & $\tilde{X}^2\Sigma^+$ & $\tilde{A}^2\Pi (a')$ & $\tilde{A}^2\Pi (a'')$ & Anion & $\tilde{X}^2\Sigma^+$ & $\tilde{A}^2\Pi (a')$ & $\tilde{A}^2\Pi (a'')$ \\
-%		 \hline\hline
-%		 $\Delta$E & 0 & 22431.21 &  26543.67 & 26543.67 & 0&	22431.21 & 26543.67	& 26543.67\\
-%		 F$_1$ & 0	& -211.28 & 286.9 &	286.9 & 0& -596.04& 641.6 & 641.6\\
-%		 F$_3$ & 0 & -1515.21 & 1257.07 & 1257.07 & 0 & -1401.53 & 1115.17 & 1115.17\\
-%		 F$_{2a}$ & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-%		 F$_{2b}$ & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
- %        F$_{11}$ & 3424.32 & 3487.03 & 3482.16 & 3482.16 & 2611.42 & 2636.57 & 2681.25 & 2681.25\\
-%         F$_{13}$ & 0.00 & -28.32 & 31.46 & 31.46 & 0.00 & -48.38 & 55.40 & 55.40\\
- %        F$_{33}$ & 1894.71 & 1830.83 & 2099.57 & 2042.21 & 1792.49 & 1747.62 & 1914.39 & 1914.39\\
-  %       F$_{2a2a}$ & 607.09 & 87.57 & 1883.48 & 658.96 & 481.89 & 120.09 & 1503.88 & 473.55\\
-   %      F$_{2b2b}$ & 607.09 & 87.57 & 658.96 & 1883.48 & 481.89 & 120.09 & 473.55 & 1503.88\\
-    %     $\lambda$ &  & & -1185.26 &  &  & & -1014.58 &  \\
-     %    \end{tabular}
-     \begin{tabular}{c | c c c c | c c c c} 
+
+	\begin{tabular}{c | r r r r | r r r r} 
 		\hline
@@
 		\hline
-     	& Anion & $\tilde{X}^2\Sigma^+$ & $\tilde{A}^2\Pi (a')$ & $\tilde{A}^2\Pi (a'')$ & Anion & $\tilde{X}^2\Sigma^+$ & $\tilde{A}^2\Pi (a')$ & $\tilde{A}^2\Pi (a'')$  \\
+		& ~~Anion~~ & ~~$\tilde{X}^2\Sigma^+$~~ & ~~$\tilde{A}^2\Pi (a')$~~ & ~~$\tilde{A}^2\Pi (a'')$~~ & ~~Anion~~ & ~~$\tilde{X}^2\Sigma^+$~~ & ~~$\tilde{A}^2\Pi (a')$~~ & ~~$\tilde{A}^2\Pi (a'')$~  \\
 		\hline
@@
 The above method was employed to simulate the photoelectron spectrum of C$_2$H$^-$, with the calculated transitions shown in Figure~\ref{fig:3}(a) alongside the experimental data at 355~nm.
-Photoelectron spectra are simulated using the xsim package of CFOUR and the model Hamiltonian generated above.
-The Hamiltonian is diagonalised using the Lanczos algorithm, to calculate transition energies and intensities that map to the measured photoelectron spectrum.
-%Calculated transitions with $\Sigma$ symmetry are in blue, and transitions with $\Pi$ symmetry are in orange.
+Photoelectron spectra are simulated using the xsim package of CFOUR~\cite{dev20} and the model Hamiltonian generated above.
+The xsim module projects the Hamiltonian (Eq.~\ref{eq:calc1}) onto a vibrational basis, which is then diagonalised using Lanczos algorithm to calculate transition energies and intensities that map to the measured photoelectron spectrum.
+In this simulation the transition moments for the two ionisation processes are assumed to be equal.
 On the $\tilde{X} ^2\Sigma^+$ surface, below 3,600~cm$^{-1}$, there is excellent agreement in both the transition positions and intensities between the simulated and experimental spectra.
@@
 \begin{figure}[th!]
-	\includegraphics[width=0.6\textwidth]{figures/Fig5.pdf}
+	\includegraphics[width=0.6\textwidth]{figures/Fig3}
 	\caption{(a) Experimental photoelectron spectrum of C$_2$H$^-$ at 355~nm, compared with the simulated spectrum, calculated using the quasidiabatic ansatz.
@@
 The calculated splitting between the levels is also similar.
-%however the relative intensity of peak $d$ appears to be underestimated.
-%The results from Figure~\ref{fig:C2H-plot} confirm that the quasiadiabtic approach is able to accurately describe the vibronic interactions between the $\Sigma$ and $\Pi$ surfaces, including deuteration effects.
 
@@
 \begin{figure}[th!]
-	\includegraphics[width=0.6\textwidth]{figures/266-plot.pdf}
+	\includegraphics[width=0.6\textwidth]{figures/Fig4}
 	\caption{Photoelectron spectrum of C$_2$H$^-$ at 266~nm, showing vibrationally excited $\tilde{A}$ state structure.
@@
 Applying this approach to similar systems will produce reliable predictions for the position and intensity of dominant transitions, and help guide the search for these molecules in laboratory experiments and astronomical observations.
-
-%Overall, figures a-c show that the quasidiabatic approach is a reliable method for simulating the spectra of molecules when strong vibornic coupling interactions are involved.
-This method may be expanded to other C$_n$H radicals that possess similar complexities, in order to help guide the search for new molecules to be found in space.
 
@@
 Therefore, measuring the anisotropy can help determine the electronic character of each individual transition, which may be compared to the calculated symmetries in Figure~\ref{fig:3}.
-Anisotropy parameters were measured over a range of detachment wavelengths for prominent transitions in the C$_2$H$^-$ photoelectron spectra, and are presented in Figure~\ref{fig:5}.
-Fitting Eq.~(\ref{eq:beta-sp}) to the anisotropy parameters from $^2\Pi$ state detachment, with $\gamma_p = 0.9$ produces a Hanstorp coefficient of $A_1=0.66(4)~$eV$^{-1}$.
-
-%\begin{equation}
-%\beta(\epsilon)_{sp} = \frac{2Z\epsilon+2\text{A}_1\epsilon^2-4\epsilon\cos\delta_{\ell\pm 1}}{\frac{1}{\text{A}_1}+2\text{A}_1\epsilon^2+Z\epsilon}
-%\label{eq:beta-sanov}
-%\end{equation}  
-%where $\epsilon$ is the electron kinetic energy, $A_1$ is the $s\rightarrow p$ Hanstorp coefficient, $f$ is the percentage of $p$ orbital character,
-%\begin{equation}
-%Z = \frac{1-f}{f}\frac{8}{3}~~ \text{and} ~~ |\psi\rangle = \sqrt{1-f}|s\rangle + \sqrt{f}|p\rangle.
-%\end{equation}
-
-%From Eq.~(\ref{eq:beta-sanov}) it can be seen that detachment from a pure $s$ orbital will have a positive anisotropy ($\beta=+2$), whereas detachment from a pure $p$ orbital will have a negative anisotropy for electron kinetic energies $\epsilon < 2/A_1$.
-Therefore, measuring the anisotropy will determine the electronic character of each individual transition, which may be compared to the calculated symmetries in Figure~\ref{fig:3}.
-The anisotropy parameters were measured for every detachment wavelength and prominent transition in the C$_2$H$^-$ photoelectron spectra from this work, and are presented in Figure~\ref{fig:5}.
-Fitting Eq.~(\ref{eq:beta-sanov}) to the anisotropy parameters from $^2\Pi$ state detachment, with f=0.9 produces a Hanstorp coefficient of $A_1$=0.66(4)~eV$^{-1}$.
+For each prominent transition in the photoelectron spectrum of C$_2$H$^-$ in Figure~\ref{fig:1} the corresponding anisotropy parameter may be calculated by fitting Eq.~(\ref{eq:beta1}) to a plot of the integrated radial intensity (across the peak) versus angle, as (for a single quadrant of the electron image) the intensity variation is linear in $P_2(\cos\theta)$ with a slope equal to $\beta\times$intercept.
+This procedure was applied to all of the photoelectron spectra measured in this work, with the energy dependent anisotropy parameters presented in Figure~\ref{fig:5}(a).
 
 \begin{figure}[th!]
-	\includegraphics[width=0.5\textwidth]{figures/PAD.pdf}
-	\caption{Photoelectron anisotropy parameters, measured for each resolved C$_2$H$^-$ transition, across a range of detachment wavelengths.
+	\includegraphics[width=0.8\textwidth]{figures/PAD}
+	\caption{(a) Photoelectron anisotropy parameters, measured for each resolved C$_2$H$^-$ transition, across a range of detachment wavelengths.
 Allowed ground state transitions $\tilde{X}^2\Sigma^+$ are shown in orange, Herzberg-Teller coupled transitions are shown in purple, and excited state transitions $\tilde{A} ^2\Pi$ are shown in blue.
-Anisotropy curves for a mixed-$sp$ model (Eq.~\ref{eq:beta-sp}) are shown for $\gamma_p=0.1$ and $\gamma_p=0.9$.}
+Anisotropy curves for a mixed-$sp$ model (Eq.~\ref{eq:beta-sp}) are shown for $\gamma_p=0.1$ and $\gamma_p=0.9$.
+Anisotropy curves from Dyson orbital calculations for the $\tilde{X}^2\Sigma^+$ and $\tilde{A} ^2\Pi$ transitions are shown in blue and orange respectively.
+(b) Dyson orbital representation of the $\tilde{X}^1\Sigma^+\rightarrow\tilde{X}^2\Sigma^+$ transition.
+(c) Dyson orbital representation of the $\tilde{X}^1\Sigma^+\rightarrow\tilde{A} ^2\Pi$ transition.}
 	\label{fig:5}
@@
 
-The sign $(+/-)$ of $\beta$ can be used to assign each accessed vibronic level to either the $^2\Sigma^+$ or $^2\Pi$ vibronic symmetry respectively.
+In Figure~\ref{fig:5}(a) allowed ground state transitions ($\tilde{X}^2\Sigma^+$) are shown in blue and have a positive anisotropy, as expected for detachment from a $s-$like orbital.
+Conversely, excited state transitions ($\tilde{A} ^2\Pi$) shown in orange have a negative anisotropy.
+However, the HT coupled transitions on the $\tilde{X} ^2\Sigma^+$ surface also have negative anisotropies, due to their $\Pi$ vibronic symmetry.
+Therefore, the sign $(+/-)$ of $\beta$ can be used to assign each accessed vibronic level to either the $\Sigma$ or $\Pi$ vibronic symmetry respectively.
 This is particularly useful around the $\tilde{A} ^2\Pi$ origin, where the two states overlap.
-It is important to note that the HT coupled transitions on the $\tilde{X} ^2\Sigma^+$ surface have negative anisotropies and $\Pi$ symmetry.
+The mixed $sp$ model from Eq.~\ref{eq:beta-sp} is fitted to the experimental data in Figure~\ref{fig:5}(a) with $\gamma_p=0.1$ and $\gamma_p=0.9$ for the ground and excited state detachment respectively.
+For detachment to the $^2\Pi$ state this produces a Hanstorp coefficient of $A_1=0.66(4)~$eV$^{-1}$.
+
+The photoelectron angular distribution may also be examined through the construction of Dyson orbitals, which provide a direct link between \emph{ab-initio} calculations and experimental anisotropy parameters.
+Q-Chem software~\cite{sha15} may be used to construct Dyson orbitals $\phi_d$ that represent the overlap between the initial $\phi_i^{(n)}$ and final $\phi_f^{(n-1)}$ states,
+\begin{equation}
+\phi_d = \sqrt{N}\int\phi_i^{(n)}(1,\dots,n)\phi_f^{(n-1)}(2,\dots,n)dn
+\end{equation}
+By representing the detached electron as a plane wave, $\psi_k=(2\pi)^{(-3/2)}e^{ik\cdot r}$ and assuming strong orthogonality between $\phi_d$, $\psi_k$, and $\phi_f^{(n-1)}$ the transition dipole moment may then be rewritten as
+\begin{equation}
+D_k \propto \langle \phi_d | e\cdot r | \psi_k\rangle.
+\label{eq:Dyson}
+\end{equation}
+The Dyson orbital representation of the C$_2$H$^-$ $\tilde{X}^1\Sigma^+\rightarrow\tilde{X}^2\Sigma^+$ transition, calculated at the EOM-CCSD/aug-cc-pVTZ level, is shown in Figure~\ref{fig:5}(b).
+The corresponding anisotropy curve was calculated using ezDyson software~\cite{goz22}, and is shown in blue in Figure~\ref{fig:5}(a) alongside the experimental data.
+Figure~\ref{fig:5} shows that above threshold there is excellent agreement between the experimental anisotropies, the mixed $sp$ model (Eq.~\ref{eq:beta-sp}), and the calculated anisotropies (Eq.~\ref{eq:Dyson}).
+The cylindrical symmetry of the molecule introduces some $p$ character into the predominantly $s-$like Dyson orbital (Fig.~\ref{fig:5}(b)) which becomes significant near threshold due to the centrifugal detachment barrier.
+This makes the near threshold anisotropy behaviour sensitive to the exact amount of $p$ orbital character included in the orbital, an effect that has also been observed in NO$_2^-$ ~\cite{law19} and the isoelectronic CN$^-$ ~\cite{har21}.
+The Dyson orbital for the $\tilde{X}^1\Sigma^+\rightarrow\tilde{A} ^2\Pi$ transition was also calculated at the EOM-CCSD/aug-cc-pVTZ level, and is shown in Figure~\ref{fig:5}(c).
+Again the calculated anisotropy curve (shown in orange in Fig.~\ref{fig:5}(a)) appears a good match to the $sp$ model (Eq.~\ref{eq:beta-sp}) and the experimental data, however it overestimates the amount of $p$ orbital character.
 
@@
 \begin{figure}[th!]
-	\includegraphics[width=0.6\textwidth]{figures/plotBeta.pdf}
+	\includegraphics[width=0.6\textwidth]{figures/Fig6}
 	\caption{Photoelectron spectrum of C$_2$H$^-$ at 300~nm, compared to anisotropy measurements, presented as $\beta\times I$.
@@
 This result demonstrates how experimental anisotropies and calculated transition intensities can be combined to help assign and understand vibronically coupled spectra.
-This is particularly useful in spectral regions where there a large number of potential vibronic transitions, making definitive assignments based on energetics alone difficult.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+This is particularly useful in spectral regions where there are a large number of potential vibronic transitions, making definitive assignments based on energetics alone difficult.
 
 \section{Conclusions} 
-High-resolution photoelectron images of C$_2$H$^-$ and C$_2$D$^-$ were recorded both near and above threshold, to investigate vibronic coupling effects in the simplest C$_{2n}$H carbon monohydride chain.
+High-resolution photoelectron images of C$_2$H$^-$ and C$_2$D$^-$ were recorded at a range of wavelengths, to investigate vibronic coupling effects in the simplest C$_{2n}$H carbon monohydride chain.
 The interplay of pseudo Jahn-Teller and Renner Teller coupling between the close lying $\tilde{X}^2\Sigma^+$ and $\tilde{A}^2\Pi$ states results in a complex vibronic spectrum near the $\tilde{A}$ state surface, with the electronic origin split over multiple admixed levels.
 By transforming to a quasidiabatic representation, the effect of these coupling interactions may be accurately simulated.
-A KDC Hamiltonian was constructed, and parametrised using the high-level EOMIP-CCSDT quantum chemical approach and the quasidiabatic ansatz.
+A KDC Hamiltonian was constructed, and parametrised using the high-level EOM-CCSDT quantum chemical approach and the quasidiabatic ansatz.
 The resulting simulated photoelectron spectra of C$_2$H$^-$ and C$_2$D$^-$ resemble the experimental data, particularly in the complex energy region of the $\tilde{A}$ state origin.
@@
 
-\section{Methods}
-Details of the HR-PEI spectrometer are given in Refs~\onlinecite{cav07} and~\onlinecite{dev17}.
-C$_2$H$^-$ and C$_2$D$^-$ anions are produced by passing pure C$_2$H$_4$ or C$_2$D$_4$ gas at $\sim2$ bar pressure through a pulsed solenoid valve, into the source vacuum chamber.
-The gas undergoes adiabatic supersonic expansion into a high-voltage discharge which generates negative ions.
-The anions are extracted, accelerated to 500~eV, and focussed into a novel gating, bunching, and re-referencing unit~\cite{ded01}, before being mass separated over a 2m time-of-flight region.
-The anion of interest (C$_2$H$^-$ or C$_2$D$^-$) is then isolated by an electrostatic gate.
-The ion packet is crossed with a tuneable detachment laser beam, generated from a Continuum Sunlite EX optical parametric oscillator pumped by the third harmonic of a Continuum Powerlite 9010 Nd:YAG laser.
-The laser output is then doubled by passing through a BBO crystal, to produce UV laser pulse energies between 2-10mJ at 10Hz.
-The wavelength of the laser light is measured using a HighFinesse WS7 UV wavemeter.
-
-A modified velocity-map imaging lens images the detached photoelectrons to a 75mm diameter MCP/phosphor screen detector.
-Events are imaged by a 2048x2048 monochrome CCD camera (PCO 2000), with each frame transferred to a computer at a 10Hz repetition rate, and processed in real time to identify electron events, centroiding each position to
-a subpixel accuracy.
-The electron positions are then written to a data file for subsequent analysis.
-The velocity-map image is centred and then circularized by an angular dependent-radial scaling determined by comparing adjacent radial slice intensity profiles~\cite{gas17}.
-An inverse Abel transformation of the VMI, based on the algorithm of Hansen and Law~\cite{han85,hic19}, returns a slice image of the 3D electron source distribution.
-Absolute energy calibration of the photoelectron spectra is achieved using published measurements of species, including C$_2^-$~\cite{law19b} and NO$_2^-$~\cite{law19}, that have been studied under similar conditions and photon energies as those used for the C$_2$H$^-$ measurements.
-
 \section*{Supplementary Materials}
 See supplementary material for the complete list of C$_2$H and C$_2$D photoelectron transitions and assignments.
-%Hi~\cite{law17}
 
-\begin{acknowledgement}
+\begin{acknowledgments}
 	This research was supported by the Australian Research Council Discovery
 	Project Grants DP160102585 and DP190103151.  
-\end{acknowledgement}
+\end{acknowledgments}
 
 \section*{Data Availability}
+The data that support the findings of this study are available from the corresponding author upon reasonable request.
 
-% Create the reference section using BibTeX: 
-\bibliography{2022C2H.bib}
+\bibliography{Laws_C2H}
 
 \end{document}
-% ****** End of file apstemplate.tex ******
+%
+% ****** End of file aiptemplate.tex ******

### 2022-06-24 Resubmission/Laws_C2H_v2.tex
update resubmission

--- 2022-06-24 Resubmission/Laws_C2H.tex
@@
 \begin{abstract}
-High-resolution velocity-map imaged photoelectron spectra of the ethynyl anions C$_2$H$^-$ and C$_2$D$^-$ are measured over a range of photodetachment wavelengths, to investigate the complex interactions between the close lying $\tilde{X}^2\Sigma^+$ and $\tilde{A}^2\Pi$ electronic states.
-Vibronic coupling calculations are performed by transforming to a quasidiabatic representation, parametrised by \emph{ab-initio} CFOUR calculations, to model the interplay between pseudo Jahn-Teller and Renner-Teller coupling.
-This approach is combined with electron anisotropy measurements to assign all of the observed vibronic structure, providing a framework that may be used to accurately simulate spectra of larger C$_{2n}$H monohydride carbon chains.
+High-resolution velocity-map imaged photoelectron spectra of the ethynyl anions C$_2$H$^-$ and C$_2$D$^-$ are measured at photon wavelengths between $355-266$~nm, to investigate the complex interactions between the close lying $\tilde{X} ^2\Sigma^+$ and $\tilde{A} ^2\Pi$ electronic states.
+An indicative kinetic energy resolution of 0.4\%, together with full angular dependence of the fast electrons, provides a detailed description of the vibronically coupled structure.
+It is demonstrated that a modest quadratic vibronic coupling model, parametrized by the quasidiabatic ansatz, is sufficient to accurately recreate all of the observed vibronic interactions.
+Simulated spectra are shown to be in excellent agreement with the experimental data, verifying the proposed model, providing a framework that may be used to accurately simulate spectra of larger C$_{2n}$H monohydride carbon chains.
+New spectral assignments are supported by experimental electron anisotropy measurements and Dyson orbital calculations.
 \end{abstract}
@@
 C$_6$H$^-$ was the first negative ion detected in space, after it was observed in two distinct interstellar molecular clouds IRC+10216 and TMC-1 in 2006~\cite{mcc06}.
-More recently, anions C$_4$H$^-$~\cite{cer07} and C$_8$H$^-$~\cite{bru07,rem07} have also been detected in a range of environments, include dark clouds~\cite{cor13}, prestellar cores,~\cite{sak10} and prostellar envelopes~\cite{sak07}.
+More recently, anions C$_4$H$^-$~\cite{cer07} and C$_8$H$^-$~\cite{bru07,rem07} have also been detected in a range of environments, including dark clouds~\cite{cor13}, prestellar cores,~\cite{sak10} and prostellar envelopes~\cite{sak07}.
 
@@
 \text{C}_{2n}\text{H} + \text{C}_2\text{H}_2 \rightarrow \text{C}_{2n+2}\text{H}+\text{H}_2.
+\label{eq:1}
 \end{equation}
@@
 \begin{equation}
-\text{C}_{2n}\text{H}^- + \text{C}_2\text{H}_2 \rightarrow \text{C}_{2n+2}\text{H}^- + \text{H}_2.
+\text{C}_{2n}\text{H}^- + \text{C}_2\text{H}_2 \rightarrow \text{C}_{2n+2}\text{H}^- + \text{H}_2
+\label{eq:2}
 \end{equation}
-may be significant chain growth mechanisms that also needs to be included in astrochemical models~\cite{mil17,bas19}.
+may be significant chain growth mechanisms that should be included in astrochemical models~\cite{mil17,bas19}.
 Studies of the extraterrestrial planetary atmosphere of Saturn's moon Titan suggest that both C$_2$H and C$_2$H$^-$ play an important role in the atmospheric chemistry~\cite{dob16,vui09,des17,vri18}.
-Multiple reaction pathways involving the C$_2$H$^-$ have been proposed, including reactions with C$_2$H$_2$ and HCN.
+Many reaction pathways involving the C$_2$H$^-$ have been proposed, including reactions with C$_2$H$_2$ and HCN.
 
@@
 This creates a challenge for theory, as electronic spectral calculations are more difficult than those employed for pure rotational spectra~\cite{for10}.
-This becomes even more challenging when vibronic coupling effects are introduced, as they can be exceedingly difficult to model.
+A challenge more arduous when vibronic coupling effects are present, as they can be exceedingly difficult to model.
 
@@
 
-In this work the vibronic spectrum of the ethynyl radical C$_2$H is examined with High-Resolution Photoelectron Imaging (HR-PEI) together with CFOUR~\cite{dev20}  \emph{ab-initio} vibronic-coupling calculations.
-C$_2$H is reported to be one of the most abundant molecules in the universe, and is the most thoroughly studied of the C$_{2n}$H species~\cite{wil91,hei99,for10}.
+C$_2$H is reported to be one of the most abundant molecules in the ISM, and is the most thoroughly studied of the C$_{2n}$H species~\cite{wil91,hei99,for10}.
 Many different experimental techniques have been employed to help understand the complexities of the vibronic spectrum, including electron spin resonance~\cite{coc64,jin85}, laser magnetic resonance~\cite{bro88,pfe96,sch98}, microwave and millimeter wave spectroscopy~\cite{sas81,got83,end89,mul00}, infrared (matrix isolation~\cite{she87,jac87,for95} and Fourier Transform emission~\cite{ver88}) spectroscopy, laser induced fluorescence spectroscopy~\cite{hsu93,hsu95,chi99} and photoelectron spectroscopy of the negative ion~\cite{erv91,tay98,zho07}.
-C$_2$H has also received extensive theoretical attention to interpret the experimental results, however the large number of possible vibronic levels means this has proven to be a challenge~\cite{per90,per91,per91b,per91c,per92,car00,tar03,tar04,for10,sta21,gul21}.
-In this work we demonstrate how the construction of a quasidiabatic Hamiltonian allows the strength of vibronic interactions between coupled surfaces near a conical intersection to be estimated, sufficient to accurately simulate electronic and vibronic spectra.
-Anion HR-PEI spectroscopy maps both of the $^2\Sigma^+$ and $^2\Pi$ surfaces on an equal footing from the anion $\tilde{X}^1\Sigma^+$ state, allowing a direct comparison with \emph{ab-initio} modelling.
-
-\section{Methods}
-\subsection{Experimental Procedure}
-Details of the HR-PEI spectrometer are given in Refs~\onlinecite{cav07} and~\onlinecite{dev17}.
-Briefly, C$_2$H$^-$ and C$_2$D$^-$ anions are produced by passing pure ethylene (C$_2$H$_4$ or C$_2$D$_4$) gas at $\sim2$ bar pressure through a pulsed solenoid valve, into the source vacuum chamber.
-The gas undergoes adiabatic supersonic expansion into a high-voltage discharge which generates negative ions.
-The anions are extracted, accelerated to 500~eV, and focussed into a novel gating, bunching, and re-referencing unit~\cite{ded01}, before being mass separated over a 2m time-of-flight region.
-The anion of interest (C$_2$H$^-$ or C$_2$D$^-$) is then isolated by an electrostatic gate.
-The ion packet is crossed with a tuneable detachment laser beam, generated from a Continuum Sunlite EX optical parametric oscillator pumped by the third harmonic of a Continuum Powerlite 9010 Nd:YAG laser.
-The laser output is then doubled by passing through a BBO crystal, to produce UV laser pulse energies between 1-5mJ at 10Hz.
-The wavelength of the laser light is measured using a HighFinesse WS7 UV wavemeter.
-
-A modified velocity-map imaging lens images the detached photoelectrons to a 75mm diameter MCP/phosphor screen detector.
-Events are imaged by a 2048x2048 monochrome CCD camera (PCO 2000), with each frame transferred to a computer at a 10Hz repetition rate, and processed in real time to identify electron events, centroiding each position to
-a subpixel accuracy.
-The electron positions are then written to a data file for subsequent analysis.
-The velocity-map image is centred and then circularized by an angular dependent-radial scaling determined by comparing adjacent radial slice intensity profiles~\cite{gas17}.
-An inverse Abel transformation of the VMI, based on the algorithm of Hansen and Law~\cite{han85,hic19}, returns a slice image of the 3D electron source distribution.
-Absolute energy calibration of the photoelectron spectra is achieved using published measurements of species, including C$_2^-$~\cite{law19b} and NO$_2^-$~\cite{law19}, that have been studied under similar conditions and photon energies as those used for the C$_2$H$^-$ measurements.
-
-\subsection{Computational Details}
-Quantum chemical computations were preformed using the CFOUR computational package~\cite{dev20}.
-The equation-of-motion ionised-potential coupled-cluster singles, doubles, and triples (EOM-IP-CCSDT) level of theory with an atomic natural orbital basis set of quadruple-zeta quality (ANO2) was used on a closed-shell anionic reference to perform geometry optimisations and frequency calculations (including 1h + 2h1p + 3h2p excitations~\cite{mat16}).
-EOM is a highly accurate and robust framework that provides access to different types of target electronic states, including ionised states~\cite{gul21b,and22,bar07}.
-The linear diabatic coupling constants were calculated analytically at the EOM-IP-CCSD/ANO2 level.
-
-\section{Results and Analysis}
-Ethynyl ions were produced in a pulsed-jet discharge of pure ethylene (C$_2$H$_4$) gas, and subsequently mass isolated via time of flight.
-Electrons were detached using a tuneable Continuum Sunlite Ex Optical Parametric Oscillator (OPO) pumped with the third harmonic (355~nm) of a Nd:YAG laser.
-Higher electron counts were also obtained with the direct use of the third and fourth harmonics (266~nm) of the Nd:YAG laser.
-Detached electrons are mapped onto a micro channel plate detector using a Velocity Map Imaging (VMI) lens.
-An illustrative velocity map image containing $\sim$4 million electrons, collected from 355~nm (3.49~eV) photodetachment of C$_2$H$^-$ is shown in Fig.~\ref{fig:1}(a).
-The electrons are distributed radially according to their speed, with slow electrons near the image center, and fast electrons located towards the outer edge.
-Due to the relatively large C$_2$H electron affinity (EA) of 2.969~eV~\cite{erv91}, photodetachment at 355~nm produces photoelectrons with small (< 0.5~eV) kinetic energies.
-These slow electrons allow the use of a low repeller voltage ($-600$~V) for the VMI lens, spreading the electron velocity distribution across the whole detector to give a high electron velocity resolution.
-
-Despite the photodetachment energy being close to threshold, two electronic states of neutral C$_2$H are observed.
-The faster electrons, on the outer edge, correspond to C$_2$H$(\tilde{X}\,^2\Sigma^+)+e^- \leftarrow $C$_2$H$^-(\tilde{X}\,^1\Sigma^+)+h\nu$ photodetachment, and these are preferentially distributed around the poles of the image, indicative of a positive anisotropy parameter.
-Conversely the angular distribution of the slower electrons near the center is skewed towards the equator, indicative of a negative anisotropy parameter~\cite{buc70}.
-These electrons may be assigned to photodetachment to the first excited state C$_2$H$(\tilde{A}\,^2\Pi)+e^- \leftarrow $C$_2$H$^-(\tilde{X}\,^1\Sigma^+)+h\nu$.
-
-\begin{figure}
-	\includegraphics[width=0.8\textwidth]{figures/Fig1}
-	\caption{(a) Velocity map image of electrons from C$_2$H$^-$ photodetachment at 355~nm.
-(b) Velocity map image of C$_2$D$^-$ at 355~nm.
-Both images contain $\sim4$ million electrons.
-(c) Comparison of the corresponding 355~nm photoelectron spectra for C$_2$H$^-$ and C$_2$D$^-$.
-Structure below $\sim 27,000~$cm$^{-1}$ is associated with the ground state $\tilde{X} ^2\Sigma^+$, while structure above  $\sim 27,000~$cm$^{-1}$ is largely due to the excited neutral $\tilde{A} ^2\Pi$ state.}
-	\label{fig:1}
-\end{figure}
-
-To investigate the vibronic coupling interaction between these two nearby $\Sigma^+$ and $\Pi$ surfaces, deuterated ethynyl C$_2$D$^-$ was also studied.
-The C$_2$D$^-$ ions were produced in a discharge of pure C$_2$D$_4$ gas and measurements were performed under the same experimental conditions as those for C$_2$H$^-$.
-An illustrative velocity-map image of photodetachment at 355~nm from C$_2$D$^-$ is shown in Fig.~\ref{fig:1}(b).
-Similarly to Fig~\ref{fig:1}(a) two electronic transitions are observed.
-While the distribution of fast electrons is similar in both images, a striking difference is observed for the slow electrons, near the detector center.
-In Fig.~\ref{fig:1}(a) a series of weak rings are observed, however in Fig.~\ref{fig:1}(b) the image is dominated by two distinct rings.
-
-The velocity-map images of Fig.~\ref{fig:1} were inverted using the Abel inversion methods detailed in PyAbel~\cite{hic19} to extract the corresponding photoelectron spectra, presented in Fig.~\ref{fig:1}(c).
-Below $27,000~$cm$^{-1}$ binding energy, corresponding to the $\tilde{X} ^2\Sigma^+$ surface ,the C$_2$H$^-$ and C$_2$D$^-$ spectra are similar in structure.
-Both are dominated by the origin transition, shifted by $\sim10~$cm$^{-1}$ in the deuterated spectrum, with progressions involving the v$_2$($\pi$) bending and v$_3$($\sigma$) CC stretch vibrational normal modes.
-This structure also includes transitions involving an odd quanta of v$_2$ bending excitation ($2^{n+1}$) which are totally forbidden within the Franck-Condon approximation.
-The presence of these transitions in the spectra is an indicator of Herzberg-Teller (HT) vibronic coupling between the ground $^2\Sigma^+$ and nearby excited $^2\Pi$ electronic surfaces, as
-\begin{equation}
-\Sigma^+ \otimes \pi = \Pi. 
-\end{equation}
-
-Above $27,000~$cm$^{-1}$, near the $\tilde{A}^2\Pi$ state origin, significant differences are observed between the C$_2$H$^-$ and C$_2$D$^-$ photoelectron spectra.
-In C$_2$H$^-$, 5 sharp peaks are observed, spaced by $\sim95~$cm$^{-1}$.
-However in the deuterated spectrum, one dominant peak is observed at $27,792$~cm$^{-1}$, with 3 weaker peaks centred around $27,360~$cm$^{-1}$.
-Unlike the structure below $27,000$~cm$^{-1}$ none of these peaks are able to be readily assigned to vibronic transitions, due to the presence of strong coupling interactions between the nearby $\Sigma^+$ and $\Pi$ surfaces.
+Zhou~\emph{et al.} measured photodetachment of C$_2$H$^-$ and C$_2$D$^-$ to both the $\tilde{X} ^2\Sigma^+$ and $\tilde{A} ^2\Pi$ surfaces using slow electron velocity-map imaging (SEVI), which revealed detailed structure around the $\tilde{A} ^2\Pi$ state origin~\cite{zho07}.
+Comparison with calculations by Tarroni and Carter~\cite{tar03} resulted in detailed spectral assignments, however this was limited by the suppression of $p-$wave structure near threshold.
 
 \subsection{Vibronic Coupling Interactions}
-The complex spectral structure observed near the $\tilde{A}^2\Pi$ state origin in Fig.~\ref{fig:1}(c) may be understood by considering the $v_2$ bending vibrational mode.
+The complex spectral structure observed near the $\tilde{A}^2\Pi$ state origin in previous experiments may be understood by considering the $v_2$ bending vibrational mode.
 To account for the degeneracy of this mode, the vibronic quantum number $\ell_i$ may be introduced, representing the angular momentum associated with the bending motion.
-This may take a value of $\ell_i = v_i, v_i-2, v_i-4,\dots,1$ or $0$, where $v_i$ is the quanta of bending excitation.
+This may take a value of $\ell_i = v_i, v_i-2, v_i-4,\dots,1$ or $0$, where $v_i$ is the quantum of bending excitation.
 In the Born-Oppenheimer approximation, different vibronic energy levels $\ell_i$ are degenerate, however in cases with strong rovibronic coupling, this degeneracy in $\ell_i$ is lost.
@@
 These interactions spread the electronic orgin of the $\tilde{A}\,^2\Pi$ state over several vibronic levels.
-Therefore, instead of assigning a defined origin, the observed peaks in the spectrum may be assigned to coupled admixtures of vibronic transitions involving the three potential energy surfaces,
+Therefore, instead of assigning a defined origin, the peaks observed in experimental spectra may be assigned to coupled admixtures of vibronic transitions involving the three potential energy surfaces,
 \begin{equation}
 \Psi_f = \sum_\xi \psi_e^\xi \sum_k C_{fk}^\xi\phi_{fkm}^\xi,
-\label{eq:teller3} 
+\label{eq:3} 
 \end{equation}
@@
 $\xi$ represents the electronic states used in the expansion ($\xi=\Sigma^+(1A'),~\Pi^+(2A'),~\Pi^-(1A'')$).
-A depiction of these three interacting surfaces, generated from the parameters in Ref.~\onlinecite{tar03}, is given in Fig.~\ref{fig:2}.
+
+C$_2$H has received extensive theoretical attention in an attempt to interpret the experimental results~\cite{per90,per91,per91b,per91c,per92,car00,tar03,tar04,for10,sta21,gul21}.
+This includes the variational method of Tarroni and Carter, which has been used to calculate a multitude of admixed vibronic levels in C$_2$H.
+A depiction of the three interacting potential energy surfaces in Eq.~(\ref{eq:3}), generated from the variational parameters of Ref~\onlinecite{tar03}, is shown in Fig.~\ref{fig:1}.
+This illustrates the loss of degeneracy for the doublet $^2\Pi$ surfaces along the CCH bending coordinate, due to the Renner-Teller and pseudo Jahn-Teller interactions.
+From these surfaces more than 100 possible C$_2$H vibronic states have been calculated, up to 10,000~cm$^{-1}$ above the $\tilde{X} ^2\Sigma^+$ origin~\cite{tar03}.
+However, assigning experimental spectra has remained a challenge, partly due to the large number of calculated levels, providing multiple options for each experimentally observed transition.
+The complexity of the variational approach also limits the extension of this method to larger C$_{2n}$H chains.
+
+In this work we demonstrate that the construction of a quasidiabatic Hamiltonian allows the strength of vibronic interactions between coupled surfaces near a conical intersection to be estimated, sufficient to accurately simulate electronic and vibronic spectra.
+Anion HR-PEI spectroscopy maps both of the $^2\Sigma^+$ and $^2\Pi$ surfaces on an equal footing from the anion $\tilde{X}^1\Sigma^+$ state, allowing a direct comparison with the \emph{ab-initio} modelling.
+This is combined with experimental anisotropy measurements and Dyson orbital analysis to examine the vibronic symmetry of each observed transition to verify spectral assignments.
 
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{figures/Fig2}
+	\includegraphics[width=0.5\textwidth]{figures/Fig1}
 	\caption{Adiabatic potential energy surfaces of $\tilde{X}^2\Sigma^+$, $\tilde{A}^2\Pi^-$, and $\tilde{A}^2\Pi^+$ states, calculated using the parameters calculated by Tarroni and Carter~\cite{tar03}.}
-	\label{fig:2}
+	\label{fig:1}
 \end{figure}
 
-The adiabatic potential energy surfaces in Figure~\ref{fig:2} were evaluated from the variational parameters of Tarroni and Carter~\cite{tar03}, illustrating the loss of degeneracy for the doublet $^2\Pi$ surfaces, due to the Renner-Teller and pseudo Jahn-Teller interactions.
-This technique has been used to calculate a multitude of admixed vibronic levels.
-More than 100 possible C$_2$H vibronic states have been calculated, up to 10,000~cm$^{-1}$ above the $\tilde{X} ^2\Sigma^+$ origin.
-However, assigning experimental spectra has remained a challenge, partly due to the large number of calculated levels providing for multiple possible assignments for each experimentally observed transition.
+\section{Methods}
+\subsection{Experimental Procedure}
+Details of the HR-PEI spectrometer are given in Refs~\onlinecite{cav07} and~\onlinecite{dev17}.
+Briefly, ethynyl ions C$_2$H$^-$ and C$_2$D$^-$ were produced in a pulsed-jet discharge of pure ethylene (C$_2$H$_4$/C$_2$D$_4$) gas, and subsequently mass isolated over a 2m-long time of flight region~\cite{ded01}.
+Electrons were detached using a tuneable Continuum Sunlite Ex Optical Parametric Oscillator (OPO) pumped with the third harmonic (355~nm) of a Nd:YAG laser.
+Higher electron counts were also obtained with the direct use of the third and fourth harmonics (266~nm) from the Nd:YAG laser.
+The detached electrons are mapped onto a micro-channel plate detector using a modified Velocity Map Imaging (VMI) lens.
+Each detachment event is imaged by a 2048x2048 monochrome CCD camera (PCO 2000), with each frame transferred to a computer within the 10Hz repetition rate of the laser and processed in real time to identify electron events, centroiding each position to a subpixel accuracy.
 
-\subsection{Coupling Calculations}
-In order to guide spectral assignment of C$_2$H and future astronomical searches for other C$_n$H radicals, transition intensities are also needed.
+The resulting velocity-map image is centred and then circularized by an angular dependent-radial scaling determined by comparing adjacent radial slice intensity profiles~\cite{gas17}.
+An inverse Abel transformation of the velocity-map image, based on the algorithm of Hansen and Law~\cite{han85,hic19}, returns a slice image of the 3D electron source distribution.
+Absolute energy calibration of the photoelectron spectra is achieved using published measurements of species, including C$_2^-$~\cite{law19b} and NO$_2^-$~\cite{law19}, that have been studied under similar conditions and photon energies as those used for the C$_2$H$^-$ measurements.
+
+%--------------------------------------------------------------------
+
+\subsection{Computational Details}
+Quantum chemical computations were preformed using the CFOUR computational package~\cite{dev20}.
+The equation-of-motion ionised-potential coupled-cluster singles, doubles, and triples (EOM-IP-CCSDT) level of theory with an atomic natural orbital basis set of quadruple-zeta quality (ANO2) was used on a closed-shell anionic reference to perform geometry optimisations and frequency calculations (including 1h + 2h1p + 3h2p excitations~\cite{mat16}).
+EOM is a highly accurate and robust framework that provides access to different types of target electronic states, including ionised states, making it well suited to the study of photodetachment~\cite{gul21b,and22,bar07}.
+The linear diabatic coupling constants were calculated analytically at the EOM-IP-CCSD/ANO2 level.
+
+Dyson orbitals, that are used to analyse the experimental electron anisotropy, were generated using Q-Chem software~\cite{sha15} at the EOM-CCSD/aug-gg-pVTZ level.
+Anisotropy parameters were then calculated using the ezDyson software of Gozem and Krylov~\cite{goz22}.
+
+\subsection{The Quasidiabatic Ansatz} 
+In order to guide spectral assignment of C$_2$H and future astronomical searches for other C$_n$H radicals, transition intensities are required.
 However, due to the strong vibronic coupling interactions, transition intensities can not be obtained via simple Franck-Condon calculations based on quantum chemistry methods.
-To account for these interactions, the photoelectron spectrum of the C$_2$H$^-$ anion is simulated using a quasidiabatic Hamiltonian of the type introduced by Koeppel, Domcke and Cederbaum (KDC).~\cite{kou84,dom81} In this approach, the Hamiltonian is represented in a basis of quasidiabatic (slowly varying) electronic  states for which the kinetic energy operator can be assumed diagonal.~\cite{pac93} For C$_2$H, the KDC Hamiltonian comprises three states - the two components of the $^2\Pi$ state and the ground $^2\Sigma^+$ state - and is then projected onto a vibrational basis, usually chosen as a direct product of harmonic oscillators.
+To account for these interactions, the photoelectron spectrum of the C$_2$H$^-$ anion is simulated, in this work, using a quasidiabatic Hamiltonian of the type introduced by Koeppel, Domcke and Cederbaum (KDC).~\cite{kou84,dom81} In this approach, the Hamiltonian is represented in a basis of quasidiabatic (slowly varying) electronic  states for which the kinetic energy operator can be assumed diagonal.~\cite{pac93} For C$_2$H, the KDC Hamiltonian comprises three states - the two components of the $^2\Pi$ state and the ground $^2\Sigma^+$ state - and is then projected onto a vibrational basis, usually chosen as a direct product of harmonic oscillators.
 Diagonalization of the corresponding matrix yields the molecular states (which are given in terms of a Born-Huang expansion), and the squared projections of the corresponding eigenvectors onto the ground state of the anion yield the relative intensities.
@@
 The present calculations use the so-called quadratic vibronic coupling (QVC) model.~\cite{ich06} For the system at hand, the QVC model Hamiltonian  assumes the following form
-
 \begin{align}
@@
 	A(a'') & \lambda q_{2b} & \eta q_{2a}q_{2b} & \substack{\Delta_0^A+F_1^Aq_1+F_3^Aq_3\\+\frac{1}{2}\sum_{ij}F_{ij}^Aq_iq_j\\-\frac{1}{2}\eta(q_{2a}^2-q_{2b}^2) } } \qquad
-\label{eq:calc1}
+\label{eq:5}
 \end{align}
-
 where the summations run over the dimensionless normal modes ($q_i$) that serve as the coordinate system for the problem.~\cite{sta21,car00} For convenience, the latter are chosen to be those of the anion, which considerably facilitates calculation of the spectral intensities.
-In Eq.~(\ref{eq:calc1}), the diagonal terms of V (excluding those that carry the Renner-Teller coupling constant $\eta$) represent the quasidiabatic potential energy surfaces of the $^2\Sigma^+$ state, and the two components of the $^2\Pi$ state, chosen here as those in which the unpaired electron lies within or is perpendicular to an arbitrarily chosen plane, designated as A(a$'$) and A(a$''$), respectively.
+In Eq.~(\ref{eq:5}), the diagonal terms of V (excluding those that carry the Renner-Teller coupling constant $\eta$) represent the quasidiabatic potential energy surfaces of the $^2\Sigma^+$ state, and the two components of the $^2\Pi$ state, chosen here as those in which the unpaired electron lies within or is perpendicular to an arbitrarily chosen plane, designated as A(a$'$) and A(a$''$), respectively.
 $\Delta_0^X$ is the separation of the anion and $^2\Sigma^+$ states at the origin of the coordinate system (the vertical electron detachment energy), and $\Delta_0^{A}$ is the gap between anion and $^2\Pi$ states at the same geometry.
@@
 For each component of the $^2\Pi$ state, either the 2a or 2b component of the bending vibration will maintain the A$'$ electronic symmetry that is needed to couple with the $^2\Sigma^+$ state.
-Designating these as 2a for the A(a$'$) state and 2b for the A(a$''$) state (as is implicit in Eq.~\ref{eq:calc1}), the diabatic force constants for the bending mode in the $^2\Sigma^+$ and $^2\Pi$ states can be written as
-
+Designating these as 2a for the A(a$'$) state and 2b for the A(a$''$) state (as is implicit in Eq.~\ref{eq:5}), the diabatic force constants for the bending mode in the $^2\Sigma^+$ and $^2\Pi$ states can be written as
 \begin{align}
@@
 F_{22}^A &= f_{2a2a}^{A(a')}-\frac{2\lambda^2}{(\Delta_0^A-\Delta_0^X)}-\eta
-\label{eq:calc2}
+\label{eq:7}
 \end{align}
-
 where the Renner-Teller interaction strength ($\eta$) is determined from 
-
 \begin{equation}
 \eta = \frac{1}{2}\left[ f_{2a2a}^{A(a')}-f_{2b2b}^{A(a')}-\frac{2\lambda^2}{(\Delta_0^A-\Delta_0^X)}\right]
-\label{eq:calc3}
+\label{eq:8}
+\end{equation}
+once the interstate coupling ($\lambda$ which is calculated analytically in this work) is known.
+
+\section{Results and Analysis}
+An illustrative velocity map image containing $\sim$4 million electrons, collected from 355~nm (3.49~eV) photodetachment of C$_2$H$^-$ is shown in Fig.~\ref{fig:2}(a), and for C$_2$D$^-$ detachment under the same conditions in Fig.~\ref{fig:2}(b).
+In both images the laser polarisation is aligned along the vertical axis, and electrons are distributed radially according to their speed, with slow electrons near the image center, and fast electrons located towards the outer edge.
+Due to the relatively large C$_2$H electron affinity (EA) of 2.969~eV~\cite{erv91}, photodetachment at 355~nm produces photoelectrons with small (< 0.5~eV) kinetic energies, resulting in high electron velocity resolution, with transition widths varying from 21~cm$^{-1}$ (around 24,000~cm$^{-1}$) to only 7~cm$^{-1}$ (near 28,000~cm$^{-1}$).
+Despite the photodetachment energy being close to threshold, detachment to both the $\tilde{X} ^2\Sigma^+$ and $\tilde{A} ^2\Pi$ electronic states is observed due to the low Term energy $\sim 3,700~$cm$^{-1}$.
+The faster electrons, on the outer edge of Figs.~\ref{fig:2}(a) and (b), correspond to C$_2$H$(\tilde{X}\,^2\Sigma^+)+e^- \leftarrow $C$_2$H$^-(\tilde{X}\,^1\Sigma^+)+h\nu$ photodetachment, and are preferentially distributed around the poles of the image, indicative of a positive electron anisotropy parameter.
+Conversely the angular distribution of the slower electrons, near the center of Figs.~\ref{fig:2}(a) and (b), is skewed towards the equator, indicative of a negative anisotropy parameter~\cite{buc70}.
+These electrons may be assigned to photodetachment to the first excited state C$_2$H$(\tilde{A}\,^2\Pi)+e^- \leftarrow $C$_2$H$^-(\tilde{X}\,^1\Sigma^+)+h\nu$.
+
+\begin{figure}
+	\includegraphics[width=0.8\textwidth]{figures/Fig2}
+	\caption{(a) Velocity map image of electrons from C$_2$H$^-$ photodetachment at 355~nm.
+(b) Velocity map image of C$_2$D$^-$ at 355~nm.
+Both images contain $\sim4$ million electrons.
+(c) Comparison of the corresponding 355~nm photoelectron spectra for C$_2$H$^-$ and C$_2$D$^-$.
+Structure below $\sim 27,000~$cm$^{-1}$ is associated with the ground state $\tilde{X} ^2\Sigma^+$, while structure above  $\sim 27,000~$cm$^{-1}$ is largely due to the excited neutral $\tilde{A} ^2\Pi$ state.}
+	\label{fig:2}
+\end{figure}
+
+The velocity-map images of Fig.~\ref{fig:2} were inverted using the Abel inversion methods detailed in PyAbel~\cite{hic19} to extract the corresponding photoelectron spectra, presented in Fig.~\ref{fig:2}(c).
+The structure below $27,000~$cm$^{-1}$ in binding energy, corresponding to the $\tilde{X} ^2\Sigma^+$ surface, is similar for both C$_2$H$^-$ and C$_2$D$^-$ detachment.
+They are dominated by the origin transition, shifted by $\sim10~$cm$^{-1}$ in the deuterated spectrum, with progressions involving the v$_2$($\pi$) bending and v$_3$($\sigma$) CC stretch vibrational normal modes.
+This structure also includes transitions involving an odd quanta of v$_2$ bending excitation ($2^{n+1}$) which are totally forbidden within the Franck-Condon approximation.
+The presence of these transitions in the spectra is an indicator of Herzberg-Teller (HT) vibronic coupling between the ground $^2\Sigma^+$ and nearby excited $^2\Pi$ electronic surfaces, as
+\begin{equation}
+\Sigma^+ \otimes \pi = \Pi. 
+\label{eq:9}
 \end{equation}
 
-once the interstate coupling ($\lambda$ which is calculated analytically in this work, see below) is known.
+At binding energies above $\sim27,000~$cm$^{-1}$ in Fig.~\ref{fig:2}(c), near the $\tilde{A}^2\Pi$ state origin, significant differences are observed between the C$_2$H$^-$ and C$_2$D$^-$ photoelectron spectra.
+In C$_2$H$^-$, 5 sharp peaks are observed, spaced by $\sim95~$cm$^{-1}$.
+However in the deuterated spectrum, one dominant peak is observed near $27,790$~cm$^{-1}$, with 3 weaker peaks centred around $27,360~$cm$^{-1}$.
+Unlike the structure below $27,000$~cm$^{-1}$ none of these peaks are able to be readily assigned to vibronic transitions, due to the presence of strong coupling interactions between the nearby $\Sigma^+$ and $\Pi$ surfaces.
 
-When the potential in Eq.~(\ref{eq:calc1}) is diagonalized, the adiabatic states that are used for its parametrization are precisely recovered through terms second order in displacement.
-The parametrization of the potential in this work was completed using the CFOUR computational package~\cite{dev20} and the quasidiabatic ansatz of Ichino~\emph{et al.}~\cite{ich09} Briefly,the EOM procedure is used to operationally define quasidiabatic states (those that relax according to a well-behaved reference state wavefunction, which is that of the anion level) and the coupling constants are then evaluated as the first derivative of the off-diagonal elements of the electronic Hamiltonian in the basis defined by this representation.
+%--------------------------------------------------
+
+\subsection{Vibronic Coupling Calculations}
+The QVC model Hamiltonian (Eq.~\ref{eq:5}) generated in Section II C was employed to calculate the vibronic coupling effects observed in the photoelectron spectra of C$_2$H$^-$ and C$_2$D$^-$ in Fig.~\ref{fig:2}.
+When the QVC Hamiltonian is diagonalized, the adiabatic states that are used for its parametrization are precisely recovered through terms second order in displacement.
+The parametrization of the potential in this work was completed using the CFOUR computational package~\cite{dev20} and the quasidiabatic ansatz of Ichino~\emph{et al.}~\cite{ich09} Briefly, the EOM procedure is used to operationally define quasidiabatic states (those that relax according to a well-behaved reference state wavefunction, which is that of the anion level) and the coupling constants are then evaluated as the first derivative of the off-diagonal elements of the electronic Hamiltonian in the basis defined by this representation.
 Vertical excitation energies ($\Delta_0$), and linear diabatic force and coupling constants between the electronic states of interest were calculated analytically using the highly accurate EOM-IP-CCSDT/ANO2 procedure.
 The interstate coupling constants ($\lambda$) were calculated analytically at the EOM-IP-CCSD/ANO2 level.
-All calculated values used to parametrize the KDC potential in Eq.~(\ref{eq:calc1}) are presented in Table~\ref{tab:1}.
+All calculated values used to parametrize the KDC potential in Eq.~(\ref{eq:5}) are presented in Table~\ref{tab:1}.
 
 \begin{table}
-	\caption{Parameters for the quasidiabatic Hamiltonian Eq.~(\ref{eq:calc1}) determined using CFOUR and the quasidiabatic ansatz. Units are in cm$^{-1}$.}
+	\caption{Parameters for the quasidiabatic Hamiltonian Eq.~(\ref{eq:5}) determined using CFOUR and the quasidiabatic ansatz. Units are in cm$^{-1}$.}
 	\label{tab:1}
@@
 
-\subsection{Simulated Spectra}
-The above method was employed to simulate the photoelectron spectrum of C$_2$H$^-$, with the calculated transitions shown in Figure~\ref{fig:3}(a) alongside the experimental data at 355~nm.
-Photoelectron spectra are simulated using the xsim package of CFOUR~\cite{dev20} and the model Hamiltonian generated above.
-The xsim module projects the Hamiltonian (Eq.~\ref{eq:calc1}) onto a vibrational basis, which is then diagonalised using Lanczos algorithm to calculate transition energies and intensities that map to the measured photoelectron spectrum.
+The photdetachment transitions of C$_2$H$^-$ and C$_2$D$^-$ were calculated using the parameters in Table~\ref{tab:1} and the xsim package of CFOUR~\cite{dev20}.
+The xsim module projects the Hamiltonian (Eq.~\ref{eq:5}) onto a vibrational basis, which is then diagonalised using Lanczos algorithm to calculate transition energies and intensities that map to the measured photoelectron spectrum.
 In this simulation the transition moments for the two ionisation processes are assumed to be equal.
-On the $\tilde{X} ^2\Sigma^+$ surface, below 3,600~cm$^{-1}$, there is excellent agreement in both the transition positions and intensities between the simulated and experimental spectra.
-This includes the HT coupled (2$^{n+1}$) transitions with $\Pi$ symmetry, which would normally be missing from a simulation using the standard \emph{ab-initio} approaches.
-
-The positions of the calculated levels for the $\tilde{A}^2\Pi$ state have been shifted by 1,220~cm$^{-1}$ to account for the EOMIP-CCSDT calculations overestimating the effective Term energy.
-The experimental data show that the electronic coupling interactions induce a splitting of the $\tilde{A} ^2\Pi$ state origin over 5 vibronic levels, spaced by $\sim 95~$cm$^{-1}$ ($a-e$).
-This splitting is also observed in the calculated spectrum, which reproduces the 5 prominent transitions in this region.
-The relative intensities between the calculated transitions are also in agreement with the experimental data.
-Peak $d$ is slightly overestimated in intensity, which may in part be due to the variation of photodetachment cross section near threshold, as described by the Wigner threshold law~\cite{wig48}.
-The simulated spectrum also slightly underestimates the splitting between the vibronic levels, which may be linked to the overestimation of the calculated gap between the $^2\Sigma$ and $^2\Pi$ surfaces.
+The calculated transitions are shown in Figs.~\ref{fig:2}(a) and (b) alongside the experimental photoelectron spectra measured at 355~nm.
+Transitions with $\Sigma$ vibronic symmetry are shown in blue and transitions with $\Pi$ symmetry are in orange.
+The positions of the $\tilde{A} ^2\Pi$ transitions have been shifted by 500~cm$^{-1}$ to account for the EOMIP-CCSDT calculations overestimating the effective Term energy ($\Delta^A_0-\Delta^X_0$ in Table~\ref{tab:1}).
 
@@
 
-The photoelectron spectrum of C$_2$D$^-$ was also examined using the same approach, with the calculated transitions shown in Figure~\ref{fig:3}(b) alongside the 355~nm experimental data.
-Again, there is excellent agreement in the intensity and calculated positions of the transitions on the $\tilde{X} ^2\Sigma^+$ state surface, including the HT coupled levels.
+Figure~\ref{fig:3}(a) shows excellent agreement in both the transition positions and intensities between the calculated and experimental C$_2$H$^-$ photodetachment spectra on the $\tilde{X} ^2\Sigma^+$ surface, below $3,600~$cm$^{-1}$.
+This includes the HT coupled (2$^{n+1}$) transitions with $\Pi$ symmetry, which would normally be missing from a simulation using the standard \emph{ab-initio} approaches.
+Near the excited state surface (peaks $a-e$ in Fig.~\ref{fig:3}(a)) the experimental data shows that the electronic coupling interactions induce a splitting of the $\tilde{A} ^2\Pi$ state origin over 5 vibronic levels, spaced by $\sim 95~$cm$^{-1}$.
+This splitting is also observed in the calculated spectrum, which reproduces the 5 prominent transitions in this region.
+Fig.~\ref{fig:3}(a) shows that the relative intensities between the calculated transitions near $3,700~$cm$^{-1}$ are also in agreement with the experimental data.
+Peak $d$ is slightly overestimated in intensity, which may in part be due to the variation of photodetachment cross section near threshold, as described by the Wigner threshold law~\cite{wig48}.
+The simulated spectrum also slightly underestimates the magnitude of the splitting between the vibronic levels, which may be linked to the overestimation of the calculated gap between the $^2\Sigma^+$ and $^2\Pi$ surfaces.
+
+The photoelectron spectrum of C$_2$D$^-$ was also examined using the same approach, with the calculated transitions shown in Fig.~\ref{fig:3}(b) alongside the 355~nm experimental data.
+Again, there is excellent agreement in the intensity and calculated positions of the transitions on the $\tilde{X} ^2\Sigma^+$ state surface (below $3,600~$cm$^{-1}$ in Fig.~\ref{fig:3}(b)).
+This includes the HT coupled transitions ($2^1_0,~2^1_03^1_0,~2^3_03^1_0$).
 Near the $\tilde{A} ^2\Pi$ state origin, deuteration has a large impact on the experimental photoelectron spectrum.
-Instead of the 5 evenly split levels observed in C$_2$H, a single dominant peak ($e$) is now observed near $\sim3,845$~cm$^{-1}$ alongside a collection of weaker peaks ($a-d$) centred around 3,400~cm$^{-1}$.
+Instead of the 5 evenly split levels observed in C$_2$H$^-$ in Fig.~\ref{fig:3}(a), a single dominant peak ($e$) is now observed near $\sim3,845$~cm$^{-1}$ alongside a collection of weaker peaks ($a-d$) centred around 3,400~cm$^{-1}$.
 Based on the observed spin-orbit splitting measurements from rotationally resolved IR spectra~\cite{yan87,sch98,ste88}, peak $e$ is expected to have significant $\tilde{A} ^2\Pi$ character, with peaks $a-d$ commonly assigned to vibronic levels with predominantly HT coupled $\tilde{X} ^2\Sigma^+$ character~\cite{yan87,hsu95,chi99,wil11}.
 This suggests that deuteration effectively dampens the coupling interaction between the surfaces, as has been observed in the vinylidene photoelectron spectrum~\cite{dev17}.
+This is supported by the reduction in the calculated coupling constants $\lambda$ and $\eta$ for C$_2$D$^-$ in Table~\ref{tab:1}.
 
-The simulated spectrum reproduces the large change observed for the deuterated species.
+The calculated transitions in Fig.~\ref{fig:3}(b) reproduce the large change observed experimentally for the deuterated species.
 The calculated intensity pattern of the vibronic levels around the $\tilde{A} ^2\Pi$ origin also mirrors the experimental data, with a single intense transition observed near peak $e$, and 3 prominent transitions predicted around the experimental peaks $a-d$.
-The calculated splitting between the levels is also similar.
+The calculated splitting between the levels is also similar, verifying that the proposed QVC model is an accurate method for calculating the vibronic coupling interactions in C$_2$H and C$_2$D.
 
-To investigate the effects of coupling on the higher excited vibronic levels on the~$\tilde{A} ^2\Pi$ surface, the calculations were compared with the experimental photoelectron spectrum of C$_2$H$^-$ at 266~nm, as presented in Figure~\ref{fig:4}.
-Gaussian functions were fitted to the transitions from Figure~\ref{fig:3}(a) with a kinetic energy dependent FWHM of $\Delta\text{E}/\text{E} = 0.4\%$ ($\Gamma=55-30$~cm$^{-1}$) to match the lower resolution of the experimental data at high electron kinetic energies.
-Near 3,900~cm$^{-1}$ excitation energy the electronic origin of the $\tilde{A} ^2\Pi$ state is split over 5 vibronic levels, as has been discussed above.
-A similar effect is also observed for the $3^1_0$ band, which becomes split over 3 vibronic levels labelled $l$, $n$, and $o$.
+\subsection{Excited State Simulation}
+To investigate the effects of coupling on the higher excited vibronic levels on the~$\tilde{A} ^2\Pi$ surface, the calculations were compared with the experimental photoelectron spectrum of C$_2$H$^-$ at 266~nm, as presented in Fig.~\ref{fig:4}.
+Photodetachment at 266~nm (4.66~eV) maps out more of the $\tilde{A} ^2\Pi$ potential energy surface, at the cost of lower electron velocity resolution.
+Gaussian functions were fitted to the transitions from Fig.~\ref{fig:3}(a) with a kinetic energy dependent FWHM of $\Delta\text{E}/\text{E} = 0.4\%$ ($\Gamma=55-30$~cm$^{-1}$) to match the lower resolution of the experimental data at high electron kinetic energies.
+By showing the convolved spectrum, the suitability of the QVC model to simulate spectra capable of direct comparison to experimental or astronomical data can be examined.
+In Fig.~\ref{fig:4} the electronic origin of the $\tilde{A} ^2\Pi$ state (near $\sim3,700~$cm$^{-1}$) is split over 5 vibronic levels, as has been discussed above.
+A similar effect is also observed for the $3^1_0$ band near $\sim5,400~$cm$^{-1}$, which becomes split over 3 vibronic levels labelled $l$, $n$, and $o$.
 The calculated spectrum correctly predicts the position and intensity of peaks $n$ and $o$, but appears to strongly underestimate the intensity of peak $l$.
@@
 
-The results from Figures~\ref{fig:3} and~\ref{fig:4} confirm that the quasidiabatic approach is able to accurately describe the vibronic interactions between the $^2\Sigma^+$ and $^2\Pi$ surfaces, including deuteration effects.
+The results from Figs.~\ref{fig:3} and~\ref{fig:4} confirm that the quasidiabatic approach is able to accurately describe the vibronic interactions between the $^2\Sigma^+$ and $^2\Pi$ surfaces, including deuteration effects.
 This validates the proposed vibronic interactions, and demonstrates how this method can be employed to decode and assign even complex spectra.
-While the present calculations invoke a high level of \emph{ab-initio} theory (EOM-CCSDT), the level of parametrization of the vibronic Hamiltonian is relatively simple (QVC model).
+While the present calculations invoke a high level of \emph{ab-initio} theory (EOM-IP-CCSDT), the level of parametrization of the vibronic Hamiltonian is relatively simple (QVC model).
 The approach could be systematically improved with a more elaborate expansion, such as that used in Ref.~\onlinecite{sim12} for the NO$_3$ radical.
-Applying this approach to similar systems will produce reliable predictions for the position and intensity of dominant transitions, and help guide the search for these molecules in laboratory experiments and astronomical observations.
+Applying this approach to similar systems will likely produce reliable predictions for the position and intensity of dominant transitions and help guide the search for these molecules in laboratory experiments and astronomical observations.
 
@@
 The quasidiabatic Hamiltonian approach is able to determine the symmetry of each individual vibronic state, either $\Sigma$ or $\Pi$, which may be compared directly to the observed anisotropy of each transition.
-The velocity-map images from this work (Fig~\ref{fig:1}) were obtained using a linearly polarized detachment laser.
-Therefore, the differential cross section of emitted electrons is given by,
+The velocity-map images from this work (Fig.~\ref{fig:1}) were obtained using a linearly polarized detachment laser.
+Therefore, the differential cross section of emitted electrons is given by
 \begin{equation}
 \frac{\text{d}\sigma}{\text{d}\Omega}=\frac{\sigma_{\text{total}}}{4\pi}[1+\beta P_{2}(\cos\theta)],
-\label{eq:beta1}
+\label{eq:10}
 \end{equation}
@@
 laser polarization, and $P_2$ is the second-order Legendre polynomial.
-The anisotropy parameter $\beta$ provides a quantitative measure of the electron anisotropy, which ranges from -1 to +2, the limits representing purely perpendicular and parallel transitions respectively.
+The electron anisotropy parameter $\beta$ provides a quantitative measure of the electron anisotropy, which ranges from -1 to +2, the limits representing purely perpendicular and parallel transitions respectively.
 Through conservation of angular momentum, $\beta$ may be described in terms of the detachment partial waves, which are linked to the symmetry of the state accessed by photodetachment.
@@
 {(1-\gamma_p)B_1\epsilon+\gamma_p(1+2A_1^2\epsilon^2)}
-\label{eq:beta-sp}
+\label{eq:11}
 \end{equation}
@@
 |\psi\rangle = \sqrt{1-\gamma_p}|s\rangle + \sqrt{\gamma_p}|p\rangle.
+\label{eq:12}
 \end{equation}
-$A_1$ and $B_1$ in Eq.~(\ref{eq:beta-sp}) are the generalised Hanstorp~\cite{han89} coefficients describing the assumed Wigner-like~\cite{wig48} relative scalings of the radial transition dipole matrix elements for different allowed detachment channels.
+$A_1$ and $B_1$ in Eq.~(\ref{eq:11}) are the generalised Hanstorp~\cite{han89} coefficients describing the assumed Wigner-like~\cite{wig48} relative scalings of the radial transition dipole matrix elements for different allowed detachment channels.
 Specifically, $A_1\epsilon$ describes the energy-dependent ratio of the $p\rightarrow d$ and $p\rightarrow s$ transition amplitudes, while $B_1\epsilon$ corresponds to the $s\rightarrow p$ and $p\rightarrow s$ cross-section ratio~\cite{khu14}.
 It can be shown that under certain approximations $B_1/A_1 = 8/3$~\cite{san13}.
-Finally, $\delta_{2,0}$ in Eq.~(\ref{eq:beta-sp}) is the phase shift between the $s$ and $d$ partial waves, which in most cases of anion photodetachment is assumed to be small, corresponding to $\cos\delta_{2,0}\approx1$.
+Finally, $\delta_{2,0}$ in Eq.~(\ref{eq:11}) is the phase shift between the $s$ and $d$ partial waves, which in most cases of anion photodetachment is assumed to be small, corresponding to $\cos\delta_{2,0}\approx1$.
 
-From Eq.~(\ref{eq:beta-sp}) it can be seen that detachment from a pure $s$ orbital ($\gamma_p=0$) will have a positive anisotropy ($\beta = +2$), whereas detachment from a pure $p$ orbital ($\gamma_p=1$) will have a negative anisotropy for electron kinetic energies $\epsilon < 2/A_1$.
-Therefore, measuring the anisotropy can help determine the electronic character of each individual transition, which may be compared to the calculated symmetries in Figure~\ref{fig:3}.
-For each prominent transition in the photoelectron spectrum of C$_2$H$^-$ in Figure~\ref{fig:1} the corresponding anisotropy parameter may be calculated by fitting Eq.~(\ref{eq:beta1}) to a plot of the integrated radial intensity (across the peak) versus angle, as (for a single quadrant of the electron image) the intensity variation is linear in $P_2(\cos\theta)$ with a slope equal to $\beta\times$intercept.
-This procedure was applied to all of the photoelectron spectra measured in this work, with the energy dependent anisotropy parameters presented in Figure~\ref{fig:5}(a).
+From Eq.~(\ref{eq:11}) it can be seen that detachment from a pure $s$ orbital ($\gamma_p=0$) will have a positive anisotropy ($\beta = +2$), whereas detachment from a pure $p$ orbital ($\gamma_p=1$) will have a negative anisotropy for electron kinetic energies $\epsilon < 2/A_1$.
+Therefore, measuring the anisotropy can help determine the electronic character of each individual transition, which may be compared to the calculated symmetries in Fig.~\ref{fig:3}.
+For each prominent transition in the photoelectron spectrum of C$_2$H$^-$ in Fig.~\ref{fig:1} the corresponding anisotropy parameter may be calculated by fitting Eq.~(\ref{eq:10}) to a plot of the integrated radial intensity (across the peak) versus angle, as (for a single quadrant of the electron image) the intensity variation is linear in $P_2(\cos\theta)$ with a slope equal to $\beta\times$intercept.
+This procedure was applied to all of the photoelectron spectra measured in this work, with the energy dependent anisotropy parameters presented in Fig.~\ref{fig:5}(a).
 
 \begin{figure}[th!]
-	\includegraphics[width=0.8\textwidth]{figures/PAD}
+	\includegraphics[width=0.8\textwidth]{figures/Fig5}
 	\caption{(a) Photoelectron anisotropy parameters, measured for each resolved C$_2$H$^-$ transition, across a range of detachment wavelengths.
 Allowed ground state transitions $\tilde{X}^2\Sigma^+$ are shown in orange, Herzberg-Teller coupled transitions are shown in purple, and excited state transitions $\tilde{A} ^2\Pi$ are shown in blue.
-Anisotropy curves for a mixed-$sp$ model (Eq.~\ref{eq:beta-sp}) are shown for $\gamma_p=0.1$ and $\gamma_p=0.9$.
+Anisotropy curves for a mixed-$sp$ model (Eq.~\ref{eq:11}) are shown for $\gamma_p=0.1$ and $\gamma_p=0.9$.
 Anisotropy curves from Dyson orbital calculations for the $\tilde{X}^2\Sigma^+$ and $\tilde{A} ^2\Pi$ transitions are shown in blue and orange respectively.
@@
 
-In Figure~\ref{fig:5}(a) allowed ground state transitions ($\tilde{X}^2\Sigma^+$) are shown in blue and have a positive anisotropy, as expected for detachment from a $s-$like orbital.
+In Fig.~\ref{fig:5}(a) allowed ground state transitions ($\tilde{X}^2\Sigma^+$) are shown in blue and have a positive anisotropy, as expected for detachment from a $s-$like orbital.
 Conversely, excited state transitions ($\tilde{A} ^2\Pi$) shown in orange have a negative anisotropy.
-However, the HT coupled transitions on the $\tilde{X} ^2\Sigma^+$ surface also have negative anisotropies, due to their $\Pi$ vibronic symmetry.
+However, the HT coupled transitions on the $\tilde{X} ^2\Sigma^+$ surface (shown in purple) also have negative anisotropies, due to their $\Pi$ vibronic symmetry.
 Therefore, the sign $(+/-)$ of $\beta$ can be used to assign each accessed vibronic level to either the $\Sigma$ or $\Pi$ vibronic symmetry respectively.
 This is particularly useful around the $\tilde{A} ^2\Pi$ origin, where the two states overlap.
-The mixed $sp$ model from Eq.~\ref{eq:beta-sp} is fitted to the experimental data in Figure~\ref{fig:5}(a) with $\gamma_p=0.1$ and $\gamma_p=0.9$ for the ground and excited state detachment respectively.
+The mixed $sp$ model from Eq.~\ref{eq:11} is fitted to the experimental data in Fig.~\ref{fig:5}(a) with $\gamma_p=0.1$ and $\gamma_p=0.9$ for the ground and excited state detachment respectively.
 For detachment to the $^2\Pi$ state this produces a Hanstorp coefficient of $A_1=0.66(4)~$eV$^{-1}$.
@@
 \phi_d = \sqrt{N}\int\phi_i^{(n)}(1,\dots,n)\phi_f^{(n-1)}(2,\dots,n)dn
+\label{eq:13}
 \end{equation}
@@
 D_k \propto \langle \phi_d | e\cdot r | \psi_k\rangle.
-\label{eq:Dyson}
+\label{eq:14}
 \end{equation}
-The Dyson orbital representation of the C$_2$H$^-$ $\tilde{X}^1\Sigma^+\rightarrow\tilde{X}^2\Sigma^+$ transition, calculated at the EOM-CCSD/aug-cc-pVTZ level, is shown in Figure~\ref{fig:5}(b).
-The corresponding anisotropy curve was calculated using ezDyson software~\cite{goz22}, and is shown in blue in Figure~\ref{fig:5}(a) alongside the experimental data.
-Figure~\ref{fig:5} shows that above threshold there is excellent agreement between the experimental anisotropies, the mixed $sp$ model (Eq.~\ref{eq:beta-sp}), and the calculated anisotropies (Eq.~\ref{eq:Dyson}).
+The Dyson orbital representation of the C$_2$H$^-$ $\tilde{X}^1\Sigma^+\rightarrow\tilde{X}^2\Sigma^+$ transition, calculated at the EOM-CCSD/aug-cc-pVTZ level, is shown in Fig.~\ref{fig:5}(b).
+The corresponding anisotropy curve was calculated using ezDyson software~\cite{goz22}, and is shown in blue in Fig.~\ref{fig:5}(a) alongside the experimental data.
+Figure~\ref{fig:5} shows that above threshold there is excellent agreement between the experimental anisotropies, the mixed $sp$ model (Eq.~\ref{eq:11}), and the calculated anisotropies (Eq.~\ref{eq:14}).
 The cylindrical symmetry of the molecule introduces some $p$ character into the predominantly $s-$like Dyson orbital (Fig.~\ref{fig:5}(b)) which becomes significant near threshold due to the centrifugal detachment barrier.
-This makes the near threshold anisotropy behaviour sensitive to the exact amount of $p$ orbital character included in the orbital, an effect that has also been observed in NO$_2^-$ ~\cite{law19} and the isoelectronic CN$^-$ ~\cite{har21}.
-The Dyson orbital for the $\tilde{X}^1\Sigma^+\rightarrow\tilde{A} ^2\Pi$ transition was also calculated at the EOM-CCSD/aug-cc-pVTZ level, and is shown in Figure~\ref{fig:5}(c).
-Again the calculated anisotropy curve (shown in orange in Fig.~\ref{fig:5}(a)) appears a good match to the $sp$ model (Eq.~\ref{eq:beta-sp}) and the experimental data, however it overestimates the amount of $p$ orbital character.
+This makes the near threshold anisotropy behaviour highly sensitive to the exact amount of $p$ orbital character included in the orbital, an effect that has also been observed in NO$_2^-$ ~\cite{law19} and the isoelectronic CN$^-$ ~\cite{har21}.
+The Dyson orbital for the $\tilde{X}^1\Sigma^+\rightarrow\tilde{A} ^2\Pi$ transition was also calculated at the EOM-CCSD/aug-cc-pVTZ level, and is shown in Fig.~\ref{fig:5}(c).
+Again the calculated anisotropy curve (shown in orange in Fig.~\ref{fig:5}(a)) appears a good match to the $sp$ model (Eq.~\ref{eq:11}) and the experimental data, however it underestimates the amount of $s$ orbital character.
 
-A plot of the anisotropy parameters for C$_2$H$^-$ detachment at 300~nm, represented as $\beta\times I$, is presented in Figure~\ref{fig:6}, alongside the photoelectron spectrum.
+\subsection{Verifying Assignments}
+A plot of the anisotropy parameters for C$_2$H$^-$ detachment at 300~nm, represented as $\beta\times I$, is presented in Fig.~\ref{fig:6}, alongside the photoelectron spectrum.
 Plotting $\beta\times I$ allows the sign $(+/-)$ of each individual transition to be easily identified, even for partially resolved peaks.
@@
 The nearby peaks $h$ and $i$  are assigned to the admixed $\Pi$ transitions $\tilde{X}(0,3,2)\tilde{A}(0,0,0)$ and $\tilde{X}(0,7,1)\tilde{A}(0,1,0)$, in agreement with previous assignments~\cite{zho07,tar03}.
-Peak $j$ was tentatively assigned to the $\Sigma$ transition $\tilde{X}(1,4,0$) previously~\cite{zho07}, however Figure~\ref{fig:6} shows peak $j$ has $\Pi$ symmetry.
+Peak $j$ was tentatively assigned to the $\Sigma$ transition $\tilde{X}(1,4,0$) previously~\cite{zho07}, however Fig.~\ref{fig:6} shows peak $j$ has $\Pi$ symmetry.
 Therefore, we assign $j$ to the excited HT coupled $\Pi$ transition $\tilde{X}(0,7,1)$.
 The other dominant peaks in this region, $l$, $n$, and $o$, represent admixed $\Pi$ transitions involving the $\tilde{A}(0,0,1)$ vibrational level of the excited state.
-The complete assignments for all resolved peaks in the C$_2$H$^-$ and C$_2$D$^-$ photoelectron spectra from this work are presented in the Supplementary Materials Table~S1.
+The complete assignments for all resolved peaks in the C$_2$H$^-$ and C$_2$D$^-$ photoelectron spectra from this work are presented in the Supplementary Materials Tables~S1~and~S2.
 Transition assignments are based on a combination of the previous works of Tarroni and Carter~\cite{tar03} and Zhou~\emph{et al.}~\cite{zho07}, the transition position and symmetry outputs from the QVC calculations (Fig.~\ref{fig:3}), and the experimental electron anisotropies which define the vibronic symmetry.
@@
 	\caption{Photoelectron spectrum of C$_2$H$^-$ at 300~nm, compared to anisotropy measurements, presented as $\beta\times I$.
-For each resolved transition the anisotropy parameter was determined from Eq.~(\ref{eq:beta1}) and multiplied by the corresponding photoelectron intensity.
-This allows for the sign $(+/-)$ of each transitions to be readily determined.}
+For each resolved transition the anisotropy parameter was determined from Eq.~(\ref{eq:10}) and multiplied by the corresponding photoelectron intensity.
+This allows for the sign $(+/-)$ of each transitions to be readily identified.}
 	\label{fig:6}
@@
 This result demonstrates how experimental anisotropies and calculated transition intensities can be combined to help assign and understand vibronically coupled spectra.
-This is particularly useful in spectral regions where there are a large number of potential vibronic transitions, making definitive assignments based on energetics alone difficult.
+An approach that is particularly useful in spectral regions where there are a large number of potential vibronic transitions, making definitive assignments based on energetics alone difficult.
 
 \section{Conclusions} 
-High-resolution photoelectron images of C$_2$H$^-$ and C$_2$D$^-$ were recorded at a range of wavelengths, to investigate vibronic coupling effects in the simplest C$_{2n}$H carbon monohydride chain.
+High-resolution photoelectron images of C$_2$H$^-$ and C$_2$D$^-$ have been recorded at multiple wavelengths between 355~nm and 266~nm, to investigate vibronic coupling effects in the simplest C$_{2n}$H carbon monohydride chain.
 The interplay of pseudo Jahn-Teller and Renner Teller coupling between the close lying $\tilde{X}^2\Sigma^+$ and $\tilde{A}^2\Pi$ states results in a complex vibronic spectrum near the $\tilde{A}$ state surface, with the electronic origin split over multiple admixed levels.
@@
 A KDC Hamiltonian was constructed, and parametrised using the high-level EOM-CCSDT quantum chemical approach and the quasidiabatic ansatz.
-The resulting simulated photoelectron spectra of C$_2$H$^-$ and C$_2$D$^-$ resemble the experimental data, particularly in the complex energy region of the $\tilde{A}$ state origin.
+The resulting simulated photoelectron spectra of C$_2$H$^-$ and C$_2$D$^-$ reproduce the experimental data, particularly in the complex energy region of the $\tilde{A}$ state origin.
 Photoelectron anisotropy parameters were also measured for dominant transitions, at a range of wavelengths.
-The sign $(+/-)$ of the anisotropy parameter, when compared to the calculated vibronic symmetry, allowed even weak or partially resolved transitions to be assigned.
+The sign $(+/-)$ of the electron anisotropy parameter, when compared with the calculated vibronic symmetry, allowed even weak or partially resolved transitions to be assigned.
 
-The excellent agreement between the experimental and calculated spectra in this work
-demonstrates that electronic spectra complicated by vibronic coupling effects may still be accurately simulated using a quasidiabatic treatment, as parametrised by appropriate quantum chemical methodology.
+The excellent agreement between the experimental and calculated spectra of this work
+demonstrate that electronic spectra, complicated by vibronic coupling effects, may still be accurately simulated by using a quasidiabatic treatment, as parametrised by appropriate quantum chemical methodology.
 This approach may be applied to larger, less well known, C$_{2n}$H species, which may help guide the search for these molecules in astronomical studies, and help identify potential DIB carriers.

### 2022-06-24 Submission/Laws_C2H.tex
update resubmission

--- 2022-06-24 Resubmission/Laws_C2H.tex
@@
 Conversely, the formation of anions in space is believed to be driven by radiative electron attachment, charge transfer, and dissociative electron attachment.
-Current astrochemical modelling of interstellar clouds, such as IRC+10216, typically underestimate the observed abundances of CH$_4^-$ ~\cite{mil17,cor13,her08}.
+Current astrochemical modelling of interstellar clouds, such as IRC+10216, typically underestimate the observed abundances of CH$_4^-$~\cite{mil17,cor13,her08}.
 Therefore, it has been proposed that ion-neutral reactions
@@
 Quantum chemical computations were preformed using the CFOUR computational package~\cite{dev20}.
-The equation-of-motion ionised-potential coupled-cluster singles, doubles, and triples (EOM-IP-CCSDT) level of theory with an atomic natural orbital basis set of quadruple-zeta quality (ANO2) was used on a closed-shell anionic reference to perform geometry optimisations and frequency calculations (including 1h + 2h1p + 3h2p excitations~\cite{mat16}).
-EOM is a highly accurate and robust framework that provides access to different types of target electronic states, including ionised states~\cite{gul21b,and22,bar07}.
-The linear diabatic coupling constants were calculated analytically at the EOM-IP-CCSD/ANO2 level.
+The EOM-CCSDT/ANO2 level of theory was used to perform geometry optimisations and frequency calculations.
+The linear diabatic coupling constants were calculated analytically at the EOM-CCSD/ANO2 level.
 
@@
 However, due to the strong vibronic coupling interactions, transition intensities can not be obtained via simple Franck-Condon calculations based on quantum chemistry methods.
-To account for these interactions, the photoelectron spectrum of the C$_2$H$^-$ anion is simulated using a quasidiabatic Hamiltonian of the type introduced by Koeppel, Domcke and Cederbaum (KDC).~\cite{kou84,dom81} In this approach, the Hamiltonian is represented in a basis of quasidiabatic (slowly varying) electronic  states for which the kinetic energy operator can be assumed diagonal.~\cite{pac93} For C$_2$H, the KDC Hamiltonian comprises three states - the two components of the $^2\Pi$ state and the ground $^2\Sigma^+$ state - and is then projected onto a vibrational basis, usually chosen as a direct product of harmonic oscillators.
+To account for these interactions, the photoelectron spectrum of the C$_2$H$^-$ anion is simulated using a quasidiabatic Hamiltonian of the type advocated by Koeppel, Domcke and Cederbaum (KDC).~\cite{kou84,dom81} In this approach, the Hamiltonian is represented in a basis of quasidiabatic (slowly varying) electronic  states for which the kinetic energy operator can be assumed diagonal.~\cite{pac93} For C$_2$H, the KDC Hamiltonian comprises three states - the two components of the $^2\Pi$ state and the ground $^2\Sigma^+$ state - and is then projected onto a vibrational basis, usually chosen as a direct product of harmonic oscillators.
 Diagonalization of the corresponding matrix yields the molecular states (which are given in terms of a Born-Huang expansion), and the squared projections of the corresponding eigenvectors onto the ground state of the anion yield the relative intensities.
@@
 When the potential in Eq.~(\ref{eq:calc1}) is diagonalized, the adiabatic states that are used for its parametrization are precisely recovered through terms second order in displacement.
-The parametrization of the potential in this work was completed using the CFOUR computational package~\cite{dev20} and the quasidiabatic ansatz of Ichino~\emph{et al.}~\cite{ich09} Briefly,the EOM procedure is used to operationally define quasidiabatic states (those that relax according to a well-behaved reference state wavefunction, which is that of the anion level) and the coupling constants are then evaluated as the first derivative of the off-diagonal elements of the electronic Hamiltonian in the basis defined by this representation.
-Vertical excitation energies ($\Delta_0$), and linear diabatic force and coupling constants between the electronic states of interest were calculated analytically using the highly accurate EOM-IP-CCSDT/ANO2 procedure.
-The interstate coupling constants ($\lambda$) were calculated analytically at the EOM-IP-CCSD/ANO2 level.
-All calculated values used to parametrize the KDC potential in Eq.~(\ref{eq:calc1}) are presented in Table~\ref{tab:1}.
+The linear diabatic coupling constants between the electronic states of interest were calculated analytically at the EOM-CCSD/ANO2 level of theory, using the CFOUR computational package~\cite{dev20} and the quasidiabatic ansatz of Ichino~\emph{et al.}~\cite{ich09} Briefly, the EOM procedure is used to operationally define quasidiabatic states (those that relax according to a well-behaved reference state wavefunction, which is that of the anion level) and the coupling constants are then evaluated as the first derivative of the off-diagonal elements of the electronic Hamiltonian in the basis defined by this representation.
+The diabatic force and coupling constants calculated to parametrize the KDC potential in Eq.~(\ref{eq:calc1}) were calculated at the CCSDT/ANO2 level of theory, and are presented in Table~\ref{tab:1}.
 
@@
 The above method was employed to simulate the photoelectron spectrum of C$_2$H$^-$, with the calculated transitions shown in Figure~\ref{fig:3}(a) alongside the experimental data at 355~nm.
-Photoelectron spectra are simulated using the xsim package of CFOUR~\cite{dev20} and the model Hamiltonian generated above.
-The xsim module projects the Hamiltonian (Eq.~\ref{eq:calc1}) onto a vibrational basis, which is then diagonalised using Lanczos algorithm to calculate transition energies and intensities that map to the measured photoelectron spectrum.
-In this simulation the transition moments for the two ionisation processes are assumed to be equal.
+Photoelectron spectra are simulated using the xsim package of CFOUR and the model Hamiltonian generated above.
+The Hamiltonian is diagonalised using the Lanczos algorithm, to calculate transition energies and intensities that map to the measured photoelectron spectrum.
 On the $\tilde{X} ^2\Sigma^+$ surface, below 3,600~cm$^{-1}$, there is excellent agreement in both the transition positions and intensities between the simulated and experimental spectra.
@@
 Therefore, measuring the anisotropy can help determine the electronic character of each individual transition, which may be compared to the calculated symmetries in Figure~\ref{fig:3}.
-For each prominent transition in the photoelectron spectrum of C$_2$H$^-$ in Figure~\ref{fig:1} the corresponding anisotropy parameter may be calculated by fitting Eq.~(\ref{eq:beta1}) to a plot of the integrated radial intensity (across the peak) versus angle, as (for a single quadrant of the electron image) the intensity variation is linear in $P_2(\cos\theta)$ with a slope equal to $\beta\times$intercept.
-This procedure was applied to all of the photoelectron spectra measured in this work, with the energy dependent anisotropy parameters presented in Figure~\ref{fig:5}(a).
+Anisotropy parameters were measured over a range of detachment wavelengths for prominent transitions in the C$_2$H$^-$ photoelectron spectra, and are presented in Figure~\ref{fig:5}.
+Fitting Eq.~(\ref{eq:beta-sp}) to the anisotropy parameters from $^2\Pi$ state detachment, with $\gamma_p = 0.9$ produces a Hanstorp coefficient of $A_1=0.66(4)~$eV$^{-1}$.
 
 \begin{figure}[th!]
-	\includegraphics[width=0.8\textwidth]{figures/PAD}
-	\caption{(a) Photoelectron anisotropy parameters, measured for each resolved C$_2$H$^-$ transition, across a range of detachment wavelengths.
+	\includegraphics[width=0.5\textwidth]{figures/Fig5}
+	\caption{Photoelectron anisotropy parameters, measured for each resolved C$_2$H$^-$ transition, across a range of detachment wavelengths.
 Allowed ground state transitions $\tilde{X}^2\Sigma^+$ are shown in orange, Herzberg-Teller coupled transitions are shown in purple, and excited state transitions $\tilde{A} ^2\Pi$ are shown in blue.
-Anisotropy curves for a mixed-$sp$ model (Eq.~\ref{eq:beta-sp}) are shown for $\gamma_p=0.1$ and $\gamma_p=0.9$.
-Anisotropy curves from Dyson orbital calculations for the $\tilde{X}^2\Sigma^+$ and $\tilde{A} ^2\Pi$ transitions are shown in blue and orange respectively.
-(b) Dyson orbital representation of the $\tilde{X}^1\Sigma^+\rightarrow\tilde{X}^2\Sigma^+$ transition.
-(c) Dyson orbital representation of the $\tilde{X}^1\Sigma^+\rightarrow\tilde{A} ^2\Pi$ transition.}
+Anisotropy curves for a mixed-$sp$ model (Eq.~\ref{eq:beta-sp}) are shown for $\gamma_p=0.1$ and $\gamma_p=0.9$.}
 	\label{fig:5}
@@
 
-In Figure~\ref{fig:5}(a) allowed ground state transitions ($\tilde{X}^2\Sigma^+$) are shown in blue and have a positive anisotropy, as expected for detachment from a $s-$like orbital.
-Conversely, excited state transitions ($\tilde{A} ^2\Pi$) shown in orange have a negative anisotropy.
-However, the HT coupled transitions on the $\tilde{X} ^2\Sigma^+$ surface also have negative anisotropies, due to their $\Pi$ vibronic symmetry.
-Therefore, the sign $(+/-)$ of $\beta$ can be used to assign each accessed vibronic level to either the $\Sigma$ or $\Pi$ vibronic symmetry respectively.
+The sign $(+/-)$ of $\beta$ can be used to assign each accessed vibronic level to either the $^2\Sigma^+$ or $^2\Pi$ vibronic symmetry respectively.
 This is particularly useful around the $\tilde{A} ^2\Pi$ origin, where the two states overlap.
-The mixed $sp$ model from Eq.~\ref{eq:beta-sp} is fitted to the experimental data in Figure~\ref{fig:5}(a) with $\gamma_p=0.1$ and $\gamma_p=0.9$ for the ground and excited state detachment respectively.
-For detachment to the $^2\Pi$ state this produces a Hanstorp coefficient of $A_1=0.66(4)~$eV$^{-1}$.
-
-The photoelectron angular distribution may also be examined through the construction of Dyson orbitals, which provide a direct link between \emph{ab-initio} calculations and experimental anisotropy parameters.
-Q-Chem software~\cite{sha15} may be used to construct Dyson orbitals $\phi_d$ that represent the overlap between the initial $\phi_i^{(n)}$ and final $\phi_f^{(n-1)}$ states,
-\begin{equation}
-\phi_d = \sqrt{N}\int\phi_i^{(n)}(1,\dots,n)\phi_f^{(n-1)}(2,\dots,n)dn
-\end{equation}
-By representing the detached electron as a plane wave, $\psi_k=(2\pi)^{(-3/2)}e^{ik\cdot r}$ and assuming strong orthogonality between $\phi_d$, $\psi_k$, and $\phi_f^{(n-1)}$ the transition dipole moment may then be rewritten as
-\begin{equation}
-D_k \propto \langle \phi_d | e\cdot r | \psi_k\rangle.
-\label{eq:Dyson}
-\end{equation}
-The Dyson orbital representation of the C$_2$H$^-$ $\tilde{X}^1\Sigma^+\rightarrow\tilde{X}^2\Sigma^+$ transition, calculated at the EOM-CCSD/aug-cc-pVTZ level, is shown in Figure~\ref{fig:5}(b).
-The corresponding anisotropy curve was calculated using ezDyson software~\cite{goz22}, and is shown in blue in Figure~\ref{fig:5}(a) alongside the experimental data.
-Figure~\ref{fig:5} shows that above threshold there is excellent agreement between the experimental anisotropies, the mixed $sp$ model (Eq.~\ref{eq:beta-sp}), and the calculated anisotropies (Eq.~\ref{eq:Dyson}).
-The cylindrical symmetry of the molecule introduces some $p$ character into the predominantly $s-$like Dyson orbital (Fig.~\ref{fig:5}(b)) which becomes significant near threshold due to the centrifugal detachment barrier.
-This makes the near threshold anisotropy behaviour sensitive to the exact amount of $p$ orbital character included in the orbital, an effect that has also been observed in NO$_2^-$ ~\cite{law19} and the isoelectronic CN$^-$ ~\cite{har21}.
-The Dyson orbital for the $\tilde{X}^1\Sigma^+\rightarrow\tilde{A} ^2\Pi$ transition was also calculated at the EOM-CCSD/aug-cc-pVTZ level, and is shown in Figure~\ref{fig:5}(c).
-Again the calculated anisotropy curve (shown in orange in Fig.~\ref{fig:5}(a)) appears a good match to the $sp$ model (Eq.~\ref{eq:beta-sp}) and the experimental data, however it overestimates the amount of $p$ orbital character.
+It is important to note that the HT coupled transitions on the $\tilde{X} ^2\Sigma^+$ surface have negative anisotropies and $\Pi$ symmetry.
 

### 2022-06-24 Submission/suppInfo.tex
update resubmission

--- 2022-05-05 suppInfo.tex
@@
 Peaks are labelled with respect to the photoelectron spectrum of C$_2$H$^-$ at 300~nm in Figure~\ref{fig:1}.
-The experimental binding energy of each transition is given, alongside the anisotropy ($+/-$), the corresponding vibronic symmetry, and the calculated energy from Ref.~\onlinecite{tar03}.
-Assignments are given as $\tilde{X}(v_1,v_2,v_3)\tilde{A}(v_1,v_2,v_3)$ where superscripts represent hot-band transitions.
+The experimental binding energy of each transition is given, alongside the anisotropy parameter sign ($+/-$), the corresponding vibronic symmetry, and the calculated energy from Ref.~\onlinecite{tar03}.
+Assignments are given as $\tilde{X}(v_1,v_2,v_3)\tilde{A}(v_1,v_2,v_3)$ where any superscripts represent hot-band transitions.
 
 \begin{figure}[th!]
-	\includegraphics[width=0.6\textwidth]{figures/FigS1.pdf}
-	\caption{Photoelectron spectrum of C$_2$H$^-$ at 300~nm, showing the labelling of peaks used in this work.}
+	\includegraphics[width=0.6\textwidth]{figures/FigS1}
+	\caption{Photoelectron spectrum of C$_2$H$^-$ at 300~nm, showing the alphabetic labelling of peaks used in this work.}
 	\label{fig:1}
@@
 Peaks are labelled with respect to the photoelectron spectrum of C$_2$D$^-$ at 355~nm in Figure~\ref{fig:2}.
-The experimental binding energy of each transition is given, alongside the anisotropy ($+/-$), the corresponding vibronic symmetry, and the calculated energy from Ref.~\onlinecite{tar03}.
+The experimental binding energy of each transition is given, alongside the anisotropy parameter sign ($+/-$), the corresponding vibronic symmetry, and the calculated energy from Ref.~\onlinecite{tar03}.
 
 \begin{figure}[th!]
-	\includegraphics[width=0.6\textwidth]{figures/FigS2.pdf}
-	\caption{Photoelectron spectrum of C$_2$D$^-$ at 266~nm, showing the labelling of peaks used in this work.}
+	\includegraphics[width=0.6\textwidth]{figures/FigS2}
+	\caption{Photoelectron spectrum of C$_2$D$^-$ at 266~nm, showing the alphabetic labelling of peaks used in this work.}
 	\label{fig:2}

### 2022-06-24 suppInfo.tex
update resubmission

@@
 Peaks are labelled with respect to the photoelectron spectrum of C$_2$H$^-$ at 300~nm in Figure~\ref{fig:1}.
-The experimental binding energy of each transition is given, alongside the anisotropy ($+/-$), the corresponding vibronic symmetry, and the calculated energy from Ref.~\onlinecite{tar03}.
-Assignments are given as $\tilde{X}(v_1,v_2,v_3)\tilde{A}(v_1,v_2,v_3)$ where superscripts represent hot-band transitions.
+The experimental binding energy of each transition is given, alongside the anisotropy parameter sign ($+/-$), the corresponding vibronic symmetry, and the calculated energy from Ref.~\onlinecite{tar03}.
+Assignments are given as $\tilde{X}(v_1,v_2,v_3)\tilde{A}(v_1,v_2,v_3)$ where any superscripts represent hot-band transitions.
 
@@
 	\includegraphics[width=0.6\textwidth]{figures/FigS1.pdf}
-	\caption{Photoelectron spectrum of C$_2$H$^-$ at 300~nm, showing the labelling of peaks used in this work.}
+	\caption{Photoelectron spectrum of C$_2$H$^-$ at 300~nm, showing the alphabetic labelling of peaks used in this work.}
 	\label{fig:1}
@@
 Peaks are labelled with respect to the photoelectron spectrum of C$_2$D$^-$ at 355~nm in Figure~\ref{fig:2}.
-The experimental binding energy of each transition is given, alongside the anisotropy ($+/-$), the corresponding vibronic symmetry, and the calculated energy from Ref.~\onlinecite{tar03}.
+The experimental binding energy of each transition is given, alongside the anisotropy parameter sign ($+/-$), the corresponding vibronic symmetry, and the calculated energy from Ref.~\onlinecite{tar03}.
 
@@
 	\includegraphics[width=0.6\textwidth]{figures/FigS2.pdf}
-	\caption{Photoelectron spectrum of C$_2$D$^-$ at 266~nm, showing the labelling of peaks used in this work.}
+	\caption{Photoelectron spectrum of C$_2$D$^-$ at 266~nm, showing the alphabetic labelling of peaks used in this work.}
 	\label{fig:2}

### 2022-06-24 Stanton/scripts/266-plot.py

@@ -85,6 +85,6 @@ ax.tick_params(width=1.5)
 plt.setp(ax.spines.values(), linewidth=1.5)
 
 
-plt.savefig('266-plot.pdf', dpi=600,bbox_inches='tight')
+plt.savefig('266-plot.eps', dpi=600,bbox_inches='tight')
 plt.show()
 

### 2022-06-24 Stanton/scripts/beta/PAD.py

@@ -6,6 +6,9 @@ from matplotlib.ticker import (MultipleLocator, FormatStrFormatter,
                                AutoMinorLocator)
 
 
+aa1,bb1 = np.loadtxt('betaS.txt',usecols=(0,4),unpack=True)
+aa2,bb2 = np.loadtxt('betaP.txt',usecols=(0,4),unpack=True)
+
 
 def bet(E,A,f):
     Z = (8*(1-f))/(3*f)
@@ -131,14 +134,14 @@ A2 = grid[-1]
 #plt.errorbar(dea,dba,yerr=ddba,fmt='s',markersize=8,color='C0',mfc='white',label=r'C$_2$D $^2\Pi$')
 
 #plt.annotate(r'$A$ = 1.5(4) eV$^{-1}$',(1.15,1.200),color='C1',fontsize=13)
-plt.annotate(r'$A_1$ = 0.66(4) eV$^{-1}$',(1.15,0.18),color='C1',fontsize=13)
+plt.annotate(r'$A_1$ = 0.66(4) eV$^{-1}$',(1.15,0.18),color='k',fontsize=13)
 #plt.annotate(r'$A$ = 0.66(4) eV$^{-1}$',(1.45,-0.68),color='C0',fontsize=10)
 
 plt.annotate(r'$\gamma_p$ = 0.9',(A2+0.05,A1),va='center',fontsize=12)
 plt.annotate(r'$\gamma_p$ = 0.1',(A2+0.05,A2-0.1),va='center',fontsize=12)
 
 plt.xlabel('Electron Kinetic Energy (eV)',fontsize=14)
-plt.ylabel(r'Anisotropy ($\beta$)',fontsize=14)
+plt.ylabel(r'Anisotropy Parameter ($\beta$)',fontsize=14)
 
 plt.xticks([0,0.5,1,1.5],[0.0,0.5,1.0,1.5],fontsize=13)
 plt.yticks([-1,0,1,2],[-1.0,0.0,1.0,2.0],fontsize=13)
@@ -154,6 +157,9 @@ ax.spines['top'].set_visible(False)
 ax.spines['right'].set_visible(False)
 plt.setp(ax.spines.values(), linewidth=1.5)
 
-plt.savefig("PAD.pdf", dpi=400, bbbox_inches="tight")
+plt.plot(aa1-3,bb1*0.93)
+plt.plot((aa2-3)/2,bb2*0.9)
+
[…]

### 2022-06-24 Stanton/scripts/beta/plotBeta.py

@@ -45,7 +45,7 @@ for i in range(0,np.size(b)):
     spec+= by[i]*amp*Gauss(xx[i],FWHM,Ev)
 
 plt.plot(hv-x,y,'k',label='C$_2$H$^-$ at 300nm')
-plt.plot(hv-Ev,spec,'C3',label = r'Anisotropy ($\beta\times$I)')
+plt.plot(hv-Ev,spec,'C3',label = r'Anisotropy $\beta\times$I')
 
 #Plotting
 plt.xlim(hv-27000,hv-15000)
@@ -71,7 +71,7 @@ ax.spines['top'].set_visible(False)
 ax.spines['right'].set_visible(False)
 plt.setp(ax.spines.values(), linewidth=1.5)
 plt.xlabel('Electron Kinetic Energy (cm$^{-1}$)',fontsize=14)
-plt.ylabel(r'Anisotropy ($\beta\times$I)',fontsize=14)
+plt.ylabel(r'Intensity (arb. u.)',fontsize=14)
 plt.legend(loc='upper left',fontsize=10,frameon=False)
 ax.set_xticklabels(np.arange(6000,20000,2000),fontsize=14)
 ax.set_yticklabels([-0.2,-0.1,0.0,0.1,0.2,0.3,0.4,0.5,0.6],fontsize=14)

### 2022-06-24 scripts/Fig1b.py

@@ -23,20 +23,20 @@ vmi = ax.imshow(VMI, extent=[-r2, r2, -c2, c2], vmin=-0, cmap="jet")
 #ax.set_xlabel(r"radius (pixels)", ha='left')
 ax.axes.get_yaxis().set_ticks([])
 plt.setp(ax.spines.values(), linewidth=1.5)
-label = ax.set_xlabel("Radius (pixels)", fontsize='14')
+label = ax.set_xlabel("Radius (pixels)", fontsize='18')
 ax.xaxis.set_label_coords(0.7, -0.08)
 ax.set_xticks([0, 256])
-ax.set_xticklabels(["0", "1024"],fontsize=12)
+ax.set_xticklabels(["0", "1024"],fontsize=16)
 # colour bar
 cbaxes = fig.add_axes([0.82, 0.5, 0.018, 0.38])
 cbaxes.yaxis.set_label_coords(2, 0.5)
 plt.colorbar(vmi, cax=cbaxes, ticks=[0, int(VMI.max()/1.1/10)*10])
-cbaxes.tick_params(labelsize=12)
-cbaxes.set_ylabel("Electrons", fontsize='14')
+cbaxes.tick_params(labelsize=16)
+cbaxes.set_ylabel("Electrons", fontsize='18')
 
 ax.annotate('', xy=(-0.1, 0.2), xycoords='axes fraction', xytext=(-0.1, 0.8), 
             arrowprops=dict(arrowstyle="<-", color='k',lw=1.5))
-ax.annotate('Laser Polarisation',xy=(-0.1, 0.2), rotation=90, xycoords='axes fraction', xytext=(-0.15, 0.5),fontsize=14, ha='center', va='center')
+ax.annotate('Laser Polarisation',xy=(-0.1, 0.2), rotation=90, xycoords='axes fraction', xytext=(-0.15, 0.5),fontsize=18, ha='center', va='center')
 
 plt.setp(ax.spines.values(), linewidth=1.5)
 ax.tick_params(width=1.5)

### 2022-06-24 scripts/plotBeta.py

@@ -45,7 +45,7 @@ for i in range(0,np.size(b)):
     spec+= by[i]*amp*Gauss(xx[i],FWHM,Ev)
 
 plt.plot(x,y,'k',label='C$_2$H$^-$ at 300nm')
-plt.plot(Ev,spec,'C3',label = r'Anisotropy ($\beta\times$I)')
+plt.plot(Ev,spec,'C3',label = r'Anisotropy $\beta\times$I')
 
 #Plotting
 plt.xlim(15000,27000)
@@ -70,8 +70,8 @@ ax.spines['top'].set_visible(False)
 #ax.spines['left'].set_visible(False)
 ax.spines['right'].set_visible(False)
 plt.setp(ax.spines.values(), linewidth=1.5)
-plt.xlabel('Binding Energy (cm$^{-1}$)',fontsize=14)
-plt.ylabel(r'Anisotropy ($\beta\times$I)',fontsize=14)
+plt.xlabel('Electron Binding Energy (cm$^{-1}$)',fontsize=14)
+plt.ylabel(r'Intensity (arb. u.)',fontsize=14)
 plt.legend(loc='upper right',fontsize=10,frameon=False)
 #ax.set_xticklabels(np.arange(6000,20000,2000),fontsize=14)
 ax.set_xticks([16223.15,19887.95,23552.75,27217.55])
@@ -79,6 +79,6 @@ ax.set_xticklabels([24000,26000,28000,30000],fontsize=14)
 ax.set_yticklabels([-0.2,-0.1,0.0,0.1,0.2,0.3,0.4,0.5,0.6],fontsize=14)
 plt.minorticks_on()
 
-plt.savefig('plotBeta.pdf', dpi=600,bbox_inches='tight')
+plt.savefig('plotBeta.eps', dpi=600,bbox_inches='tight')
 
 plt.show()

### 2022-06-24 testC2H/scripts/C2H-plot.py

@@ -58,8 +58,8 @@ for i in range(0,np.size(c)):
 plt.plot(x,y,'k',label=r'C$_2$H$^-$ PES')
 plt.xlim(-630,4225)
 
-plt.plot((0,0),(0,0),'C1',label=r'$\Sigma$ Symmetry')
-plt.plot((0,0),(0,0),'C0',label=r'$\Pi$ Symmetry')
+plt.plot((0,0),(0,0),'C0',label=r'$\Sigma$ Symmetry')
+plt.plot((0,0),(0,0),'C1',label=r'$\Pi$ Symmetry')
 plt.legend(loc=9,fontsize=10,frameon=False)
 
 ax.spines['top'].set_visible(False)

### 2022-06-24 testC2H/scripts/Fig6-C2H-UV.py

@@ -58,6 +58,6 @@ ax.tick_params(width=1.5)
 plt.setp(ax.spines.values(), linewidth=1.5)
 
 
-plt.savefig("FigS1.pdf",dpi=300,bb_inches="tight")
+plt.savefig("FigS1.eps",dpi=600,bb_inches="tight")
 plt.show()
 

### 2022-06-24 testC2H/scripts/SM-C2D.py

@@ -49,7 +49,7 @@ plt.yticks([])
 plt.xticks([23000,24000,25000,26000,27000,28000])
 ax.set_xticklabels(['23000','24000','25000','26000','27000','28000'],fontsize=14)
 plt.minorticks_on()
-plt.xlabel('Excitation Energy (cm$^{-1}$)',fontsize=14)
+plt.xlabel('Binding Energy (cm$^{-1}$)',fontsize=14)
 ax.tick_params(width=1.5)
 plt.setp(ax.spines.values(), linewidth=1.5)
 
@@ -72,6 +72,6 @@ plt.annotate(r'f',(27898,0.159),ha='center')
 #plt.annotate(r'd',(4028,0.228),ha='center')
 #plt.annotate(r'e',(4118,0.287),ha='center')
 
-plt.savefig('SM2-plot.pdf', dpi=600,bbox_inches='tight')
+plt.savefig('FigS2.eps', dpi=600,bbox_inches='tight')
 plt.show()
 

### 2022-06-30 Resubmission/Laws_C2H_v2.tex
v3

@@
 
-These interactions spread the electronic orgin of the $\tilde{A}\,^2\Pi$ state over several vibronic levels.
+These interactions spread the electronic origin of the $\tilde{A}\,^2\Pi$ state over several vibronic levels.
 Therefore, instead of assigning a defined origin, the peaks observed in experimental spectra may be assigned to coupled admixtures of vibronic transitions involving the three potential energy surfaces,
@@
 \subsection{Experimental Procedure}
-Details of the HR-PEI spectrometer are given in Refs~\onlinecite{cav07} and~\onlinecite{dev17}.
+Details of the HR-PEI spectrometer are given in Refs.~\onlinecite{cav07} and~\onlinecite{dev17}.
 Briefly, ethynyl ions C$_2$H$^-$ and C$_2$D$^-$ were produced in a pulsed-jet discharge of pure ethylene (C$_2$H$_4$/C$_2$D$_4$) gas, and subsequently mass isolated over a 2m-long time of flight region~\cite{ded01}.
@@
 Quantum chemical computations were preformed using the CFOUR computational package~\cite{dev20}.
-The equation-of-motion ionised-potential coupled-cluster singles, doubles, and triples (EOM-IP-CCSDT) level of theory with an atomic natural orbital basis set of quadruple-zeta quality (ANO2) was used on a closed-shell anionic reference to perform geometry optimisations and frequency calculations (including 1h + 2h1p + 3h2p excitations~\cite{mat16}).
-EOM is a highly accurate and robust framework that provides access to different types of target electronic states, including ionised states, making it well suited to the study of photodetachment~\cite{gul21b,and22,bar07}.
+The equation-of-motion ionized-potential coupled-cluster singles, doubles, and triples (EOM-IP-CCSDT) level of theory with an atomic natural orbital basis set of quadruple-zeta quality (ANO2) was used on a closed-shell anionic reference to perform geometry optimisations and frequency calculations (including 1h + 2h1p + 3h2p excitations~\cite{mat16}).
+EOM is a highly accurate and robust framework that provides access to different types of target electronic states, including ionized states, making it well suited to the study of photodetachment~\cite{gul21b,and22,bar07}.
 The linear diabatic coupling constants were calculated analytically at the EOM-IP-CCSD/ANO2 level.
@@
 The photdetachment transitions of C$_2$H$^-$ and C$_2$D$^-$ were calculated using the parameters in Table~\ref{tab:1} and the xsim package of CFOUR~\cite{dev20}.
-The xsim module projects the Hamiltonian (Eq.~\ref{eq:5}) onto a vibrational basis, which is then diagonalised using Lanczos algorithm to calculate transition energies and intensities that map to the measured photoelectron spectrum.
-In this simulation the transition moments for the two ionisation processes are assumed to be equal.
-The calculated transitions are shown in Figs.~\ref{fig:2}(a) and (b) alongside the experimental photoelectron spectra measured at 355~nm.
+The xsim module projects the Hamiltonian (Eq.~\ref{eq:5}) onto a vibrational basis, which is then diagonalized using Lanczos algorithm to calculate transition energies and intensities that map to the measured photoelectron spectrum.
+In this simulation the transition moments for the two ionization processes are assumed to be equal.
+The calculated transitions are shown in Figs.~\ref{fig:3}(a) and (b) alongside the experimental photoelectron spectra measured at 355~nm.
 Transitions with $\Sigma$ vibronic symmetry are shown in blue and transitions with $\Pi$ symmetry are in orange.
@@
 By transforming to a quasidiabatic representation, the effect of these coupling interactions may be accurately simulated.
-A KDC Hamiltonian was constructed, and parametrised using the high-level EOM-CCSDT quantum chemical approach and the quasidiabatic ansatz.
+A KDC Hamiltonian was constructed, and parametrized using the high-level EOM-CCSDT quantum chemical approach and the quasidiabatic ansatz.
 The resulting simulated photoelectron spectra of C$_2$H$^-$ and C$_2$D$^-$ reproduce the experimental data, particularly in the complex energy region of the $\tilde{A}$ state origin.
@@
 The excellent agreement between the experimental and calculated spectra of this work
-demonstrate that electronic spectra, complicated by vibronic coupling effects, may still be accurately simulated by using a quasidiabatic treatment, as parametrised by appropriate quantum chemical methodology.
+demonstrate that electronic spectra, complicated by vibronic coupling effects, may still be accurately simulated by using a quasidiabatic treatment, as parametrized by appropriate quantum chemical methodology.
 This approach may be applied to larger, less well known, C$_{2n}$H species, which may help guide the search for these molecules in astronomical studies, and help identify potential DIB carriers.
-It is especially encouraging that the fairly modest parametrisation used here works so well for C$_2$H, as this bodes well for its extension to larger systems.
+It is especially encouraging that the fairly modest parametrization used here works so well for C$_2$H, as this bodes well for its extension to larger systems.
 
@@
 
-\bibliography{Laws_C2H}
+%\bibliography{Laws_C2H}
+%merlin.mbs aipnum4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
+%Control: key (0)
+%Control: author (8) initials jnrlst
+%Control: editor formatted (1) identically to author
+%Control: production of article title (0) allowed
+%Control: page (1) range
+%Control: year (1) truncated
+%Control: production of eprint (0) enabled
+\begin{thebibliography}{98}%
+	\makeatletter
+	\providecommand \@ifxundefined [1]{%
+		\@ifx{#1\undefined}
+	}%
+	\providecommand \@ifnum [1]{%
+		\ifnum #1\expandafter \@firstoftwo
+		\else \expandafter \@secondoftwo
+		\fi
+	}%
+	\providecommand \@ifx [1]{%
+		\ifx #1\expandafter \@firstoftwo
+		\else \expandafter \@secondoftwo
+		\fi
+	}%
+	\providecommand \natexlab [1]{#1}%
+	\providecommand \enquote  [1]{``#1''}%
+	\providecommand \bibnamefont  [1]{#1}%
+	\providecommand \bibfnamefont [1]{#1}%
+	\providecommand \citenamefont [1]{#1}%
+	\providecommand \href@noop [0]{\@secondoftwo}%
+	\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
+	\providecommand \@href[1]{\@@startlink{#1}\@@href}%
+	\providecommand \@@href[1]{\endgroup#1\@@endlink}%
+	\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
+		`\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
+	\providecommand \@@startlink[1]{}%
+	\providecommand \@@endlink[0]{}%
+	\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
+	\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
+	\providecommand \urlprefix  [0]{URL }%
+	\providecommand \Eprint [0]{\href }%
+	\providecommand \doibase [0]{http://dx.doi.org/}%
+	\providecommand \selectlanguage [0]{\@gobble}%
+	\providecommand \bibinfo  [0]{\@secondoftwo}%
+	\providecommand \bibfield  [0]{\@secondoftwo}%
+	\providecommand \translation [1]{[#1]}%
+	\providecommand \BibitemOpen [0]{}%
+	\providecommand \bibitemStop [0]{}%
+	\providecommand \bibitemNoStop [0]{.\EOS\space}%
+	\providecommand \EOS [0]{\spacefactor3000\relax}%
+	\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
+	\let\auto@bib@innerbib\@empty
+	%</preamble>
+	\bibitem [{\citenamefont {Kiefer}, \citenamefont {Von~Drasek},\ and\
+		\citenamefont {Von~Drasek}(1990)}]{kie90}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~H.}\ \bibnamefont
+			{Kiefer}}, \bibinfo {author} {\bibfnamefont {W.~A.}\ \bibnamefont
+			{Von~Drasek}}, \ and\ \bibinfo {author} {\bibfnamefont {W.~A.}\ \bibnamefont
+			{Von~Drasek}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {The
+				mechanism of the homogeneous pyrolysis of acetylene},}\ }\href {\doibase
+		https://doi.org/10.1002/kin.550220710} {\bibfield  {journal} {\bibinfo
+			{journal} {International Journal of Chemical Kinetics}\ }\textbf {\bibinfo
+			{volume} {22}},\ \bibinfo {pages} {747--786} (\bibinfo {year}
+		{1990})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Kiefer}\ \emph {et~al.}(1992)\citenamefont {Kiefer},
+		\citenamefont {Sidhu}, \citenamefont {Kern}, \citenamefont {Xie},
+		\citenamefont {Chen},\ and\ \citenamefont {Harding}}]{kie92}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~H.}\ \bibnamefont
+			{Kiefer}}, \bibinfo {author} {\bibfnamefont {S.~S.}\ \bibnamefont {Sidhu}},
+		\bibinfo {author} {\bibfnamefont {R.~D.}\ \bibnamefont {Kern}}, \bibinfo
+		{author} {\bibfnamefont {K.}~\bibnamefont {Xie}}, \bibinfo {author}
+		{\bibfnamefont {H.}~\bibnamefont {Chen}}, \ and\ \bibinfo {author}
+		{\bibfnamefont {L.~B.}\ \bibnamefont {Harding}},\ }\bibfield  {title}
+	{\enquote {\bibinfo {title} {The homogeneous pyrolysis of acetylene ii: The
+				high temperature radical chain mechanism},}\ }\href {\doibase
+		10.1080/00102209208951815} {\bibfield  {journal} {\bibinfo  {journal}
+			{Combustion Science and Technology}\ }\textbf {\bibinfo {volume} {82}},\
+		\bibinfo {pages} {101--130} (\bibinfo {year} {1992})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Boullart}\ \emph {et~al.}(1996)\citenamefont
+		{Boullart}, \citenamefont {Devriendt}, \citenamefont {Borms},\ and\
+		\citenamefont {Peeters}}]{bou96}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
+			{Boullart}}, \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Devriendt}},
+		\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Borms}}, \ and\ \bibinfo
+		{author} {\bibfnamefont {J.}~\bibnamefont {Peeters}},\ }\bibfield  {title}
+	{\enquote {\bibinfo {title} {{Identification of the Sequence CH($^2\Pi$) +
+					C$_2$H$_2$ $\rightarrow$ C$_3$H$_2$ + H (and C$_3$H + H$_2$) Followed by
+					C$_3$H$_2$ + O $\rightarrow$ C$_2$H + HCO (or H + CO) as C$_2$H Source in
+					C$_2$H$_2$/O/H Atomic Flames}},}\ }\href {\doibase 10.1021/jp951995o}
+	{\bibfield  {journal} {\bibinfo  {journal} {The Journal of Physical
+				Chemistry}\ }\textbf {\bibinfo {volume} {100}},\ \bibinfo {pages} {998--1007}
+		(\bibinfo {year} {1996})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Irvine}, \citenamefont {Ohishi},\ and\ \citenamefont
+		{Kaifu}(1991)}]{wil91}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.~M.}\ \bibnamefont
+			{Irvine}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Ohishi}}, \
+		and\ \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Kaifu}},\ }\bibfield
+	{title} {\enquote {\bibinfo {title} {Chemical abundances in cold, dark
+				interstellar clouds},}\ }\href {\doibase
+		https://doi.org/10.1016/0019-1035(91)90120-I} {\bibfield  {journal} {\bibinfo
+			{journal} {Icarus}\ }\textbf {\bibinfo {volume} {91}},\ \bibinfo {pages}
+		{2--6} (\bibinfo {year} {1991})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Vuitton}\ \emph {et~al.}(2001)\citenamefont
+		{Vuitton}, \citenamefont {Scemama}, \citenamefont {Gazeau}, \citenamefont
+		{Chaquin},\ and\ \citenamefont {B\'{e}nilan}}]{vui01}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
+			{Vuitton}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Scemama}},
+		\bibinfo {author} {\bibfnamefont {M.-C.}\ \bibnamefont {Gazeau}}, \bibinfo
+		{author} {\bibfnamefont {P.}~\bibnamefont {Chaquin}}, \ and\ \bibinfo
+		{author} {\bibfnamefont {Y.}~\bibnamefont {B\'{e}nilan}},\ }\bibfield
+	{title} {\enquote {\bibinfo {title} {{IR and UV spectroscopic data for
+					polyynes: Predictions for long carbon chain compounds in Titan's
+					atmosphere}},}\ }\href {\doibase
+		https://doi.org/10.1016/S0273-1177(01)00059-X} {\bibfield  {journal}
+		{\bibinfo  {journal} {Advances in Space Research}\ }\textbf {\bibinfo
+			{volume} {27}},\ \bibinfo {pages} {283--288} (\bibinfo {year}
+		{2001})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Wilson}\ and\ \citenamefont {Atreya}(2003)}]{wil03}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+			{Wilson}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+			{Atreya}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Chemical sources
+				of haze formation in {Titan's} atmosphere},}\ }\href {\doibase
+		https://doi.org/10.1016/j.pss.2003.06.003} {\bibfield  {journal} {\bibinfo
+			{journal} {Planetary and Space Science}\ }\textbf {\bibinfo {volume} {51}},\
+		\bibinfo {pages} {1017--1033} (\bibinfo {year} {2003})},\ \bibinfo {note}
+	{surfaces and Atmospheres of the Outer Planets their Satellites and Ring
+		Systems}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Dobrijevic}\ \emph {et~al.}(2016)\citenamefont
+		{Dobrijevic}, \citenamefont {Loison}, \citenamefont {Hickson},\ and\
+		\citenamefont {Gronoff}}]{dob16}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+			{Dobrijevic}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Loison}},
+		\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Hickson}}, \ and\
+		\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Gronoff}},\ }\bibfield
+	{title} {\enquote {\bibinfo {title} {{1D}-coupled photochemical model of
+				neutrals, cations and anions in the atmosphere of {Titan}},}\ }\href
+	{\doibase https://doi.org/10.1016/j.icarus.2015.12.045} {\bibfield  {journal}
+		{\bibinfo  {journal} {Icarus}\ }\textbf {\bibinfo {volume} {268}},\ \bibinfo
+		{pages} {313 -- 339} (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Jackson}\ \emph {et~al.}(1996)\citenamefont
+		{Jackson}, \citenamefont {Blunt}, \citenamefont {Lin}, \citenamefont {Green},
+		\citenamefont {Olivera}, \citenamefont {Fink}, \citenamefont {Bao},
+		\citenamefont {Urdahl}, \citenamefont {Mohammad},\ and\ \citenamefont
+		{Zahedi}}]{jac96}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.~M.}\ \bibnamefont
+			{Jackson}}, \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Blunt}},
+		\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Lin}}, \bibinfo {author}
+		{\bibfnamefont {M.}~\bibnamefont {Green}}, \bibinfo {author} {\bibfnamefont
+			{G.}~\bibnamefont {Olivera}}, \bibinfo {author} {\bibfnamefont {W.~H.}\
+			\bibnamefont {Fink}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+			{Bao}}, \bibinfo {author} {\bibfnamefont {R.~S.}\ \bibnamefont {Urdahl}},
+		\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Mohammad}}, \ and\
+		\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Zahedi}},\ }\bibfield
+	{title} {\enquote {\bibinfo {title} {Non-adiabatic interactions in excited
+				{C$_2$H} molecules and their relationship to {C$_2$} formation in comets},}\
+	}\href {\doibase 10.1007/BF00644319} {\bibfield  {journal} {\bibinfo
+			{journal} {Astrophysics and Space Science}\ }\textbf {\bibinfo {volume}
+			{236}},\ \bibinfo {pages} {29--47} (\bibinfo {year} {1996})}\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {{Ziurys}}\ \emph {et~al.}(1982)\citenamefont
+		{{Ziurys}}, \citenamefont {{Saykally}}, \citenamefont {{Plambeck}},\ and\
+		\citenamefont {{Erickson}}}]{ziu82}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~M.}\ \bibnamefont
+			{{Ziurys}}}, \bibinfo {author} {\bibfnamefont {R.~J.}\ \bibnamefont
+			{{Saykally}}}, \bibinfo {author} {\bibfnamefont {R.~L.}\ \bibnamefont
+			{{Plambeck}}}, \ and\ \bibinfo {author} {\bibfnamefont {N.~R.}\ \bibnamefont
+			{{Erickson}}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Detection
+					of the N=3-2 transition of CCH in Orion and determination of the molecular
+					rotational constants}},}\ }\href {\doibase 10.1086/159709} {\bibfield
+		{journal} {\bibinfo  {journal} {The Astrophysical Journal}\ }\textbf
+		{\bibinfo {volume} {254}},\ \bibinfo {pages} {94--99} (\bibinfo {year}
+		{1982})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Gupta}\ \emph {et~al.}(2009)\citenamefont {Gupta},
+		\citenamefont {Gottlieb}, \citenamefont {McCarthy},\ and\ \citenamefont
+		{Thaddeus}}]{gup09}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+			{Gupta}}, \bibinfo {author} {\bibfnamefont {C.~A.}\ \bibnamefont {Gottlieb}},
+		\bibinfo {author} {\bibfnamefont {M.~C.}\ \bibnamefont {McCarthy}}, \ and\
+		\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Thaddeus}},\ }\bibfield
+	{title} {\enquote {\bibinfo {title} {A survey of {C$_4$H, C$_6$H, and
+					C$_6$H$^-$ with the Green Bank Telescope}},}\ }\href {\doibase
+		10.1088/0004-637x/691/2/1494} {\bibfield  {journal} {\bibinfo  {journal} {The
+				Astrophysical Journal}\ }\textbf {\bibinfo {volume} {691}},\ \bibinfo {pages}
+		{1494--1500} (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Beuther}\ \emph {et~al.}(2008)\citenamefont
+		{Beuther}, \citenamefont {Semenov}, \citenamefont {Henning},\ and\
+		\citenamefont {Linz}}]{beu08}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+			{Beuther}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Semenov}},
+		\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Henning}}, \ and\
+		\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Linz}},\ }\bibfield
+	{title} {\enquote {\bibinfo {title} {Ethynyl ({C$_2$H}) in massive star
+				formation: Tracing the initial conditions?}}\ }\href
+	{http://stacks.iop.org/1538-4357/675/i=1/a=L33} {\bibfield  {journal}
+		{\bibinfo  {journal} {The Astrophysical Journal Letters}\ }\textbf {\bibinfo
+			{volume} {675}},\ \bibinfo {pages} {L33} (\bibinfo {year}
+		{2008})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Jiang}\ \emph {et~al.}(2015)\citenamefont {Jiang},
+		\citenamefont {Liu}, \citenamefont {Zhang}, \citenamefont {Wang},
+		\citenamefont {Zhang}, \citenamefont {Li}, \citenamefont {Gao},\ and\
+		\citenamefont {Gu}}]{jia15}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {X.-J.}\ \bibnamefont
+			{Jiang}}, \bibinfo {author} {\bibfnamefont {H.~B.}\ \bibnamefont {Liu}},
+		\bibinfo {author} {\bibfnamefont {Q.}~\bibnamefont {Zhang}}, \bibinfo
+		{author} {\bibfnamefont {J.}~\bibnamefont {Wang}}, \bibinfo {author}
+		{\bibfnamefont {Z.-Y.}\ \bibnamefont {Zhang}}, \bibinfo {author}
+		{\bibfnamefont {J.}~\bibnamefont {Li}}, \bibinfo {author} {\bibfnamefont
+			{Y.}~\bibnamefont {Gao}}, \ and\ \bibinfo {author} {\bibfnamefont
+			{Q.}~\bibnamefont {Gu}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+			{{{SMA} Observations of C$_2$H in High-Mass Star-Forming Regions}},}\ }\href
+	{\doibase 10.1088/0004-637x/808/2/114} {\bibfield  {journal} {\bibinfo
+			{journal} {The Astrophysical Journal}\ }\textbf {\bibinfo {volume} {808}},\
+		\bibinfo {pages} {114} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Douglas}(1977)}]{dou77}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+			{Douglas}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Origin of
+				diffuse interstellar lines},}\ }\href
+	{https://www.nature.com/articles/269130a0} {\bibfield  {journal} {\bibinfo
+			{journal} {Nature}\ }\textbf {\bibinfo {volume} {269}},\ \bibinfo {pages}
+		{130--132} (\bibinfo {year} {1977})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Fulara}\ \emph {et~al.}(1993)\citenamefont {Fulara},
+		\citenamefont {Lessen}, \citenamefont {Freivogel},\ and\ \citenamefont
+		{Maier}}]{ful93}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+			{Fulara}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Lessen}},
+		\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Freivogel}}, \ and\
+		\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Maier}},\ }\bibfield
+	{title} {\enquote {\bibinfo {title} {Laboratory evidence for highly
+				unsaturated hydrocarbons as carriers of some of the diffuse interstellar
+				bands},}\ }\href {https://www.nature.com/articles/366439a0} {\bibfield
+		{journal} {\bibinfo  {journal} {Nature}\ }\textbf {\bibinfo {volume} {366}},\
+		\bibinfo {pages} {439--441} (\bibinfo {year} {1993})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {{Watson}}(1994)}]{wat94}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~K.}\ \bibnamefont
+			{{Watson}}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Homologous
+					Series of Diffuse Interstellar Bands}},}\ }\href {\doibase 10.1086/175030}
+	{\bibfield  {journal} {\bibinfo  {journal} {The Astrophysical Journal}\
+		}\textbf {\bibinfo {volume} {437}},\ \bibinfo {pages} {678} (\bibinfo {year}
+		{1994})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Fulara}\ and\ \citenamefont
+		{Krelowski}(2000)}]{ful00}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+			{Fulara}}\ and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+			{Krelowski}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Origin of
+				diffuse interstellar bands: spectroscopic studies of their possible
+				carriers},}\ }\href {\doibase https://doi.org/10.1016/S1387-6473(00)00108-1}
+	{\bibfield  {journal} {\bibinfo  {journal} {New Astronomy Reviews}\ }\textbf
+		{\bibinfo {volume} {44}},\ \bibinfo {pages} {581--597} (\bibinfo {year}
+		{2000})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Schmidt Timothy~W.}(2005)}]{sch05}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~R.~G.}\
+			\bibnamefont {Schmidt Timothy~W.}},\ }\bibfield  {title} {\enquote {\bibinfo
+			{title} {The optical spectroscopy of extraterrestrial molecules.}}\ }\href
+	{https://www.publish.csiro.au/ch/Fulltext/CH04269#R14} {\bibfield  {journal}
+		{\bibinfo  {journal} {Australian Journal of Chemistry}\ }\textbf {\bibinfo
+			{volume} {58}},\ \bibinfo {pages} {69--81} (\bibinfo {year}
+		{2005})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Millar}, \citenamefont {Walsh},\ and\ \citenamefont
+		{Field}(2017)}]{mil17}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.~J.}\ \bibnamefont
+			{Millar}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Walsh}}, \
+		and\ \bibinfo {author} {\bibfnamefont {T.~A.}\ \bibnamefont {Field}},\
+	}\bibfield  {title} {\enquote {\bibinfo {title} {Negative ions in space},}\
+	}\href {\doibase 10.1021/acs.chemrev.6b00480} {\bibfield  {journal} {\bibinfo
+			{journal} {Chemical Reviews}\ }\textbf {\bibinfo {volume} {117}},\ \bibinfo
+		{pages} {1765--1795} (\bibinfo {year} {2017})},\ \bibinfo {note} {pMID:
+		28112897}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {McCarthy}\ \emph {et~al.}(2006)\citenamefont
+		{McCarthy}, \citenamefont {Gottlieb}, \citenamefont {Gupta},\ and\
+		\citenamefont {Thaddeus}}]{mcc06}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~C.}\ \bibnamefont
+			{McCarthy}}, \bibinfo {author} {\bibfnamefont {C.~A.}\ \bibnamefont
+			{Gottlieb}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Gupta}}, \
+		and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Thaddeus}},\
+	}\bibfield  {title} {\enquote {\bibinfo {title} {{Laboratory and Astronomical
+					Identification of the Negative Molecular Ion C$_6$H$^-$}},}\ }\href {\doibase
+		10.1086/510238} {\bibfield  {journal} {\bibinfo  {journal} {The Astrophysical
+				Journal}\ }\textbf {\bibinfo {volume} {652}},\ \bibinfo {pages} {L141--L144}
+		(\bibinfo {year} {2006})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Cernicharo}\ \emph {et~al.}(2007)\citenamefont
+		{Cernicharo}, \citenamefont {Gu\'elin}, \citenamefont {Ag\'undez},
+		\citenamefont {Kawaguchi}, \citenamefont {McCarthy},\ and\ \citenamefont
+		{Thaddeus}}]{cer07}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+			{Cernicharo}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+			{Gu\'elin}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Ag\'undez}},
+		\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Kawaguchi}}, \bibinfo
+		{author} {\bibfnamefont {M.}~\bibnamefont {McCarthy}}, \ and\ \bibinfo
+		{author} {\bibfnamefont {P.}~\bibnamefont {Thaddeus}},\ }\bibfield  {title}
+	{\enquote {\bibinfo {title} {{Astronomical detection of C$_4$H$^-$, the
+					second interstellar anion*}},}\ }\href {\doibase 10.1051/0004-6361:20077415}
+	{\bibfield  {journal} {\bibinfo  {journal} {Astronomy \& Astropysics}\
+		}\textbf {\bibinfo {volume} {467}},\ \bibinfo {pages} {L37--L40} (\bibinfo
+		{year} {2007})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Br\"{u}nken}\ \emph {et~al.}(2007)\citenamefont
+		{Br\"{u}nken}, \citenamefont {Gupta}, \citenamefont {Gottlieb}, \citenamefont
+		{McCarthy},\ and\ \citenamefont {Thaddeus}}]{bru07}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+			{Br\"{u}nken}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Gupta}},
+		\bibinfo {author} {\bibfnamefont {C.~A.}\ \bibnamefont {Gottlieb}}, \bibinfo
+		{author} {\bibfnamefont {M.~C.}\ \bibnamefont {McCarthy}}, \ and\ \bibinfo
+		{author} {\bibfnamefont {P.}~\bibnamefont {Thaddeus}},\ }\bibfield  {title}
+	{\enquote {\bibinfo {title} {{Detection of the Carbon Chain Negative Ion
+					C$_8$H$^-$ in {TMC}-1}},}\ }\href {\doibase 10.1086/520703} {\bibfield
+		{journal} {\bibinfo  {journal} {The Astrophysical Journal}\ }\textbf
+		{\bibinfo {volume} {664}},\ \bibinfo {pages} {L43--L46} (\bibinfo {year}
+		{2007})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Remijan}\ \emph {et~al.}(2007)\citenamefont
+		{Remijan}, \citenamefont {Hollis}, \citenamefont {Lovas}, \citenamefont
+		{Cordiner}, \citenamefont {Millar}, \citenamefont {Markwick-Kemper},\ and\
+		\citenamefont {Jewell}}]{rem07}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont
+			{Remijan}}, \bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont {Hollis}},
+		\bibinfo {author} {\bibfnamefont {F.~J.}\ \bibnamefont {Lovas}}, \bibinfo
+		{author} {\bibfnamefont {M.~A.}\ \bibnamefont {Cordiner}}, \bibinfo {author}
+		{\bibfnamefont {T.~J.}\ \bibnamefont {Millar}}, \bibinfo {author}
+		{\bibfnamefont {A.~J.}\ \bibnamefont {Markwick-Kemper}}, \ and\ \bibinfo
+		{author} {\bibfnamefont {P.~R.}\ \bibnamefont {Jewell}},\ }\bibfield  {title}
+	{\enquote {\bibinfo {title} {{Detection of C$_8$H$^-$ and Comparison with
+					C$_8$H toward {IRC} $+$10 216}},}\ }\href {\doibase 10.1086/520704}
+	{\bibfield  {journal} {\bibinfo  {journal} {The Astrophysical Journal}\
+		}\textbf {\bibinfo {volume} {664}},\ \bibinfo {pages} {L47--L50} (\bibinfo
+		{year} {2007})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Cordiner}\ \emph {et~al.}(2013)\citenamefont
+		{Cordiner}, \citenamefont {Buckle}, \citenamefont {Wirstr\"{o}m},
+		\citenamefont {Olofsson},\ and\ \citenamefont {Charnley}}]{cor13}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont
+			{Cordiner}}, \bibinfo {author} {\bibfnamefont {J.~V.}\ \bibnamefont
+			{Buckle}}, \bibinfo {author} {\bibfnamefont {E.~S.}\ \bibnamefont
+			{Wirstr\"{o}m}}, \bibinfo {author} {\bibfnamefont {A.~O.~H.}\ \bibnamefont
+			{Olofsson}}, \ and\ \bibinfo {author} {\bibfnamefont {S.~B.}\ \bibnamefont
+			{Charnley}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{On the
+					Ubiquity of Molecular Anions in the Dense Interstellar Medium}},}\ }\href
+	{\doibase 10.1088/0004-637x/770/1/48} {\bibfield  {journal} {\bibinfo
+			{journal} {The Astrophysical Journal}\ }\textbf {\bibinfo {volume} {770}},\
+		\bibinfo {pages} {48} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Sakai}\ \emph {et~al.}(2010)\citenamefont {Sakai},
+		\citenamefont {Shiino}, \citenamefont {Hirota}, \citenamefont {Sakai},\ and\
+		\citenamefont {Yamamoto}}]{sak10}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+			{Sakai}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Shiino}},
+		\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Hirota}}, \bibinfo
+		{author} {\bibfnamefont {T.}~\bibnamefont {Sakai}}, \ and\ \bibinfo {author}
+		{\bibfnamefont {S.}~\bibnamefont {Yamamoto}},\ }\bibfield  {title} {\enquote
+		{\bibinfo {title} {{Long Carbon-Chain Molecules and their Anions in the
+					Starless Core LUPUS-1A}},}\ }\href {\doibase 10.1088/2041-8205/718/2/l49}
+	{\bibfield  {journal} {\bibinfo  {journal} {The Astrophysical Journal}\
+		}\textbf {\bibinfo {volume} {718}},\ \bibinfo {pages} {L49--L52} (\bibinfo
+		{year} {2010})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Sakai}, \citenamefont {Sakai},\ and\ \citenamefont
+		{Yamamoto}(2007)}]{sak07}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+			{Sakai}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Sakai}}, \ and\
+		\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Yamamoto}},\ }\bibfield
+	{title} {\enquote {\bibinfo {title} {Tentative detection of {C$_4$H$^-$
+					toward the Low-Mass Protostar {IRAS} 04368$+$2557 in L1527}},}\ }\href
+	{\doibase 10.1086/527376} {\bibfield  {journal} {\bibinfo  {journal} {The
+				Astrophysical Journal}\ }\textbf {\bibinfo {volume} {673}},\ \bibinfo {pages}
+		{L71--L74} (\bibinfo {year} {2007})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Herbst}\ and\ \citenamefont {Osamura}(2008)}]{her08}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+			{Herbst}}\ and\ \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+			{Osamura}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Calculations on
+				the formation rates and mechanisms for {CnH} anions in interstellar and
+				circumstellar media},}\ }\href {\doibase 10.1086/587803} {\bibfield
+		{journal} {\bibinfo  {journal} {The Astrophysical Journal}\ }\textbf
+		{\bibinfo {volume} {679}},\ \bibinfo {pages} {1670--1679} (\bibinfo {year}
+		{2008})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Bastian}\ \emph {et~al.}(2019)\citenamefont
+		{Bastian}, \citenamefont {Michaelsen}, \citenamefont {Meyer},\ and\
+		\citenamefont {Wester}}]{bas19}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
+			{Bastian}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Michaelsen}},
+		\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Meyer}}, \ and\ \bibinfo
+		{author} {\bibfnamefont {R.}~\bibnamefont {Wester}},\ }\bibfield  {title}
+	{\enquote {\bibinfo {title} {{Anionic Carbon Chain Growth in Reactions of
+					C$_2^-$, C$_4^-$, C$_6^-$, C$_2$H$^-$, C$_4$H$^-$, and C$_6$H$^-$ with
+					C$_2$H$_2$}},}\ }\href {\doibase 10.3847/1538-4357/ab2042} {\bibfield
+		{journal} {\bibinfo  {journal} {The Astrophysical Journal}\ }\textbf
+		{\bibinfo {volume} {878}},\ \bibinfo {pages} {162} (\bibinfo {year}
+		{2019})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Vuitton}\ \emph {et~al.}(2009)\citenamefont
+		{Vuitton}, \citenamefont {Lavvas}, \citenamefont {Yelle}, \citenamefont
+		{Galand}, \citenamefont {Wellbrock}, \citenamefont {Lewis}, \citenamefont
+		{Coates},\ and\ \citenamefont {Wahlund}}]{vui09}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
+			{Vuitton}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Lavvas}},
+		\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Yelle}}, \bibinfo
+		{author} {\bibfnamefont {M.}~\bibnamefont {Galand}}, \bibinfo {author}
+		{\bibfnamefont {A.}~\bibnamefont {Wellbrock}}, \bibinfo {author}
+		{\bibfnamefont {G.}~\bibnamefont {Lewis}}, \bibinfo {author} {\bibfnamefont
+			{A.}~\bibnamefont {Coates}}, \ and\ \bibinfo {author} {\bibfnamefont {J.-E.}\
+			\bibnamefont {Wahlund}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+			{{Negative ion chemistry in Titan's upper atmosphere}},}\ }\href {\doibase
+		https://doi.org/10.1016/j.pss.2009.04.004} {\bibfield  {journal} {\bibinfo
+			{journal} {Planetary and Space Science}\ }\textbf {\bibinfo {volume} {57}},\
+		\bibinfo {pages} {1558--1572} (\bibinfo {year} {2009})},\ \bibinfo {note}
+	{surfaces and Atmospheres of the Outer Planets, Their Satellites and Ring
+		Systems: Part V}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Desai}\ \emph {et~al.}(2017)\citenamefont {Desai},
+		\citenamefont {Coates}, \citenamefont {Wellbrock}, \citenamefont {Vuitton},
+		\citenamefont {Crary}, \citenamefont {Gonz{\'{a}}lez-Caniulef}, \citenamefont
+		{Shebanits}, \citenamefont {Jones}, \citenamefont {Lewis}, \citenamefont
+		{Waite}, \citenamefont {Cordiner}, \citenamefont {Taylor}, \citenamefont
+		{Kataria}, \citenamefont {Wahlund}, \citenamefont {Edberg},\ and\
+		\citenamefont {Sittler}}]{des17}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~T.}\ \bibnamefont
+			{Desai}}, \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont {Coates}},
+		\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Wellbrock}}, \bibinfo
+		{author} {\bibfnamefont {V.}~\bibnamefont {Vuitton}}, \bibinfo {author}
+		{\bibfnamefont {F.~J.}\ \bibnamefont {Crary}}, \bibinfo {author}
+		{\bibfnamefont {D.}~\bibnamefont {Gonz{\'{a}}lez-Caniulef}}, \bibinfo
+		{author} {\bibfnamefont {O.}~\bibnamefont {Shebanits}}, \bibinfo {author}
+		{\bibfnamefont {G.~H.}\ \bibnamefont {Jones}}, \bibinfo {author}
+		{\bibfnamefont {G.~R.}\ \bibnamefont {Lewis}}, \bibinfo {author}
+		{\bibfnamefont {J.~H.}\ \bibnamefont {Waite}}, \bibinfo {author}
+		{\bibfnamefont {M.}~\bibnamefont {Cordiner}}, \bibinfo {author}
+		{\bibfnamefont {S.~A.}\ \bibnamefont {Taylor}}, \bibinfo {author}
+		{\bibfnamefont {D.~O.}\ \bibnamefont {Kataria}}, \bibinfo {author}
+		{\bibfnamefont {J.-E.}\ \bibnamefont {Wahlund}}, \bibinfo {author}
+		{\bibfnamefont {N.~J.~T.}\ \bibnamefont {Edberg}}, \ and\ \bibinfo {author}
+		{\bibfnamefont {E.~C.}\ \bibnamefont {Sittler}},\ }\bibfield  {title}
+	{\enquote {\bibinfo {title} {Carbon chain anions and the growth of complex
+				organic molecules in titan's ionosphere},}\ }\href {\doibase
+		10.3847/2041-8213/aa7851} {\bibfield  {journal} {\bibinfo  {journal} {The
+				Astrophysical Journal}\ }\textbf {\bibinfo {volume} {844}},\ \bibinfo {pages}
+		{L18} (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Mukundan}\ and\ \citenamefont
+		{Bhardwaj}(2018)}]{vri18}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
+			{Mukundan}}\ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+			{Bhardwaj}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {A model for
+				negative ion chemistry in {Titan's} ionosphere},}\ }\href {\doibase
+		10.3847/1538-4357/aab1f5} {\bibfield  {journal} {\bibinfo  {journal} {The
+				Astrophysical Journal}\ }\textbf {\bibinfo {volume} {856}},\ \bibinfo {pages}
+		{168} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Maier}(1997)}]{mai97}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~P.}\ \bibnamefont
+			{Maier}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Electronic
+				spectroscopy of carbon chains},}\ }\href {\doibase 10.1039/CS9972600021}
+	{\bibfield  {journal} {\bibinfo  {journal} {Chemical Society Reviews}\
+		}\textbf {\bibinfo {volume} {26}},\ \bibinfo {pages} {21--28} (\bibinfo
+		{year} {1997})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Fortenberry}\ \emph {et~al.}(2010)\citenamefont
+		{Fortenberry}, \citenamefont {King}, \citenamefont {Stanton},\ and\
+		\citenamefont {Crawford}}]{for10}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~C.}\ \bibnamefont
+			{Fortenberry}}, \bibinfo {author} {\bibfnamefont {R.~A.}\ \bibnamefont
+			{King}}, \bibinfo {author} {\bibfnamefont {J.~F.}\ \bibnamefont {Stanton}}, \
+		and\ \bibinfo {author} {\bibfnamefont {T.~D.}\ \bibnamefont {Crawford}},\
+	}\bibfield  {title} {\enquote {\bibinfo {title} {{A benchmark study of the
+					vertical electronic spectra of the linear chain radicals C$_2$H and C4H}},}\
+	}\href {\doibase 10.1063/1.3376073} {\bibfield  {journal} {\bibinfo
+			{journal} {The Journal of Chemical Physics}\ }\textbf {\bibinfo {volume}
+			{132}},\ \bibinfo {pages} {144303} (\bibinfo {year} {2010})}\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {Curl}, \citenamefont {Carrick},\ and\ \citenamefont
+		{Merer}(1985)}]{cur85}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~F.}\ \bibnamefont
+			{Curl}}, \bibinfo {author} {\bibfnamefont {P.~G.}\ \bibnamefont {Carrick}}, \
+		and\ \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont {Merer}},\
+	}\bibfield  {title} {\enquote {\bibinfo {title} {{Rotational analysis of the
+					$\tilde{A}\leftarrow\tilde{X}$ system of C$_2$H}},}\ }\href {\doibase
+		10.1063/1.448927} {\bibfield  {journal} {\bibinfo  {journal} {The Journal of
+				Chemical Physics}\ }\textbf {\bibinfo {volume} {82}},\ \bibinfo {pages}
+		{3479--3486} (\bibinfo {year} {1985})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Tarroni}\ and\ \citenamefont {Carter}(2003)}]{tar03}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+			{Tarroni}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+			{Carter}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Theoretical
+					calculation of vibronic levels of C$_2$H and C$_2$D to 10,000 cm$^{-1}$}},}\
+	}\href {\doibase 10.1063/1.1627755} {\bibfield  {journal} {\bibinfo
+			{journal} {The Journal of Chemical Physics}\ }\textbf {\bibinfo {volume}
+			{119}},\ \bibinfo {pages} {12878--12889} (\bibinfo {year}
+		{2003})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Zhou}, \citenamefont {Garand},\ and\ \citenamefont
+		{Neumark}(2007{\natexlab{a}})}]{zho07b}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+			{Zhou}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Garand}}, \ and\
+		\bibinfo {author} {\bibfnamefont {D.~M.}\ \bibnamefont {Neumark}},\
+	}\bibfield  {title} {\enquote {\bibinfo {title} {{Slow electron velocity-map
+					imaging spectroscopy of the C$_4$H$^-$ and C$_4$D$^-$ anions}},}\ }\href
+	{\doibase 10.1063/1.2795723} {\bibfield  {journal} {\bibinfo  {journal} {The
+				Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {127}},\ \bibinfo
+		{pages} {154320} (\bibinfo {year} {2007}{\natexlab{a}})}\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {Linnartz}\ \emph {et~al.}(1999)\citenamefont
+		{Linnartz}, \citenamefont {Motylewski}, \citenamefont {Vaizert},
+		\citenamefont {Maier}, \citenamefont {Apponi}, \citenamefont {McCarthy},
+		\citenamefont {Gottlieb},\ and\ \citenamefont {Thaddeus}}]{lin99}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+			{Linnartz}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+			{Motylewski}}, \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Vaizert}},
+		\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Maier}}, \bibinfo
+		{author} {\bibfnamefont {A.}~\bibnamefont {Apponi}}, \bibinfo {author}
+		{\bibfnamefont {M.}~\bibnamefont {McCarthy}}, \bibinfo {author}
+		{\bibfnamefont {C.}~\bibnamefont {Gottlieb}}, \ and\ \bibinfo {author}
+		{\bibfnamefont {P.}~\bibnamefont {Thaddeus}},\ }\bibfield  {title} {\enquote
+		{\bibinfo {title} {{Electronic Ground and Excited State Spectroscopy of
+					C$_6$H and C$_6$D}},}\ }\href {\doibase
+		https://doi.org/10.1006/jmsp.1999.7885} {\bibfield  {journal} {\bibinfo
+			{journal} {Journal of Molecular Spectroscopy}\ }\textbf {\bibinfo {volume}
+			{197}},\ \bibinfo {pages} {1--11} (\bibinfo {year} {1999})}\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {Taylor}, \citenamefont {Xu},\ and\ \citenamefont
+		{Neumark}(1998)}]{tay98}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.~R.}\ \bibnamefont
+			{Taylor}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Xu}}, \ and\
+		\bibinfo {author} {\bibfnamefont {D.~M.}\ \bibnamefont {Neumark}},\
+	}\bibfield  {title} {\enquote {\bibinfo {title} {{Photoelectron spectra of
+					the C$_{2n}$H$^-$ (n=1-4) and C$_{2n}$D$^-$ (n=1-3) anions}},}\ }\href
+	{\doibase 10.1063/1.476462} {\bibfield  {journal} {\bibinfo  {journal} {The
+				Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {108}},\ \bibinfo
+		{pages} {10018--10026} (\bibinfo {year} {1998})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {{Heikkil{\"a}}}, \citenamefont {{Johansson}},\ and\
+		\citenamefont {{Olofsson}}(1999)}]{hei99}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+			{{Heikkil{\"a}}}}, \bibinfo {author} {\bibfnamefont {L.~E.~B.}\ \bibnamefont
+			{{Johansson}}}, \ and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+			{{Olofsson}}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Molecular
+					abundance variations in the Magellanic Clouds}},}\ }\href@noop {} {\bibfield
+		{journal} {\bibinfo  {journal} {Astronomy $\&$ Astrophysics}\ }\textbf
+		{\bibinfo {volume} {344}},\ \bibinfo {pages} {817--847} (\bibinfo {year}
+		{1999})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Cochran}, \citenamefont {Adrian},\ and\ \citenamefont
+		{Bowers}(1964)}]{coc64}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.~L.}\ \bibnamefont
+			{Cochran}}, \bibinfo {author} {\bibfnamefont {F.~J.}\ \bibnamefont {Adrian}},
+		\ and\ \bibinfo {author} {\bibfnamefont {V.~A.}\ \bibnamefont {Bowers}},\
+	}\bibfield  {title} {\enquote {\bibinfo {title} {{ESR Study of Ethynyl and
+					Vinyl Free Radicals}},}\ }\href {\doibase 10.1063/1.1724865} {\bibfield
+		{journal} {\bibinfo  {journal} {The Journal of Chemical Physics}\ }\textbf
+		{\bibinfo {volume} {40}},\ \bibinfo {pages} {213--220} (\bibinfo {year}
+		{1964})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Jinguji}, \citenamefont {McDowell},\ and\
+		\citenamefont {Shimokoshi}(1985)}]{jin85}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+			{Jinguji}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {McDowell}}, \
+		and\ \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Shimokoshi}},\
+	}\bibfield  {title} {\enquote {\bibinfo {title} {{High-resolution ESR
+					spectrum of the ethynyl radical in an argon matrix at 4.2 K}},}\ }\href
+	{\doibase https://doi.org/10.1016/0022-2860(85)87014-9} {\bibfield  {journal}
+		{\bibinfo  {journal} {Journal of Molecular Structure}\ }\textbf {\bibinfo
+			{volume} {130}},\ \bibinfo {pages} {317--326} (\bibinfo {year}
+		{1985})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Brown}\ and\ \citenamefont {Evenson}(1988)}]{bro88}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont
+			{Brown}}\ and\ \bibinfo {author} {\bibfnamefont {K.~M.}\ \bibnamefont
+			{Evenson}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{The
+					far-infrared laser magnetic resonance spectrum of vibrationally excited
+					C$_2$H}},}\ }\href {\doibase https://doi.org/10.1016/0022-2852(88)90115-4}
+	{\bibfield  {journal} {\bibinfo  {journal} {Journal of Molecular
+				Spectroscopy}\ }\textbf {\bibinfo {volume} {131}},\ \bibinfo {pages}
+		{161--171} (\bibinfo {year} {1988})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Pfelzer}\ \emph {et~al.}(1996)\citenamefont
+		{Pfelzer}, \citenamefont {Havenith}, \citenamefont {Peri\'{c}}, \citenamefont
+		{M\"{u}rtz},\ and\ \citenamefont {Urban}}]{pfe96}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+			{Pfelzer}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Havenith}},
+		\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Peri\'{c}}}, \bibinfo
+		{author} {\bibfnamefont {P.}~\bibnamefont {M\"{u}rtz}}, \ and\ \bibinfo
+		{author} {\bibfnamefont {W.}~\bibnamefont {Urban}},\ }\bibfield  {title}
+	{\enquote {\bibinfo {title} {{Faraday Laser Magnetic Resonance Spectroscopy
+					of Vibrationally Excited C$_2$H}},}\ }\href {\doibase
+		https://doi.org/10.1006/jmsp.1996.0058} {\bibfield  {journal} {\bibinfo
+			{journal} {Journal of Molecular Spectroscopy}\ }\textbf {\bibinfo {volume}
+			{176}},\ \bibinfo {pages} {28--37} (\bibinfo {year} {1996})}\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {Schmidt}\ \emph {et~al.}(1998)\citenamefont
+		{Schmidt}, \citenamefont {Peri\'{c}}, \citenamefont {M\"{u}rtz},
+		\citenamefont {Wienkoop}, \citenamefont {Havenith},\ and\ \citenamefont
+		{Urban}}]{sch98}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+			{Schmidt}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Peri\'{c}}},
+		\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {M\"{u}rtz}}, \bibinfo
+		{author} {\bibfnamefont {M.}~\bibnamefont {Wienkoop}}, \bibinfo {author}
+		{\bibfnamefont {M.}~\bibnamefont {Havenith}}, \ and\ \bibinfo {author}
+		{\bibfnamefont {W.}~\bibnamefont {Urban}},\ }\bibfield  {title} {\enquote
+		{\bibinfo {title} {{Faraday Laser Magnetic Resonance Spectroscopy of
+					Vibrationally Excited C$_2$D}},}\ }\href {\doibase
+		https://doi.org/10.1006/jmsp.1998.7563} {\bibfield  {journal} {\bibinfo
+			{journal} {Journal of Molecular Spectroscopy}\ }\textbf {\bibinfo {volume}
+			{190}},\ \bibinfo {pages} {112--124} (\bibinfo {year} {1998})}\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {{Sastry}}\ \emph {et~al.}(1981)\citenamefont
+		{{Sastry}}, \citenamefont {{Helminger}}, \citenamefont {{Charo}},
+		\citenamefont {{Herbst}},\ and\ \citenamefont {{De Lucia}}}]{sas81}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.~V.~L.~N.}\
+			\bibnamefont {{Sastry}}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+			{{Helminger}}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+			{{Charo}}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {{Herbst}}}, \
+		and\ \bibinfo {author} {\bibfnamefont {F.~C.}\ \bibnamefont {{De Lucia}}},\
+	}\bibfield  {title} {\enquote {\bibinfo {title} {{Laboratory millimeter and
+					submillimeter spectrum of CCH}},}\ }\href {\doibase 10.1086/183706}
+	{\bibfield  {journal} {\bibinfo  {journal} {The Astrophysical Journal}\
+		}\textbf {\bibinfo {volume} {251}},\ \bibinfo {pages} {L119} (\bibinfo {year}
+		{1981})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {{Gottlieb}}, \citenamefont {{Gottlieb}},\ and\
+		\citenamefont {{Thaddeus}}(1983)}]{got83}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~A.}\ \bibnamefont
+			{{Gottlieb}}}, \bibinfo {author} {\bibfnamefont {E.~W.}\ \bibnamefont
+			{{Gottlieb}}}, \ and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+			{{Thaddeus}}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Laboratory
+					and astronomical measurement of the millimeter wave spectrum of the ethynyl
+					radical CCH}},}\ }\href {\doibase 10.1086/160647} {\bibfield  {journal}
+		{\bibinfo  {journal} {The Astrophysical Journal}\ }\textbf {\bibinfo {volume}
+			{264}},\ \bibinfo {pages} {740--745} (\bibinfo {year} {1983})}\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {Endo}, \citenamefont {Kanamori},\ and\ \citenamefont
+		{Hirota}(1989)}]{end89}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+			{Endo}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Kanamori}}, \
+		and\ \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Hirota}},\
+	}\bibfield  {title} {\enquote {\bibinfo {title} {{Millimeter- and
+					submillimeter-wave spectra of the vibrationally excited CCD radical}},}\
+	}\href {\doibase https://doi.org/10.1016/0009-2614(89)87596-7} {\bibfield
+		{journal} {\bibinfo  {journal} {Chemical Physics Letters}\ }\textbf {\bibinfo
+			{volume} {160}},\ \bibinfo {pages} {280--284} (\bibinfo {year}
+		{1989})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {{M{\"u}ller}}, \citenamefont {{Klaus}},\ and\
+		\citenamefont {{Winnewisser}}(2000)}]{mul00}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.~S.~P.}\
+			\bibnamefont {{M{\"u}ller}}}, \bibinfo {author} {\bibfnamefont
+			{T.}~\bibnamefont {{Klaus}}}, \ and\ \bibinfo {author} {\bibfnamefont
+			{G.}~\bibnamefont {{Winnewisser}}},\ }\bibfield  {title} {\enquote {\bibinfo
+			{title} {{Submillimeter-wave spectrum of the ethynyl radical, CCH, up to 1
+					THz}},}\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Astronomy
+				and Astrophysics}\ }\textbf {\bibinfo {volume} {357}},\ \bibinfo {pages}
+		{L65--L67} (\bibinfo {year} {2000})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Shepherd}\ and\ \citenamefont
+		{Graham}(1987)}]{she87}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~A.}\ \bibnamefont
+			{Shepherd}}\ and\ \bibinfo {author} {\bibfnamefont {W.~R.~M.}\ \bibnamefont
+			{Graham}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{FTIR study of D
+					and 13C substituted C$_2$H in solid argon}},}\ }\href {\doibase
+		10.1063/1.452062} {\bibfield  {journal} {\bibinfo  {journal} {The Journal of
+				Chemical Physics}\ }\textbf {\bibinfo {volume} {86}},\ \bibinfo {pages}
+		{2600--2605} (\bibinfo {year} {1987})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Jacox}\ and\ \citenamefont {Olson}(1987)}]{jac87}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~E.}\ \bibnamefont
+			{Jacox}}\ and\ \bibinfo {author} {\bibfnamefont {W.~B.}\ \bibnamefont
+			{Olson}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{The
+					$\tilde{A}^2\Pi-\tilde{X}^2\Sigma^+$ transition of HC$_2$ isolated in solid
+					argon}},}\ }\href {\doibase 10.1063/1.452024} {\bibfield  {journal} {\bibinfo
+			{journal} {The Journal of Chemical Physics}\ }\textbf {\bibinfo {volume}
+			{86}},\ \bibinfo {pages} {3134--3142} (\bibinfo {year} {1987})}\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {Forney}, \citenamefont {Jacox},\ and\ \citenamefont
+		{Thompson}(1995)}]{for95}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+			{Forney}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Jacox}}, \
+		and\ \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Thompson}},\
+	}\bibfield  {title} {\enquote {\bibinfo {title} {{The Infrared and
+					Near-Infrared Spectra of HCC and DCC Trapped in Solid Neon}},}\ }\href
+	{\doibase https://doi.org/10.1006/jmsp.1995.1065} {\bibfield  {journal}
+		{\bibinfo  {journal} {Journal of Molecular Spectroscopy}\ }\textbf {\bibinfo
+			{volume} {170}},\ \bibinfo {pages} {178--214} (\bibinfo {year}
+		{1995})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Vervloet}\ and\ \citenamefont
+		{Herman}(1988)}]{ver88}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+			{Vervloet}}\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+			{Herman}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Fourier
+					transform emission spectroscopy of C$_2$H}},}\ }\href {\doibase
+		https://doi.org/10.1016/0009-2614(88)87087-8} {\bibfield  {journal} {\bibinfo
+			{journal} {Chemical Physics Letters}\ }\textbf {\bibinfo {volume} {144}},\
+		\bibinfo {pages} {48--50} (\bibinfo {year} {1988})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Hsu}\ \emph {et~al.}(1993)\citenamefont {Hsu},
+		\citenamefont {Lin}, \citenamefont {Papousek},\ and\ \citenamefont
+		{Tsai}}]{hsu93}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+			{Hsu}}, \bibinfo {author} {\bibfnamefont {J.~J.}\ \bibnamefont {Lin}},
+		\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Papousek}}, \ and\
+		\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Tsai}},\ }\bibfield
+	{title} {\enquote {\bibinfo {title} {The low-lying bending vibrational levels
+				of the {CCH} ($\tilde{X}^2\sigma^+$) radical studied by laser-induced
+				fluorescence},}\ }\href {\doibase 10.1063/1.464761} {\bibfield  {journal}
+		{\bibinfo  {journal} {The Journal of Chemical Physics}\ }\textbf {\bibinfo
+			{volume} {98}},\ \bibinfo {pages} {6690--6696} (\bibinfo {year}
+		{1993})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Hsu}, \citenamefont {Shiu},\ and\ \citenamefont
+		{Lin}(1995)}]{hsu95}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+			{Hsu}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Shiu}}, \ and\
+		\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Lin}},\ }\bibfield
+	{title} {\enquote {\bibinfo {title} {{Laser-induced fluorescence spectroscopy
+					of CCH ($\tilde{X}^2 \Sigma^+$) in vibrationally excited levels up to 4500
+					cm$^{-1}$}},}\ }\href {\doibase 10.1063/1.470472} {\bibfield  {journal}
+		{\bibinfo  {journal} {The Journal of Chemical Physics}\ }\textbf {\bibinfo
+			{volume} {103}},\ \bibinfo {pages} {5919--5930} (\bibinfo {year}
+		{1995})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Chiang}\ and\ \citenamefont {Hsu}(1999)}]{chi99}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.-Y.}\ \bibnamefont
+			{Chiang}}\ and\ \bibinfo {author} {\bibfnamefont {Y.-C.}\ \bibnamefont
+			{Hsu}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Laser spectroscopy
+					of CCH in the 36,600-39,700 cm$^{-1}$ region}},}\ }\href {\doibase
+		10.1063/1.479389} {\bibfield  {journal} {\bibinfo  {journal} {The Journal of
+				Chemical Physics}\ }\textbf {\bibinfo {volume} {111}},\ \bibinfo {pages}
+		{1454--1461} (\bibinfo {year} {1999})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Ervin}\ and\ \citenamefont
+		{Lineberger}(1991)}]{erv91}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.~M.}\ \bibnamefont
+			{Ervin}}\ and\ \bibinfo {author} {\bibfnamefont {W.~C.}\ \bibnamefont
+			{Lineberger}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+			{Photoelectron spectra of dicarbon(1-) and ethynyl(1-)},}\ }\href {\doibase
+		10.1021/j100156a026} {\bibfield  {journal} {\bibinfo  {journal} {The Journal
+				of Physical Chemistry}\ }\textbf {\bibinfo {volume} {95}},\ \bibinfo {pages}
+		{1167--1177} (\bibinfo {year} {1991})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Zhou}, \citenamefont {Garand},\ and\ \citenamefont
+		{Neumark}(2007{\natexlab{b}})}]{zho07}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+			{Zhou}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Garand}}, \ and\
+		\bibinfo {author} {\bibfnamefont {D.~M.}\ \bibnamefont {Neumark}},\
+	}\bibfield  {title} {\enquote {\bibinfo {title} {{Vibronic structure in
+					C$_2$H$^-$ and C$_2$D$^-$ from anion slow electron velocity-map imaging
+					spectroscopy}},}\ }\href {\doibase 10.1063/1.2768932} {\bibfield  {journal}
+		{\bibinfo  {journal} {The Journal of Chemical Physics}\ }\textbf {\bibinfo
+			{volume} {127}},\ \bibinfo {pages} {114313} (\bibinfo {year}
+		{2007}{\natexlab{b}})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Peri\'{c}}, \citenamefont {Peyerimhoff},\ and\
+		\citenamefont {Buenker}(1990)}]{per90}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+			{Peri\'{c}}}, \bibinfo {author} {\bibfnamefont {S.~D.}\ \bibnamefont
+			{Peyerimhoff}}, \ and\ \bibinfo {author} {\bibfnamefont {R.~J.}\ \bibnamefont
+			{Buenker}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Ab initio
+					investigation of the vibronic structure of the C$_2$H spectrum}},}\ }\href
+	{\doibase 10.1080/00268979000102071} {\bibfield  {journal} {\bibinfo
+			{journal} {Molecular Physics}\ }\textbf {\bibinfo {volume} {71}},\ \bibinfo
+		{pages} {693--719} (\bibinfo {year} {1990})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Peri\'{c}}, \citenamefont {Reuter},\ and\
+		\citenamefont {Peyerimhoff}(1991)}]{per91}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+			{Peri\'{c}}}, \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Reuter}}, \
+		and\ \bibinfo {author} {\bibfnamefont {S.~D.}\ \bibnamefont {Peyerimhoff}},\
+	}\bibfield  {title} {\enquote {\bibinfo {title} {{Ab initio investigation of
+					the vibronic structure in the C$_2$H spectrum: Spin-orbit splitting of the
+					vibronic levels}},}\ }\href {\doibase
+		https://doi.org/10.1016/0022-2852(91)90047-E} {\bibfield  {journal} {\bibinfo
+			{journal} {Journal of Molecular Spectroscopy}\ }\textbf {\bibinfo {volume}
+			{148}},\ \bibinfo {pages} {201--212} (\bibinfo {year} {1991})}\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {Peri\'{c}}, \citenamefont {Peyerimhoff},\ and\
+		\citenamefont {Buenker}(1991)}]{per91b}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+			{Peri\'{c}}}, \bibinfo {author} {\bibfnamefont {S.~D.}\ \bibnamefont
+			{Peyerimhoff}}, \ and\ \bibinfo {author} {\bibfnamefont {R.~J.}\ \bibnamefont
+			{Buenker}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Ab initio
+					investigation of the vibronic structure in the C$_2$H spectrum: Calculation
+					of vibronic energies and wavefunctions for various isotopomers}},}\ }\href
+	{\doibase https://doi.org/10.1016/0022-2852(91)90046-D} {\bibfield  {journal}
+		{\bibinfo  {journal} {Journal of Molecular Spectroscopy}\ }\textbf {\bibinfo
+			{volume} {148}},\ \bibinfo {pages} {180--200} (\bibinfo {year}
+		{1991})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Peri\'{c}}, \citenamefont {Engels},\ and\
+		\citenamefont {Peyerimhoff}(1991)}]{per91c}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+			{Peri\'{c}}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Engels}}, \
+		and\ \bibinfo {author} {\bibfnamefont {S.~D.}\ \bibnamefont {Peyerimhoff}},\
+	}\bibfield  {title} {\enquote {\bibinfo {title} {{Ab initio investigation of
+					the vibronic structure of the C$_2$H spectrum: Computation of the
+					vibronically averaged values for the hyperfine coupling constants}},}\ }\href
+	{\doibase https://doi.org/10.1016/0022-2852(91)90194-F} {\bibfield  {journal}
+		{\bibinfo  {journal} {Journal of Molecular Spectroscopy}\ }\textbf {\bibinfo
+			{volume} {150}},\ \bibinfo {pages} {70--85} (\bibinfo {year}
+		{1991})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Peri\'{c}}, \citenamefont {Peyerimhoff},\ and\
+		\citenamefont {Buenker}(1992)}]{per92}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+			{Peri\'{c}}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+			{Peyerimhoff}}, \ and\ \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+			{Buenker}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Analysis and
+					predictions of the vibronic spectrum of the ethynyl radical C$_2$H by ab
+					initio methods}},}\ }\href
+	{https://link.springer.com/article/10.1007/BF01426704} {\bibfield  {journal}
+		{\bibinfo  {journal} {Z Phys D - Atoms, Molecules and Clusters}\ }\textbf
+		{\bibinfo {volume} {24}},\ \bibinfo {pages} {177--198} (\bibinfo {year}
+		{1992})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Carter}\ \emph {et~al.}(2000)\citenamefont {Carter},
+		\citenamefont {Handy}, \citenamefont {Puzzarini}, \citenamefont {Tarroni},\
+		and\ \citenamefont {Palmieri}}]{car00}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+			{Carter}}, \bibinfo {author} {\bibfnamefont {N.~C.}\ \bibnamefont {Handy}},
+		\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Puzzarini}}, \bibinfo
+		{author} {\bibfnamefont {R.}~\bibnamefont {Tarroni}}, \ and\ \bibinfo
+		{author} {\bibfnamefont {P.}~\bibnamefont {Palmieri}},\ }\bibfield  {title}
+	{\enquote {\bibinfo {title} {A variational method for the calculation of
+				spin-rovibronic energy levels of triatomic molecules with three interacting
+				electronic states},}\ }\href {\doibase 10.1080/00268970009483375} {\bibfield
+		{journal} {\bibinfo  {journal} {Molecular Physics}\ }\textbf {\bibinfo
+			{volume} {98}},\ \bibinfo {pages} {1697--1712} (\bibinfo {year}
+		{2000})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Tarroni}\ and\ \citenamefont {Carter}(2004)}]{tar04}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+			{Tarroni}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+			{Carter}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Theoretical
+				calculation of absorption intensities of {C$_2$H} and {C$_2$D}},}\ }\href
+	{\doibase 10.1080/00268970410001713254} {\bibfield  {journal} {\bibinfo
+			{journal} {Molecular Physics}\ }\textbf {\bibinfo {volume} {102}},\ \bibinfo
+		{pages} {2167--2179} (\bibinfo {year} {2004})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Stanton}(2021)}]{sta21}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~F.}\ \bibnamefont
+			{Stanton}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Why the CC
+					Stretch in HCC Is So Anharmonic}},}\ }\href {\doibase
+		10.1021/acs.jpca.1c06372} {\bibfield  {journal} {\bibinfo  {journal} {The
+				Journal of Physical Chemistry A}\ }\textbf {\bibinfo {volume} {125}},\
+		\bibinfo {pages} {7694--7698} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Gulania}\ and\ \citenamefont {Krylov}(2021)}]{gul21}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+			{Gulania}}\ and\ \bibinfo {author} {\bibfnamefont {A.~I.}\ \bibnamefont
+			{Krylov}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Dissociative
+					electron attachment in C$_2$H via electronic resonances}},}\ }\href {\doibase
+		10.1080/00268976.2021.1979262} {\bibfield  {journal} {\bibinfo  {journal}
+			{Molecular Physics}\ }\textbf {\bibinfo {volume} {119}},\ \bibinfo {pages}
+		{e1979262} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Cavanagh}\ \emph {et~al.}(2007)\citenamefont
+		{Cavanagh}, \citenamefont {Gibson}, \citenamefont {Gale}, \citenamefont
+		{Dedman}, \citenamefont {Roberts},\ and\ \citenamefont {Lewis}}]{cav07}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~J.}\ \bibnamefont
+			{Cavanagh}}, \bibinfo {author} {\bibfnamefont {S.~T.}\ \bibnamefont
+			{Gibson}}, \bibinfo {author} {\bibfnamefont {M.~N.}\ \bibnamefont {Gale}},
+		\bibinfo {author} {\bibfnamefont {C.~J.}\ \bibnamefont {Dedman}}, \bibinfo
+		{author} {\bibfnamefont {E.~H.}\ \bibnamefont {Roberts}}, \ and\ \bibinfo
+		{author} {\bibfnamefont {B.~R.}\ \bibnamefont {Lewis}},\ }\bibfield  {title}
+	{\enquote {\bibinfo {title} {{High resolution velocity-map imaging
+					photoelectron spectroscopy of the O$^-$ fine-structure transitions}},}\
+	}\href {\doibase 10.1103/PhysRevA.76.052708} {\bibfield  {journal} {\bibinfo
+			{journal} {Physical Review A}\ }\textbf {\bibinfo {volume} {76}},\ \bibinfo
+		{pages} {052708} (\bibinfo {year} {2007})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {DeVine}\ \emph {et~al.}(2017)\citenamefont {DeVine},
+		\citenamefont {Weichman}, \citenamefont {Laws}, \citenamefont {Chang},
+		\citenamefont {Babin}, \citenamefont {Balerdi}, \citenamefont {Xie},
+		\citenamefont {Malbon}, \citenamefont {Lineberger}, \citenamefont {Yarkony},
+		\citenamefont {Field}, \citenamefont {Gibson}, \citenamefont {Ma},
+		\citenamefont {Guo},\ and\ \citenamefont {Neumark}}]{dev17}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~A.}\ \bibnamefont
+			{DeVine}}, \bibinfo {author} {\bibfnamefont {M.~L.}\ \bibnamefont
+			{Weichman}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Laws}},
+		\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Chang}}, \bibinfo
+		{author} {\bibfnamefont {M.~C.}\ \bibnamefont {Babin}}, \bibinfo {author}
+		{\bibfnamefont {G.}~\bibnamefont {Balerdi}}, \bibinfo {author} {\bibfnamefont
+			{C.}~\bibnamefont {Xie}}, \bibinfo {author} {\bibfnamefont {C.~L.}\
+			\bibnamefont {Malbon}}, \bibinfo {author} {\bibfnamefont {W.~C.}\
+			\bibnamefont {Lineberger}}, \bibinfo {author} {\bibfnamefont {D.~R.}\
+			\bibnamefont {Yarkony}}, \bibinfo {author} {\bibfnamefont {R.~W.}\
+			\bibnamefont {Field}}, \bibinfo {author} {\bibfnamefont {S.~T.}\ \bibnamefont
+			{Gibson}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Ma}}, \bibinfo
+		{author} {\bibfnamefont {H.}~\bibnamefont {Guo}}, \ and\ \bibinfo {author}
+		{\bibfnamefont {D.~M.}\ \bibnamefont {Neumark}},\ }\bibfield  {title}
+	{\enquote {\bibinfo {title} {Encoding of vinylidene isomerization in its
+				anion photoelectron spectrum},}\ }\href {\doibase 10.1126/science.aao1905}
+	{\bibfield  {journal} {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo
+			{volume} {358}},\ \bibinfo {pages} {336--339} (\bibinfo {year}
+		{2017})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Dedman}\ \emph {et~al.}(2001)\citenamefont {Dedman},
+		\citenamefont {Roberts}, \citenamefont {Gibson},\ and\ \citenamefont
+		{Lewis}}]{ded01}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~J.}\ \bibnamefont
+			{Dedman}}, \bibinfo {author} {\bibfnamefont {E.~H.}\ \bibnamefont {Roberts}},
+		\bibinfo {author} {\bibfnamefont {S.~T.}\ \bibnamefont {Gibson}}, \ and\
+		\bibinfo {author} {\bibfnamefont {B.~R.}\ \bibnamefont {Lewis}},\ }\bibfield
+	{title} {\enquote {\bibinfo {title} {{Fast 1 kV metal-oxide-semiconductor
+					field-effect transistor switch}},}\ }\href {\doibase 10.1063/1.1389488}
+	{\bibfield  {journal} {\bibinfo  {journal} {Review of Scientific
+				Instruments}\ }\textbf {\bibinfo {volume} {72}},\ \bibinfo {pages}
+		{3718--3720} (\bibinfo {year} {2001})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Gascooke}, \citenamefont {Gibson},\ and\
+		\citenamefont {Lawrance}(2017)}]{gas17}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~R.}\ \bibnamefont
+			{Gascooke}}, \bibinfo {author} {\bibfnamefont {S.~T.}\ \bibnamefont
+			{Gibson}}, \ and\ \bibinfo {author} {\bibfnamefont {W.~D.}\ \bibnamefont
+			{Lawrance}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {A
+				circularisation method to repair deformations and determine the centre of
+				velocity map images},}\ }\href {\doibase 10.1063/1.4981024} {\bibfield
+		{journal} {\bibinfo  {journal} {The Journal of Chemical Physics}\ }\textbf
+		{\bibinfo {volume} {147}},\ \bibinfo {pages} {013924} (\bibinfo {year}
+		{2017})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Hansen}\ and\ \citenamefont {Law}(1985)}]{han85}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.~W.}\ \bibnamefont
+			{Hansen}}\ and\ \bibinfo {author} {\bibfnamefont {P.-L.}\ \bibnamefont
+			{Law}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Recursive methods
+				for computing the abel transform and its inverse},}\ }\href {\doibase
+		10.1364/JOSAA.2.000510} {\bibfield  {journal} {\bibinfo  {journal} {Journal
+				of the Optical Society of America A}\ }\textbf {\bibinfo {volume} {2}},\
+		\bibinfo {pages} {510--520} (\bibinfo {year} {1985})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Hickstein}\ \emph {et~al.}(2019)\citenamefont
+		{Hickstein}, \citenamefont {Gibson}, \citenamefont {Yurchak}, \citenamefont
+		{Das},\ and\ \citenamefont {Ryazanov}}]{hic19}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~D.}\ \bibnamefont
+			{Hickstein}}, \bibinfo {author} {\bibfnamefont {S.~T.}\ \bibnamefont
+			{Gibson}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Yurchak}},
+		\bibinfo {author} {\bibfnamefont {D.~D.}\ \bibnamefont {Das}}, \ and\
+		\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Ryazanov}},\ }\bibfield
+	{title} {\enquote {\bibinfo {title} {A direct comparison of high-speed
+				methods for the numerical abel transform},}\ }\href {\doibase
+		10.1063/1.5092635} {\bibfield  {journal} {\bibinfo  {journal} {Review of
+				Scientific Instruments}\ }\textbf {\bibinfo {volume} {90}},\ \bibinfo {pages}
+		{065115} (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Laws}\ \emph
+		{et~al.}(2019{\natexlab{a}})\citenamefont {Laws}, \citenamefont {Lewis},
+		\citenamefont {Gibson},\ and\ \citenamefont {Field}}]{law19b}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.~A.}\ \bibnamefont
+			{Laws}}, \bibinfo {author} {\bibfnamefont {B.~R.}\ \bibnamefont {Lewis}},
+		\bibinfo {author} {\bibfnamefont {S.~T.}\ \bibnamefont {Gibson}}, \ and\
+		\bibinfo {author} {\bibfnamefont {R.~W.}\ \bibnamefont {Field}},\ }\bibfield
+	{title} {\enquote {\bibinfo {title} {The dicarbon bonding puzzle viewed with
+				photoelectron imaging},}\ }\href {\doibase 10.1038/s41467-019-13039-y}
+	{\bibfield  {journal} {\bibinfo  {journal} {Nature Communications}\ }\textbf
+		{\bibinfo {volume} {10}},\ \bibinfo {pages} {5199} (\bibinfo {year}
+		{2019}{\natexlab{a}})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Laws}\ \emph
+		{et~al.}(2019{\natexlab{b}})\citenamefont {Laws}, \citenamefont {Cavanagh},
+		\citenamefont {Lewis},\ and\ \citenamefont {Gibson}}]{law19}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.~A.}\ \bibnamefont
+			{Laws}}, \bibinfo {author} {\bibfnamefont {S.~J.}\ \bibnamefont {Cavanagh}},
+		\bibinfo {author} {\bibfnamefont {B.~R.}\ \bibnamefont {Lewis}}, \ and\
+		\bibinfo {author} {\bibfnamefont {S.~T.}\ \bibnamefont {Gibson}},\ }\bibfield
+	{title} {\enquote {\bibinfo {title} {{Wigner Near-Threshold Effects in the
+					Photoelectron Angular Distribution of NO$_2^-$}},}\ }\href {\doibase
+		10.1021/acs.jpca.9b09073} {\bibfield  {journal} {\bibinfo  {journal} {The
+				Journal of Physical Chemistry A}\ }\textbf {\bibinfo {volume} {123}},\
+		\bibinfo {pages} {10418--10425} (\bibinfo {year}
+		{2019}{\natexlab{b}})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Matthews}\ \emph {et~al.}(2020)\citenamefont
+		{Matthews}, \citenamefont {Cheng}, \citenamefont {Harding}, \citenamefont
+		{Lipparini}, \citenamefont {Stopkowicz}, \citenamefont {Jagau}, \citenamefont
+		{Szalay}, \citenamefont {Gauss},\ and\ \citenamefont {Stanton}}]{dev20}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~A.}\ \bibnamefont
+			{Matthews}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Cheng}},
+		\bibinfo {author} {\bibfnamefont {M.~E.}\ \bibnamefont {Harding}}, \bibinfo
+		{author} {\bibfnamefont {F.}~\bibnamefont {Lipparini}}, \bibinfo {author}
+		{\bibfnamefont {S.}~\bibnamefont {Stopkowicz}}, \bibinfo {author}
+		{\bibfnamefont {T.-C.}\ \bibnamefont {Jagau}}, \bibinfo {author}
+		{\bibfnamefont {P.~G.}\ \bibnamefont {Szalay}}, \bibinfo {author}
+		{\bibfnamefont {J.}~\bibnamefont {Gauss}}, \ and\ \bibinfo {author}
+		{\bibfnamefont {J.~F.}\ \bibnamefont {Stanton}},\ }\bibfield  {title}
+	{\enquote {\bibinfo {title} {Coupled-cluster techniques for computational
+				chemistry: The {CFOUR} program package},}\ }\href {\doibase
+		10.1063/5.0004837} {\bibfield  {journal} {\bibinfo  {journal} {The Journal of
+				Chemical Physics}\ }\textbf {\bibinfo {volume} {152}},\ \bibinfo {pages}
+		{214108} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Matthews}\ and\ \citenamefont
+		{Stanton}(2016)}]{mat16}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~A.}\ \bibnamefont
+			{Matthews}}\ and\ \bibinfo {author} {\bibfnamefont {J.~F.}\ \bibnamefont
+			{Stanton}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {A new approach
+				to approximate equation-of-motion coupled cluster with triple excitations},}\
+	}\href {\doibase 10.1063/1.4962910} {\bibfield  {journal} {\bibinfo
+			{journal} {The Journal of Chemical Physics}\ }\textbf {\bibinfo {volume}
+			{145}},\ \bibinfo {pages} {124102} (\bibinfo {year} {2016})}\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {Gulania}\ \emph {et~al.}(2021)\citenamefont
+		{Gulania}, \citenamefont {Kj\o{}nstad}, \citenamefont {Stanton},
+		\citenamefont {Koch},\ and\ \citenamefont {Krylov}}]{gul21b}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+			{Gulania}}, \bibinfo {author} {\bibfnamefont {E.~F.}\ \bibnamefont
+			{Kj\o{}nstad}}, \bibinfo {author} {\bibfnamefont {J.~F.}\ \bibnamefont
+			{Stanton}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Koch}}, \
+		and\ \bibinfo {author} {\bibfnamefont {A.~I.}\ \bibnamefont {Krylov}},\
+	}\bibfield  {title} {\enquote {\bibinfo {title} {Equation-of-motion
+				coupled-cluster method with double electron-attaching operators: Theory,
+				implementation, and benchmarks},}\ }\href {\doibase 10.1063/5.0041822}
+	{\bibfield  {journal} {\bibinfo  {journal} {The Journal of Chemical Physics}\
+		}\textbf {\bibinfo {volume} {154}},\ \bibinfo {pages} {114115} (\bibinfo
+		{year} {2021})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Andersen}\ \emph {et~al.}(2022)\citenamefont
+		{Andersen}, \citenamefont {Nanda}, \citenamefont {Krylov},\ and\
+		\citenamefont {Coriani}}]{and22}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~H.}\ \bibnamefont
+			{Andersen}}, \bibinfo {author} {\bibfnamefont {K.~D.}\ \bibnamefont {Nanda}},
+		\bibinfo {author} {\bibfnamefont {A.~I.}\ \bibnamefont {Krylov}}, \ and\
+		\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Coriani}},\ }\bibfield
+	{title} {\enquote {\bibinfo {title} {Probing molecular chirality of ground
+				and electronically excited states in the {UV-vis} and {X-ray} regimes: An
+				{EOM-CCSD} study},}\ }\href {\doibase 10.1021/acs.jctc.1c00937} {\bibfield
+		{journal} {\bibinfo  {journal} {Journal of Chemical Theory and Computation}\
+		}\textbf {\bibinfo {volume} {18}},\ \bibinfo {pages} {1748--1764} (\bibinfo
+		{year} {2022})},\ \bibinfo {note} {pMID: 35187935}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Bartlett}\ and\ \citenamefont
+		{Musia\l{}}(2007)}]{bar07}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~J.}\ \bibnamefont
+			{Bartlett}}\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+			{Musia\l{}}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+			{Coupled-cluster theory in quantum chemistry},}\ }\href {\doibase
+		10.1103/RevModPhys.79.291} {\bibfield  {journal} {\bibinfo  {journal} {Rev.
+				Mod. Phys.}\ }\textbf {\bibinfo {volume} {79}},\ \bibinfo {pages} {291--352}
+		(\bibinfo {year} {2007})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Shao}\ \emph {et~al.}(2015)\citenamefont {Shao},
+		\citenamefont {Gan}, \citenamefont {Epifanovsky}, \citenamefont {Gilbert},
+		\citenamefont {Wormit}, \citenamefont {Kussmann}, \citenamefont {Lange},
+		\citenamefont {Behn}, \citenamefont {Deng}, \citenamefont {Feng},
+		\citenamefont {Ghosh}, \citenamefont {Goldey}, \citenamefont {Horn},
+		\citenamefont {Jacobson}, \citenamefont {Kaliman}, \citenamefont
+		{Khaliullin}, \citenamefont {Kus}, \citenamefont {Landau}, \citenamefont
+		{Liu}, \citenamefont {Proynov}, \citenamefont {Rhee}, \citenamefont
+		{Richard}, \citenamefont {Rohrdanz}, \citenamefont {Steele}, \citenamefont
+		{Sundstrom}, \citenamefont {III}, \citenamefont {Zimmerman}, \citenamefont
+		{Zuev}, \citenamefont {Albrecht}, \citenamefont {Alguire}, \citenamefont
+		{Austin}, \citenamefont {Beran}, \citenamefont {Bernard}, \citenamefont
+		{Berquist}, \citenamefont {Brandhorst}, \citenamefont {Bravaya},
+		\citenamefont {Brown}, \citenamefont {Casanova}, \citenamefont {Chang},
+		\citenamefont {Chen}, \citenamefont {Chien}, \citenamefont {Closser},
+		\citenamefont {Crittenden}, \citenamefont {Diedenhofen}, \citenamefont {Jr.},
+		\citenamefont {Do}, \citenamefont {Dutoi}, \citenamefont {Edgar},
+		\citenamefont {Fatehi}, \citenamefont {Fusti-Molnar}, \citenamefont
+		{Ghysels}, \citenamefont {Golubeva-Zadorozhnaya}, \citenamefont {Gomes},
+		\citenamefont {Hanson-Heine}, \citenamefont {Harbach}, \citenamefont
+		{Hauser}, \citenamefont {Hohenstein}, \citenamefont {Holden}, \citenamefont
+		{Jagau}, \citenamefont {Ji}, \citenamefont {Kaduk}, \citenamefont
+		{Khistyaev}, \citenamefont {Kim}, \citenamefont {Kim}, \citenamefont {King},
+		\citenamefont {Klunzinger}, \citenamefont {Kosenkov}, \citenamefont
+		{Kowalczyk}, \citenamefont {Krauter}, \citenamefont {Lao}, \citenamefont
+		{Laurent}, \citenamefont {Lawler}, \citenamefont {Levchenko}, \citenamefont
+		{Lin}, \citenamefont {Liu}, \citenamefont {Livshits}, \citenamefont {Lochan},
+		\citenamefont {Luenser}, \citenamefont {Manohar}, \citenamefont {Manzer},
+		\citenamefont {Mao}, \citenamefont {Mardirossian}, \citenamefont {Marenich},
+		\citenamefont {Maurer}, \citenamefont {Mayhall}, \citenamefont {Neuscamman},
+		\citenamefont {Oana}, \citenamefont {Olivares-Amaya}, \citenamefont
+		{O'Neill}, \citenamefont {Parkhill}, \citenamefont {Perrine}, \citenamefont
+		{Peverati}, \citenamefont {Prociuk}, \citenamefont {Rehn}, \citenamefont
+		{Rosta}, \citenamefont {Russ}, \citenamefont {Sharada}, \citenamefont
+		{Sharma}, \citenamefont {Small}, \citenamefont {Sodt}, \citenamefont {Stein},
+		\citenamefont {St\"{u}ck}, \citenamefont {Su}, \citenamefont {Thom},
+		\citenamefont {Tsuchimochi}, \citenamefont {Vanovschi}, \citenamefont {Vogt},
+		\citenamefont {Vydrov}, \citenamefont {Wang}, \citenamefont {Watson},
+		\citenamefont {Wenzel}, \citenamefont {White}, \citenamefont {Williams},
+		\citenamefont {Yang}, \citenamefont {Yeganeh}, \citenamefont {Yost},
+		\citenamefont {You}, \citenamefont {Zhang}, \citenamefont {Zhang},
+		\citenamefont {Zhao}, \citenamefont {Brooks}, \citenamefont {Chan},
+		\citenamefont {Chipman}, \citenamefont {Cramer}, \citenamefont {III},
+		\citenamefont {Gordon}, \citenamefont {Hehre}, \citenamefont {Klamt},
+		\citenamefont {III}, \citenamefont {Schmidt}, \citenamefont {Sherrill},
+		\citenamefont {Truhlar}, \citenamefont {Warshel}, \citenamefont {Xu},
+		\citenamefont {Aspuru-Guzik}, \citenamefont {Baer}, \citenamefont {Bell},
+		\citenamefont {Besley}, \citenamefont {Chai}, \citenamefont {Dreuw},
+		\citenamefont {Dunietz}, \citenamefont {Furlani}, \citenamefont {Gwaltney},
+		\citenamefont {Hsu}, \citenamefont {Jung}, \citenamefont {Kong},
+		\citenamefont {Lambrecht}, \citenamefont {Liang}, \citenamefont {Ochsenfeld},
+		\citenamefont {Rassolov}, \citenamefont {Slipchenko}, \citenamefont
+		{Subotnik}, \citenamefont {Voorhis}, \citenamefont {Herbert}, \citenamefont
+		{Krylov}, \citenamefont {Gill},\ and\ \citenamefont {Head-Gordon}}]{sha15}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+			{Shao}}, \bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont {Gan}}, \bibinfo
+		{author} {\bibfnamefont {E.}~\bibnamefont {Epifanovsky}}, \bibinfo {author}
+		{\bibfnamefont {A.~T.}\ \bibnamefont {Gilbert}}, \bibinfo {author}
+		{\bibfnamefont {M.}~\bibnamefont {Wormit}}, \bibinfo {author} {\bibfnamefont
+			{J.}~\bibnamefont {Kussmann}}, \bibinfo {author} {\bibfnamefont {A.~W.}\
+			\bibnamefont {Lange}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+			{Behn}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Deng}}, \bibinfo
+		{author} {\bibfnamefont {X.}~\bibnamefont {Feng}}, \bibinfo {author}
+		{\bibfnamefont {D.}~\bibnamefont {Ghosh}}, \bibinfo {author} {\bibfnamefont
+			{M.}~\bibnamefont {Goldey}}, \bibinfo {author} {\bibfnamefont {P.~R.}\
+			\bibnamefont {Horn}}, \bibinfo {author} {\bibfnamefont {L.~D.}\ \bibnamefont
+			{Jacobson}}, \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Kaliman}},
+		\bibinfo {author} {\bibfnamefont {R.~Z.}\ \bibnamefont {Khaliullin}},
+		\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Kus}}, \bibinfo {author}
+		{\bibfnamefont {A.}~\bibnamefont {Landau}}, \bibinfo {author} {\bibfnamefont
+			{J.}~\bibnamefont {Liu}}, \bibinfo {author} {\bibfnamefont {E.~I.}\
+			\bibnamefont {Proynov}}, \bibinfo {author} {\bibfnamefont {Y.~M.}\
+			\bibnamefont {Rhee}}, \bibinfo {author} {\bibfnamefont {R.~M.}\ \bibnamefont
+			{Richard}}, \bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont
+			{Rohrdanz}}, \bibinfo {author} {\bibfnamefont {R.~P.}\ \bibnamefont
+			{Steele}}, \bibinfo {author} {\bibfnamefont {E.~J.}\ \bibnamefont
+			{Sundstrom}}, \bibinfo {author} {\bibfnamefont {H.~L.~W.}\ \bibnamefont
+			{III}}, \bibinfo {author} {\bibfnamefont {P.~M.}\ \bibnamefont {Zimmerman}},
+		\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Zuev}}, \bibinfo {author}
+		{\bibfnamefont {B.}~\bibnamefont {Albrecht}}, \bibinfo {author}
+		{\bibfnamefont {E.}~\bibnamefont {Alguire}}, \bibinfo {author} {\bibfnamefont
+			{B.}~\bibnamefont {Austin}}, \bibinfo {author} {\bibfnamefont {G.~J.~O.}\
+			\bibnamefont {Beran}}, \bibinfo {author} {\bibfnamefont {Y.~A.}\ \bibnamefont
+			{Bernard}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Berquist}},
+		\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Brandhorst}}, \bibinfo
+		{author} {\bibfnamefont {K.~B.}\ \bibnamefont {Bravaya}}, \bibinfo {author}
+		{\bibfnamefont {S.~T.}\ \bibnamefont {Brown}}, \bibinfo {author}
+		{\bibfnamefont {D.}~\bibnamefont {Casanova}}, \bibinfo {author}
+		{\bibfnamefont {C.-M.}\ \bibnamefont {Chang}}, \bibinfo {author}
+		{\bibfnamefont {Y.}~\bibnamefont {Chen}}, \bibinfo {author} {\bibfnamefont
+			{S.~H.}\ \bibnamefont {Chien}}, \bibinfo {author} {\bibfnamefont {K.~D.}\
+			\bibnamefont {Closser}}, \bibinfo {author} {\bibfnamefont {D.~L.}\
+			\bibnamefont {Crittenden}}, \bibinfo {author} {\bibfnamefont
+			{M.}~\bibnamefont {Diedenhofen}}, \bibinfo {author} {\bibfnamefont
+			{R.~A.~D.}\ \bibnamefont {Jr.}}, \bibinfo {author} {\bibfnamefont
+			{H.}~\bibnamefont {Do}}, \bibinfo {author} {\bibfnamefont {A.~D.}\
+			\bibnamefont {Dutoi}}, \bibinfo {author} {\bibfnamefont {R.~G.}\ \bibnamefont
+			{Edgar}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Fatehi}},
+		\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Fusti-Molnar}}, \bibinfo
+		{author} {\bibfnamefont {A.}~\bibnamefont {Ghysels}}, \bibinfo {author}
+		{\bibfnamefont {A.}~\bibnamefont {Golubeva-Zadorozhnaya}}, \bibinfo {author}
+		{\bibfnamefont {J.}~\bibnamefont {Gomes}}, \bibinfo {author} {\bibfnamefont
+			{M.~W.}\ \bibnamefont {Hanson-Heine}}, \bibinfo {author} {\bibfnamefont
+			{P.~H.}\ \bibnamefont {Harbach}}, \bibinfo {author} {\bibfnamefont {A.~W.}\
+			\bibnamefont {Hauser}}, \bibinfo {author} {\bibfnamefont {E.~G.}\
+			\bibnamefont {Hohenstein}}, \bibinfo {author} {\bibfnamefont {Z.~C.}\
+			\bibnamefont {Holden}}, \bibinfo {author} {\bibfnamefont {T.-C.}\
+			\bibnamefont {Jagau}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+			{Ji}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Kaduk}}, \bibinfo
+		{author} {\bibfnamefont {K.}~\bibnamefont {Khistyaev}}, \bibinfo {author}
+		{\bibfnamefont {J.}~\bibnamefont {Kim}}, \bibinfo {author} {\bibfnamefont
+			{J.}~\bibnamefont {Kim}}, \bibinfo {author} {\bibfnamefont {R.~A.}\
+			\bibnamefont {King}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+			{Klunzinger}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+			{Kosenkov}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Kowalczyk}},
+		\bibinfo {author} {\bibfnamefont {C.~M.}\ \bibnamefont {Krauter}}, \bibinfo
+		{author} {\bibfnamefont {K.~U.}\ \bibnamefont {Lao}}, \bibinfo {author}
+		{\bibfnamefont {A.~D.}\ \bibnamefont {Laurent}}, \bibinfo {author}
+		{\bibfnamefont {K.~V.}\ \bibnamefont {Lawler}}, \bibinfo {author}
+		{\bibfnamefont {S.~V.}\ \bibnamefont {Levchenko}}, \bibinfo {author}
+		{\bibfnamefont {C.~Y.}\ \bibnamefont {Lin}}, \bibinfo {author} {\bibfnamefont
+			{F.}~\bibnamefont {Liu}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+			{Livshits}}, \bibinfo {author} {\bibfnamefont {R.~C.}\ \bibnamefont
+			{Lochan}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Luenser}},
+		\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Manohar}}, \bibinfo
+		{author} {\bibfnamefont {S.~F.}\ \bibnamefont {Manzer}}, \bibinfo {author}
+		{\bibfnamefont {S.-P.}\ \bibnamefont {Mao}}, \bibinfo {author} {\bibfnamefont
+			{N.}~\bibnamefont {Mardirossian}}, \bibinfo {author} {\bibfnamefont {A.~V.}\
+			\bibnamefont {Marenich}}, \bibinfo {author} {\bibfnamefont {S.~A.}\
+			\bibnamefont {Maurer}}, \bibinfo {author} {\bibfnamefont {N.~J.}\
+			\bibnamefont {Mayhall}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+			{Neuscamman}}, \bibinfo {author} {\bibfnamefont {C.~M.}\ \bibnamefont
+			{Oana}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+			{Olivares-Amaya}}, \bibinfo {author} {\bibfnamefont {D.~P.}\ \bibnamefont
+			{O'Neill}}, \bibinfo {author} {\bibfnamefont {J.~A.}\ \bibnamefont
+			{Parkhill}}, \bibinfo {author} {\bibfnamefont {T.~M.}\ \bibnamefont
+			{Perrine}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Peverati}},
+		\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Prociuk}}, \bibinfo
+		{author} {\bibfnamefont {D.~R.}\ \bibnamefont {Rehn}}, \bibinfo {author}
+		{\bibfnamefont {E.}~\bibnamefont {Rosta}}, \bibinfo {author} {\bibfnamefont
+			{N.~J.}\ \bibnamefont {Russ}}, \bibinfo {author} {\bibfnamefont {S.~M.}\
+			\bibnamefont {Sharada}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+			{Sharma}}, \bibinfo {author} {\bibfnamefont {D.~W.}\ \bibnamefont {Small}},
+		\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Sodt}}, \bibinfo {author}
+		{\bibfnamefont {T.}~\bibnamefont {Stein}}, \bibinfo {author} {\bibfnamefont
+			{D.}~\bibnamefont {St\"{u}ck}}, \bibinfo {author} {\bibfnamefont {Y.-C.}\
+			\bibnamefont {Su}}, \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont
+			{Thom}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Tsuchimochi}},
+		\bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Vanovschi}}, \bibinfo
+		{author} {\bibfnamefont {L.}~\bibnamefont {Vogt}}, \bibinfo {author}
+		{\bibfnamefont {O.}~\bibnamefont {Vydrov}}, \bibinfo {author} {\bibfnamefont
+			{T.}~\bibnamefont {Wang}}, \bibinfo {author} {\bibfnamefont {M.~A.}\
+			\bibnamefont {Watson}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+			{Wenzel}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {White}},
+		\bibinfo {author} {\bibfnamefont {C.~F.}\ \bibnamefont {Williams}}, \bibinfo
+		{author} {\bibfnamefont {J.}~\bibnamefont {Yang}}, \bibinfo {author}
+		{\bibfnamefont {S.}~\bibnamefont {Yeganeh}}, \bibinfo {author} {\bibfnamefont
+			{S.~R.}\ \bibnamefont {Yost}}, \bibinfo {author} {\bibfnamefont {Z.-Q.}\
+			\bibnamefont {You}}, \bibinfo {author} {\bibfnamefont {I.~Y.}\ \bibnamefont
+			{Zhang}}, \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Zhang}},
+		\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Zhao}}, \bibinfo {author}
+		{\bibfnamefont {B.~R.}\ \bibnamefont {Brooks}}, \bibinfo {author}
+		{\bibfnamefont {G.~K.}\ \bibnamefont {Chan}}, \bibinfo {author}
+		{\bibfnamefont {D.~M.}\ \bibnamefont {Chipman}}, \bibinfo {author}
+		{\bibfnamefont {C.~J.}\ \bibnamefont {Cramer}}, \bibinfo {author}
+		{\bibfnamefont {W.~A.~G.}\ \bibnamefont {III}}, \bibinfo {author}
+		{\bibfnamefont {M.~S.}\ \bibnamefont {Gordon}}, \bibinfo {author}
+		{\bibfnamefont {W.~J.}\ \bibnamefont {Hehre}}, \bibinfo {author}
+		{\bibfnamefont {A.}~\bibnamefont {Klamt}}, \bibinfo {author} {\bibfnamefont
+			{H.~F.~S.}\ \bibnamefont {III}}, \bibinfo {author} {\bibfnamefont {M.~W.}\
+			\bibnamefont {Schmidt}}, \bibinfo {author} {\bibfnamefont {C.~D.}\
+			\bibnamefont {Sherrill}}, \bibinfo {author} {\bibfnamefont {D.~G.}\
+			\bibnamefont {Truhlar}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+			{Warshel}}, \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Xu}},
+		\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Aspuru-Guzik}}, \bibinfo
+		{author} {\bibfnamefont {R.}~\bibnamefont {Baer}}, \bibinfo {author}
+		{\bibfnamefont {A.~T.}\ \bibnamefont {Bell}}, \bibinfo {author}
+		{\bibfnamefont {N.~A.}\ \bibnamefont {Besley}}, \bibinfo {author}
+		{\bibfnamefont {J.-D.}\ \bibnamefont {Chai}}, \bibinfo {author}
+		{\bibfnamefont {A.}~\bibnamefont {Dreuw}}, \bibinfo {author} {\bibfnamefont
+			{B.~D.}\ \bibnamefont {Dunietz}}, \bibinfo {author} {\bibfnamefont {T.~R.}\
+			\bibnamefont {Furlani}}, \bibinfo {author} {\bibfnamefont {S.~R.}\
+			\bibnamefont {Gwaltney}}, \bibinfo {author} {\bibfnamefont {C.-P.}\
+			\bibnamefont {Hsu}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+			{Jung}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Kong}}, \bibinfo
+		{author} {\bibfnamefont {D.~S.}\ \bibnamefont {Lambrecht}}, \bibinfo {author}
+		{\bibfnamefont {W.}~\bibnamefont {Liang}}, \bibinfo {author} {\bibfnamefont
+			{C.}~\bibnamefont {Ochsenfeld}}, \bibinfo {author} {\bibfnamefont {V.~A.}\
+			\bibnamefont {Rassolov}}, \bibinfo {author} {\bibfnamefont {L.~V.}\
+			\bibnamefont {Slipchenko}}, \bibinfo {author} {\bibfnamefont {J.~E.}\
+			\bibnamefont {Subotnik}}, \bibinfo {author} {\bibfnamefont {T.~V.}\
+			\bibnamefont {Voorhis}}, \bibinfo {author} {\bibfnamefont {J.~M.}\
+			\bibnamefont {Herbert}}, \bibinfo {author} {\bibfnamefont {A.~I.}\
+			\bibnamefont {Krylov}}, \bibinfo {author} {\bibfnamefont {P.~M.}\
+			\bibnamefont {Gill}}, \ and\ \bibinfo {author} {\bibfnamefont
+			{M.}~\bibnamefont {Head-Gordon}},\ }\bibfield  {title} {\enquote {\bibinfo
+			{title} {Advances in molecular quantum chemistry contained in the {Q-Chem} 4
+				program package},}\ }\href {\doibase 10.1080/00268976.2014.952696} {\bibfield
+		{journal} {\bibinfo  {journal} {Molecular Physics}\ }\textbf {\bibinfo
+			{volume} {113}},\ \bibinfo {pages} {184--215} (\bibinfo {year}
+		{2015})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Gozem}\ and\ \citenamefont {Krylov}(2022)}]{goz22}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+			{Gozem}}\ and\ \bibinfo {author} {\bibfnamefont {A.~I.}\ \bibnamefont
+			{Krylov}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {The {ezSpectra}
+				suite: An easy-to-use toolkit for spectroscopy modeling},}\ }\href {\doibase
+		https://doi.org/10.1002/wcms.1546} {\bibfield  {journal} {\bibinfo  {journal}
+			{WIREs Computational Molecular Science}\ }\textbf {\bibinfo {volume} {12}},\
+		\bibinfo {pages} {e1546} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {K\"{o}ppel}, \citenamefont {Domcke},\ and\
+		\citenamefont {Cederbaum}(1984)}]{kou84}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+			{K\"{o}ppel}}, \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Domcke}},
+		\ and\ \bibinfo {author} {\bibfnamefont {L.~S.}\ \bibnamefont {Cederbaum}},\
+	}\enquote {\bibinfo {title} {Multimode molecular dynamics beyond the
+			born-oppenheimer approximation},}\ in\ \href {\doibase
+		https://doi.org/10.1002/9780470142813.ch2} {\emph {\bibinfo {booktitle}
+			{Advances in Chemical Physics}}}\ (\bibinfo  {publisher} {{John Wiley \&
+			Sons, Ltd}},\ \bibinfo {year} {1984})\ pp.\ \bibinfo {pages}
+	{59--246}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Domcke}, \citenamefont {K\"{o}ppel},\ and\
+		\citenamefont {Cederbaum}(1981)}]{dom81}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
+			{Domcke}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {K\"{o}ppel}},
+		\ and\ \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Cederbaum}},\
+	}\bibfield  {title} {\enquote {\bibinfo {title} {Spectroscopic effects of
+				conical intersections of molecular potential energy surfaces},}\ }\href
+	{\doibase 10.1080/00268978100101721} {\bibfield  {journal} {\bibinfo
+			{journal} {Molecular Physics}\ }\textbf {\bibinfo {volume} {43}},\ \bibinfo
+		{pages} {851--875} (\bibinfo {year} {1981})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Pacher}, \citenamefont {Cederbaum},\ and\
+		\citenamefont {K\"{o}ppel}(1993)}]{pac93}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+			{Pacher}}, \bibinfo {author} {\bibfnamefont {L.~S.}\ \bibnamefont
+			{Cederbaum}}, \ and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+			{K\"{o}ppel}},\ }\enquote {\bibinfo {title} {Adiabatic and quasidiabatic
+			states in a gauge theoretical framework},}\ in\ \href {\doibase
+		https://doi.org/10.1002/9780470141427.ch4} {\emph {\bibinfo {booktitle}
+			{Advances in Chemical Physics}}}\ (\bibinfo  {publisher} {John Wiley \& Sons,
+		Ltd},\ \bibinfo {year} {1993})\ pp.\ \bibinfo {pages} {293--391}\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {Stanton}(2011)}]{sta11}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~F.}\ \bibnamefont
+			{Stanton}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Quantitative
+				vibronic coupling calculations. the visible spectrum of propadienylidene},}\
+	}\href {\doibase 10.1039/C0FD00029A} {\bibfield  {journal} {\bibinfo
+			{journal} {Faraday Discuss.}\ }\textbf {\bibinfo {volume} {150}},\ \bibinfo
+		{pages} {331--343} (\bibinfo {year} {2011})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Ichino}\ \emph {et~al.}(2006)\citenamefont {Ichino},
+		\citenamefont {Gianola}, \citenamefont {Lineberger},\ and\ \citenamefont
+		{Stanton}}]{ich06}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+			{Ichino}}, \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont {Gianola}},
+		\bibinfo {author} {\bibfnamefont {W.~C.}\ \bibnamefont {Lineberger}}, \ and\
+		\bibinfo {author} {\bibfnamefont {J.~F.}\ \bibnamefont {Stanton}},\
+	}\bibfield  {title} {\enquote {\bibinfo {title} {Nonadiabatic effects in the
+				photoelectron spectrum of the pyrazolide-d3 anion: Three-state interactions
+				in the pyrazolyl-d3 radical},}\ }\href {\doibase 10.1063/1.2338043}
+	{\bibfield  {journal} {\bibinfo  {journal} {The Journal of Chemical Physics}\
+		}\textbf {\bibinfo {volume} {125}},\ \bibinfo {pages} {084312} (\bibinfo
+		{year} {2006})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Ichino}\ \emph {et~al.}(2008)\citenamefont {Ichino},
+		\citenamefont {Wren}, \citenamefont {Vogelhuber}, \citenamefont {Gianola},
+		\citenamefont {Lineberger},\ and\ \citenamefont {Stanton}}]{ich08}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+			{Ichino}}, \bibinfo {author} {\bibfnamefont {S.~W.}\ \bibnamefont {Wren}},
+		\bibinfo {author} {\bibfnamefont {K.~M.}\ \bibnamefont {Vogelhuber}},
+		\bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont {Gianola}}, \bibinfo
+		{author} {\bibfnamefont {W.~C.}\ \bibnamefont {Lineberger}}, \ and\ \bibinfo
+		{author} {\bibfnamefont {J.~F.}\ \bibnamefont {Stanton}},\ }\bibfield
+	{title} {\enquote {\bibinfo {title} {The vibronic level structure of the
+				cyclopentadienyl radical},}\ }\href {\doibase 10.1063/1.2973631} {\bibfield
+		{journal} {\bibinfo  {journal} {The Journal of Chemical Physics}\ }\textbf
+		{\bibinfo {volume} {129}},\ \bibinfo {pages} {084310} (\bibinfo {year}
+		{2008})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Ichino}, \citenamefont {Gauss},\ and\ \citenamefont
+		{Stanton}(2009)}]{ich09}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+			{Ichino}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Gauss}}, \
+		and\ \bibinfo {author} {\bibfnamefont {J.~F.}\ \bibnamefont {Stanton}},\
+	}\bibfield  {title} {\enquote {\bibinfo {title} {Quasidiabatic states
+				described by coupled-cluster theory},}\ }\href {\doibase 10.1063/1.3127246}
+	{\bibfield  {journal} {\bibinfo  {journal} {The Journal of Chemical Physics}\
+		}\textbf {\bibinfo {volume} {130}},\ \bibinfo {pages} {174105} (\bibinfo
+		{year} {2009})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Weichman}\ \emph {et~al.}(2017)\citenamefont
+		{Weichman}, \citenamefont {Cheng}, \citenamefont {Kim}, \citenamefont
+		{Stanton},\ and\ \citenamefont {Neumark}}]{wei17}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~L.}\ \bibnamefont
+			{Weichman}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Cheng}},
+		\bibinfo {author} {\bibfnamefont {J.~B.}\ \bibnamefont {Kim}}, \bibinfo
+		{author} {\bibfnamefont {J.~F.}\ \bibnamefont {Stanton}}, \ and\ \bibinfo
+		{author} {\bibfnamefont {D.~M.}\ \bibnamefont {Neumark}},\ }\bibfield
+	{title} {\enquote {\bibinfo {title} {Low-lying vibronic level structure of
+				the ground state of the methoxy radical: Slow electron velocity-map imaging
+				{(SEVI)} spectra and {K\"{o}ppel-Domcke-Cederbaum (KDC)} vibronic hamiltonian
+				calculations},}\ }\href {\doibase 10.1063/1.4984963} {\bibfield  {journal}
+		{\bibinfo  {journal} {The Journal of Chemical Physics}\ }\textbf {\bibinfo
+			{volume} {146}},\ \bibinfo {pages} {224309} (\bibinfo {year}
+		{2017})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Buckingham}, \citenamefont {Orr},\ and\ \citenamefont
+		{Sichel}(1970)}]{buc70}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~D.}\ \bibnamefont
+			{Buckingham}}, \bibinfo {author} {\bibfnamefont {B.~J.}\ \bibnamefont {Orr}},
+		\ and\ \bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont {Sichel}},\
+	}\bibfield  {title} {\enquote {\bibinfo {title} {A discussion on
+				photoelectron spectroscopy - angular distributions and intensity in molecular
+				photoelectron spectroscopy i. general theory for diatomic molecules},}\
+	}\href {\doibase 10.1098/rsta.1970.0068} {\bibfield  {journal} {\bibinfo
+			{journal} {Phil. Trans. A: Math. Phys. Eng. Sci.}\ }\textbf {\bibinfo
+			{volume} {268}},\ \bibinfo {pages} {147--157} (\bibinfo {year}
+		{1970})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Wigner}(1948)}]{wig48}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.~P.}\ \bibnamefont
+			{Wigner}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {On the behavior
+				of cross sections near thresholds},}\ }\href {\doibase
+		10.1103/PhysRev.73.1002} {\bibfield  {journal} {\bibinfo  {journal} {Physical
+				Review}\ }\textbf {\bibinfo {volume} {73}},\ \bibinfo {pages} {1002--1009}
+		(\bibinfo {year} {1948})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Yan}\ \emph {et~al.}(1987)\citenamefont {Yan},
+		\citenamefont {Dane}, \citenamefont {Zeitz}, \citenamefont {Hall},\ and\
+		\citenamefont {Curl}}]{yan87}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.-B.}\ \bibnamefont
+			{Yan}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Dane}}, \bibinfo
+		{author} {\bibfnamefont {D.}~\bibnamefont {Zeitz}}, \bibinfo {author}
+		{\bibfnamefont {J.~L.}\ \bibnamefont {Hall}}, \ and\ \bibinfo {author}
+		{\bibfnamefont {R.}~\bibnamefont {Curl}},\ }\bibfield  {title} {\enquote
+		{\bibinfo {title} {{Color center laser spectroscopy of C$_2$H and C$_2$D}},}\
+	}\href {\doibase https://doi.org/10.1016/0022-2852(87)90294-3} {\bibfield
+		{journal} {\bibinfo  {journal} {Journal of Molecular Spectroscopy}\ }\textbf
+		{\bibinfo {volume} {123}},\ \bibinfo {pages} {486--495} (\bibinfo {year}
+		{1987})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Stephens}\ \emph {et~al.}(1988)\citenamefont
+		{Stephens}, \citenamefont {Yan}, \citenamefont {Richnow}, \citenamefont
+		{Solka},\ and\ \citenamefont {Curl}}]{ste88}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+			{Stephens}}, \bibinfo {author} {\bibfnamefont {W.-B.}\ \bibnamefont {Yan}},
+		\bibinfo {author} {\bibfnamefont {M.~L.}\ \bibnamefont {Richnow}}, \bibinfo
+		{author} {\bibfnamefont {H.}~\bibnamefont {Solka}}, \ and\ \bibinfo {author}
+		{\bibfnamefont {R.}~\bibnamefont {Curl}},\ }\bibfield  {title} {\enquote
+		{\bibinfo {title} {{Infrared kinetic spectroscopy of C$_2$H and C$_2$D}},}\
+	}\href {\doibase https://doi.org/10.1016/0022-2860(88)80269-2} {\bibfield
+		{journal} {\bibinfo  {journal} {Journal of Molecular Structure}\ }\textbf
+		{\bibinfo {volume} {190}},\ \bibinfo {pages} {41 -- 60} (\bibinfo {year}
+		{1988})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Sharp-Williams}, \citenamefont {Roberts},\ and\
+		\citenamefont {Nesbitt}(2011)}]{wil11}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.~N.}\ \bibnamefont
+			{Sharp-Williams}}, \bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont
+			{Roberts}}, \ and\ \bibinfo {author} {\bibfnamefont {D.~J.}\ \bibnamefont
+			{Nesbitt}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Dark state
+					vibronic coupling in the $\tilde{A}^2\Pi \leftarrow \tilde{X}^2\Sigma^+$ band
+					of ethynyl radical via high resolution infrared absorption spectroscopy}},}\
+	}\href {\doibase 10.1039/C1CP21523J} {\bibfield  {journal} {\bibinfo
+			{journal} {Physical Chemistry Chemical Physics}\ }\textbf {\bibinfo {volume}
+			{13}},\ \bibinfo {pages} {17474--17483} (\bibinfo {year} {2011})}\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {Simmons}, \citenamefont {Ichino},\ and\ \citenamefont
+		{Stanton}(2012)}]{sim12}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~S.}\ \bibnamefont
+			{Simmons}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Ichino}}, \
+		and\ \bibinfo {author} {\bibfnamefont {J.~F.}\ \bibnamefont {Stanton}},\
+	}\bibfield  {title} {\enquote {\bibinfo {title} {The $\nu$3 fundamental in
+				{NO$_3$} has been seen near 1060 cm$^{-1}$, albeit some time ago},}\ }\href
+	{\doibase 10.1021/jz300721b} {\bibfield  {journal} {\bibinfo  {journal} {The
+				Journal of Physical Chemistry Letters}\ }\textbf {\bibinfo {volume} {3}},\
+		\bibinfo {pages} {1946--1950} (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Khuseynov}\ \emph {et~al.}(2014)\citenamefont
+		{Khuseynov}, \citenamefont {Blackstone}, \citenamefont {Culberson},\ and\
+		\citenamefont {Sanov}}]{khu14}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+			{Khuseynov}}, \bibinfo {author} {\bibfnamefont {C.~C.}\ \bibnamefont
+			{Blackstone}}, \bibinfo {author} {\bibfnamefont {L.~M.}\ \bibnamefont
+			{Culberson}}, \ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+			{Sanov}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Photoelectron
+				angular distributions for states of any mixed character: An
+				experiment-friendly model for atomic, molecular, and cluster anions},}\
+	}\href {\doibase 10.1063/1.4896241} {\bibfield  {journal} {\bibinfo
+			{journal} {The Journal of Chemical Physics}\ }\textbf {\bibinfo {volume}
+			{141}},\ \bibinfo {pages} {124312} (\bibinfo {year} {2014})}\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {Hanstorp}, \citenamefont {Bengtsson},\ and\
+		\citenamefont {Larson}(1989)}]{han89}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+			{Hanstorp}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Bengtsson}},
+		\ and\ \bibinfo {author} {\bibfnamefont {D.~J.}\ \bibnamefont {Larson}},\
+	}\bibfield  {title} {\enquote {\bibinfo {title} {{Angular distributions in
+					photodetachment from ${\mathrm{O}}^{\mathrm{\ensuremath{-}}}$}},}\ }\href
+	{\doibase 10.1103/PhysRevA.40.670} {\bibfield  {journal} {\bibinfo  {journal}
+			{Physical Review A}\ }\textbf {\bibinfo {volume} {40}},\ \bibinfo {pages}
+		{670--675} (\bibinfo {year} {1989})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Sanov}\ \emph {et~al.}(2013)\citenamefont {Sanov},
+		\citenamefont {Grumbling}, \citenamefont {Goebbert},\ and\ \citenamefont
+		{Culberson}}]{san13}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+			{Sanov}}, \bibinfo {author} {\bibfnamefont {E.~R.}\ \bibnamefont
+			{Grumbling}}, \bibinfo {author} {\bibfnamefont {D.~J.}\ \bibnamefont
+			{Goebbert}}, \ and\ \bibinfo {author} {\bibfnamefont {L.~M.}\ \bibnamefont
+			{Culberson}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+			{Photodetachment anisotropy for mixed s-p states: 8/3 and other fractions},}\
+	}\href {\doibase 10.1063/1.4789811} {\bibfield  {journal} {\bibinfo
+			{journal} {The Journal of Chemical Physics}\ }\textbf {\bibinfo {volume}
+			{138}},\ \bibinfo {pages} {054311} (\bibinfo {year} {2013})}\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {Hart}\ \emph {et~al.}(2021)\citenamefont {Hart},
+		\citenamefont {Lyle}, \citenamefont {Spellberg}, \citenamefont {Krylov},\
+		and\ \citenamefont {Mabbs}}]{har21}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~A.}\ \bibnamefont
+			{Hart}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Lyle}}, \bibinfo
+		{author} {\bibfnamefont {J.}~\bibnamefont {Spellberg}}, \bibinfo {author}
+		{\bibfnamefont {A.~I.}\ \bibnamefont {Krylov}}, \ and\ \bibinfo {author}
+		{\bibfnamefont {R.}~\bibnamefont {Mabbs}},\ }\bibfield  {title} {\enquote
+		{\bibinfo {title} {Role of the electron-dipole interaction in photodetachment
+				angular distributions},}\ }\href {\doibase 10.1021/acs.jpclett.1c02882}
+	{\bibfield  {journal} {\bibinfo  {journal} {The Journal of Physical Chemistry
+				Letters}\ }\textbf {\bibinfo {volume} {12}},\ \bibinfo {pages} {10086--10092}
+		(\bibinfo {year} {2021})},\ \bibinfo {note} {pMID: 34624197}\BibitemShut
+	{NoStop}%
+\end{thebibliography}%
 

### 2022-06-30 v3_Resubmission/CoverLetter.tex
v3

\documentclass[a4paper,12pt]{letter}
\usepackage{fancyhdr,color,graphicx,afterpage,enumitem}
\usepackage[top=50mm,head=40mm,bottom=40mm,foot=30mm,left=20mm,right=20mm]{geometry}
\usepackage{tabularx}
\usepackage{sansmathfonts}
\usepackage[scaled]{helvet}
\renewcommand\familydefault{\sfdefault} 
\usepackage[T1]{fontenc}
\renewcommand{\headrule}{
\vskip-13ex \hrule width\headwidth height\headrulewidth \vskip-\headrulewidth}
%== adjust line position -13.ex by trial an error, if # of lines in 
%== the header boxes below is changed 
\rhead{
 \begin{minipage}[t]{.4\textwidth}
  \raggedleft
   \includegraphics[width=.5\textwidth]{unsw}\vspace*{1ex}\ \\
   \begin{footnotesize}
   \begin{sf}
   \begin{tabular}{l@{\ :\ }l}
    T& +61 2 9065 4259\\
    E& B.Laws@unsw.edu.au\\
    \multicolumn{2}{l}{research.unsw.edu.au/people/dr-ben-laws}
   \end{tabular}
  \end{sf}
  \end{footnotesize}
 \end{minipage}
}
\lhead{
 \begin{minipage}[t]{.6\textwidth}
  \begin{footnotesize}
  \begin{sf}
  \raggedright
  {\textsc\textbf{UNSW FACULTY OF SCIENCE}}
  \vspace*{2ex}\ \\
          \textbf{Dr Benjamin A. Laws}\\
          Postdoctoral Fellow\\
          Molecular Photonics Laboratories\\
          School of Chemistry\\
          The University of New South Wales\\
          Sydney NSW 2052 Australia\\
  \end{sf}
  \end{footnotesize}
 \end{minipage}
}
\cfoot{}
\lfoot{}
\rfoot{}
\setlength{\parskip}{1em}
\pagestyle{plain}
% =============== Add your input below =================================
\address{\vspace*{-8ex}\ \\
} 
\signature{\sf \vspace*{-8ex}Dr Benjamin A. Laws.}
\begin{document}
\begin{sf}
%\date{ }                  % comment this line to specify today's date
\begin{letter}{%
Editor\\
The Journal of Chemical Physics
}
\opening{Dear Editor,}
\thispagestyle{fancy}

The following manuscript is for your consideration for publication in
The Journal of Chemical Physics:

\begin{tabularx}{.95\textwidth}{ll}
Title: & \hspace*{.4em}\mbox{\it Velocity Map Imaging Spectroscopy of C$_2$H$^-$ and C$_2$D$^-$:}\\
 & \hspace*{.4em}\mbox{\it a benchmark study of vibronic coupling interactions}
\\
 \\
Authors: & 
{\begin{tabular}[t]{lll}
Dr Benjamin~A.~Laws & Postdoctoral Fellow & B.Laws@unsw.edu.au\\
Zachariah~D.~Levey & PhD Student & Z.Levey@unsw.edu.au\\
Prof. Andrei Sanov & Professor & Sanov@arizona.edu\\
Prof. John F. Stanton & Professor & Johnstanton@chem.ufl.edu\\
Prof. Timothy~W.~Schmidt & Professor & Timothy.Schmidt@unsw.edu.au\\
Dr Stephen~T.~Gibson & Senior Fellow & Stephen.Gibson@anu.edu.au
\end{tabular}}\\
 \\
\parbox[t]{6em}{
	Addresses: \\ 
	(1,2,5)} & 
{\begin{tabular}[t]{l}
		School of Chemistry, The University of New South Wales\\
		Sydney, NSW 2052, Australia
\end{tabular}} \\
(1, 6) & 
{\begin{tabular}[t]{l}
Research School of Physics and Engineering, The Australian National University\\
Canberra, ACT 2601, Australia
\end{tabular}} \\
(3) & 
{\begin{tabular}[t]{l}
		Department of Chemistry \& Biochemistry, The University of Arizona\\
		Tucson, Arizona 85721, United States
\end{tabular}} \\
(4) & 
{\begin{tabular}[t]{l}
		Department of Chemistry, University of Florida\\
		Gainesville, Florida 32611, United States
\end{tabular}} \\

\\
\parbox[t]{6em}{
Conflict of Interest} &
\hspace*{.4em}The authors declare no competing financial interest.
\end{tabularx}

\vspace*{0ex}\ \\
\textbf{Significance}\\[.5ex]
This research uses High Resolution Photoelectron Imaging (HR-PEI) to examine complex vibronic coupling effects in the ethynyl radical C$_2$H. Monohydride carbon chains play an important role in combustion and interstellar chemistry, with C$_2$H reported to be one of the most abundant molecules in the universe. However, these radicals are exceedingly difficult to model, due to the introduction of vibronic coupling interactions between the close lying $\tilde{X}^2\Sigma^+$ and $\tilde{A}^2\Pi$ electronic states. As our knowledge of interstellar chemistry relies critically on theory, a new approach is required that can both accurately model the complexity of the coupled spectra, and be efficiently extended to larger C$_{2n}$H radicals.

In this paper we apply a quasidiabtaic approach to construct a QVC (quadratic vibronic coupling) model Hamiltonian to account for the Renner-Teller and pseudo Jahn-Teller coupling in C$_2$H. We show how the Hamiltonian can be parameterised using the outputs of standard quantum chemical \emph{ab-initio} calculations, to simulate the vibronic coupling effects in the photoelectron spectrum of C$_2$H and C$_2$D.  Comparisons to the HR-PEI experimental spectra confirm that the QVC model accurately reproduces the coupling effects observed near the $\tilde{A}^2\Pi$ state origin. Anion HR-PEI spectroscopy maps both of the $\tilde{X}^2\Sigma^+$ and $\tilde{A}^2\Pi$ surfaces on an equal footing from the anion $\tilde{X}^1\Sigma^+$ state, allowing for a direct comparison with the \emph{ab-initio} modelling. We also show that detailed analysis of the experimental electron anisotropy allows for transitions with $\sigma$ and $\pi$ vibronic symmetry to be distinguished, providing definitive assignments of the calculated transitions.

As the QVC quasidiabatic model can be readily extended to larger systems, this work provides a roadmap for future studies to follow, which will help to determine the role of C$_{2n}$H and C$_{2n}$H$^-$ in interstellar chemistry.

\vspace*{0ex}\ \\ 
\textbf{Recommended Reviewers}\\[.5ex]
\begin{tabularx}{.5\textwidth}{lll}
	Caroline~Chick~Jarrold & Indiana U. & cjarrold@indiana.edu\\
	Anna Krylov  & USC  & krylov@usc.edu\\
	Richard Mabbs  & Washington U.   & mabbs@wustl.edu\\
	Ryan Fortenberry & U. Mississippi & r410@olemiss.edu\\
	Mark Johnson & Yale & mark.johnson@yale.edu\\
	Michael~Heaven & Emory & mheaven@emory.edu\\
	Arthur~Suits & U. Missouri & suitsa@missouri.edu\\
\end{tabularx}

\vspace*{0ex}\ \\ 
\textbf{Statement}\\[.5ex]
This manuscript is not being considered by any other journal.

%\closing{Regards,\\
\   
\includegraphics[width=.2\textwidth,clip]{signatureXX}
               \closing{Regards,}
\end{letter}
\end{sf}
\end{document}

### 2022-06-30 v3_Resubmission/Laws_C2H_v3.tex
v3

--- 2022-06-30 Resubmission/Laws_C2H_v2.tex
@@
 However for some species, particularly those with low abundances or no dipole moment, UV/vis spectroscopic methods are required for identification~\cite{mai97}.
-This creates a challenge for theory, as electronic spectral calculations are more difficult than those employed for pure rotational spectra~\cite{for10}.
-A challenge more arduous when vibronic coupling effects are present, as they can be exceedingly difficult to model.
+This creates a challenge for theory, as electronic spectral calculations are more difficult than those employed for pure rotational spectra, particularly when vibronic coupling effects are present as they can be exceedingly difficult to model~\cite{for10}.
 
